### 2020-03-30 main.tex
First push

\documentclass[twocolumn]{aastex63}
\usepackage{natbib}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
\bibliographystyle{aasjournal}

\begin{document}

\title{PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS}

\author{Spencer C. Wallace}
\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195}

\author{Thomas R. Quinn}
\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195}

\begin{abstract}
Abstract goes here
\end{abstract}

\section{Introduction} \label{sec:intro}

Intro text goes here \citep{2019MNRAS.489.2159W}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/test.png}
    \caption{Caption goes here.\label{fig:test}}
\end{figure}

\section{Summary and Discussion} \label{sec:discuss}

Summary and discussion text goes here

\bibliography{references}

\clearpage

\end{document}

### 2020-03-30 makeFig.py

@@ -1,0 +1,47 @@
+#/bin/bash
+import matplotlib.pylab as plt
+import matplotlib as mpl
+import numpy as np
+import pandas as pd
+import pynbody as pb
+import natsort as ns
+import glob as gl
+import os
+
+from astropy import units as u
+from astropy.constants import G
+simT = u.year/(2*np.pi)
+simV = u.AU / simT
+
+from scipy import stats
+
+import sys
+sys.path.insert(0, '../OrbitTools/')
+import OrbitTools
+
+mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
+                            'image.cmap': 'viridis'})
+
+simT = u.year/(2*np.pi)
+simV = u.AU/simT
+
+clobber = True
+fmt = 'png'
+s = 0.005
+
+def make_plot():
+	file_str = 'figures/test.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	xmodel = np.linspace(0, 10)
+	ymodel = np.cos(xmodel)
+
+	fig, axes = plt.subplots(figsize=(8,8))
+	axes.plot(xmodel, ymodel)
+	axes.set_xlabel('X')
+	axes.set_ylabel('Y')
+
+	plt.savefig(file_str, format=fmt, bbox_inches='tight')
+
+make_plot()

### 2020-03-30 main.tex
Write up of collision and relaxation time scaling with orbital distance

@@
-\documentclass[twocolumn]{aastex63}
+\documentclass[onecolumn]{aastex63}
 \usepackage{natbib}
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/test.png}
+    \includegraphics[width=0.5\columnwidth]{figures/test.png}
     \caption{Caption goes here.\label{fig:test}}
 \end{figure}
+
+\section{Collision and Relaxation Timescale}
+
+The motivation for this project comes from the realization that the collision timescale and the relaxation time (which sets the timescales for things like viscous stirring and dynamical friction (cite ida 1993)) do not scale proportionately with orbital period.
+At sufficiently long orbital periods, the relaxation time is shorter than the collision time.
+This means that as planetesimals grow, the velocity distribution of bodies reacts to the changing mass distribution, which alters the growth mode.
+When this condition is met, oligarchic growth can commence (cite ki 1998), which keeps the planetary embryos on circular orbits and restricts their growth.
+
+Because these two timescales scale differently with orbital period (or equivalently semimajor axis), they should eventually cross as one gets close enough to the host star.
+In regions where the collision timescale is shorter than the growth time, the embryos will maintain eccentric orbits as they grow, which greatly widens their feeding zones.
+Because they do not settle onto circular orbits, the timescale for orbital instability, which marks the beginning of the final planet-forming phase, should be much shorter.
+
+\subsection{Collision Timescale}
+
+The timescale for collisions is set by
+
+\begin{equation}
+	t_{coll} = \frac{1}{n \sigma v}
+\end{equation}
+
+\noindent where $n$ is the number density of planetesimals, $\sigma$ is the cross section for collisions and $v$ is the typical encounter velocity between planetesimals.
+
+The number density of planetesimals is set by
+
+\begin{equation}
+    n = \frac{\Sigma \Omega}{2 m v}
+\end{equation}
+
+\noindent where $\Sigma$ is the surface density of solids in the disk, $\Omega$ is the orbital frequency and $m$ is the mass of a planetesimal.
+For our purposes, we will assume that the surface density profile follows a power law such that $\Sigma = A r^{-\alpha}$.
+Planetesimals are typically large enough to exert a significant gravitational pull on each other, which enhances the collision cross section beyond its geometric value
+
+\begin{equation}
+	\sigma = \pi s^{2} \left( 1 + \frac{v_{esc}^{2}}{v^{2}} \right)
+\end{equation}
+
+\noindent where $s$ is the radius of a planetesimal and $v_{esc}$ is the escape velocity from the surface of a planetesimal. Finally, $v$ is given by
+
+\begin{equation}
+	v = \sqrt{\left<  e^{2} \right>^{1/2} + \left< i^{2} \right>^{1/2}} v_{k}
+\end{equation}
+
+\noindent For simplicity, we will assume that the rms eccentricity and inclination of the planetesimals does not vary with orbital distance.
+Putting this all together, the collision timescale scales with the orbital distance and the surface density profile parameters ($A$, $\alpha$) like
+
+\begin{equation}
+	t_{coll} \sim A^{-1} r^{\alpha + 1/2}
+\end{equation}
+
+\noindent Note that a surface density profile with $\alpha < -1$ produces a collision timescale that scales more steeply than the orbital timescale.
+In this case, an N-body simulation will get more computationally expensive with orbital distance because the time step size scales with the orbital timescale.
+
+\subsection{Relaxation Timescale}
+
+The relaxation timescale is given by (citation)
+
+\begin{equation}
+    t_{relax} = \frac{v^3}{n \pi G^{2} m^{2} \ln \lambda}
+\end{equation}
+
+\noindent where $G$ is the gravitational constant and $\ln \lambda$ is the Coulomb logarithm.
+Using the same assumptions as above, the relaxation time scales with orbital distance and the surface density profile parameters as
+
+\begin{equation}
+    t_{relax} \sim A^{-1} r^{\alpha - 1/2}
+\end{equation}
+
+Note that this has a different dependence on $r$ than the collision timescale. Taking the ratio of these two timescales gives
+
+\begin{equation}
+\frac{t_{relax}}{t_{coll}} \sim r^{-1}
+\end{equation}
+
+The relaxation time drops relative to the collision timescale with distance.
 

### 2020-03-31 main.tex
Add explanation of isolation mass

@@
 
-Intro text goes here \citep{2019MNRAS.489.2159W}
+Intro text goes here \citep{Wallace2019}
 
@@
 
-\noindent where $s$ is the radius of a planetesimal and $v_{esc}$ is the escape velocity from the surface of a planetesimal. Finally, $v$ is given by
+\noindent where $s$ is the radius of a planetesimal and $v_{esc}$ is the escape velocity from the surface of a planetesimal. Finally, $v$ is given by (cite Lissauer 1993)
 
@@
 
+\subsection{Isolation Mass}
+
+The isolation mass of a planetary embryo, which represents the largest mass that a body can attain by accreting adjacent planetesimals in the disk, is given by
+
+\begin{equation}
+    M_{iso} = 2 \pi a \left( 2 \Delta a \right) \Sigma
+\end{equation}
+
+\noindent where $a$ is the semimajor axis of the embryo and $\Delta a$ is the maximum encounter distance that results in accretion.
+$\Delta a$ scales with the Hill radius of the growing body, which also depends on the isolation mass.
+
+\begin{equation}
+    \Delta a = \tilde{b} R_{h} = \tilde{b} \left( \frac{M_{iso}}{3 M_{*}} \right)^{1/3} a
+\end{equation}
+
+The constant $\tilde{b}$ can be determined by requiring that adjacent protoplanets do not enter each other's Hill spheres.
+This is equivalent to requiring that the Jacobi energy of these bodies be negative such that \citep{Hayashi1977}
+
+\begin{equation}
+    E_{J} = \frac{1}{2} \left( \tilde{e}^{2} + \tilde{i}^{2} \right) - \frac{3}{8} \tilde{b}^{2} + \frac{9}{2}  \geq 0
+\end{equation}
+
+\noindent where $\tilde{e}$ and  $\tilde{i}$ is the eccentricity and inclination of a protoplanet in Hill units and $\tilde{b}$ is the separation between adjacent protoplanets, also in Hill units.
+Solving for $\tilde{b}$ gives
+
+\begin{equation}
+    \tilde{b} = \frac{2}{\sqrt{3}} \left( 9 + \tilde{e}^{2} + \tilde{i}^{2} \right)^{1/2}
+\end{equation}
+
+Finally, combining the above equations and solving for $M_{iso}$ gives
+
+\begin{equation}
+    M_{iso} = \frac{8}{\sqrt{3}} \pi^{3/2} \tilde{b}^{3/2} \Sigma^{3/2} \left( 3 M_{*} \right)^{-1/2} a^{3}
+\end{equation}
+
+Most importantly, the isolation mass depends on the eccentricities and inclinations of the planetary embryos.
+At large orbital periods, these quantities are damped by dynamical friction (note that this also heats the planetesimal population and makes the timescale to reach the isolation mass extremely long).
+At short period, however, $\tilde{e}$ and  $\tilde{i}$ can be nonzero.
+
 \section{Summary and Discussion} \label{sec:discuss}

### 2020-03-31 main.tex
Timescale scaling with dynamical excitation

@@
 
-\noindent Note that a surface density profile with $\alpha < -1$ produces a collision timescale that scales more steeply than the orbital timescale.
+Note that a surface density profile with $\alpha < -1$ produces a collision timescale that scales more steeply than the orbital timescale.
 In this case, an N-body simulation will get more computationally expensive with orbital distance because the time step size scales with the orbital timescale.
+
+In terms of encounter velocity, gravitational focusing is the only thing that effects collision timescale.
+This is because number density of planetesimals $n$ scales with $v^{-1}$, which cancels with the other $v$ term.
+This leaves us with $t_{coll} \sim v^{2}$ or, in terms of the rms eccentricity (assuming the rms inclination is coupled to the eccentricity)
+
+\begin{equation}
+    t_{coll} \sim \left< e^{2} \right>^{1/2}
+\end{equation}
 
@@
 The relaxation time drops relative to the collision timescale with distance.
+
+In terms of encounter velocity, the relaxation time scales as $t_{relax} \sim v^{4}$.
+Taking the ratio of the scaling for the collision and relaxation time with rms eccentricity gives (because there is a geometric term in the collision cross section, the ratio of these two timescales still goes as $v^{4}$)
+
+\begin{equation}
+    \frac{t_{relax}}{t_{coll}} \sim \left< e^{2} \right>
+\end{equation}
+
+Therefore, a dynamically hot disk will have a better chance of inhibiting oligarchic growth.
+All planetesimal disks will tend toward this state because gravitational stirring is most effective in a cold disk.
+So long as gas drag does not strongly damp things, this condition could be met.
+Why doesn't this happen for Kokubo + Ida simulations?
 

### 2020-04-01 main.tex
Collision timescale scaling with no gravitational focusing
Add discussion of gravitational focusing suppression

@@
 Intro text goes here \citep{Wallace2019}
-
-\begin{figure}
-    \includegraphics[width=0.5\columnwidth]{figures/test.png}
-    \caption{Caption goes here.\label{fig:test}}
-\end{figure}
 
@@
 
+Figure \ref{fig:time_eq_gf} shows the Hill eccentricity required for these two timescales to be equal as a function of orbital period (solid lines).
+Regions above the curves represent parameter combinations in which the relaxation timescale is longer.
+This is assuming that the planetesimals have an internal bulk density of 2 g cm$^{-3}$ and their collision cross section is enhanced by a factor of $f_{pl}$ to make the computation faster.
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.5\columnwidth]{figures/time_eq_gf.png}
+    \caption{Caption goes here.\label{fig:time_eq_gf}}
+    \end{center}
+\end{figure}
+
+\subsection{Inhibition of Gravitational Focusing}
+
+The scaling relations derived above assume that the collision cross section scales as $v^{-2}$ or linearly with $r$.
+This is only true when the planetesimal encounter velocity is small compared to the mutual escape velocity of two planetesimals.
+Close to the star, this condition is violated because the encounter velocity grows with the Keplerian velocity.
+The minimum orbital distance at which gravitational focusing is effective can be derived by equating the encounter velocity with the mutual escape velocity
+
+\begin{equation}
+    r_{gf} \geq \frac{3 M_{*} \left< e^{2} \right> s}{4 m}
+\end{equation}
+
+Another way to think of this effect is that the gravitational capture radius of a planetesimal decreases with encounter velocity.
+$r_{gf}$ is the orbital distance at which the capture radius is smaller than the geometric cross section of a planetesimal.
+In this case, the collision timescale instead scales as
+
+\begin{equation}
+    t_{coll} \sim A^{-1} r^{\alpha + 3/2}
+\end{equation}
+
+\noindent and the number of timesteps required to resolve a collision stays constant with $r$ for a flat ($\alpha = 0$) surface density profile.
+
+Figure \ref{fig:time_eq_gf} also shows the minimum Hill eccentricity required to suppress gravitational focusing at a given orbital period for different values of $f_{pl}$ (dashed lines).
+Comparing with the solid curves, it is nearly always the case that a disk sufficiently hot enough to cause the relaxation time to exceed the collision timescale will also suppress gravitational focusing.
+
 \subsection{Isolation Mass}

### 2020-04-01 makeFig.py

@@ -29,6 +29,95 @@ clobber = True
 fmt = 'png'
 s = 0.005
 
+from scipy.integrate import quad
+
+def lnLam(b1, b2):
+    return quad(lambda x: 1/x, b1, b2)[0]
+
+sigma1 = 6
+f_disk = 1
+z = 1
+h = 1
+alpha = 1
+
+rhop = 2
+m_central = (0.14*u.M_sun).to(u.g).value
+Rp = (50*u.km).to(u.cm).value
+mp = 4/3*np.pi*Rp**3*rhop
+f_pl = [1., 3., 6.]
+
+# R in AU, returns units of g cm^-2
+def surf_den(r, sigma1, f_disk, z, alpha):
+    return sigma1*f_disk*z*r**(-alpha)*(m_central*u.g).to(u.M_sun).value**h
+
+def e_i(e_h):
+    return e_h*(mp/(3*m_central))**(1/3)
+
+def e_h(e):
+    return e*(mp/(3*m_central))**(-1/3)
+
+a_vals_au = np.logspace(-2, 0.8)
+e_h_vals = np.logspace(0, 2)
+
+t_relax_vals = np.empty((len(a_vals_au), len(e_h_vals)))
+t_coll_vals = np.empty((len(a_vals_au), len(e_h_vals)))
+t_eq_eh_vals = np.empty((len(f_pl), len(a_vals_au)))
+
+a_vals = (a_vals_au*u.AU).to(u.cm).value
+t_orbit = (2*np.pi*np.sqrt((a_vals)**3/(G.cgs.value*m_central))*u.s).to(u.d).value
+
+def plot_trel_tcoll_eq_gf():
+	file_str = 'figures/time_eq_gf.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	for f_pl_idx in range(len(f_pl)):
+	    for idx in range(len(a_vals)):
+	        for idx1 in range(len(e_h_vals)):
+	            e_std = e_i(e_h_vals[idx1])
+	            i_std = e_std/2
+	            Sigma = surf_den(a_vals_au[idx], sigma1, f_disk, z, alpha)
+	            omega = np.sqrt(G.cgs.value*m_central/a_vals[idx]**3)
+	            vk = np.sqrt(G.cgs.value*m_central/a_vals[idx])
+	            sigma = np.sqrt(e_std**2 + i_std**2)*vk
+	            n = Sigma*omega/(2*mp*sigma)
+
[…]

### 2020-04-01 main.tex
Calculate isolation mass for noncircular orbits

@@
 
-Finally, combining the above equations and solving for $M_{iso}$ gives
+If the growing protoplanets stay on circular orbits, $\tilde{b} \approx 2 \sqrt{3}$ and the above equations can be combined to solve for the isolation mass, which gives
 
 \begin{equation}
-    M_{iso} = \frac{8}{\sqrt{3}} \pi^{3/2} \tilde{b}^{3/2} \Sigma^{3/2} \left( 3 M_{*} \right)^{-1/2} a^{3}
+    M_{iso} = \frac{8}{\sqrt{3}} \left(2 \pi \Sigma \right)^{3/2} 3^{3/4} \left( 3 M_{*} \right)^{-1/2} a^{3}
 \end{equation}
 
-Most importantly, the isolation mass depends on the eccentricities and inclinations of the planetary embryos.
-At large orbital periods, these quantities are damped by dynamical friction (note that this also heats the planetesimal population and makes the timescale to reach the isolation mass extremely long).
-At short period, however, $\tilde{e}$ and  $\tilde{i}$ can be nonzero.
+At short orbital periods where oligarchic growth may not operate, $\tilde{b}$ also depends on $\tilde{e}$ and $\tilde{h}$, which are functions of the eccentricity and inclination of the planetesimals, along with the final isolation mass of the embryos.
+$M_{iso}$ must be solved for numerically, which is shown in figure \ref{fig:m_iso} as a function of orbital period and the initial rms Hill eccentricity of the planetesimals.
+As expected, the isolation mass grows at larger orbital periods, as embryos have access to a wider region of the disk.
+With a sufficiently hot planetesimal population, the isolation mass also grows.
+These results imply that if oligarchic growth does not operate, embryos will form fewer and larger.
+It is also plausible that the total mass in embryos will be larger, as a dynamically hot planetesimal population that is difficult to accrete will not form.
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.5\columnwidth]{figures/m_iso.png}
+    \caption{Caption goes here.\label{fig:m_iso}}
+    \end{center}
+\end{figure}
 

### 2020-04-01 makeFig.py

@@ -13,7 +13,7 @@ from astropy.constants import G
 simT = u.year/(2*np.pi)
 simV = u.AU / simT
 
-from scipy import stats
+from scipy import stats, optimize
 
 import sys
 sys.path.insert(0, '../OrbitTools/')
@@ -118,6 +118,35 @@ def plot_trel_tcoll_eq_gf():
 	axes.set_ylabel(r'Equilibirum $\left< \tilde{e}^{2} \right>^{1/2}$')
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
+def plot_m_iso():
+	file_str = 'figures/m_iso.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	m_iso_vals = np.empty((len(a_vals_au), len(e_h_vals)))
+	for idx in range(len(a_vals)):
+	    for idx1 in range(len(e_h_vals)):
+	        def func(x):
+	            Sigma = surf_den(a_vals_au[idx], sigma1, f_disk, z, alpha)
+	            e_std = e_i(e_h_vals[idx1])
+	            i_std = e_std/2
+	            return np.log10(4*np.pi*a_vals[idx]**2*Sigma*2/np.sqrt(3)*(10**x/(3*m_central))**(1/3)* \
+	                            np.sqrt(9 + (10**x/(3*m_central))**(-2/3)*(e_std**2 + i_std**2))) - x
+	        m_iso_vals[idx][idx1] = 10**optimize.root(func, 25).x
+
+	from matplotlib import cm
+	fig, axes = plt.subplots(figsize=(8,8))
+	cmap = mpl.cm.get_cmap('jet', 10)
+	cax = axes.pcolormesh(t_orbit, e_h_vals, np.flipud(np.rot90(m_iso_vals)), \
+	                      norm=mpl.colors.LogNorm(), cmap=cmap)
+	cb = fig.colorbar(cax)
+	cb.set_label('Isolation Mass [g]')
+	axes.set_xlabel(r'Orbital Period [d]')
+	axes.set_ylabel(r'$\left< \tilde{e}^{2} \right>^{1/2}$')
+	axes.set_xscale('log')
+	axes.set_yscale('log')
+	plt.savefig(file_str, format=fmt, bbox_inches='tight')
+
 def make_plot():
 	file_str = 'figures/test.' + fmt
 	if not clobber and os.path.exists(file_str):
[…]

### 2020-04-02 makeFig.py
Change eccentricties in plots to non-hill values, add plot for stopping and radial drift times due to gas

@@ -7,6 +7,7 @@ import pynbody as pb
 import natsort as ns
 import glob as gl
 import os
+import profileTools as pt
 
 from astropy import units as u
 from astropy.constants import G
@@ -36,19 +37,22 @@ def lnLam(b1, b2):
 
 sigma1 = 6
 f_disk = 1
-z = 1
 h = 1
 alpha = 1
 
+# Values for M stars from Backus + Quinn 2016
+q = 0.59
+T0 = 130
+mu = 2.34 # Hayashi 1981
+
+C_D = 1
+dust_to_gas = [0.01, 0.1, 0.5]
+
 rhop = 2
-m_central = (0.14*u.M_sun).to(u.g).value
+m_central = (0.13*u.M_sun).to(u.g).value
 Rp = (50*u.km).to(u.cm).value
 mp = 4/3*np.pi*Rp**3*rhop
 f_pl = [1., 3., 6.]
-
-# R in AU, returns units of g cm^-2
-def surf_den(r, sigma1, f_disk, z, alpha):
-    return sigma1*f_disk*z*r**(-alpha)*(m_central*u.g).to(u.M_sun).value**h
 
 def e_i(e_h):
     return e_h*(mp/(3*m_central))**(1/3)
@@ -56,31 +60,36 @@ def e_i(e_h):
 def e_h(e):
     return e*(mp/(3*m_central))**(-1/3)
 
-a_vals_au = np.logspace(-2, 0.8)
+a_vals_au = np.logspace(-2, 0.5)
 e_h_vals = np.logspace(0, 2)
 
-t_relax_vals = np.empty((len(a_vals_au), len(e_h_vals)))
-t_coll_vals = np.empty((len(a_vals_au), len(e_h_vals)))
-t_eq_eh_vals = np.empty((len(f_pl), len(a_vals_au)))
-
 a_vals = (a_vals_au*u.AU).to(u.cm).value
-t_orbit = (2*np.pi*np.sqrt((a_vals)**3/(G.cgs.value*m_central))*u.s).to(u.d).value
+t_orbit = pt.t_orb(a_vals, m_central)
+t_orbit_d = (t_orbit*u.s).to(u.d).value
+
+sigma_pl = pt.sigma_pl(alpha, sigma1, a_vals_au, f_disk)
+
+omega = np.sqrt(G.cgs.value*m_central/a_vals**3)
+vk = np.sqrt(G.cgs.value*m_central/a_vals)
 
 def plot_trel_tcoll_eq_gf():
[…]

### 2020-04-02 profileTools.py

@@ -1,0 +1,75 @@
+# Tools for generating planetesimal and gas profiles in a PPD
+
+import numpy as np
+import astropy.units as u
+from astropy.constants import G, k_B, m_p
+
+# Convert between semimajor axis and orbital period (cgs units)
+def sma(t_orb, m_central):
+    return (G.cgs.value*m_central*(t_orb/(2*np.pi))**2)**(1/3)
+def t_orb(sma, m_central):
+    return 2*np.pi*np.sqrt(sma**3/(G.cgs.value*m_central))
+
+# Planetesimal surface density profile, r in AU
+def sigma_pl(alpha, A, r, f):
+    return f*A*r**(-alpha)
+
+# Convert solid surface density to gas surface density
+def sigma_gas(surf_den_pl, gas_to_dust):
+    return surf_den_pl/gas_to_dust
+
+# Midplane mass density of gas
+def rho_gas(cs, omega, surf_den_pl, gas_to_dust):
+    surf_den_gas = sigma_gas(surf_den_pl, gas_to_dust)
+    h_gas = cs/omega
+    return surf_den_gas/h_gas
+
+# Temperature profile of disk, r in AU
+def T_prof(T0, q, r):
+    return T0*r**(-q)
+
+# Sound speed profile of disk
+def soundspeed(T0, mu, q, r_AU):
+    T = T_prof(T0, q, r_AU)
+    return np.sqrt(k_B.cgs.value*T/(mu*m_p.cgs.value))
+
+# Toomre q parameter
+def toom_q(cs, omega, sigma):
+    return cs*omega/(np.pi*G.cgs*sigma)
+
+# Headwind velocity of gas in pressure-supported disk
+# r and m_central in cm and M_sun, cs in cm/s
+# q is the power law index of the pressure profile, which should be same as
+# temperature profile for an ideal gas
+def v_gas(m_central, r, cs, q):
+    m_central_cgs = (m_central*u.M_sun).to(u.g).value
+    v_k = np.sqrt(G.cgs.value*m_central_cgs/r)
+    return v_k*(1 - np.sqrt(1 - (q*cs**2/v_k**2)))
+
+# Stopping time of planetesimal in stokes regime
+def t_stop(m_pl, s_pl, C_D, rho_gas, v_gas):
+    return 2*m_pl/(C_D*np.pi*s_pl**2*rho_gas*v_gas)
+
[…]

### 2020-04-03 makeFig.py
Calculate relaxation and collision time crossing properly

@@ -36,9 +36,9 @@ def lnLam(b1, b2):
     return quad(lambda x: 1/x, b1, b2)[0]
 
 sigma1 = 6
-f_disk = 1
+f_disk = 0.13
 h = 1
-alpha = 1
+alpha = 3/2
 
 # Values for M stars from Backus + Quinn 2016
 q = 0.59
@@ -60,12 +60,12 @@ def e_i(e_h):
 def e_h(e):
     return e*(mp/(3*m_central))**(-1/3)
 
-a_vals_au = np.logspace(-2, 0.5)
-e_h_vals = np.logspace(0, 2)
+t_orbit_d = np.logspace(0, 3)
+t_orbit = (t_orbit_d*u.d).to(u.s).value
+a_vals = pt.sma(t_orbit, m_central)
+a_vals_au = (a_vals*u.cm).to(u.AU).value
 
-a_vals = (a_vals_au*u.AU).to(u.cm).value
-t_orbit = pt.t_orb(a_vals, m_central)
-t_orbit_d = (t_orbit*u.s).to(u.d).value
+e_h_vals = np.logspace(0, 2)
 
 sigma_pl = pt.sigma_pl(alpha, sigma1, a_vals_au, f_disk)
 
@@ -77,47 +77,28 @@ def plot_trel_tcoll_eq_gf():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	t_relax_vals = np.empty((len(a_vals_au), len(e_h_vals)))
-	t_coll_vals = np.empty((len(a_vals_au), len(e_h_vals)))
-	t_eq_e_vals = np.empty((len(f_pl), len(a_vals_au)))
+	def func(x, sigma_pl, a_val, f_pl_val):
+	    i_std = 10**x/2
+	    vk = np.sqrt(G.cgs.value*m_central/a_val)
+	    v = np.sqrt((10**x)**2 + i_std**2)*vk
+	    vesc = np.sqrt(G.cgs.value*mp/Rp)
+	    bmin = 2*G.cgs.value*mp/v**2
+	    bmax = a_val
+	    lnLamVal = lnLam(bmin, bmax)
+	    
+	    return np.log10((v**4*(f_pl_val*Rp)**2*(1 + vesc**2/v**2))/(G.cgs.value**2*mp**2*lnLamVal))
 
-	for f_pl_idx in range(len(f_pl)):
-	    for idx in range(len(a_vals)):
[…]

### 2021-09-20 main.tex
Change eccentricties in plots to non-hill values, add plot for stopping and radial drift times due to gas
Abstract and intro

--- 2020-03-31 main.tex
@@
 \begin{abstract}
-Abstract goes here
+Formation models in which terrestrial bodies grow via the pairwise accretion of planetesimals have been reasonably successful at reproducing the general properties of the solar system, including small body populations.
+However, planetesimal accretion has not yet been fully explored in the context of more exotic terrestrial systems, particularly those that host short-period planets.
+In this work, we use direct N-body simulations to explore and understand the growth of planetary embryos from planetesimals in disks extending down to $\simeq$ 1 day orbital periods.
+We show that planetesimal accretion becomes nearly 100 percent efficient at short orbital periods, leading to embryo masses that are roughly twice as large as the classical isolation mass.
+For rocky bodies, the physical size of the object begins to occupy a significant fraction of its Hill sphere at orbital periods less than about 50 days.
+In this regime, most close encounters result in collisions, rather than scattering, and the system cannot bifurcate into a collection of dynamically hot planetesimals and dynamically cold oligarchs, like is seen in most models.
+The highly efficient accretion seen at short orbital periods implies that systems of tightly-packed inner planets should be almost completely devoid of any residual small bodies.
+We demonstrate the robustness of our results to assumptions about the initial disk model, and also investigate how far material can radially mix across the accretion boundary.
 \end{abstract}
+
+%\begin{list}
+%\item Explain $\alpha$ controls importance of scattering vs accretion
+%\item Also mention $\beta$. Introduces another relevant size scale, but we seem to get runaway growth no matter how large or small this is (is this true?)
+%\item Show full disk vhi f6 and f4 simulations. Boundary of efficient accretion moves with density of bodies. Roughly lies where $\alpha = 0.1$.
+%\item Eccentricities reach v = vesc regardless of alpha. Show narrow annulus simulations in which embryo 'cools' in planetesimal disk with varying $\alpha$.
+%\item Show collision tree plot for full disk vhi f6. Do planetesimals move around much? How does motion of condensation fronts (due to pre-MS evolution of M stars) affect this?
+%\item What about fragmentation?
+%\item Planetesimals get completely consumed in inner disk. May have implications for planetesimal driven migration (outward, counteract type I migration)?
+%\item Embryos form first in the inner disk. What are the implications of this? Might make outward planetesimal driven migration easier
+%\end{list}
 
@@
 
+Planetesimal accretion is one of a number of stages in which micron-sized solids from the protostellar nebula coalesce to eventually build terrestrial planets.
+In the earliest stages, aerodynamic forces dominate the growth and evolution of the solids.
+Millimeter-sized bodies grow through adhesive pairwise collisions and stay well-coupled to the surrounding gas.
+Beyond this size, however, a number of growth barriers present themselves.
+Most notably, larger solids orbit the central star at Keplerian speeds as they decouple from the gas, which orbits at a sub-keplerian speed due to radial pressure support.
+This leads the solids to feel a headwind, which is maximally effective at sapping away angular momentum for objects around 1 meter in size.
+At this size, the timescale for the growing solids to fall onto the star is catastrophically short and leads to what is known as the drift barrier.
+In addition, two-body collisions between mm- to cm-sized bodies tend to result in bouncing or destruction, rather than continued growth.
+For these reasons, a number of mechanisms have been proposed which facilitate fast growth from mm to km sizes by locally concentrating solids.
+Dust traps, streaming instability, pebble piles...etc.
+
+Beyond kilometer scales, gravity begins to dominate and aerodynamic gas drag plays a smaller and smaller role.
+During this phase, collision cross sections are enhanced as gravitational focusing (safronov citation) acts to bend the trajectories of bodies undergoing close encounters.
+Large bodies are most effective at focusing the trajectories of nearby planetesimals, leading to a period of runaway growth (citations to wetherill, kokubo+ida, barnes).
+Eventually, the largest bodies (known as oligarchs) dynamically heat the surrounding planetesimals, severely limiting further growth (cite kokubo+ida).
+The end result of this phase is a bimodal population of dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals.
+Lines of evidence suggest that the asteroid belt, kuiper belt and the oort cloud are largely composed of the leftovers of this stage of planet formation.
+(Mention more specific evidence, morbidelli 09 paper, CAIs?)
+
+Although gas drag has a minimal influence on the Moon to Mars-sized oligarchs, it is enough to prevent these largest bodies from perturbing each other onto crossing orbits.
+Simulations show that evaporation of the gas disk is required to allow instability to trigger a phase of giant impacts (Mention that disk fraction decay timescale roughly matches timing of giant impacts in SS).
+It is during this phase that oligarchs collide to form Earth-sized planets (chambers wetherill 1998, raymond 2006).
+
+N body simulations allow us to work back to the planetesimal accretion phase. No one has applied this model to the in situ formation of STIPs yet. Does runaway and oligarchic growth still operate?
+
+Outline of paper
+
 Intro text goes here \citep{Wallace2019}
 
-\begin{figure}
-    \includegraphics[width=0.5\columnwidth]{figures/test.png}
-    \caption{Caption goes here.\label{fig:test}}
-\end{figure}
+\section{Overview of Planetesimal Accretion}
 
-\section{Collision and Relaxation Timescale}
+\section{Methods}
 
-The motivation for this project comes from the realization that the collision timescale and the relaxation time (which sets the timescales for things like viscous stirring and dynamical friction (cite ida 1993)) do not scale proportionately with orbital period.
-At sufficiently long orbital periods, the relaxation time is shorter than the collision time.
-This means that as planetesimals grow, the velocity distribution of bodies reacts to the changing mass distribution, which alters the growth mode.
-When this condition is met, oligarchic growth can commence (cite ki 1998), which keeps the planetary embryos on circular orbits and restricts their growth.
+\subsection{The Code}
 
-Because these two timescales scale differently with orbital period (or equivalently semimajor axis), they should eventually cross as one gets close enough to the host star.
-In regions where the collision timescale is shorter than the growth time, the embryos will maintain eccentric orbits as they grow, which greatly widens their feeding zones.
-Because they do not settle onto circular orbits, the timescale for orbital instability, which marks the beginning of the final planet-forming phase, should be much shorter.
+\subsection{Initial Conditions}
 
-\subsection{Collision Timescale}
+\section{Results}
 
-The timescale for collisions is set by
+\subsection{Narrow Annulus}
 
-\begin{equation}
-	t_{coll} = \frac{1}{n \sigma v}
-\end{equation}
+\subsection{Full Disk}
 
-\noindent where $n$ is the number density of planetesimals, $\sigma$ is the cross section for collisions and $v$ is the typical encounter velocity between planetesimals.
+\section{Simplifying Assumptions}
 
-The number density of planetesimals is set by
+\subsection{Collision Cross Section}
 
-\begin{equation}
-    n = \frac{\Sigma \Omega}{2 m v}
-\end{equation}
-
-\noindent where $\Sigma$ is the surface density of solids in the disk, $\Omega$ is the orbital frequency and $m$ is the mass of a planetesimal.
-For our purposes, we will assume that the surface density profile follows a power law such that $\Sigma = A r^{-\alpha}$.
-Planetesimals are typically large enough to exert a significant gravitational pull on each other, which enhances the collision cross section beyond its geometric value
-
-\begin{equation}
-	\sigma = \pi s^{2} \left( 1 + \frac{v_{esc}^{2}}{v^{2}} \right)
-\end{equation}
-
-\noindent where $s$ is the radius of a planetesimal and $v_{esc}$ is the escape velocity from the surface of a planetesimal. Finally, $v$ is given by (cite Lissauer 1993)
-
-\begin{equation}
-	v = \sqrt{\left<  e^{2} \right>^{1/2} + \left< i^{2} \right>^{1/2}} v_{k}
-\end{equation}
-
-\noindent For simplicity, we will assume that the rms eccentricity and inclination of the planetesimals does not vary with orbital distance.
-Putting this all together, the collision timescale scales with the orbital distance and the surface density profile parameters ($A$, $\alpha$) like
-
-\begin{equation}
-	t_{coll} \sim A^{-1} r^{\alpha + 1/2}
-\end{equation}
-
-Note that a surface density profile with $\alpha < -1$ produces a collision timescale that scales more steeply than the orbital timescale.
-In this case, an N-body simulation will get more computationally expensive with orbital distance because the time step size scales with the orbital timescale.
-
-In terms of encounter velocity, gravitational focusing is the only thing that effects collision timescale.
-This is because number density of planetesimals $n$ scales with $v^{-1}$, which cancels with the other $v$ term.
-This leaves us with $t_{coll} \sim v^{2}$ or, in terms of the rms eccentricity (assuming the rms inclination is coupled to the eccentricity)
-
-\begin{equation}
-    t_{coll} \sim \left< e^{2} \right>^{1/2}
-\end{equation}
-
-\subsection{Relaxation Timescale}
-
-The relaxation timescale is given by (citation)
-
-\begin{equation}
-    t_{relax} = \frac{v^3}{n \pi G^{2} m^{2} \ln \lambda}
-\end{equation}
-
-\noindent where $G$ is the gravitational constant and $\ln \lambda$ is the Coulomb logarithm.
-Using the same assumptions as above, the relaxation time scales with orbital distance and the surface density profile parameters as
-
-\begin{equation}
-    t_{relax} \sim A^{-1} r^{\alpha - 1/2}
-\end{equation}
-
-Note that this has a different dependence on $r$ than the collision timescale. Taking the ratio of these two timescales gives
-
-\begin{equation}
-    \frac{t_{relax}}{t_{coll}} \sim r^{-1}
-\end{equation}
-
-The relaxation time drops relative to the collision timescale with distance.
-
-In terms of encounter velocity, the relaxation time scales as $t_{relax} \sim v^{4}$.
-Taking the ratio of the scaling for the collision and relaxation time with rms eccentricity gives (because there is a geometric term in the collision cross section, the ratio of these two timescales still goes as $v^{4}$)
-
-\begin{equation}
-    \frac{t_{relax}}{t_{coll}} \sim \left< e^{2} \right>
-\end{equation}
-
-Therefore, a dynamically hot disk will have a better chance of inhibiting oligarchic growth.
-All planetesimal disks will tend toward this state because gravitational stirring is most effective in a cold disk.
-So long as gas drag does not strongly damp things, this condition could be met.
-Why doesn't this happen for Kokubo + Ida simulations?
-
-\subsection{Isolation Mass}
-
-The isolation mass of a planetary embryo, which represents the largest mass that a body can attain by accreting adjacent planetesimals in the disk, is given by
-
-\begin{equation}
-    M_{iso} = 2 \pi a \left( 2 \Delta a \right) \Sigma
-\end{equation}
-
-\noindent where $a$ is the semimajor axis of the embryo and $\Delta a$ is the maximum encounter distance that results in accretion.
-$\Delta a$ scales with the Hill radius of the growing body, which also depends on the isolation mass.
-
-\begin{equation}
-    \Delta a = \tilde{b} R_{h} = \tilde{b} \left( \frac{M_{iso}}{3 M_{*}} \right)^{1/3} a
-\end{equation}
-
-The constant $\tilde{b}$ can be determined by requiring that adjacent protoplanets do not enter each other's Hill spheres.
-This is equivalent to requiring that the Jacobi energy of these bodies be negative such that \citep{Hayashi1977}
-
-\begin{equation}
-    E_{J} = \frac{1}{2} \left( \tilde{e}^{2} + \tilde{i}^{2} \right) - \frac{3}{8} \tilde{b}^{2} + \frac{9}{2}  \geq 0
-\end{equation}
-
-\noindent where $\tilde{e}$ and  $\tilde{i}$ is the eccentricity and inclination of a protoplanet in Hill units and $\tilde{b}$ is the separation between adjacent protoplanets, also in Hill units.
-Solving for $\tilde{b}$ gives
-
-\begin{equation}
-    \tilde{b} = \frac{2}{\sqrt{3}} \left( 9 + \tilde{e}^{2} + \tilde{i}^{2} \right)^{1/2}
-\end{equation}
-
-Finally, combining the above equations and solving for $M_{iso}$ gives
-
-\begin{equation}
-    M_{iso} = \frac{8}{\sqrt{3}} \pi^{3/2} \tilde{b}^{3/2} \Sigma^{3/2} \left( 3 M_{*} \right)^{-1/2} a^{3}
-\end{equation}
-
-Most importantly, the isolation mass depends on the eccentricities and inclinations of the planetary embryos.
-At large orbital periods, these quantities are damped by dynamical friction (note that this also heats the planetesimal population and makes the timescale to reach the isolation mass extremely long).
-At short period, however, $\tilde{e}$ and  $\tilde{i}$ can be nonzero.
+\subsection{Collision Model}
 

### 2021-09-21 main.tex
Fill out more of intro

@@
 
-N body simulations allow us to work back to the planetesimal accretion phase. No one has applied this model to the in situ formation of STIPs yet. Does runaway and oligarchic growth still operate?
+Over the last few decades, terrestrial planet formation models have largely advanced by matching properties of the solar system.
+Compared to exoplanetary systems, the solar system provides a rich set of constraints (isotopic ratios, cratering records, small body populations) that are mostly unmeasurable for even the closest neighboring planet forming systems.
+However, the system architectures discovered by spaced-based missions in the last decade reveal that the solar system could very well be an outlier in terms of what a typical planet-forming disk produces.
+In addition, the sizes and compositions of the terrestrial planets likely rely on a series of finely-tuned events to play out that involve truncation of the primordial planetesimal disk \citep{raymond17}, inward, followed by outward migration of an outer giant planet \citep{walsh11}, or a large-scale instability triggered by a pair of convergently migrating giant planets \citep{tsiganis05, levison11, nesvorny11}.
+Given qualitatively similar initial conditions, solar system formation models can even occasionally reproduce the correct masses and orbital periods of the terrestrial planets without invoking any of the aforementioned scenarios, given the right random number seed \citep{fischer14}.
+
+Given the difficult question of whether to treat the solar system as an outlier, the best way forward is to use statistical samples of exoplanetary architectures to develop and inform formation models.
+This is generally done through the use of population synthesis models (ida + lin, alibert), but many of the mechanisms in these models are informed and tuned by solar system constraints.
+One pervasive and exotic result revealed by the Kepler space telescope has the discovery of hundreds of compact multi-planet terrestrial systems, dubbed systems of tightly-packed inner planets (STIPs).
+Although there is no formal definition of a STIP, they typically contain 3 or more Earth-sized planets with orbital periods extending between 1 and 100 days.
+Reconciling the structural differences between the solar system (devoid of large bodies interior to 88 days) and STIPs is going to be an important step in building a general, widely-applicable planet formation model.
+
+To date, a large body of work exists that has attempted to reproduce the architectures of STIPs, starting from planetary embryos (cite some examples).
+However, the runaway and oligarchic growth phases, which precede the assembly of the embryos, are assumed to be ubiquitous.
+Given that the timescales for accretion and gravitational scattering scale differently with encounter velocity, which itself scales with orbital period, it is not entirely clear that planetary embryos should form in the same way close to the star as they do at much longer, more thoroughly studied orbital periods.
+In this paper, we use direct N-body simulations to explore the outcome of the planetesimal accretion stage at orbital periods shorter than 100 days.
+In particular, we seek to understand what the orbital and mass distributions of the embryos and residual planetesimals look like, and to assess whether the initial conditions used by late-stage simulations of STIP assembly are reasonable.
 

### 2021-09-22 main.tex
Summary at end of intro

@@
 
-Outline of paper
+In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and argue that assumptions to derive the well-known modes of growth are only valid at sufficiently long orbital periods.
+We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}.
+In section \ref{sec:results}, we present parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods.
+We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
+Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}.
+In section \ref{sec:discuss}, we discuss the implications of this multimodal accretion behavior throughout the disk for planet formation models and conclude.
 
-Intro text goes here \citep{Wallace2019}
+\section{Overview of Planetesimal Accretion}\label{sec:theory}
 
-\section{Overview of Planetesimal Accretion}
-
-\section{Methods}
+\section{Methods}\label{sec:methods}
 
@@
 
-\section{Results}
+\section{Results}\label{sec:results}
 
@@
 
-\section{Simplifying Assumptions}
+\section{Simplifying Assumptions}\label{sec:assump}
 

### 2021-09-27 main.tex
Outline for plots

@@
 For rocky bodies, the physical size of the object begins to occupy a significant fraction of its Hill sphere at orbital periods less than about 50 days.
-In this regime, most close encounters result in collisions, rather than scattering, and the system cannot bifurcate into a collection of dynamically hot planetesimals and dynamically cold oligarchs, like is seen in most models.
+In this regime, most close encounters result in collisions, rather than scattering, and the system cannot bifurcate into a collection of dynamically hot planetesimals and dynamically cold oligarchs, like is seen in previous work.
 The highly efficient accretion seen at short orbital periods implies that systems of tightly-packed inner planets should be almost completely devoid of any residual small bodies.
@@
 
-In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and argue that assumptions to derive the well-known modes of growth are only valid at sufficiently long orbital periods.
+In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and show that assumptions used to derive the well-known modes of growth are only valid at sufficiently long orbital periods.
 We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}.
@@
 \section{Overview of Planetesimal Accretion}\label{sec:theory}
+
+% analytic conditions for runaway and orderly growth
+% not clear what happens as gravitational focusing factor approaches 1
+
+% mass and velocity distributions both evolve, two-body relaxation time works to describe velocity evolution when dispersion dominated
+% if relaxation time shorter than collision time, oligarchic growth operates
+% but what happens if these timescales are flipped? not clear, because the timescales themselves depend on mass and velocity, which both evolve with time
+
+% a cleaner formalism: compare planetesimal size to hill and gravitational radius (alpha, beta)
+% alpha does not evolve with time, beta will tend towards 1
+
+% motivation for n-body simulations: what do masses and orbital properties of embryos look like as we change alpha and beta?
+% at short period, alpha and beta are large
 
@@
 
+% show 4 panel plot of period-e distribution for large, small alpha and beta
+% show that runaway growth still operates for large beta
+
 \subsection{Full Disk}
+
+% show period-e distribution
+% show show period-mass distribution, with isolation mass curve overlaid
+% show plot of period vs alpha, mass. drop in embryo mass occurs where alpha = 0.1
+% also plot period vs sigma/Sigma and mass with alpha=0.1 location marked. residual planetesimal population missing interior to alpha=0.1
+
+\section{Radial Transport of Material}
+
+% from how far do embryos accumulate material
+% do embryos migrate at all? might need to run a simulation without gas to demonstrate whether this is due to PDM
 
@@
 
+% compare f=4 and f=6 disk. show that the mass transition moves inwards by the correct amount as alpha changes
+
 \subsection{Collision Model}
+
+% show alpha, beta study again with bounce vs merge model
 

### 2021-09-28 makeFig.py
Material for figure 1

@@ -15,10 +15,7 @@ simT = u.year/(2*np.pi)
 simV = u.AU / simT
 
 from scipy import stats, optimize
-
-import sys
-sys.path.insert(0, '../OrbitTools/')
-import OrbitTools
+import KeplerOrbit as ko
 
 mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
                             'image.cmap': 'viridis'})
@@ -38,7 +35,7 @@ def lnLam(b1, b2):
 sigma1 = 6
 f_disk = 0.13
 h = 1
-alpha = 3/2
+alpha = 1
 
 # Values for M stars from Backus + Quinn 2016
 q = 0.59
@@ -71,6 +68,42 @@ sigma_pl = pt.sigma_pl(alpha, sigma1, a_vals_au, f_disk)
 
 omega = np.sqrt(G.cgs.value*m_central/a_vals**3)
 vk = np.sqrt(G.cgs.value*m_central/a_vals)
+
+# Input in sim units, output in days
+def p_orbit(sma, m_central):
+	return (2*np.pi*np.sqrt(sma**3/m_central)*simT).to(u.d).value
+
+def plot_alpha_beta():
+	file_str = 'figures/alpha_beta.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+		
+	def subplot(ax, prefix, title):
+		mcen = 1
+		ih = True
+		if prefix == 'disk4000':
+			ih = False
+		snap0 = pb.load('data/'+prefix+'.ic')
+		pl0 = ko.orb_params(snap0, isHelio=ih, mCentral=mcen)
+		snap = pb.load('data/'+prefix+'.end')
+		pl = ko.orb_params(snap, isHelio=ih, mCentral=mcen)
+		ax.scatter(p_orbit(pl0['a'], mcen), pl0['e'], s=pl0['mass']/np.max(pl['mass'])*100)
+		ax.scatter(p_orbit(pl['a'], mcen), pl['e'], s=pl['mass']/np.max(pl['mass'])*100)
+		ax.set_xlabel('Orbital Period [d]')
+		ax.set_ylabel('Eccentricity')
+		ax.set_title(title)
+
+	fig, ax = plt.subplots(figsize=(16,16), nrows=2, ncols=2, sharex=True, sharey=True)
[…]

### 2021-09-28 makeFig.py
Add more figures

@@ -27,47 +27,24 @@ clobber = True
 fmt = 'png'
 s = 0.005
 
-from scipy.integrate import quad
+num_bins = 50
+mCentral = 0.08
 
-def lnLam(b1, b2):
-    return quad(lambda x: 1/x, b1, b2)[0]
+bins = np.linspace(0.01, 0.3, num_bins)
+snap = pb.load('data/fullDiskVHi.ic')
+plVHiIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+p_vhi_ic = pb.analysis.profile.Profile(plVHiIC.d, bins=bins)
 
-sigma1 = 6
-f_disk = 0.13
-h = 1
-alpha = 1
+snap = pb.load('data/fullDiskVHi.258000')
+plVHi = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+p_vhi = pb.analysis.profile.Profile(plVHi.d, bins=bins)
 
-# Values for M stars from Backus + Quinn 2016
-q = 0.59
-T0 = 130
-mu = 2.34 # Hayashi 1981
+perIC = 2*np.pi*np.sqrt((plVHiIC['a']*u.AU).to(u.cm)**3/(G.cgs*(mCentral*u.M_sun).to(u.g))).to(u.d)
+prof_perIC = 2*np.pi*np.sqrt((p_vhi_ic['rbins']*u.AU).to(u.cm)**3/(G.cgs*(mCentral*u.M_sun).to(u.g))).to(u.d)
+per = 2*np.pi*np.sqrt((plVHi['a']*u.AU).to(u.cm)**3/(G.cgs*(mCentral*u.M_sun).to(u.g))).to(u.d)
 
-C_D = 1
-dust_to_gas = [0.01, 0.1, 0.5]
-
-rhop = 2
-m_central = (0.13*u.M_sun).to(u.g).value
-Rp = (50*u.km).to(u.cm).value
-mp = 4/3*np.pi*Rp**3*rhop
-f_pl = [1., 3., 6.]
-
-def e_i(e_h):
-    return e_h*(mp/(3*m_central))**(1/3)
-
-def e_h(e):
-    return e*(mp/(3*m_central))**(-1/3)
-
-t_orbit_d = np.logspace(0, 3)
-t_orbit = (t_orbit_d*u.d).to(u.s).value
-a_vals = pt.sma(t_orbit, m_central)
[…]

### 2021-09-30 main.tex
Material for figure 1
Add more figures
Add reference to wallace 2017

@@
 
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/alpha_beta.png}
+    \caption{Caption goes here.\label{fig:alpha_beta}}
+\end{center}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
+    \caption{Caption goes here.\label{fig:alpha_beta_evo}}
+\end{center}
+\end{figure}
+
 % show 4 panel plot of period-e distribution for large, small alpha and beta
@@
 
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/fulldisk_e_m.png}
+    \caption{Caption goes here.\label{fig:fulldisk_e_m}}
+\end{center}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/alpha_pl_frac.png}
+    \caption{Caption goes here.\label{fig:alpha_pl_frac}}
+\end{center}
+\end{figure}
+
 % show period-e distribution
@@
 % also plot period vs sigma/Sigma and mass with alpha=0.1 location marked. residual planetesimal population missing interior to alpha=0.1
+
+% is there a clever, succinct way to show the evolution of sigma/Sigma in each period bin? to demonstrate that the accretion boundary is static
 
@@
 
+How to reconcile our concerns with the results of \citet{wallace17}?
+
 \section{Summary and Discussion} \label{sec:discuss}

### 2021-11-18 main.tex
Add text to theory section

@@
-\documentclass[onecolumn]{aastex63}
+\documentclass[twocolumn]{aastex63}
 \usepackage{natbib}
@@
 
+We begin our analysis by considering a disk of equal planetesimals with radius $s$, mass $m_{pl}$ and surface density $\Sigma_{pl}$.
+The collision rate in the vicinity of an orbit defined by Keplerian frequency $\Omega$ can be written as $n \Gamma v$, where $n = \Sigma_{pl} \Omega / 2 m_{pl} v$, $\Gamma$ is the effective collision cross section and $v$ is the typical encounter velocity between planetesimals.
+Assuming that every collision results in a perfect merger, the growth rate of a planetesimal is given by
+
+\begin{equation}\label{eq:growth}
+	\frac{dM}{dt} = \frac{\Sigma \Omega}{2 m_{pl}} \Gamma.
+\end{equation}
+
+In the case where the collision cross section $\Gamma$ depends only on the physical size of the planetesimals, the growth scales linearly with mass and the mass distribution is expected to evolve in an `orderly' fashion.
+However, bodies larger than $\sim 100$ km in size are expected to exert a significant gravitational force on each other during encounters and the collision cross section depends on both the size of the bodies and their encounter velocities.
+In this case, $\Gamma = \Gamma_{geo} \left( 1 + v_{esc}^2 / v^2 \right)$, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
+
+In the limit that $v_{esc} \gg v$, it can be shown that $M \propto M^{4/3}$, which implies a runaway scenario, in which growth accelerates with mass.
+This mode of growth was confirmed with N-body simulations by \citet{kokubo96} and appears necessary to construct protoplanets within the lifetime of a protoplanetary disk.
+Due to the velocity dependence of the gravitational focusing effect, it isn't clear how ubiquitous this mode of growth is.
+In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied.
+The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:results}.
+
+An important feature is missing from the model described above, which limits its applicability at late times.
+Encounters between planetesimals that do not result in a collision play a crucial role over long timescales.
+These close encounters act to convert energy from Keplerian shear into random motion.
+Over time, this gravitational stirring effect will raise the typical encounter velocities between bodies and diminish the effectiveness of gravitational focusing.
+With a spectrum of masses, these velocity differences become even more pronounced because as system drifts towards a state of quasi-equilibrium where $v \sim m^{1/2}$.
+For a system of equal mass bodies in which encounters are driven by random motions rather than Keplerian shear (dispersion dominated), the timescale for gravitational stirring is described by the two-body relaxation time \citep{ida93}
+
+\begin{equation}\label{eq:relax}
+	t_{relax} = \frac{v^3}{n \pi G^2 m_{pl} ln \Lambda},
+\end{equation}
+
+\noindent where $ln \Lambda$ is the Coulomb logarithm.
+As mentioned above, the system will tend toward a state of energy equipartition for a non-uniform mass distribution.
+\citet{kokubo98} showed that runaway growth is actually self-limiting.
+As the runaway bodies grow larger, they become more effective at heating the remaining planetesimals, which diminishes the effectiveness of gravitational focusing and throttles the growth rate.
+Around the time that the massive runaway bodies make up about 50 percent of the solid surface density (citation), a period of less vigorous `oligarchic' growth commences, in which the few largest bodies continue to accrete planetesimals at similar rates.
+
+The picture described above relies upon an important factor, which is that the mass distribution evolves slow enough for gravitational stirring to maintain energy equipartition.
+In other words, the relaxation timescale must remain short relative to the growth timescale.
+For typical conditions near the terrestrial planet forming region of the solar system, this timescale condition is satisfied.
+Due to the steep dependence of the relaxation time on encounter velocity, this condition can easily be violated at shorter orbital periods.
+
+In figure \ref{fig:timescales}, we show ratio between the relaxation and collision timescale for a population of equal-mass planetesimals as a function of orbital period.
+Here, the encounter velocity is described by $v = \left( 5/8 \left< e^2 \right>^{1/2} + \left< i^2 \right>^{1/2} \right)^{1/2} v_{k}$, where $\left< e^2 \right>^{1/2}$ and $\left< i^2 \right>^{1/2}$ are the eccentricity and inclination dispersions of the planetesimal disk and $v_{k}$ is the Keplerian velocity.
+For simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2 \right>{1/2}$ \citep{ida93a} and that the eccentricity dispersion is constant with orbital period.
+The eccentricity dispersion is described in units scaled by the Hill factor $m_{pl}/ 3 M_{star}$ such that $e_{h} = 1$ corresponds to the boundary between shear and dispersion dominated encounters.
+The horizontal dashed line indicates where $t_{relax} = t_{coll}$.
+The timescale criterion for oligarchic growth is only satisfied in regions where the disk is sufficiently dynamically cold and the orbital period is sufficiently long.
+In section \ref{sec:results} we will explore the behavior and outcome of planetesimal accretion in regions where this criterion is \textit{not} satisfied.
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/timescales.png}
+    \caption{The ratio between the two-body relaxation and collision timescale for a population of equal-mass planetesimals.
+Only in regions where $t_{relax} \ll t_{coll}$ can the velocity distribution respond to changes in the mass of the bodies such that oligarchic growth can operate.
+This condition is no longer satisfied for a dynamically hot disk at sufficiently short orbital periods.\label{fig:timescales}}
+\end{center}
+\end{figure}
+
 % analytic conditions for runaway and orderly growth
@@
 % show show period-mass distribution, with isolation mass curve overlaid
+% what about 'maximum planetary mass' from Schlichting 2014?
 % show plot of period vs alpha, mass. drop in embryo mass occurs where alpha = 0.1
@@
 % is there a clever, succinct way to show the evolution of sigma/Sigma in each period bin? to demonstrate that the accretion boundary is static
+
+% does the accretion boundary always fall somewhere within the PPD, or can it lie inside the magnetic truncation radius sometimes?
+how does this depend on spectral type?
+(this is complicated, depends on radius + magnetic field strength of star, plus accretion rate of PPD)
 
@@
 
+As was pointed out in \citet{clement20},  late stage initial conditions with a uniform distribution of embryos is not accurate.
+Evolution happens in the inner part of the disk first, so bodies will be more massive there.
+
 Summary and discussion text goes here

### 2021-11-18 makeFig.py

@@ -6,6 +6,7 @@ import pandas as pd
 import pynbody as pb
 import natsort as ns
 import glob as gl
+import re
 import os
 import profileTools as pt
 
@@ -49,6 +50,59 @@ e_min, e_max = 1e-3, 1
 # Input in sim units, output in days
 def p_orbit(sma, m_central):
 	return (2*np.pi*np.sqrt(sma**3/m_central)*simT).to(u.d).value
+
+def plot_timescales():
+	file_str = 'figures/timescales.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	# r in AU
+	def surf_den(r):
+		sigma0 = 10 # g/cm^2
+		alpha = 3/2
+		return (sigma0*(r)**(-alpha)).value*u.g/u.cm**2
+
+	rhop = 3*u.g/u.cm**3
+	rp = (100*u.km).to(u.cm) # Timescale ratio is independent of size at fixed density
+	mp = 4/3*np.pi*rhop*rp**3
+
+	mstar = (1*u.M_sun).to(u.g)
+	p_bins = (np.logspace(-4, 0)*u.yr).to(u.s)
+	r_bins = ((p_bins/(2*np.pi))**2*G.cgs*mstar)**(1/3)
+
+	def timescale_ratio(eh):
+		Sigma = surf_den(r_bins.to(u.AU))
+
+		vk = np.sqrt(G.cgs*mstar/r_bins)
+		lnLam = 5
+		omega = 2*np.pi/p_bins
+		vesc = np.sqrt(G.cgs*mp/rp)
+
+		# Dispersion dominated boundary
+		ecc = eh*(mp/(3*mstar))**(1/3)
+		inc = ecc/2
+		sigma = np.sqrt(5/8*ecc**2 + inc**2)*vk
+
+		n = Sigma*omega/(2*mp*sigma)
+		theta = vesc/sigma
+		cross = np.pi*rp**2*(1 + theta**2)
+		t_coll_vals = 1/(n*cross*sigma)
+		t_relax_vals = sigma**3/(n*np.pi*G.cgs**2*mp**2*lnLam)
+
+		return t_relax_vals/t_coll_vals
+
+	fig, axes = plt.subplots(figsize=(8,8))
+	ehvals = [16, 8, 4, 2, 1]
+	for eh in ehvals:
+		axes.plot(p_bins.to(u.d), timescale_ratio(eh), label=r'e$_{h}$ = '+str(eh))
[…]

### 2021-11-19 main.tex
Add more content

@@
 
-We begin our analysis by considering a disk of equal planetesimals with radius $s$, mass $m_{pl}$ and surface density $\Sigma_{pl}$.
+\subsection{Oligarchic and Runaway Growth}
+
+We begin our analysis by considering a disk of equal planetesimals with radius $r_{pl}$, mass $m_{pl}$ and surface density $\Sigma_{pl}$.
 The collision rate in the vicinity of an orbit defined by Keplerian frequency $\Omega$ can be written as $n \Gamma v$, where $n = \Sigma_{pl} \Omega / 2 m_{pl} v$, $\Gamma$ is the effective collision cross section and $v$ is the typical encounter velocity between planetesimals.
@@
 
+\subsection{Planetesimal Size and Extent of Hill Sphere}
+
+In the formalism described above, the mass and velocity distribution of the bodies are both a function of time.
+Due to the interdependence of these quantities, it is not clear whether the timescales for gravitational scattering and growth will remain proportional as the oligarchs develop.
+In the case of many studies of planetesimal accretion in the solar system (cite examples), the $t_{relax} \ll t_{coll}$ condition must remain true, otherwise runaway growth would have continued until all of the planetesimals were consumed.
+However, it isn't immediately clear what will happen if the system begins in a state where $t_{coll} \ll t_{relax}$.
+
+An insight into the expected behavior in this regime can be gained by defining the dimensionless parameter $\alpha$, which is the ratio between the physical size of a body and it's Hill radius
+
+\begin{equation}\label{eq:alpha}
+	\alpha = \frac{r_{pl}}{r_{h}} = \frac{1}{a} \left( \frac{9 M_{*}}{4 \pi \rho_{pl}} \right)^{1/3},
+\end{equation}
+
+\noindent where $a$ is the semimajor axis of the body and $\rho_{pl}$ is its bulk density.
+Assuming a fixed bulk density as bodies collide and grow, and that no large-scale migration occurs, the scaling of both $r_{pl}$ and $r_{h}$ with $m_{pl}^{1/3}$ means that $\alpha$ will be constant with time.
+For a composition of ice and rock, $\alpha$ is small for any populated region of the solar system ($\alpha \sim 10^{-2}$ for Earth and $\alpha \sim 10^{-4}$ in the Kuiper belt).
+As one moves close to the star $\alpha$ becomes larger than 1, which implies that the physical extent of a body exceeds its Hill sphere.
+(also mention that hill sphere size independent of velocity for small eccentricity)
+
+The size of $\alpha$ controls the relative importance of gravitational scattering and collisions in driving the evolution of the planetesimal disk.
+In the case that $\alpha$ is small, most close encounters will result in a gravitational interaction only, moving the system toward a state of relaxation.
+If, however, the Hill sphere is largely filled by the body itself, these same encounters will instead drive evolution of the masses.
+Because $\alpha$ is independent of time, the innermost region of the planetesimal disk, where collisions dominate over scattering events, should remain that way.
+
+Need a transition to next section here.
+
 % analytic conditions for runaway and orderly growth
@@
 
-\section{Methods}\label{sec:methods}
+\section{Numerical Methods}\label{sec:methods}
 
-\subsection{The Code}
+We use the tree-based N-body code {\sc ChaNGa} \footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}} to model the gravitational and collisional evolution of planetesimals at short orbital periods (where $\alpha$ is large).
+{\sc ChaNGa} is written using the {\sc CHARM++} parallel programming language and has been shown to perform well on up to half a million processors \citep{menon15} and can follow the evolution of gravitationally interacting swarms of up to billions of particles.
+Using a modified Barnes-Hut tree with hexadecapole expansions of the moments to approximate forces, {\sc ChaNGa} integrates the equations of motion using a kick-drift-kick leapfrog scheme.
+For all of the simulations presented in this paper, we use a node opening criteria of $\theta_{BH}$ = 0.7.
+Additional information about the code is available in \citep{jetley08}.
 
-\subsection{Initial Conditions}
+Using the neighbor-finding algorithm in {\sc ChaNGa}, originally designed for SPH calculations, we have recently implemented a solid body collision module in the code.This work is largely based on the solid-body collision implementation in {\sc PKDGRAV}, which is described in \citet{richardson94} and \citet{richardson00}.
+To summarize, imminent collisions are detected during the `drift' phase by extrapolating positions of bodies forward in time, using the velocity calculated at the opening `kick'.
+For each body, any neighboring particles which fall within a search ball of radius $fill in later$ are tested for an imminent collision.
+In the case that a collision is detected, the particles are merged into a single larger body, which is given the center of mass position and velocity of the two children.
+Resolving a collision can produce another imminent collision, so collisions are handled one-by-one and another full collision check is run after the previous event is resolved.
+For a more detailed description of the collision module in {\sc ChaNGa}, see \citep{wallace19}.
+(mention grav stepping here as well, since its used for all simulations)
 
-\section{Results}\label{sec:results}
+\section{Narrow Annulus Simulations}\label{sec:narrow}
 
-\subsection{Narrow Annulus}
+We begin by exploring a parameter study of planetesimal accretion, motivated by two questions raised in section \ref{sec:theory}.
+1.
+Does runaway growth still operate when the condition that $v \ll v_{esc}$ is not satisfied?
+2.
+How does planetesimal accretion proceed when $\alpha$ is no longer small?
+
+To answer these questions, we run a series of simulations in which a narrow annulus of planetesimals orbits a star.
+The values of $\alpha$ and $\beta = v / v_{esc}$ are varied individually.
+4000 planetesimals with individual masses of $5 \times 10^{23}$ g are placed with semimajor axes randomly drawn between 0.95 and 1.05 AU about a 1 $M_{\odot}$ star.
+The argument of perihelion $\omega$, longitude of ascending node $\Omega$, and mean anomaly M for each body is drawn from a uniform distribution $\in [0, 2 \pi)$.
+The inclination dispersion $\left< i^{2} \right>^{1/2}$ is chosen to be half the eccentricity dispersion $\left< e^{2} \right>^{1/2}$ \citep{ida93a}.
+
+In the `nominal' case, we give the bodies a bulk density of 3 g cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, where $e_{h} = e a/r_{h}$ (define this in the previous section instead) which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
+These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth.
+To vary the value of $\alpha$, we alter the bulk density of the particles.
+In the high-$\alpha$ case, the bulk density is reduced by a factor of $\sim$ 7100, which produces $\alpha = 1$.
+To vary $\beta$, the eccentricity dispersion is increased.
+For the high-$\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
+% Should I choose beta = 1 instead? I did beta >> 1 to see if inelastic mergers will cool things off. Havent decided if that's important here
+
+In all cases, the simulations are evolved with a base timestep of 1.7 days, which corresponds to 3\% of an orbital dynamical time $\sqrt{a^3/G M_{*}}$.
+Due to the vastly differing growth timescales in each case, a simulation is stopped when the growth of the most massive body flattens out.
+In figure \ref{fig:alpha_beta}, we show the a-e distribution of bodies in the initial (blue) and final (orange) snapshots from each of the 4 simulations.
+The size of the points indicates the relative masses of the bodies.
+Only in the case of small $\alpha$ does a residual population of dynamically hot planetesimals develop.
+The lack of high eccentricity planetesimals in the large $\alpha$ case suggests that most encounters instead result in accretion.
+In the case of large $\beta$, the protoplanets and remaining planetesimals end up in a dynamically cool state, compared to the initial conditions.
+Here, the only mechanism that can remove energy are the merger events which result in an inelastic collision.
+
+%If we run a cooler version of the high-beta simulations (so that the masses can evolve further), does the high alpha case end up cooler?
+If so, that would be a second indication that 'collisions are driving the dynamics at high alpha'.
+
+To investigate whether any of these planetesimal disks underwent runaway growth, we examine the time evolution of the maximum and mean masses in each simulation.
+The ratio $m_{max}/\left< m \right>$ is plotted in figure \ref{fig:alpha_beta_evo}.
+On this plot, a positive slope indicates that the growth rate is accelerating with mass, which is evident in all four cases.
+Even with large $\beta$, runaway growth still appears to operate for some duration of time.
+
+\section{Full Disk Simulation}\label{sec:fulldisk}
 
@@
     \includegraphics[width=\textwidth]{figures/alpha_beta.png}
-    \caption{Caption goes here.\label{fig:alpha_beta}}
+    \caption{The initial (blue) and final (orange) states of the simulations described in section \ref{sec:narrow}.
+Relative masses of the bodies are indicated by point size.
+In the case of large $\alpha$, almost no residual planetesimal population remains.
+Regardless of the choice of $\beta$, the protoplanets that form attain similar eccentricities.
+\label{fig:alpha_beta}}
 \end{center}
@@
 % show that runaway growth still operates for large beta
-
-\subsection{Full Disk}
 

### 2021-11-19 makeFig.py

@@ -118,9 +118,9 @@ def plot_alpha_beta():
 		pl0 = ko.orb_params(snap0, isHelio=ih, mCentral=mcen)
 		snap = pb.load('data/'+prefix+'.end')
 		pl = ko.orb_params(snap, isHelio=ih, mCentral=mcen)
-		ax.scatter(p_orbit(pl0['a'], mcen), pl0['e'], s=pl0['mass']/np.max(pl['mass'])*100)
-		ax.scatter(p_orbit(pl['a'], mcen), pl['e'], s=pl['mass']/np.max(pl['mass'])*100)
-		ax.set_xlabel('Orbital Period [d]')
+		ax.scatter(pl0['a'], pl0['e'], s=pl0['mass']/np.max(pl['mass'])*100)
+		ax.scatter(pl['a'], pl['e'], s=pl['mass']/np.max(pl['mass'])*100)
+		ax.set_xlabel('Semimajor Axis [AU3]')
 		ax.set_ylabel('Eccentricity')
 		ax.set_title(title)
 
@@ -131,7 +131,7 @@ def plot_alpha_beta():
 	subplot(ax[1][1], 'ki_superhot', r'Small $\alpha$, Large $\beta$')
 
 	ax[1][1].set_yscale('log')
-	ax[1][1].set_xlim(330, 400)
+	ax[1][1].set_xlim(0.9, 1.1)
 	ax[1][1].set_ylim(1e-5, 0.3)
 
 	plt.tight_layout()
@@ -288,7 +288,7 @@ def plot_pl_frac_time():
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 plot_timescales()
-#plot_alpha_beta()
+plot_alpha_beta()
 #plot_alpha_beta_evo()
 #plot_fulldisk_e_m()
 #plot_alpha_pl_frac()

### 2021-11-20 main.tex
More text

@@
 % Should I choose beta = 1 instead? I did beta >> 1 to see if inelastic mergers will cool things off. Havent decided if that's important here
+% Another concern: using too large of a beta makes the apo-peri distances larger than the width of the annulus
 
@@
 On this plot, a positive slope indicates that the growth rate is accelerating with mass, which is evident in all four cases.
-Even with large $\beta$, runaway growth still appears to operate for some duration of time.
+Even with a large value of $\beta$, runaway growth still appears to operate for some duration of time.
+
+Most importantly, these results suggest that the value of $\alpha$, which is a function of only the initial conditions, controls the qualitative outcome of accretion.
+For most regions in a planet-forming disk, $\alpha$ is small and frequent gravitational encounters between the growing bodies allows oligarchic growth to operate.
+At shorter orbital periods, the Hill sphere shrinks and it appears as if the gravitational encounters play a less significant role.
+In this regime, it appears that runaway growth still commences, but the enhanced role that collisions play means that nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered onto high eccentricity orbits, where they remain as a remnant of the early stages of planet formation \citep{kokubo98, kokubo00}.
 
 \section{Full Disk Simulation}\label{sec:fulldisk}
+
+Motivated by the apparent dependence of accretion modes on $\alpha$, we next investigate whether this highly efficient, non-oligarchic growth mode should be expected to operate in nature.
+Given the dearth of short period terrestrial planets observed around M stars (citation), we model a series of much wider disks, which span from 1 to 100 days in orbital period orbiting a star of mass 0.08 $M_{\odot}$.
+For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this corresponds to $\alpha \in (0.7, 0.05)$.
+By modeling a fuller range of orbital periods, we can determine the critical value of $\alpha$ that divides these two modes of accretion, and what effect the accretion boundary itself has on the resulting protoplanet distribution.
+
+More stuff about initial conditions, timestepping issues, gas drag
 
@@
 % show alpha, beta study again with bounce vs merge model
+% mergers still happen for 'lo' simulations but not 'hi'
+% this is because the eccentricity dispersion is significantly higher in the 'hi' case
+% mostly because stirring rate increases with surface density
+% criteria should get less restrictive as larger bodies grow, what if we turn on bounces partway thru growth process?
 

### 2021-11-20 makeFig.py

@@ -120,7 +120,7 @@ def plot_alpha_beta():
 		pl = ko.orb_params(snap, isHelio=ih, mCentral=mcen)
 		ax.scatter(pl0['a'], pl0['e'], s=pl0['mass']/np.max(pl['mass'])*100)
 		ax.scatter(pl['a'], pl['e'], s=pl['mass']/np.max(pl['mass'])*100)
-		ax.set_xlabel('Semimajor Axis [AU3]')
+		ax.set_xlabel('Semimajor Axis [AU]')
 		ax.set_ylabel('Eccentricity')
 		ax.set_title(title)
 

### 2021-11-24 main.tex
More content

--- 2021-11-19 main.tex
@@
 For simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2 \right>{1/2}$ \citep{ida93a} and that the eccentricity dispersion is constant with orbital period.
-The eccentricity dispersion is described in units scaled by the Hill factor $m_{pl}/ 3 M_{star}$ such that $e_{h} = 1$ corresponds to the boundary between shear and dispersion dominated encounters.
+The eccentricity dispersion is described in units scaled by the Hill factor $\left( m_{pl}/ 3 M_{star} \right)^{1/3}$ such that $e_{h} = 1$ corresponds to the boundary between shear and dispersion dominated encounters.
 The horizontal dashed line indicates where $t_{relax} = t_{coll}$.
@@
 
+We also introduce a second dimensionless quantity, which relates the physical size of the bodies to the velocity state of the system
+
+\begin{equation}\label{eq:beta}
+	\beta = \frac{r_{pl}}{r_{g}}.
+\end{equation}
+
+\noindent where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body.
+Encounters between bodies inside of a distance of $r_{g}$ result in significant deflections of their trajectories.
+It should be noted that the gravitational focusing enhancement factor $v^{2}/v_{esc}^{2}$ is equal to 1 for $\beta = 1$.
+In the case where $r_{g}$ is smaller than the size of a planetesimal, the gravitational focusing enhancement factor will be between 0 and 1.
+
 Need a transition to next section here.
@@
 
-We begin by exploring a parameter study of planetesimal accretion, motivated by two questions raised in section \ref{sec:theory}.
+We begin by presenting a parameter study of planetesimal accretion, motivated by two questions raised in section \ref{sec:theory}.
 1.
@@
 2.
-How does planetesimal accretion proceed when $\alpha$ is no longer small?
+How does planetesimal accretion proceed when the planetesimals themselves occupy a significant fraction of their Hill spheres?
 
 To answer these questions, we run a series of simulations in which a narrow annulus of planetesimals orbits a star.
-The values of $\alpha$ and $\beta = v / v_{esc}$ are varied individually.
+The values of $\alpha$ and $\beta$ are varied individually.
 4000 planetesimals with individual masses of $5 \times 10^{23}$ g are placed with semimajor axes randomly drawn between 0.95 and 1.05 AU about a 1 $M_{\odot}$ star.
@@
 In the case of large $\beta$, the protoplanets and remaining planetesimals end up in a dynamically cool state, compared to the initial conditions.
-Here, the only mechanism that can remove energy are the merger events which result in an inelastic collision.
+(Are the inelastic collisions playing a significant role here?)
+
+In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four cases.
+In addition to leaving fewer residual planetesimals, the large $\alpha$ simulations produce significantly larger embryos.
+Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ appears to have no significant effect on the final distribution of masses.
 
@@
 
-To investigate whether any of these planetesimal disks underwent runaway growth, we examine the time evolution of the maximum and mean masses in each simulation.
+To investigate whether any of these planetesimal disks underwent runaway growth, we examine the time evolution of the maximum and mean masses in each case.
 The ratio $m_{max}/\left< m \right>$ is plotted in figure \ref{fig:alpha_beta_evo}.
 On this plot, a positive slope indicates that the growth rate is accelerating with mass, which is evident in all four cases.
-Even with large $\beta$, runaway growth still appears to operate for some duration of time.
+Even with a large value of $\beta$, which means that the effective collision cross section is very near the geometric value, runaway growth still appears to operate.
+This seems to imply that, as bodies collide and grow, the relative increase in their gravitational focusing factors, rather than its absolute size, is what drives the system towards runaway growth.
+Although larger encounter velocities will lengthen the growth timescales, this mode of growth appears to be inevitable, so long as gravity is the dominant force in the system.
+
+Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions, controls the qualitative outcome of accretion.
+Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will allow oligarchic growth to operate.
+At shorter orbital periods, however, the Hill sphere of a body is no longer mostly empty space, and it appears as if collisions play a more significant role.
+In this regime, we observe that runaway growth still commences, but nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of planet formation \citep{kokubo98, kokubo00}.
+
+\begin{table}
+\begin{center}
+\caption{Summary of Full Disk Simulations Run}
+\begin{tabular}{lllll} \hline \hline
+Name     & A & $\alpha$ &  &  \\ \hline
+fdHi                 & 100                                                         & 1.5                              &  &  \\
+fdHiShallow     & 100                                                        & 0.5                              &  &  \\
+fdHiSteep       & 100                                                         & 2.5                              &  &  \\
+fdLo                & 1                                                             & 1.5                              &  &  \\ \hline
+\end{tabular}
+\label{tab:sims}
+\end{center}
+\end{table}
 
 \section{Full Disk Simulation}\label{sec:fulldisk}
+
+Motivated by the apparent dependence of accretion modes on $\alpha$, we next investigate whether this highly efficient, non-oligarchic growth mode should be expected to operate in nature.
+Given the dearth of short period terrestrial planets observed around M stars (citation), we model a series of much wider disks, which span from 1 to 100 days in orbital period orbiting a late-type M star of mass 0.08 $M_{\odot}$.
+For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this orbital period range corresponds to $\alpha \in (0.7, 0.05)$.
+By simultaneously modeling a broad range of orbital periods, we can determine the critical value of $\alpha$ that divides these two modes of accretion, and also explore how the oligarchic/non-oligarchic accretion boundary affects the resulting distribution of protoplanets.
+
+Four wide disk simulations are run in total (see table \ref{tab:sims}). In each case, the solid surface density follows a power law profile
+
+\begin{equation}
+	\Sigma(r) = \left( \frac{M_{*}}{M_{\odot}} \right) A \Sigma_{mmsn} \left( \frac{r}{1 AU} \right)^{-\alpha},
+\end{equation}
+
+\noindent where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g cm$^{-2}$ is surface density of the minimum-mass solar nebula \citep{hayashi81} at 1 AU, and $A$ is an enhancement factor.
+In the first case (fdHi), we model a disk that follows the surface density
+
+More stuff about initial conditions, timestepping issues, gas drag
 
@@
 \end{figure*}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_mass.png}
+    \caption{Caption goes here.\label{fig:alpha_beta_mass}}
+\end{center}
+\end{figure}
 

### 2021-11-24 makeFig.py

@@ -126,9 +126,9 @@ def plot_alpha_beta():
 
 	fig, ax = plt.subplots(figsize=(16,16), nrows=2, ncols=2, sharex=True, sharey=True)
 	subplot(ax[0][0], 'ki_fluffy_cold', r'Large $\alpha$, Small $\beta$')
-	subplot(ax[0][1], 'ki_fluffy_superhot', r'Large $\alpha$, Large $\beta$')
+	subplot(ax[0][1], 'ki_fluffy_hot', r'Large $\alpha$, Large $\beta$')
 	subplot(ax[1][0], 'disk4000', r'Small $\alpha$, Small $\beta$')
-	subplot(ax[1][1], 'ki_superhot', r'Small $\alpha$, Large $\beta$')
+	subplot(ax[1][1], 'ki_hot', r'Small $\alpha$, Large $\beta$')
 
 	ax[1][1].set_yscale('log')
 	ax[1][1].set_xlim(0.9, 1.1)
@@ -148,18 +148,62 @@ def plot_alpha_beta_evo():
 	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_fluffy_cold.txt')
 	axes.loglog(stepnumber, max_mass/mean_mass, label=r'Large $\alpha$, Small $\beta$')
 
-	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_fluffy_superhot.txt')
+	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_fluffy_hot.txt')
 	axes.loglog(stepnumber, max_mass/mean_mass, label=r'Large $\alpha$, Large $\beta$')
 
 	stepnumber, max_mass, mean_mass = np.loadtxt('data/disk4000.txt')
 	axes.loglog(stepnumber, max_mass/mean_mass, label=r'Small $\alpha$, Small $\beta$')
 
-	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_superhot.txt')
+	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_hot.txt')
 	axes.loglog(stepnumber, max_mass/mean_mass, label=r'Small $\alpha$, Large $\beta$')
 
 	axes.set_xlabel('Time Steps')
 	axes.set_ylabel(r'M / $\langle$ m $\rangle$')
 	axes.legend()
+
+	plt.savefig(file_str, format=fmt, bbox_inches='tight')
+
+def plot_alpha_beta_mass():
[…]

### 2021-11-24 main.tex
Gas drag and viscous stirring equations

@@
 
+% Mention Rayleigh distribution
 In the `nominal' case, we give the bodies a bulk density of 3 g cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, where $e_{h} = e a/r_{h}$ (define this in the previous section instead) which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
@@
 For the high-$\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
+% Important note: need to use f=6 for the low alpha case, otherwise the simulation takes forever. Do these alpha values reflect the artifically enhanced collision cross section im using?
 % Should I choose beta = 1 instead? I did beta >> 1 to see if inelastic mergers will cool things off. Havent decided if that's important here
@@
 
-Motivated by the apparent dependence of accretion modes on $\alpha$, we next investigate whether this highly efficient, non-oligarchic growth mode should be expected to operate in nature.
-Given the dearth of short period terrestrial planets observed around M stars (citation), we model a series of much wider disks, which span from 1 to 100 days in orbital period orbiting a late-type M star of mass 0.08 $M_{\odot}$.
+\subsection{Initial Conditions}
+
+Motivated by the apparent dependence of accretion modes on $\alpha$, we next investigate whether this highly efficient, non-oligarchic growth mode should be expected to operate in a typical planet-forming disk.
+Given the dearth of short period terrestrial planets observed around M stars (citation), we model a series of wide planetesimal disks, which span from 1 to 100 days in orbital period orbiting a late-type M star of mass 0.08 $M_{\odot}$.
 For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this orbital period range corresponds to $\alpha \in (0.7, 0.05)$.
@@
 \noindent where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g cm$^{-2}$ is surface density of the minimum-mass solar nebula \citep{hayashi81} at 1 AU, and $A$ is an enhancement factor.
-In the first case (fdHi), we model a disk that follows the surface density
+In the first case (fdHi), we model a disk that follows a MMSN power law slope, with the overall normalization enhanced by a factor of 100.
+This choice of parameters for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \citep{hansen12}.
+Additionally, we vary the power law index (fdHiShallow, fdHiSteep) and overall normalization (fdLo) of the solids profile.
+
+In all cases, the eccentricities and inclinations of the bodies are randomly drawn from a Rayleigh distribution, with $\left< e^{2} \right>^{1/2} = 2\left<i^{2} \right>^{1/2} = e_{eq}$.
+The value of $e_{eq}$ is chosen such that the timescales for viscous stirring and aerodynamic gas drag on the planetesimals are in equilibrium.
+The viscous stirring timescale is given by \citet{ida93} as
+
+\begin{equation}\label{eq:vs_timescale}
+    \tau_{vs}  = \frac{\left< e^2 \right>}{d \left< e^2 \right> / dt} \approx \frac{1}{40}\left(\frac{\Omega^{2} a^{3}}{2 G m_{pl}}\right)^{2} \frac{4 m_{pl} \langle e^{2} \rangle^{2}}{\Sigma a^{2} \Omega},
+\end{equation}
+
+\noindent where $\Omega$, $a$ and $e$ are the orbital frequencies, semimajor axes and eccentricities of the individual planetesimals.
+In the Stokes regime, the gas drag timescale is given by \citet{adachi76} as
+
+\begin{equation}\label{eq:ts_stokes}
+    t_{s} = \frac{2 m_{pl}}{C_{D} \pi r_{pl}^{2} \rho_{g} v_{g}},
+\end{equation}
+
+\noindent where $C_{D}$ is a drag coefficient of order unity, $\rho_{g}$ is the local gas volume density and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal.
+The local gas volume density is given by
+
+\begin{equation}\label{eq:rho_gas}
+	\rho_{g} = \frac{\Sigma_{g}}{\sqrt{2 \pi} h_{g} \exp\left[ -z^{2} / \left( 2 h_{g}^{2} \right) \right]},
+\end{equation}
+
+\noindent where $\Sigma_{g}$ is the gas surface density (taken to be 240x the solid surface density), $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
+The sound speed profile is given by $c_{s} = \sqrt{k_{B} T(r) / \left( \mu m_{H} \right)}$, where $k_{B}$ is Boltzmann's constant, $T(r) = T_{0} r^{-Q}$, $\mu = 2.34$ and $m_{h}$ is the mass of a hydrogen atom.
+For a protoplanetary disk around a typical M star, $T_{0} = 148$ K and $Q$ = 0.58 \citep{andrews05}.
+
+Finally, the headwind velocity of the gas, due to the fact that the gas disk is pressure supported, is given by
+
+\begin{equation}\label{eq:v_gas}
+	v_{g} = v_{k} \left[ 1 - \sqrt{ Q c_{s}^2 / v_{k}^2} \right],
+\end{equation}
+
+\noindent where $v_{k}$ is the local Keplerian velocity.
 
@@
 
-\section{Radial Transport of Material}
+\section{Assembly History of Embryos}
 
@@
 % do embryos migrate at all? might need to run a simulation without gas to demonstrate whether this is due to PDM
+% major vs minor mergers?
 

### 2021-11-27 main.tex
Fix up alpha beta data

@@
 \noindent where $v_{k}$ is the local Keplerian velocity.
+As in section \ref{sec:narrow}, the argument of perihelion $\omega$, longitude of ascending node $\Omega$, and mean anomaly M for the planetesimals drawn from a uniform distribution $\in [0, 2 \pi)$.
 
-More stuff about initial conditions, timestepping issues, gas drag
+\subsection{Gas Drag Force}
+
+In addition to the mutual gravitational forces, a Stokes drag force from to the gas disk is applied to each particle, following the prescription described in section 2.2.1 of \citet{morishima10}.
+The surface density and temperature profile are identical to those used to construct the initial conditions and the cylindrical coordinate system is centered on the host star.
+
+\subsection{Timestepping Criterion}
+
+In the case of the fdHi simulation, there are nearly 1 million particles, whose orbital periods two orders of magnitude in time.
+Due to the very short interaction timescales near the inner edge of the disk, a fixed timestep size would required a prohibitively large number of steps to follow planetesimal growth throughout the entire disk.
+For this reason, we use a multi-tiered timestepping scheme, in which particles are placed onto the nearest power of two timestep based on their most recently calculated gravitational acceleration.
+(Mention that this scheme is used in other works with ChaNGa).
+
+This more efficient scheme, however, introduces two additional issues related to particles interacting on different timesteps.
+First, momentum is not completely conserved when bodies switch timesteps.
+The error introduced becomes particularly severe for a particle on an eccentric Keplerian orbit, whose perihelion and aphelion distances straddle a timestep boundary.
+For a large collection of particles, this problem manifests itself as a V-shaped gap in the semimajor axis-eccentricity plane, which is centered on the boundary itself.
+To correct this problem, we introduce a second timestepping criterion, which is based on the gravitational acceleration on the particle by the central star at perihelion.
+Only in the case of a close encounter with another planetesimal (in which the acceleration is no longer dominated by the star) is the timestep allowed to reduce based on the original criterion.
+
+A second issue is introduced when two particles on different timesteps undergo a collision.
+As in the previous case, momentum is not completely conserved because the most recent `kick' steps did not happen simultaneously for these bodies.
+Early in the simulation, we find that runaway growth tends to trigger first at the timestep boundaries.
+Unfortunately, this issue carries itself forward through the embryo formation phase and protoplanets tend to form at the boundaries.
+To correct this issue, we ignore collisions between bodies on different timesteps early in the simulation.
+We find that enabling multi-timestep collisions after the maximum mass grows by a factor of 10 prevents any artifacts from forming at the timestep boundaries, while also minimizing the number of `skipped' collisions\footnote{In the case of fdHi, only about 20 collisions out of an eventual 900,000 are ignored.}.
 

### 2021-11-27 makeFig.py

@@ -111,13 +111,11 @@ def plot_alpha_beta():
 
 	def subplot(ax, prefix, title):
 		mcen = 1
-		ih = True
-		if prefix == 'disk4000':
-			ih = False
 		snap0 = pb.load('data/'+prefix+'.ic')
-		pl0 = ko.orb_params(snap0, isHelio=ih, mCentral=mcen)
+		pl0 = ko.orb_params(snap0, isHelio=True, mCentral=mcen)
 		snap = pb.load('data/'+prefix+'.end')
-		pl = ko.orb_params(snap, isHelio=ih, mCentral=mcen)
+		pl = ko.orb_params(snap, isHelio=True, mCentral=mcen)
+		print()
 		ax.scatter(pl0['a'], pl0['e'], s=pl0['mass']/np.max(pl['mass'])*100)
 		ax.scatter(pl['a'], pl['e'], s=pl['mass']/np.max(pl['mass'])*100)
 		ax.set_xlabel('Semimajor Axis [AU]')
@@ -125,9 +123,9 @@ def plot_alpha_beta():
 		ax.set_title(title)
 
 	fig, ax = plt.subplots(figsize=(16,16), nrows=2, ncols=2, sharex=True, sharey=True)
-	subplot(ax[0][0], 'ki_fluffy_cold', r'Large $\alpha$, Small $\beta$')
+	subplot(ax[0][0], 'ki_fluffy', r'Large $\alpha$, Small $\beta$')
 	subplot(ax[0][1], 'ki_fluffy_hot', r'Large $\alpha$, Large $\beta$')
-	subplot(ax[1][0], 'disk4000', r'Small $\alpha$, Small $\beta$')
+	subplot(ax[1][0], 'ki', r'Small $\alpha$, Small $\beta$')
 	subplot(ax[1][1], 'ki_hot', r'Small $\alpha$, Large $\beta$')
 
 	ax[1][1].set_yscale('log')
@@ -145,16 +143,18 @@ def plot_alpha_beta_evo():
 
 	fig, axes = plt.subplots(figsize=(8,8))
 
-	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_fluffy_cold.txt')
+	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_fluffy.txt')
 	axes.loglog(stepnumber, max_mass/mean_mass, label=r'Large $\alpha$, Small $\beta$')
 
[…]

### 2021-11-28 main.tex
Add text discussing full disk sims

@@
 \begin{table}
-\begin{center}
 \caption{Summary of Full Disk Simulations Run}
-\begin{tabular}{lllll} \hline \hline
-Name     & A & $\alpha$ &  &  \\ \hline
-fdHi                 & 100                                                         & 1.5                              &  &  \\
-fdHiShallow     & 100                                                        & 0.5                              &  &  \\
-fdHiSteep       & 100                                                         & 2.5                              &  &  \\
-fdLo                & 1                                                             & 1.5                              &  &  \\ \hline
+\begin{tabular}{llllll} \hline \hline
+Name    & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\alpha^{d}$ &  \\ \hline
+fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &   \\
+fdHiShallow    & $5 \times 10^{22}$ & 903,687 & 100                                                        & 0.5                              &   \\
+fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &   \\
+fdLo                & $1 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &   \\ \hline
 \end{tabular}
+\begin{flushleft}
+\textsc{Note} \\ {$^a$ Planetesimal mass [g] \\
+		       $^b$ Number of planetesimals \\
+		       $^c$ Solid surface density normalization (relative to MMSN) \\
+		       $^d$ Solid surface density power law index } \\
+\end{flushleft}
 \label{tab:sims}
-\end{center}
 \end{table}
@@
 We find that enabling multi-timestep collisions after the maximum mass grows by a factor of 10 prevents any artifacts from forming at the timestep boundaries, while also minimizing the number of `skipped' collisions\footnote{In the case of fdHi, only about 20 collisions out of an eventual 900,000 are ignored.}.
+
+\subsection{Results}
+
+\begin{table}
+\caption{Final Properties of Full Disk Simulations}
+\begin{tabular}{lllll} \hline \hline
+Name     & $M_{PP}^a$ & $T_{int}^b$ & $T_{int 1}^c$ &  \\ \hline
+fdHi                 & 100                                                         & 1.5                              & 4  &  \\
+fdHiShallow     & 100                                                        & 0.5                              & 4  &  \\
+fdHiSteep       & 100                                                         & 2.5                              & 4 &  \\
+fdLo                & 1                                                             & 1.5                              & 4 &  \\ \hline
+\end{tabular}
+\label{tab:sim_properties}
+\begin{flushleft}
+\textsc{Note} \\ {$^a$ Maximum protoplanet mass [$M_{earth}$] \\
+		       $^b$ Integration time [yr] \\
+		       $^c$ Rescaled integration time [yr]} \\
+\end{flushleft}
+\end{table}
+
+In all four simulations, the timescales for embryo formation depend on the chosen surface density profile, along with the particular location in the disk.
+Protoplanets form first near the inner edge of the disk, where the dynamical timescales are short.
+Growth proceeds in an inside-out fashion, with the outermost regions of the disk completing the protoplanet assembly phase last.
+This fact is not typically accounted for in planet formation simulations, and appears to be an important component to forming realistic solar system analogs \citep{clement20}.
+As with the narrow annulus simulations, we stop the integration once the mass of protoplanets in the outermost region of the disk reach a steady value.
+In table \ref{tab:sim_properties}, we summarize the outcomes of the four `full disk' cases.
+
+We show the final state of the `fiHi' simulation in figure \ref{fig:fulldisk_e_m}.
+In the top panel, the initial (contours) and final (points) state of the simulation is shown in orbital period and eccentricity.
+The size of the points indicates the relative mass of the bodies.
+In the bottom panel, the mass of the largest bodies is shown as a function of orbital period.
+The solid curves indicate the isolation mass
+
+\begin{equation}\label{eq:iso}
+	M_{iso} = \left[ \frac{\left( 2 \pi a^2 \Sigma \tilde{b} \right)^3}{3 M_{*}} \right]^{1/2},
+\end{equation}
+
+\noindent where $\tilde{b}$ is the size of the feeding zone in units of Hill radii.
+For a body on a circular orbit $\tilde{b} = 2 \sqrt{3}$, while a protoplanet formed by oligarchic growth typically has $\tilde{b} = 10$ \citep{kokubo98}.
+The isolation mass is plotted in blue and orange for these two values of $\tilde{b}$, respectively.
+
+A qualitative shift in the protoplanet and planetesimal distribution is visible at $\sim$ 60 days.
+Interior to this location, there are very few remaining planetesimals and the embryos formed are noticeably more massive.
+Protoplanets in this region appear to closely follow the isolation mass curve for $\tilde{b} = 10$.
+Exterior to the boundary, the residual planetesimal population is much more numerous, and protoplanets more closely follow the $\tilde{b} = 2 \sqrt{3}$ curve.
+This tentatively suggests that the transition between the low $\alpha$ and high $\alpha$ accretion modes seen in section \ref{sec:narrow} happens near this location.
+
+In figure \ref{fig:alpha_pl_frac}, we show $\alpha$ (left axis) and the fraction of remaining planetesimals (right axis) as a function of orbital period.
+Here, the fraction of remaining planetesimals is measured by dividing the disk into 15 semimajor axis bins and using the profile function in {\sc pynbody} to measure the total solid surface density $\Sigma$ in each of those bins, and also the planetesimal surface density $\sigma$.
+Here, a planetesimal is defined to any body with $m < 10 m_{pl}$.
+Exterior to 60 days in orbital period, $\sigma/\Sigma$ sharply increases, indicating that the highly efficient accretion mode seen previously does not operate here.
+As can be seen from the plot, the accretion boundary roughly corresponds to $\alpha = 0.1$.
 

### 2021-11-28 makeFig.py

@@ -332,9 +332,9 @@ def plot_pl_frac_time():
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 #plot_timescales()
-plot_alpha_beta()
-plot_alpha_beta_evo()
-plot_alpha_beta_mass()
+#plot_alpha_beta()
+#plot_alpha_beta_evo()
+#plot_alpha_beta_mass()
 #plot_fulldisk_e_m()
 #plot_alpha_pl_frac()
 #plot_pl_frac_time()

### 2021-11-29 main.tex
More content

@@
 For the high-$\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
-% Important note: need to use f=6 for the low alpha case, otherwise the simulation takes forever. Do these alpha values reflect the artifically enhanced collision cross section im using?
-% Should I choose beta = 1 instead? I did beta >> 1 to see if inelastic mergers will cool things off. Havent decided if that's important here
-% Another concern: using too large of a beta makes the apo-peri distances larger than the width of the annulus
 
@@
 
-%If we run a cooler version of the high-beta simulations (so that the masses can evolve further), does the high alpha case end up cooler?
-If so, that would be a second indication that 'collisions are driving the dynamics at high alpha'.
-
 To investigate whether any of these planetesimal disks underwent runaway growth, we examine the time evolution of the maximum and mean masses in each case.
@@
 In this regime, we observe that runaway growth still commences, but nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of planet formation \citep{kokubo98, kokubo00}.
+
+% Additional idea: run a simulation with an oligarch embedded in a disk of planetesimals for large and small alpha.
+Allow oligarch and planetesimals to collide.
+What does the eccentricity evolution of the oligarch look like in each case?
+% See equation 32 from goldreich 2004: b_scat ~ sqrt(u/vh) R_H
+% How does b_scat compare to particle size here?
+
+% One thing im still not clear on: In dispersion dominated regime, distant encounters are what drive VS + DF.
+These encounters happen well outside of the Hill sphere.
+Why does it appear to matter if the geometric cross section fills a significant chunk of the hill sphere?
+And why doesn't the velocity dispersion (beta large or small) appear to matter?
 
@@
 
+To ensure that the boundary seen near 60 days in orbital period is not simply a transient product of the inside out growth throughout the disk, we examine the time evolution of $\sigma/\Sigma$ at multiple locations.
+In figure \ref{fig:pl_frac_time}, the value of $\sigma/\Sigma$ is plotted as a function of time in 10 orbital period bins.
+Bins interior to 60 days are indicated with a dashed line, while those exterior are indicated with a solid line.
+The planetesimal surface density fraction has decelerated and is approaching an asymptotic value in all cases.
+In the inner disk, this is driven by the near-total depletion of the planetesimal reservoir.
+In the outer disk, dynamical friction between the embryos and planetesimals throttles subsequent accretion.
+
+% Since we are using f=6, do we want to stick to plotting things in terms of timestep number, and then provide rescaled time estimates at the end?
+
 \begin{figure*}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/alpha_pl_frac.png}
+    \includegraphics[width=\textwidth]{figures/alpha_pl_frac.png}
     \caption{Caption goes here.\label{fig:alpha_pl_frac}}
 \end{center}
-\end{figure}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/pl_frac_time.png}
+    \caption{Caption goes here.\label{fig:pl_frac_time}}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/surfden_profiles.png}
+    \caption{Caption goes here.\label{fig:surfden_profiles}}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/surfden_iso.png}
+    \caption{Caption goes here.\label{fig:surfden_iso}}
+\end{center}
+\end{figure*}
 
@@
 % also plot period vs sigma/Sigma and mass with alpha=0.1 location marked. residual planetesimal population missing interior to alpha=0.1
-
-% is there a clever, succinct way to show the evolution of sigma/Sigma in each period bin? to demonstrate that the accretion boundary is static
 

### 2021-11-29 makeFig.py

@@ -30,19 +30,39 @@ s = 0.005
 
 num_bins = 50
 mCentral = 0.08
+mCentralg = (mCentral*u.M_sun).to(u.g)
 
 bins = np.linspace(0.01, 0.3, num_bins)
+
 snap = pb.load('data/fullDiskVHi.ic')
 plVHiIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi_ic = pb.analysis.profile.Profile(plVHiIC.d, bins=bins)
-
-snap = pb.load('data/fullDiskVHi.258000')
+snap = pb.load('data/fullDiskVHi1.348000')
 plVHi = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi = pb.analysis.profile.Profile(plVHi.d, bins=bins)
+perIC = 2*np.pi*np.sqrt((plVHiIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+prof_perIC = 2*np.pi*np.sqrt((p_vhi_ic['rbins']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+per = 2*np.pi*np.sqrt((plVHi['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 
-perIC = 2*np.pi*np.sqrt((plVHiIC['a']*u.AU).to(u.cm)**3/(G.cgs*(mCentral*u.M_sun).to(u.g))).to(u.d)
-prof_perIC = 2*np.pi*np.sqrt((p_vhi_ic['rbins']*u.AU).to(u.cm)**3/(G.cgs*(mCentral*u.M_sun).to(u.g))).to(u.d)
-per = 2*np.pi*np.sqrt((plVHi['a']*u.AU).to(u.cm)**3/(G.cgs*(mCentral*u.M_sun).to(u.g))).to(u.d)
+snap = pb.load('data/fullDiskVHiSteep.ic')
+plVHiICSt = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+p_vhi_ic_st = pb.analysis.profile.Profile(plVHiICSt.d, bins=bins)
+snap = pb.load('data/fullDiskVHiSteep1.348000')
+plVHiSt = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+p_vhi_st = pb.analysis.profile.Profile(plVHiSt.d, bins=bins)
[…]

### 2021-12-01 main.tex
Add content

@@
 In addition to leaving fewer residual planetesimals, the large $\alpha$ simulations produce significantly larger embryos.
-Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ appears to have no significant effect on the final distribution of masses.
+Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) appears to have no significant effect on the final distribution of masses.
 
@@
 Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will allow oligarchic growth to operate.
-At shorter orbital periods, however, the Hill sphere of a body is no longer mostly empty space, and it appears as if collisions play a more significant role.
+In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and embryos \citep{weidenschilling89, ida90}.
+When $\alpha$ is large, the Hill sphere of a body is no longer mostly empty space, and close encounters that would otherwise result in stirring instead result in accretion.
 In this regime, we observe that runaway growth still commences, but nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of planet formation \citep{kokubo98, kokubo00}.
@@
 What does the eccentricity evolution of the oligarch look like in each case?
-% See equation 32 from goldreich 2004: b_scat ~ sqrt(u/vh) R_H
-% How does b_scat compare to particle size here?
 
@@
 And why doesn't the velocity dispersion (beta large or small) appear to matter?
+
+% According to Ida 1990, 'distant encounters are not important' (but viscous stirring timescale can be described by Chandresehkar time).
+Also Weidenschilling 1989.
+This is also consistent with Goldreich 2004.
+So then why does the Armitage book describe viscous stirring in terms of distant encounters (b > b_min)?
+
+% Wetherill + Stewart 1989, Ohtsuki 1990, Spaute 1991 find that runaway growth happens when velocity decreases with mass. Is that what we're seeing at high alpha?
 
@@
 
+% Also mention that no eccentricity difference between large and small alpha regions, as we saw in the narrow annulus simulations
+
 In figure \ref{fig:alpha_pl_frac}, we show $\alpha$ (left axis) and the fraction of remaining planetesimals (right axis) as a function of orbital period.
@@
 As can be seen from the plot, the accretion boundary roughly corresponds to $\alpha = 0.1$.
+
+% A mystery: what's so special about alpha = 0.1?
 

### 2021-12-01 makeFig.py

@@ -64,6 +64,16 @@ perICSh = 2*np.pi*np.sqrt((plVHiICSh['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).t
 prof_perIC_sh = 2*np.pi*np.sqrt((p_vhi_ic_sh['rbins']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 perSh = 2*np.pi*np.sqrt((plVHiSh['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 
+snap = pb.load('data/fullDiskLo.ic')
+plLoIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+p_lo_ic = pb.analysis.profile.Profile(plLoIC.d, bins=bins)
+snap = pb.load('data/fullDiskLo1.426000')
+plLo = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+p_lo = pb.analysis.profile.Profile(plLo.d, bins=bins)
+perICLo = 2*np.pi*np.sqrt((plLoIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+prof_perIC_lo = 2*np.pi*np.sqrt((p_lo_ic['rbins']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+perLo = 2*np.pi*np.sqrt((plLo['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+
 p_min, p_max = -5, 100
 e_min, e_max = 1e-3, 1
 
@@ -357,15 +367,17 @@ def plot_surfden_profiles():
 
 	fig, axes = plt.subplots(figsize=(16,8))
 
-	axes.scatter(per.value, plVHi['e'], s=0.005*plVHi['mass']/np.min(plVHi['mass']))
-	axes.scatter(perSt.value, plVHiSt['e'], s=0.005*plVHiSt['mass']/np.min(plVHiSt['mass']))
-	axes.scatter(perSh.value, plVHiSh['e'], s=0.005*plVHiSh['mass']/np.min(plVHiSh['mass']))
+	axes.scatter(per.value, plVHi['e'], s=0.005*plVHi['mass']/np.min(plVHi['mass']), label='fdHi')
[…]

### 2022-01-11 main.tex
Add discussion of figure 8

@@
 \begin{table}
+% I'm going to replace the fdLo simulation with a lower resolution version m_pl = 5e22 for consistency
+% Originally wanted to run everything at m_pl = 1e22, which corresponds to 100km bodies, but this wasn't feasible at higher Sigma
 \caption{Summary of Full Disk Simulations Run}
@@
 
+% Another important point: the accretion boundary doesn't move as we change surface density (how does t_relax and t_coll scale with sigma?). More evidence that it just depends on alpha(r)
+
 \begin{figure*}
@@
 
+Next, we compare the effect of varying the initial solid surface density profile on the resulting planetesimal and embryo distribution.
+The final orbital period-eccentricity state of the particles is shown in figure \ref{fig:surfden_profiles}, with point sizes indicating the relative masses of the bodies.
+There is a clear trend between solid surface density at a given orbital period and the eccentricities of the remaining planetesimals.
+This trend is largely set by the initial conditions, as the gravitational stirring is more vigorous when bodies are packed together closely and higher eccentricities are required to produce an equilibrating aerodynamic drag force (see equations \ref{eq:eq:vs_timescale} and \ref{eq:ts_stokes}).
+Despite having significantly different masses, the planetary embryos formed in each case have remarkably similar eccentricities.
+This is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which offsets the fact that the initial bodies started off in a dynamically hotter state.
+
 \section{Assembly History of Embryos}
@@
 How to reconcile our concerns with the results of \citet{wallace17}?
+Show inner disk test with different collision models.
+Bounce/merge model delays onset of runaway growth, with smaller planetesimals being delayed by longer.
+Does not affect eccentricity or mass of resulting embryos.
+Because $v_{esc}$ grows with mass, a more realistic collision model only delays the onset of runaway growth.
 

### 2022-01-12 main.tex
Add figure showing smooth accretion history, add discussion of figure 9

@@
 There is a clear trend between solid surface density at a given orbital period and the eccentricities of the remaining planetesimals.
-This trend is largely set by the initial conditions, as the gravitational stirring is more vigorous when bodies are packed together closely and higher eccentricities are required to produce an equilibrating aerodynamic drag force (see equations \ref{eq:eq:vs_timescale} and \ref{eq:ts_stokes}).
+This trend is largely set by the initial conditions, as the gravitational stirring is more vigorous when bodies are packed together closely and higher eccentricities are required to produce an equilibrating aerodynamic drag force (see equations \ref{eq:vs_timescale} and \ref{eq:ts_stokes}).
 Despite having significantly different masses, the planetary embryos formed in each case have remarkably similar eccentricities.
@@
 
+In figure \ref{fig:surfden_iso}, we compare the masses of the resulting protoplanets and planetesimals in all four simulations to each other.
+Here, the masses are scaled by the isolation mass at the given orbital distance (see equation \ref{eq:iso}).
+In all four cases, the masses follow a similar trend: interior to about 60 days in orbital period, protoplanets grow to a factor of a few larger than $M_{iso}$.
+Exterior to this point, the protoplanet masses roughly stay near the isolation mass.
+Despite the drastically different solid surface density profiles used, the masses of the largest bodies in all four cases follow a similar trend with orbital period.
+This indicates that the highly efficient accretion mode seen at shorter orbital periods is dependent on the sizes of the individual bodies themselves, rather than how they are distributed.
+The transition visible near 60 days in all cases also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
+% fdLo needs to run a bit longer
+
 \section{Assembly History of Embryos}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/smooth_frac.png}
+    \caption{Caption goes here.\label{fig:smooth_frac}}
+\end{center}
+\end{figure}
+
+Show planetesimal distribution for each embryo, will look at this in more detail in paper 2
+
+Show smooth vs chunky accretion plot for each embryo. Boundary visible at 60d
 

### 2022-01-12 makeFig.py

@@ -77,9 +77,15 @@ perLo = 2*np.pi*np.sqrt((plLo['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 p_min, p_max = -5, 100
 e_min, e_max = 1e-3, 1
 
+def prev_iorder(new_iord, num_original, del_iord):
+    indices = np.zeros(num_original, dtype=bool)
+    indices[del_iord] = True
+    prev_iord = np.where(indices == False)[0][new_iord]
+    return prev_iord
+
 # Input in sim units, output in days
-def p_orbit(sma, m_central):
-	return (2*np.pi*np.sqrt(sma**3/m_central)*simT).to(u.d).value
+def p_orbit(sma):
+	return (2*np.pi*np.sqrt(sma**3/mCentral)*simT).to(u.d).value
 
 def plot_timescales():
 	file_str = 'figures/timescales.' + fmt
@@ -420,6 +426,85 @@ def plot_surfden_iso():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
+# Extract information about the 'surviving' members from a collision table
+def coll_info(df):
+    mass_mask = df['m1'].values >= df['m2'].values
+    
+    del_x = df['x1x'].values
+    del_x[mass_mask] = df['x2x'].values[mass_mask]
+    
+    del_y = df['x1y'].values
+    del_y[mass_mask] = df['x2y'].values[mass_mask]
+    
+    del_z = df['x1z'].values
+    del_z[mass_mask] = df['x2z'].values[mass_mask]
+    
+    del_vx = df['v1x'].values
+    del_vx[mass_mask] = df['v2x'].values[mass_mask]
+    
+    del_vy = df['v1y'].values
+    del_vy[mass_mask] = df['v2y'].values[mass_mask]
+    
+    del_vz = df['v1z'].values
+    del_vz[mass_mask] = df['v2z'].values[mass_mask]
+    
+    del_a, del_e, del_inc, del_omega, del_Omega, del_M = ko.cart2kep(del_x, del_y, del_z, del_vx, del_vy, del_vz, 0.08, 1e-20)
+    
+    del_r = np.sqrt(del_x**2 + del_y**2, del_z**2)
+    
+    dvx = df['v1x'].values - df['v2x'].values
[…]

### 2022-01-19 main.tex
Add figures for section 6

@@
 
-\subsection{Planetesimal Size and Extent of Hill Sphere}
+\subsection{Planetesimal Size and Extent of Hill Sphere}\label{sec:sizeandhill}
 
@@
 
-\section{Assembly History of Embryos}
+\subsection{Assembly History of Embryos}\label{sec:assembly}
+
+Further insight into the difference between the short vs long period accretion modes can be gained by examining the merger history of the planetary embryos.
+Because all collisions are directly resolved by the N-body code, a direct lineage can be traced between each embryo and a set of initial planetesimals.
+
+We begin by investigating the `smoothness' of the accretion events that give rise to each embryo.
+Drawing from a common technique used for cosmological simulations (citation?), we divide growth events for a given body into `major' and `minor' mergers.
+Minor events are defined as any collision involving an initial planetesimal, while major events consist of any two larger bodies.
+In figure \ref{fig:minor_frac}, we show the total mass fraction gained by minor events as a function of mass for the 100 largest bodies at the end of fdHi.
+Blue dots represent bodies interior to the 60 day orbital period boundary, while red crosses indicate bodies exterior.
+For the outer bodies in the oligarchic growth region, we see a very weak trend between minor accretion mass fraction and total mass.
+Regardless of how much an embryo has grown, the initial mass planetesimals contribute about the same relative amount to its total mass.
+At shorter orbital periods, however, there is a somewhat stronger trend.
+The largest bodies in this region gain about an order of magnitude more of their mass fraction from major mergers, compared to the smallest bodies.
 
@@
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/smooth_frac.png}
-    \caption{Caption goes here.\label{fig:smooth_frac}}
+    \includegraphics[width=0.5\textwidth]{figures/minor_frac.png}
+    \caption{Caption goes here.\label{fig:minor_frac}}
 \end{center}
@@
 
-Show planetesimal distribution for each embryo, will look at this in more detail in paper 2
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
+    \caption{Caption goes here.\label{fig:acc_zones}}
+\end{center}
+\end{figure}
 
-Show smooth vs chunky accretion plot for each embryo. Boundary visible at 60d
+The difference in slope of the short vs longer period bodies in figure \ref{fig:minor_frac} indicates a difference in how the planetesimal-embryo populations interact in each region.
+In the long period oligarchic growth region, embryos continue to accrete planetesimals as they grow and the minor mass fraction stays mostly flat.
+At short period, collisions mostly occur between equal mass bodies as the embryos grow and the contribution from planetesimals becomes less significant over time.
+This suggests that embryo-embryo collisions are common at short period.
+As discussed in section \ref{sec:sizeandhill}, the importance of gravitational scattering is greatly reduced here.
+Without frequent gravitational interactions between the embryos and planetesimals, orbital repulsion \citep{kokubo98} and isolation of the embryos does not occur.
+As we showed in figure \ref{fig:surfden_iso}, the embryos formed in this region exceed the isolation mass.
+
+Further evidence for the lack of gravitational scattering events can be seen in figure \ref{fig:acc_zones}.
+Here, we have chosen the 20 most massive bodies from the fdHi simulation and arranged them in order of present orbital period.
+The vertical black line indicates the orbital period of each embryo.
+The associated histogram for each body denotes where the planetesimals used to construct that embryo originated in the disk.
+The peaks of the histograms have all been normalized to the same value, so that the distributions only show the relative widths and locations of the feeding zones.
+Beyond the 60 day boundary, the ordering of the feeding zones and the embryo locations become much less consistent.
+This suggests that scattering events between embryos are much more common beyond this accretion mode boundary.
+In the inner region of the disk, close encounters between embryos often result in a merger, which allows them to grow beyond the isolation mass while only a minor alteration to their orbital period.
+With few close encounters resulting in a scattering event, embryos are unable to move away from their birth location.
 
@@
 
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/f6f4.png}
+    \caption{Caption goes here.\label{fig:f6f4}}
+\end{center}
+\end{figure}
+
 % compare f=4 and f=6 disk. show that the mass transition moves inwards by the correct amount as alpha changes
@@
 \subsection{Collision Model}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/frag_ecc.png}
+    \caption{Caption goes here.\label{fig:frag_ecc}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/frag_evo.png}
+    \caption{Caption goes here.\label{fig:frag_evo}}
+\end{center}
+\end{figure}
 
@@
 
+\subsection{Type I Migration}
+
 \section{Summary and Discussion} \label{sec:discuss}

### 2022-01-19 makeFig.py

@@ -44,6 +44,22 @@ perIC = 2*np.pi*np.sqrt((plVHiIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.
 prof_perIC = 2*np.pi*np.sqrt((p_vhi_ic['rbins']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 per = 2*np.pi*np.sqrt((plVHi['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 
+m_pl = np.min(plVHi['mass'])
+# For some reason, the 'eps' field doesnt read correctly, so I can't
+# pull the planeteismal radius from the snapshots
+rho = 3 # Rocky bodies
+r_pl = ((3*(m_pl*u.M_sun).to(u.g).value/(4*np.pi*rho))**(1/3)*u.cm).to(u.AU).value
+
+snap = pb.load('data/fullDiskVHif4.ic')
+plVHif4IC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+p_vhif4_ic = pb.analysis.profile.Profile(plVHif4IC.d, bins=bins)
+snap = pb.load('data/fullDiskVHif41.152000')
+plVHif4 = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+p_vhif4 = pb.analysis.profile.Profile(plVHif4.d, bins=bins)
+perf4IC = 2*np.pi*np.sqrt((plVHif4IC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+prof_perf4IC = 2*np.pi*np.sqrt((p_vhif4_ic['rbins']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+perf4 = 2*np.pi*np.sqrt((plVHif4['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+
 snap = pb.load('data/fullDiskVHiSteep.ic')
 plVHiICSt = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi_ic_st = pb.analysis.profile.Profile(plVHiICSt.d, bins=bins)
@@ -457,51 +473,207 @@ def coll_info(df):
     dvz = df['v1z'].values - df['v2z'].values
     speed = np.sqrt(dvx**2 + dvy**2 + dvz**2)
[…]

### 2022-01-20 makeFig.py
Clean up figure 7

@@ -360,10 +360,9 @@ def plot_pl_frac_time():
 	for idx, f in enumerate(files_sub):
 		snap = pb.load('data/'+f)
 		plVHi = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
-		mask1 = plVHi['mass'] < 10*np.min(plVHi['mass'])
-		mask2 = plVHi['mass'] > 0
-		p_vhi_m1 = pb.analysis.profile.Profile(plVHi[mask1], bins=bins1)
-		p_vhi_m2 = pb.analysis.profile.Profile(plVHi[mask2], bins=bins1)
+		mask = plVHi['mass'] < 10*np.min(plVHi['mass'])
+		p_vhi_m1 = pb.analysis.profile.Profile(plVHi[mask], bins=bins1)
+		p_vhi_m2 = pb.analysis.profile.Profile(plVHiIC, bins=bins1)
 
 		time_arr[idx] = snap.properties['time'].in_units('yr')
 		prof_arr[:,idx] = (p_vhi_m1['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)/(p_vhi_m2['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)
@@ -683,11 +682,11 @@ def plot_frag_evo():
 #plot_alpha_beta_mass()
 #plot_fulldisk_e_m()
 #plot_alpha_pl_frac()
-#plot_pl_frac_time()
+plot_pl_frac_time()
 #plot_surfden_profiles()
 #plot_surfden_iso()
 #plot_smooth_acc()
 #plot_acc_zones()
 #plot_f6f4()
 #plot_frag_ecc()
-plot_frag_evo()
+#plot_frag_evo()

### 2022-01-25 main.tex
Add text discussing figure 12, include alpha curves for various compositions

@@
 
+% Period vs mass for each model?
+% Positive trend for trappist-1 planets, excluding a,b
+
 In figure \ref{fig:surfden_iso}, we compare the masses of the resulting protoplanets and planetesimals in all four simulations to each other.
@@
 
+In all cases shown so far, the boundary between the standard oligarchic growth and the highly-efficient short period accretion region lies around 60 days in orbital period.
+The mode of accretion is set entirely by the local value of $\alpha$, which scales with both distance from the star and the bulk density of the planetesimals (see equation \ref{eq:alpha}).
+The artificial inflation of the collision cross section of the particles in our simulations, which is meant to reduce the computational expense, has the side effect of reducing the bulk densities.
+Because $\alpha \sim \rho_{pl}^{-1/3}$, increasing the particle sizes by a factor of f=6 reduces the orbital period at which $\alpha$ has a given value by a factor of approximately 15.
+Therefore, one would expect the accretion boundary to lie near 5 days in orbital period for 3 g $cm^{-3}$ bodies.
+
+Although a simulation with f=1 is not computationally tractable, we can test whether the accretion boundary moves in the way we expect by modestly changing the value of $f$.
+In figure \ref{fig:f6f4}, we compare the fdHi simulation to a nearly identical run using f=4.
+In the top panel, the embryo masses in units of the isolation mass are shown as a function of orbital period.
+In the bottom panel, the value of $\alpha$ as a function of orbital period is shown for 3 g $cm^{-3}$ bodies with an artificial radius enhancement of f=1, 4 and 6.
+The horizontal dashed line indicates the value of alpha below which the accretion mode switches to oligarchic growth.
+Comparing the top and bottom panels, the intersection of the embryo masses and local isolation mass matches well with the orbital period at which $\alpha \sim 0.1$.
+Also shown by the curved dotted lines are the $\alpha$ curves for realistic-sized bodies with $\rho_{pl}$ = 1, 5 and 10 g $cm^{-3}$.
+In all cases, the accretion boundary still lies within the part of the disk in which solids would be expected to accumulate (citation?).
+
 \begin{figure}
@@
 % compare f=4 and f=6 disk. show that the mass transition moves inwards by the correct amount as alpha changes
+% how does density affect results? trappist-1 planets are 5 g/cc (agol+ 2021)
 
@@
 
+% Compare with ICs used in Ogihara 22
+
 \bibliography{references}

### 2022-01-25 makeFig.py

@@ -606,6 +606,21 @@ def plot_f6f4():
 	alpha = r_pl*f/(p_vhi_ic['a']*(m_pl/(3*mCentral))**(1/3))
 	axes.semilogy(prof_perIC, alpha)
 
+	rhoval = (1*u.g/u.cm**3).to(u.M_sun/u.AU**3).value
+	r_pl_varyrho = (3*m_pl/(4*np.pi*rhoval))**(1/3)
+	alpha = r_pl_varyrho/(p_vhi_ic['a']*(m_pl/(3*mCentral))**(1/3))
+	axes.semilogy(prof_perIC, alpha, ls=':')
+
+	rhoval = (5*u.g/u.cm**3).to(u.M_sun/u.AU**3).value
+	r_pl_varyrho = (3*m_pl/(4*np.pi*rhoval))**(1/3)
+	alpha = r_pl_varyrho/(p_vhi_ic['a']*(m_pl/(3*mCentral))**(1/3))
+	axes.semilogy(prof_perIC, alpha, ls=':')
+
+	rhoval = (10*u.g/u.cm**3).to(u.M_sun/u.AU**3).value
+	r_pl_varyrho = (3*m_pl/(4*np.pi*rhoval))**(1/3)
+	alpha = r_pl_varyrho/(p_vhi_ic['a']*(m_pl/(3*mCentral))**(1/3))
+	axes.semilogy(prof_perIC, alpha, ls=':')
+
 	axes.axhline(0.1, ls='--')
 	axes.set_xlabel('Orbital Period [d]')
 	axes.set_ylabel(r'$\alpha$')
@@ -674,6 +689,8 @@ def plot_frag_evo():
 	axes.set_ylabel(r'M / $\langle$ m $\rangle$')
 	axes.legend()
 
+	fig.tight_layout()
+
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 #plot_timescales()
@@ -682,11 +699,11 @@ def plot_frag_evo():
 #plot_alpha_beta_mass()
 #plot_fulldisk_e_m()
 #plot_alpha_pl_frac()
-plot_pl_frac_time()
+#plot_pl_frac_time()
 #plot_surfden_profiles()
 #plot_surfden_iso()
 #plot_smooth_acc()
 #plot_acc_zones()
-#plot_f6f4()
+plot_f6f4()
 #plot_frag_ecc()
 #plot_frag_evo()

### 2022-01-26 main.tex
Add text for collision model section

@@
 
+In the simulations presented in this work, all collisions result in a complete merging of a pair of bodies with no loss of mass or momentum.
+Although simple to model, this assumption of perfect accretion may result in overly efficient growth, particularly at the innermost region of the disk where encounter velocities are the largest.
+To handle this issue properly, semianalytic collision resolution models have been developed and implemented in N-body codes (see \citep{leinhardt12}).
+However, resolving collisional debris fragments using a direct approach as we have done with {\sc ChaNGa} would result in an intractably large number of particles.
+
+To test whether a more restrictive collision model should modify our results, we present a smaller scale test using a slightly more sophisticated collision model.
+In this case, a collision can result in one of two outcomes: if the impact velocity is smaller than the mutual escape velocity of the colliding particles, defined as
+
+\begin{equation}\label{eq:v_mut}
+	v_{mut, esc} = \sqrt(\frac{G (m_{1} + m_{2}}{r_{1} r_{2}}),
+\end{equation}
+
+\noindent where $m_{1}, m_{2}$ and $r_{1}, r_{2}$ are the masses and radii of colliding particles 1 and 2, then the bodies perfectly merge.
+For impact velocities larger than $v_{mut, esc}$, no mass is transferred and the bodies undergo a completely elastic bounce.
+Because there is no possibility of partial accretion, this model likely restricts growth more than the model used by \citet{leinhardt12}.
+However, we will show below that the bounce-merge model does not meaningfully affect the outcome of the planetesimal accretion phase, and so a partial accretion model should do the same.
+
+For the configuration of initial conditions we have chosen, the typical encounter velocity (defined by $v_{enc} = \left< e^{2} \right>^{1/2} v_{k}$, where $v_{k}$ is the local Keplerian velocity) is about 25 percent larger than $v_{mut, esc}$.
+Because the encounter velocities follow a Gaussian distribution, there should be some small subset of collisions that still meet the merger criteria.
+In addition, $v_{mut, esc}$ becomes larger as the bodies grow and the merger criteria should become easier to meet as the system evolves.
+
+In figure \ref{fig:frag_ecc}, we show the results of two versions of the fdLo simulation, one with mergers only (shown in orange) and one with the bounce-merge model (shown in green).
+The blue points in the top panel show the initial conditions used for both cases.
+Because the bounce-merge model greatly increases the number of timesteps required, we choose to model only the innermost part of the disk to reduce the computational cost.
+Although the bounce-merge simulation takes much longer to reach the same phase of evolution, the resulting orbits and masses of the embryos are indistinguishable from the merger-only case.
+
+To investigate the differences between the two collision models early in the simulations, we show the time evolution of the ratio between the maximum and mean mass in figure \ref{fig:frag_evo}.
+In both cases, this ratio grows at early times, which indicates that runaway growth still operates, regardless of the collision model used.
+In the bounce-merge case, the mass ratio peaks at a higher value, while also undergoing a longer runaway growth phase.
+This suggests that the mass distribution becomes much less unimodal during this growth process, but as figure \ref{fig:frag_ecc} shows, this does not affect the resulting embryos or allow for a residual planetesimal population.
+
+% Maybe also show a plot of M vs time. The embryos should form quicker with the perfect accretion model.
+
 % show alpha, beta study again with bounce vs merge model
@@
 % criteria should get less restrictive as larger bodies grow, what if we turn on bounces partway thru growth process?
-
-How to reconcile our concerns with the results of \citet{wallace17}?
-Show inner disk test with different collision models.
-Bounce/merge model delays onset of runaway growth, with smaller planetesimals being delayed by longer.
-Does not affect eccentricity or mass of resulting embryos.
-Because $v_{esc}$ grows with mass, a more realistic collision model only delays the onset of runaway growth.
 

### 2022-01-31 main.tex
Finish discussion + conclusion

@@
 
-% Maybe also show a plot of M vs time. The embryos should form quicker with the perfect accretion model.
-
 % show alpha, beta study again with bounce vs merge model
@@
 
+What is the migration timescale for the embryos to move to the inner edge of the disk? Maybe this section isn't terribly important and should be excluded?
+
 \section{Summary and Discussion} \label{sec:discuss}
 
-As was pointed out in \citet{clement20},  late stage initial conditions with a uniform distribution of embryos is not accurate.
-Evolution happens in the inner part of the disk first, so bodies will be more massive there.
+In this work, we have demonstrated that planetary embryo formation operates in two distinct modes in a planet-forming disk.
+In the first mode, gravitational feedback from the growing embryos heats the remaining planetesimals and results in a dynamically cold population of embryos with a significant amount of residual planetesimals.
+This corresponds to the `oligarchic growth' case revealed by \citep{kokubo98}.
+In the second mode, the gravitational feedback does not operate, embryos quickly sweep up all planetesimals, and grow about twice as large as is predicted by oligarchic growth.
+The distinction between these modes is determined by ratio between the physical size of the bodies and their Hill radius.
 
-Summary and discussion text goes here
+We have demonstrated the outcome of both accretion modes through a low resolution parameter study.
+The initial planetesimal distribution can be described in terms of two dimensionless constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) and gravitational ($r_{g}$) radii, respectively.
+For a fixed planetesimal mass and radius, $\alpha$ scales with the orbital period and $\beta$ scales with the level of dynamical excitation of the disk.
+We showed that $\alpha \ll 1$ leads to oligarchic growth, while a non-negligible $\alpha$ produces this new non-oligarchic growth mode.
+We find that the resulting mass distribution, along with the final eccentricities of the embryos and residual planetesimals, ends up the same, regardless of the initial value of $\beta$.
 
-% Compare with ICs used in Ogihara 22
+So long as the density of the bodies does not significantly change as their mass distribution evolves, this ratio, and therefore the boundary between these accretion modes is set entirely by the distance from the star.
+Because both the physical and Hill radius of the bodies grows as $M^{1/3}$, the boundary between growth remains at a fixed location in the disk during the planetesimal accretion process.
+
+We have verified this fact by testing the outcome of the planetesimal accretion process for a variety of solid surface density profiles.
+Although altering the surface density does affect the resulting masses of the embryos, the location of the boundary separating the growth modes is remarkably similar between all of our simulations.
+We have verified this by comparing the resulting embryo masses to the isolation mass, in addition to highlighting qualitative differences in the accretion history of embryos on both sides of the boundary.
+
+Lastly, we quantified the way in which our use of perfect accretion and an inflated collision cross section, both meant to make the simulations more computationally tractable, affect the non-oligarchic growth mode and the location of the accretion boundary.
+We showed that although the use of perfect accretion speeds up the growth of the embryos, it does not affect the masses or orbital properties of the resulting bodies.
+Because the inflated collision cross sections artificially reduce the density of the planetesimals, this shortcut does shift the accretion boundary outward.
+However, it moves in a predictable fashion and we verified this by running an extra simulation with a modestly smaller collision cross section.
+In a real planet-forming disk, one would expect this boundary to lie somewhere between 2 and 10 days, depending on the composition of the planetesimals.
+
+Presently, the implications that this non-oligarchic accretion mode has for the formation of short-period terrestrial planets, and whether the accretion boundary would leave any lasting imprint on the final orbital architecture, is unclear.
+One point that our results do highlight is that the initial conditions used for most late stage planet formation simulations are overly simplistic.
+\citet{clement20} recently simulated planetesimal accretion in a disk extending from the orbit of Mercury to the asteroid belt and found that the disk never reaches a state in which equally-spaced, isolation mass embryos are present everywhere simultaneously.
+Instead, different annuli reach a `giant impact' phase at different times, preventing the onset of a global instability throughout the entire disk, as is common in classic terrestrial planet formation models \citep{chambers01, raymond09}.
+
+% Any examples of studies of STIPs that use these simplistic ICs? Could the accretion boundary help reconcile differences with kepler systems?
+
+To connect these accretion modes to the final orbital architecture, and to ultimate determine what implications an in situ formation model has for the growth of STIPs, we will continue to evolve the final simulation snaphots presented here with a hybrid symplectic integrator.
+The final distribution of planets formed, along with composition predictions generated by applying cosmochemical models to our initial planetesimal distributions and propagating compositions through the merger trees, will be examined in a follow-up paper.
 

### 2022-02-02 main.tex
Fill out figure captions, make some figures smaller, remove alpha_pl_frac figure

@@
 
-In figure \ref{fig:alpha_pl_frac}, we show $\alpha$ (left axis) and the fraction of remaining planetesimals (right axis) as a function of orbital period.
+In figure (removed), we show $\alpha$ (left axis) and the fraction of remaining planetesimals (right axis) as a function of orbital period.
 Here, the fraction of remaining planetesimals is measured by dividing the disk into 15 semimajor axis bins and using the profile function in {\sc pynbody} to measure the total solid surface density $\Sigma$ in each of those bins, and also the planetesimal surface density $\sigma$.
@@
 As can be seen from the plot, the accretion boundary roughly corresponds to $\alpha = 0.1$.
+% This figure could be turned into a few sentences in the text.
 
@@
 In the case of large $\alpha$, almost no residual planetesimal population remains.
-Regardless of the choice of $\beta$, the protoplanets that form attain similar eccentricities.
+Regardless of the initial choice of $\beta$, the protoplanets that form attain similar eccentricities.
 \label{fig:alpha_beta}}
@@
     \includegraphics[width=0.5\textwidth]{figures/alpha_beta_mass.png}
-    \caption{Caption goes here.\label{fig:alpha_beta_mass}}
+    \caption{The final state of the mass distribution for the simulations described in section \ref{sec:narrow}.
+For small $\alpha$, a few embryos form alongside a power law tail of planetesimals.
+For larger values of $\alpha$, the mass distribution takes on a more unimodal form.
+As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.\label{fig:alpha_beta_mass}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
-    \caption{Caption goes here.\label{fig:alpha_beta_evo}}
+    \caption{The evolution of the ratio between the maximum and mean mass for the four simulations presented in section \ref{sec:narrow}.
+The runaway growth phase can be identified by a positive slope in this ratio.
+For all values of $\alpha$, an increase in $\beta$ has the effect of delaying the growth of the embryos.\label{fig:alpha_beta_evo}}
 \end{center}
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-    \includegraphics[width=\textwidth]{figures/fulldisk_e_m.png}
-    \caption{Caption goes here.\label{fig:fulldisk_e_m}}
+    \includegraphics[width=0.5\textwidth]{figures/fulldisk_e_m.png}
+    \caption{The final state of the fdHi simulation.
+In the top panel, the contours denote the initial period-eccentricity distribution of the planetesimals.
+Point sizes indicate the relative masses of bodies.
+In the bottom panel, the solid line indicates the isolation mass for $b = 2 \sqrt{3}$.
+The vertical dashed line marks the approximate location of the accretion mode boundary.
+For $P_{orb} < 60$ days, the high $\alpha$ accretion mode produces embryos that exceed the isolation mass.\label{fig:fulldisk_e_m}}
 \end{center}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-    \includegraphics[width=\textwidth]{figures/alpha_pl_frac.png}
-    \caption{Caption goes here.\label{fig:alpha_pl_frac}}
+    \includegraphics[width=0.5\textwidth]{figures/pl_frac_time.png}
+    \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi simulation.
+Each curve represents a radial slice of the disk.
+The innermost region evolves the quickest, and is therefore represented by the lowest curve.
+The dashed lines indicate radial zones interior to the 60 day orbital period boundary.\label{fig:pl_frac_time}}
 \end{center}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-    \includegraphics[width=\textwidth]{figures/pl_frac_time.png}
-    \caption{Caption goes here.\label{fig:pl_frac_time}}
+    \includegraphics[width=0.5\textwidth]{figures/surfden_profiles.png}
+    \caption{The final state of all simulations listed in table \ref{tab:sim_properties}. Point sizes indicate the relative masses.\label{fig:surfden_profiles}}
 \end{center}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-    \includegraphics[width=\textwidth]{figures/surfden_profiles.png}
-    \caption{Caption goes here.\label{fig:surfden_profiles}}
+    \includegraphics[width=0.5\textwidth]{figures/surfden_iso.png}
+    \caption{Masses of the remaining bodies from the simulations listed in table \ref{tab:sim_properties}, in units of the isolation mass for $b = 2 \sqrt{3}$.
+Despite the vastly different initial solid surface density profiles, the orbital period inside of which the embryo masses exceed the isolation mass is very consistent.\label{fig:surfden_iso}}
 \end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-    \includegraphics[width=\textwidth]{figures/surfden_iso.png}
-    \caption{Caption goes here.\label{fig:surfden_iso}}
-\end{center}
-\end{figure*}
+\end{figure}
 
@@
     \includegraphics[width=0.5\textwidth]{figures/minor_frac.png}
-    \caption{Caption goes here.\label{fig:minor_frac}}
+    \caption{For the 100 most massive bodies at the end of the fdHi simulation, the fraction of their total mass attained through mergers with initial mass planetesimals (smooth accretion) as a function of total mass.
+Bodies that reside beyond the 60 day accretion boundary are shown with red crosses, while bodies interior to the boundary are shown with blue dots.
+For the short period bodies, there is a decreasing correlation between smooth accretion fraction and mass, which suggests that most growth occurs between equal mass bodies.
+For the longer period bodies in the oligarchic growth region, this trend is flat, indicating that accretion of planetesimals is important during all phases of evolution.\label{fig:minor_frac}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
-    \caption{Caption goes here.\label{fig:acc_zones}}
+    \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown.
+The black hash marks indicate the present position of the body.
+The accretion distributions indicate the initial locations of the planetesimals that were used to assemble a body, rather than the locations at which collisions with the massive body occurred.\label{fig:acc_zones}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/f6f4.png}
-    \caption{Caption goes here.\label{fig:f6f4}}
+    \caption{In the top panel, we show the final masses of the bodies from the fdHi and fdHif4 simulations in units of the isolation mass for $b = 2\sqrt{3}$.
+The bottom panel shows the variation of $\alpha$ with orbital period for the bodies used in each case (solid curves).
+The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of the embryo mass distribution and isolation mass.
+The dotted curves in the bottom panel show the values of alpha for realistic-sized planetesimals with $\rho =$ 1, 3, 5 and 10 g cm$^{-3}$.
+(need to fix the green curve)\label{fig:f6f4}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/frag_ecc.png}
-    \caption{Caption goes here.\label{fig:frag_ecc}}
+    \caption{A comparison between the innermost regions of the fdLo (orange) simulation, and a second version using a bounce-merge collision model (green).
+In the top panel, the period-eccentricity state of the particles is shown, with marker sizes indicating relative mass.
+The blue points represent the initial state of the simulations.
+The bottom panel compares the final masses of the bodies.
+\label{fig:frag_ecc}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/frag_evo.png}
-    \caption{Caption goes here.\label{fig:frag_evo}}
+    \caption{The evolution of the ratio between the maximum and mean mass of the simulations shown in figure \ref{fig:frag_ecc}.
+In both cases, the system first evolves through a phase of runaway growth, before the massive bodies consume the smaller bodies, driving down the mean mass.
+With the bounce-merge model, the mass ratio decreases later because not all collisions result in growth.\label{fig:frag_evo}}
 \end{center}

### 2022-02-02 makeFig.py

@@ -214,6 +214,8 @@ def plot_alpha_beta_evo():
 	axes.set_ylabel(r'M / $\langle$ m $\rangle$')
 	axes.legend()
 
+	plt.tight_layout()
+
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 def plot_alpha_beta_mass():
@@ -265,7 +267,7 @@ def plot_fulldisk_e_m():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	fig, ax = plt.subplots(figsize=(16,16), nrows=2, sharex=True)
+	fig, ax = plt.subplots(figsize=(8,8), nrows=2, sharex=True)
 
 	axes = ax[0]
 	xbins = np.linspace(p_min, p_max, num=num_bins)
@@ -284,7 +286,7 @@ def plot_fulldisk_e_m():
 
 	surf_den = (p_vhi_ic['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)
 	a_vals = (p_vhi_ic['rbins']*u.AU).to(u.cm).value
-	btilde = 5
+	btilde = 2*np.sqrt(3)
 	m_iso_vhi = np.sqrt((2*np.pi*a_vals**2*btilde*surf_den)**3/(3*mCentralg))
 	btilde = 10
 	m_iso_vhi1 = np.sqrt((2*np.pi*a_vals**2*btilde*surf_den)**3/(3*mCentralg))
@@ -293,7 +295,7 @@ def plot_fulldisk_e_m():
 	axes.scatter(per.value, (plVHi['mass']*u.M_sun).to(u.g).value)
 	axes.set_yscale('log')
 	axes.plot(prof_perIC, m_iso_vhi)
-	axes.plot(prof_perIC, m_iso_vhi1)
+	#axes.plot(prof_perIC, m_iso_vhi1)
 	axes.set_xlim(p_min, p_max)
 	axes.set_ylim(1e25, 1e28)
 	axes.set_ylabel('Mass [g]')
@@ -367,7 +369,7 @@ def plot_pl_frac_time():
 		time_arr[idx] = snap.properties['time'].in_units('yr')
 		prof_arr[:,idx] = (p_vhi_m1['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)/(p_vhi_m2['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)
 
-	fig, axes = plt.subplots(figsize=(16,8))
[…]

### 2022-02-22 main.tex
Add short discussion of coulomb logarithm

@@
 Beyond kilometer scales, gravity begins to dominate and aerodynamic gas drag plays a smaller and smaller role.
-During this phase, collision cross sections are enhanced as gravitational focusing (safronov citation) acts to bend the trajectories of bodies undergoing close encounters.
-Large bodies are most effective at focusing the trajectories of nearby planetesimals, leading to a period of runaway growth (citations to wetherill, kokubo+ida, barnes).
-Eventually, the largest bodies (known as oligarchs) dynamically heat the surrounding planetesimals, severely limiting further growth (cite kokubo+ida).
+During this phase, collision cross sections are enhanced as gravitational focusing \citep{safronov69} acts to bend the trajectories of bodies undergoing close encounters.
+Large bodies are most effective at focusing the trajectories of nearby planetesimals, leading to a period of runaway growth \citep{wetherill89, kokubo96, barnes09}.
+Eventually, the largest bodies (known as oligarchs) dynamically heat the surrounding planetesimals, severely limiting further growth \citep{kokubo98}.
 The end result of this phase is a bimodal population of dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals.
@@
 Simulations show that evaporation of the gas disk is required to allow instability to trigger a phase of giant impacts (Mention that disk fraction decay timescale roughly matches timing of giant impacts in SS).
-It is during this phase that oligarchs collide to form Earth-sized planets (chambers wetherill 1998, raymond 2006).
+It is during this phase that oligarchs collide to form Earth-sized planets \citep{chambers98, raymond06}.
 
@@
 Given the difficult question of whether to treat the solar system as an outlier, the best way forward is to use statistical samples of exoplanetary architectures to develop and inform formation models.
-This is generally done through the use of population synthesis models (ida + lin, alibert), but many of the mechanisms in these models are informed and tuned by solar system constraints.
+This is generally done through the use of population synthesis models \citep{ida04, alibert11}, but many of the mechanisms in these models are informed and tuned by solar system constraints.
 One pervasive and exotic result revealed by the Kepler space telescope has the discovery of hundreds of compact multi-planet terrestrial systems, dubbed systems of tightly-packed inner planets (STIPs).
@@
 
-\noindent where $ln \Lambda$ is the Coulomb logarithm.
+\noindent where $\mathrm{ln} \Lambda$ is the Coulomb logarithm, typically taken to be $\approx 10$ for a planetesimal disk.
+Despite the fact that the behavior of gravitational stirring is well-described by two-body formalism, \citep{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters.
+As we will show in section \ref{sec:narrow}, gravitational stirring effectively shuts off when the Hill sphere of a body becomes comparable to its physical size.
+In this case, close encounters tend to result in collisions, and the main pathway for energy exchange between planetesimals is unable to operate.
+
  As mentioned above, the system will tend toward a state of energy equipartition for a non-uniform mass distribution.

### 2022-02-22 main.tex
Discussion of circumplanetary accretion in conclusion

@@
 
+To date, there have been no other studies of planetesimal accretion with such a large value of $\alpha$.
+However, a value of $\alpha = 1$ corresponds to the Roche limit of a three-body system, and so one might wonder this high-$\alpha$ accretion mode might be relevant for a circumplanetary system.
+There is a small collection of previous works which use N-body methods to examine in-situ satellitesimal accretion \citep{ida97, richardson00, ida20}.
+\citet{ida97} was able to form 1-2 large moon just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over.
+The widest disk they modeled extended out to $\alpha = 0.5$.
+Qualitatively, this result is very similar to the short period planetesimal accretion mode observed in our simulations.
+\citet{ida20} modeled a much wider satellitesimal disk, which extends out to about $\alpha \approx 0.05$.
+Inside to the $\alpha = 0.1$ accretion boundary (which lies near $15 R_{U}$ in figure 1 of \citet{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary.
+In addition, a residual population of satellitesimals is still present beyond the boundary, which suggests that oligarchic growth is indeed operating on the far side.
+
 Presently, the implications that this non-oligarchic accretion mode has for the formation of short-period terrestrial planets, and whether the accretion boundary would leave any lasting imprint on the final orbital architecture, is unclear.

### 2022-02-24 main.tex
Edits through eq. 2.

@@
 \begin{abstract}
-Formation models in which terrestrial bodies grow via the pairwise accretion of planetesimals have been reasonably successful at reproducing the general properties of the solar system, including small body populations.
-However, planetesimal accretion has not yet been fully explored in the context of more exotic terrestrial systems, particularly those that host short-period planets.
-In this work, we use direct N-body simulations to explore and understand the growth of planetary embryos from planetesimals in disks extending down to $\simeq$ 1 day orbital periods.
-We show that planetesimal accretion becomes nearly 100 percent efficient at short orbital periods, leading to embryo masses that are roughly twice as large as the classical isolation mass.
-For rocky bodies, the physical size of the object begins to occupy a significant fraction of its Hill sphere at orbital periods less than about 50 days.
-In this regime, most close encounters result in collisions, rather than scattering, and the system cannot bifurcate into a collection of dynamically hot planetesimals and dynamically cold oligarchs, like is seen in previous work.
-The highly efficient accretion seen at short orbital periods implies that systems of tightly-packed inner planets should be almost completely devoid of any residual small bodies.
-We demonstrate the robustness of our results to assumptions about the initial disk model, and also investigate how far material can radially mix across the accretion boundary.
+Formation models in which terrestrial bodies grow via the pairwise
+accretion of planetesimals have been reasonably successful at
+reproducing the general properties of the solar system, including
+small body populations. However, planetesimal accretion has not yet
+been fully explored in the context of more exotic terrestrial systems,
+particularly those that host short-period planets. In this work, we
+use direct N-body simulations to explore and understand the growth of
+planetary embryos from planetesimals in disks extending down to
+$\simeq$ 1 day orbital periods. We show that planetesimal accretion
+becomes nearly 100 percent efficient at short orbital periods, leading
+to embryo masses that are roughly twice as large as the classical
+isolation mass. For rocky bodies, the physical size of the object
+begins to occupy a significant fraction of its Hill sphere at orbital
+periods less than about 50 days. In this regime, most close encounters
+result in collisions, rather than scattering, and the system cannot
+bifurcate into a collection of dynamically hot planetesimals and
+dynamically cold oligarchs, like is seen in previous work. The highly
+efficient accretion seen at short orbital periods implies that systems
+of tightly-packed inner planets should be almost completely devoid of
+any residual small bodies. We demonstrate the robustness of our
+results to assumptions about the initial disk model, and also
+investigate how far material can radially mix across the boundary
+between modes.
 \end{abstract}
@@
 
+% TRQ: the following paragraph (particularly the last sentence could
+% use citations: probably to review articles.
 Planetesimal accretion is one of a number of stages in which micron-sized solids from the protostellar nebula coalesce to eventually build terrestrial planets.
@@
 
-Given the difficult question of whether to treat the solar system as an outlier, the best way forward is to use statistical samples of exoplanetary architectures to develop and inform formation models.
-This is generally done through the use of population synthesis models \citep{ida04, alibert11}, but many of the mechanisms in these models are informed and tuned by solar system constraints.
-One pervasive and exotic result revealed by the Kepler space telescope has the discovery of hundreds of compact multi-planet terrestrial systems, dubbed systems of tightly-packed inner planets (STIPs).
+Given the difficult question of whether to treat the solar system as
+an outlier, the best way forward is to use statistical samples of
+exoplanetary architectures to develop and inform formation
+models. This is generally done through the use of population synthesis
+models \citep{ida04, alibert11}, but many of the mechanisms in these
+models are informed and tuned by solar system constraints. One
+pervasive and exotic result revealed by the Kepler space telescope is the discovery of hundreds of compact multi-planet terrestrial systems, dubbed systems of tightly-packed inner planets (STIPs).
 Although there is no formal definition of a STIP, they typically contain 3 or more Earth-sized planets with orbital periods extending between 1 and 100 days.
@@
 
-To date, a large body of work exists that has attempted to reproduce the architectures of STIPs, starting from planetary embryos (cite some examples).
-However, the runaway and oligarchic growth phases, which precede the assembly of the embryos, are assumed to be ubiquitous.
-Given that the timescales for accretion and gravitational scattering scale differently with encounter velocity, which itself scales with orbital period, it is not entirely clear that planetary embryos should form in the same way close to the star as they do at much longer, more thoroughly studied orbital periods.
-In this paper, we use direct N-body simulations to explore the outcome of the planetesimal accretion stage at orbital periods shorter than 100 days.
+To date, a large body of work exists that has attempted to reproduce
+the architectures of STIPs, starting from planetary embryos (cite some
+examples). However, the runaway and oligarchic growth phases, which
+precede the assembly of the embryos, are assumed to be
+ubiquitous. Given that the timescales for accretion and gravitational
+scattering scale differently with encounter velocity, which itself
+scales with orbital period, it is not entirely clear that planetary
+embryos should form in the same way close to the star as they do at
+much longer, more thoroughly studied orbital periods. In this paper,
+we use direct N-body simulations to explore the outcome of the
+planetesimal accretion stage at orbital periods shorter than 100 days
+around an M star.
+% TRQ perhaps mention habitable zone here.  Somewhere, a discussion of
+% the importance of understanding habitable zones around M-stars,
+% where STIPS are found, needs to be discussed.
 In particular, we seek to understand what the orbital and mass distributions of the embryos and residual planetesimals look like, and to assess whether the initial conditions used by late-stage simulations of STIP assembly are reasonable.
 
-In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and show that assumptions used to derive the well-known modes of growth are only valid at sufficiently long orbital periods.
-We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}.
-In section \ref{sec:results}, we present parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods.
-We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
+In section \ref{sec:theory} we provide an overview of the theory
+behind planetesimal accretion and show that assumptions used to derive
+the well-known modes of growth are only valid at sufficiently long
+orbital periods. We then motivate the need for N-body simulations to
+study this problem and describe the code used, along with how our
+initial conditions were constructed in section \ref{sec:methods}. In
+section \ref{sec:narrow}, we present a parameter study of planetesimal
+accretion using a series of simulations of narrow annuli at various
+orbital periods.
+In section \ref{sec:fulldisk}, we present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
 Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}.
@@
 
-We begin our analysis by considering a disk of equal planetesimals with radius $r_{pl}$, mass $m_{pl}$ and surface density $\Sigma_{pl}$.
-The collision rate in the vicinity of an orbit defined by Keplerian frequency $\Omega$ can be written as $n \Gamma v$, where $n = \Sigma_{pl} \Omega / 2 m_{pl} v$, $\Gamma$ is the effective collision cross section and $v$ is the typical encounter velocity between planetesimals.
+We begin our analysis by considering a disk of equal planetesimals
+with radius $r_{pl}$, mass $m_{pl}$ and surface density
+$\Sigma_{pl}$. The collision rate in the vicinity of an orbit defined
+by Keplerian frequency $\Omega$ can be written as $n \Gamma v$, where
+$n = \Sigma_{pl} \Omega / 2 m_{pl} v$, $\Gamma$ is the effective
+collision cross section and $v$ is the typical encounter velocity
+between planetesimals.
+% TRQ: mention that $v$ is related to the velocity dispersion of the
+% planetesimals.
 Assuming that every collision results in a perfect merger, the growth rate of a planetesimal is given by
@@
 
-In the case where the collision cross section $\Gamma$ depends only on the physical size of the planetesimals, the growth scales linearly with mass and the mass distribution is expected to evolve in an `orderly' fashion.
+In the case where the collision cross section, $\Gamma$, depends only
+on the physical size of the planetesimals, the growth scales linearly
+with mass and the mass distribution is expected to evolve in an
+``orderly'' fashion.
 However, bodies larger than $\sim 100$ km in size are expected to exert a significant gravitational force on each other during encounters and the collision cross section depends on both the size of the bodies and their encounter velocities.
 In this case, $\Gamma = \Gamma_{geo} \left( 1 + v_{esc}^2 / v^2 \right)$, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
+%TRQ: reference Safranov?
 
-In the limit that $v_{esc} \gg v$, it can be shown that $M \propto M^{4/3}$, which implies a runaway scenario, in which growth accelerates with mass.
-This mode of growth was confirmed with N-body simulations by \citet{kokubo96} and appears necessary to construct protoplanets within the lifetime of a protoplanetary disk.
-Due to the velocity dependence of the gravitational focusing effect, it isn't clear how ubiquitous this mode of growth is.
+In the limit that $v_{esc} \gg v$, it can be shown that $M \propto
+M^{4/3}$, which implies a runaway scenario, in which growth
+accelerates with mass. This mode of growth was confirmed with N-body
+simulations by \citet{kokubo96} and appears necessary to construct
+protoplanets within the lifetime of a protoplanetary disk. Due to the
+velocity dependence of the gravitational focusing effect, it is not clear how ubiquitous this mode of growth is.
 In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied.
 The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:results}.
+%TRQ: fix section reference.
 
-An important feature is missing from the model described above, which limits its applicability at late times.
-Encounters between planetesimals that do not result in a collision play a crucial role over long timescales.
-These close encounters act to convert energy from Keplerian shear into random motion.
-Over time, this gravitational stirring effect will raise the typical encounter velocities between bodies and diminish the effectiveness of gravitational focusing.
-With a spectrum of masses, these velocity differences become even more pronounced because as system drifts towards a state of quasi-equilibrium where $v \sim m^{1/2}$.
+An important feature is missing from the model described above, which
+limits its applicability at late times. Encounters between
+planetesimals that do not result in a collision play a crucial role
+over long timescales. These close encounters act to convert energy
+from Keplerian shear into random motion. Over time, this gravitational
+stirring effect will raise the typical encounter velocities between
+bodies and diminish the effectiveness of gravitational focusing. With
+a spectrum of masses, these velocity differences become even more
+pronounced because as system evolves towards a state of quasi-equilibrium where $v \sim m^{1/2}$.
 For a system of equal mass bodies in which encounters are driven by random motions rather than Keplerian shear (dispersion dominated), the timescale for gravitational stirring is described by the two-body relaxation time \citep{ida93}
@@
 \begin{equation}\label{eq:relax}
-	t_{relax} = \frac{v^3}{n \pi G^2 m_{pl} ln \Lambda},
+	t_{relax} = \frac{v^3}{n \pi G^2 m_{pl} \ln \Lambda},
 \end{equation}
 
-\noindent where $\mathrm{ln} \Lambda$ is the Coulomb logarithm, typically taken to be $\approx 10$ for a planetesimal disk.
-Despite the fact that the behavior of gravitational stirring is well-described by two-body formalism, \citep{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters.
+\noindent where $\mathrm{ln} \Lambda$ is the Coulomb logarithm,
+typically taken to be $\approx 10$ for a planetesimal disk. Despite
+the fact that the behavior of gravitational stirring is well-described
+by the two-body formalism, \citep{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters.
 As we will show in section \ref{sec:narrow}, gravitational stirring effectively shuts off when the Hill sphere of a body becomes comparable to its physical size.
@@
 
- As mentioned above, the system will tend toward a state of energy equipartition for a non-uniform mass distribution.
-\citet{kokubo98} showed that runaway growth is actually self-limiting.
-As the runaway bodies grow larger, they become more effective at heating the remaining planetesimals, which diminishes the effectiveness of gravitational focusing and throttles the growth rate.
-Around the time that the massive runaway bodies make up about 50 percent of the solid surface density (citation), a period of less vigorous `oligarchic' growth commences, in which the few largest bodies continue to accrete planetesimals at similar rates.
+As mentioned above, the system will tend toward a state of energy
+equipartition for a non-uniform mass distribution. \citet{kokubo98}
+showed that runaway growth is actually self-limiting. As the runaway
+bodies grow larger, they become more effective at heating the
+remaining planetesimals, which diminishes the effectiveness of
+gravitational focusing and throttles the growth rate. Around the time
+that the massive runaway bodies make up about 50 percent of the solid
+surface density (citation), a period of less vigorous ``oligarchic'' growth commences, in which the few largest bodies continue to accrete planetesimals at similar rates.
 
@@
 
+%TRQ: I corrected this off the top of my head: CHECK!
 \begin{equation}\label{eq:v_mut}
-	v_{mut, esc} = \sqrt(\frac{G (m_{1} + m_{2}}{r_{1} r_{2}}),
+	v_{mut, esc} = \sqrt{\frac{G (m_{1} + m_{2})}{r_{1} + r_{2}}},
 \end{equation}

### 2022-05-24 makeFig.py
Start making figures look nicer

@@ -27,6 +27,7 @@ simV = u.AU/simT
 clobber = True
 fmt = 'png'
 s = 0.005
+lw = 4
 
 num_bins = 50
 mCentral = 0.08
@@ -80,10 +81,10 @@ perICSh = 2*np.pi*np.sqrt((plVHiICSh['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).t
 prof_perIC_sh = 2*np.pi*np.sqrt((p_vhi_ic_sh['rbins']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 perSh = 2*np.pi*np.sqrt((plVHiSh['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 
-snap = pb.load('data/fullDiskLo.ic')
+snap = pb.load('data/fullDiskLoLarge.ic')
 plLoIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_lo_ic = pb.analysis.profile.Profile(plLoIC.d, bins=bins)
-snap = pb.load('data/fullDiskLo1.426000')
+snap = pb.load('data/fullDiskLoLarge.1000000')
 plLo = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_lo = pb.analysis.profile.Profile(plLo.d, bins=bins)
 perICLo = 2*np.pi*np.sqrt((plLoIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
@@ -143,12 +144,12 @@ def plot_timescales():
 
 		return t_relax_vals/t_coll_vals
 
-	fig, axes = plt.subplots(figsize=(8,8))
+	fig, axes = plt.subplots(figsize=(8,6))
 	ehvals = [16, 8, 4, 2, 1]
 	colors = plt.cm.viridis(np.linspace(0, 1, len(ehvals)))
 	for idx, eh in enumerate(ehvals):
-		axes.plot(p_bins.to(u.d), timescale_ratio(eh), c=colors[idx], label=r'e$_{h}$ = '+str(eh))
-	axes.axhline(1, ls='--')
+		axes.plot(p_bins.to(u.d), timescale_ratio(eh), c=colors[idx], label=r'e$_{h}$ = '+str(eh), lw=lw)
+	axes.axhline(1, ls='--', color='gray')
 	axes.legend()
 	axes.set_xscale('log')
[…]

### 2022-05-25 makeFig.py
Finish editing figures

@@ -287,7 +287,9 @@ def plot_fulldisk_e_m():
 	fig, ax = plt.subplots(figsize=(8,8), nrows=2, sharex=True)
 
 	axes = ax[0]
-	xbins = np.linspace(p_min, p_max, num=num_bins)
+	# Not sure why I have to set the bin minimum this way, but it prevents a weird
+	# artifact from appearing on the left side of the contours
+	xbins = np.linspace(-1, p_max, num=num_bins)
 	ybins = np.logspace(np.log10(e_min), np.log10(e_max), num=num_bins)
 	H, xedges, yedges = np.histogram2d(perIC.value, plVHiIC['e'], bins=(xbins, ybins))
 	binsX = 0.5*(xedges[1:] + xedges[:-1])
@@ -295,7 +297,7 @@ def plot_fulldisk_e_m():
 	l = np.logspace(np.log10(30), np.log10(np.max(H)), 10)
 	c = axes.contour(binsX, binsY, np.flipud(np.rot90(H)), colors='black', linewidths=0.2, levels=l)
 
-	axes.scatter(per.value, plVHi['e'], s=0.005*plVHi['mass']/np.min(plVHi['mass']))
+	axes.scatter(per.value, plVHi['e'], s=plVHi['mass']/np.max(plVHi['mass'])*500)
 	axes.set_ylabel('Eccentricity')
 	axes.set_xlim(p_min, p_max)
 	axes.set_ylim(e_min, e_max)
@@ -309,9 +311,9 @@ def plot_fulldisk_e_m():
 	m_iso_vhi1 = np.sqrt((2*np.pi*a_vals**2*btilde*surf_den)**3/(3*mCentralg))
 
 	axes = ax[1]
-	axes.scatter(per.value, (plVHi['mass']*u.M_sun).to(u.g).value)
+	axes.scatter(per.value, (plVHi['mass']*u.M_sun).to(u.g).value, s=plVHi['mass']/np.max(plVHi['mass'])*500)
 	axes.set_yscale('log')
-	axes.plot(prof_perIC, m_iso_vhi)
+	axes.plot(prof_perIC, m_iso_vhi, lw=lw)
 	#axes.plot(prof_perIC, m_iso_vhi1)
 	axes.set_xlim(p_min, p_max)
 	axes.set_ylim(1e25, 1e28)
[…]

### 2022-05-25 main.tex
Start making figures look nicer
Finish editing figures
Fix broken references, update figure captions

--- 2022-02-22 main.tex
@@
 We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}.
-In section \ref{sec:results}, we present parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods.
+In section \ref{sec:narrow}, we present a parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods.
 We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
@@
 In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied.
-The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:results}.
+The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:narrow}.
 
@@
     \includegraphics[width=0.5\textwidth]{figures/timescales.png}
-    \caption{The ratio between the two-body relaxation and collision timescale for a population of equal-mass planetesimals.
+    \caption{The ratio between the two-body relaxation and collision timescale for a population of equal-mass planetesimals with an internal density of 3 g cm$^{-3}$.
 Only in regions where $t_{relax} \ll t_{coll}$ can the velocity distribution respond to changes in the mass of the bodies such that oligarchic growth can operate.
@@
     \includegraphics[width=0.5\textwidth]{figures/surfden_profiles.png}
-    \caption{The final state of all simulations listed in table \ref{tab:sim_properties}. Point sizes indicate the relative masses.\label{fig:surfden_profiles}}
+    \caption{The final state of all simulations listed in table \ref{tab:sim_properties}. Point sizes indicate mass relative to the largest body in the fdHi simulation.\label{fig:surfden_profiles}}
 \end{center}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
+    \includegraphics[width=\textwidth]{figures/acc_zones.png}
     \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown.
@@
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of the embryo mass distribution and isolation mass.
-The dotted curves in the bottom panel show the values of alpha for realistic-sized planetesimals with $\rho =$ 1, 3, 5 and 10 g cm$^{-3}$.
-(need to fix the green curve)\label{fig:f6f4}}
+The shaded region in the bottom panel show the values of alpha for realistic-sized (f=1) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4}}
 \end{center}
@@
 Although simple to model, this assumption of perfect accretion may result in overly efficient growth, particularly at the innermost region of the disk where encounter velocities are the largest.
-To handle this issue properly, semianalytic collision resolution models have been developed and implemented in N-body codes (see \citep{leinhardt12}).
+To handle this issue properly, semianalytic collision resolution models have been developed and implemented in N-body codes (see \citet{leinhardt12}).
 However, resolving collisional debris fragments using a direct approach as we have done with {\sc ChaNGa} would result in an intractably large number of particles.

### 2022-05-25 makeFig.py

@@ -629,7 +629,7 @@ def plot_f6f4():
 
 	f = 1
 	alpha = r_pl*f/(p_vhi_ic['a']*(m_pl/(3*mCentral))**(1/3))
-	axes.semilogy(prof_perIC, alpha, lw=lw)
+	#axes.semilogy(prof_perIC, alpha, lw=lw)
 
 	rhoval = (1*u.g/u.cm**3).to(u.M_sun/u.AU**3).value
 	r_pl_varyrho = (3*m_pl/(4*np.pi*rhoval))**(1/3)
@@ -739,7 +739,7 @@ def plot_frag_evo():
 #plot_surfden_profiles()
 #plot_surfden_iso()
 #plot_smooth_acc()
-plot_acc_zones()
-#plot_f6f4()
+#plot_acc_zones()
+plot_f6f4()
 #plot_frag_ecc()
 #plot_frag_evo()

### 2022-06-03 main.tex

--- 2022-02-24 main.tex
@@
 
-In section \ref{sec:theory} we provide an overview of the theory
-behind planetesimal accretion and show that assumptions used to derive
-the well-known modes of growth are only valid at sufficiently long
-orbital periods. We then motivate the need for N-body simulations to
-study this problem and describe the code used, along with how our
-initial conditions were constructed in section \ref{sec:methods}. In
-section \ref{sec:narrow}, we present a parameter study of planetesimal
-accretion using a series of simulations of narrow annuli at various
-orbital periods.
-In section \ref{sec:fulldisk}, we present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
+In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and show that assumptions used to derive the well-known modes of growth are only valid at sufficiently long orbital periods.
+We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}.
+In section \ref{sec:narrow}, we present a parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods.
+We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
 Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}.
@@
 
-In the limit that $v_{esc} \gg v$, it can be shown that $M \propto
-M^{4/3}$, which implies a runaway scenario, in which growth
-accelerates with mass. This mode of growth was confirmed with N-body
-simulations by \citet{kokubo96} and appears necessary to construct
-protoplanets within the lifetime of a protoplanetary disk. Due to the
-velocity dependence of the gravitational focusing effect, it is not clear how ubiquitous this mode of growth is.
+In the limit that $v_{esc} \gg v$, it can be shown that $M \propto M^{4/3}$, which implies a runaway scenario, in which growth accelerates with mass.
+This mode of growth was confirmed with N-body simulations by \citet{kokubo96} and appears necessary to construct protoplanets within the lifetime of a protoplanetary disk.
+Due to the velocity dependence of the gravitational focusing effect, it isn't clear how ubiquitous this mode of growth is.
 In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied.
-The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:results}.
-%TRQ: fix section reference.
+The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:narrow}.
 

### 2022-07-21 main.tex
TRQ edits through figure 3.

@@
 
-In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and show that assumptions used to derive the well-known modes of growth are only valid at sufficiently long orbital periods.
-We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}.
-In section \ref{sec:narrow}, we present a parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods.
-We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
+In section \ref{sec:theory} we provide an overview of the theory
+behind planetesimal accretion and show that assumptions used to derive
+the well-known modes of growth are only valid at sufficiently long
+orbital periods. We then motivate the need for N-body simulations to
+study this problem and describe the code used, along with how our
+initial conditions were constructed in section \ref{sec:methods}. In
+section \ref{sec:narrow}, we present a parameter study of planetesimal
+accretion using a series of simulations of narrow annuli at various
+orbital periods.
+In section \ref{sec:fulldisk} we present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
 Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}.
@@
 % TRQ: mention that $v$ is related to the velocity dispersion of the
-% planetesimals.
+% planetesimals.  Also: mention that the scale height of the disk is
+% assumed to be \Omega/(2v)
 Assuming that every collision results in a perfect merger, the growth rate of a planetesimal is given by
-
 \begin{equation}\label{eq:growth}
@@
 
-In the limit that $v_{esc} \gg v$, it can be shown that $M \propto M^{4/3}$, which implies a runaway scenario, in which growth accelerates with mass.
-This mode of growth was confirmed with N-body simulations by \citet{kokubo96} and appears necessary to construct protoplanets within the lifetime of a protoplanetary disk.
-Due to the velocity dependence of the gravitational focusing effect, it isn't clear how ubiquitous this mode of growth is.
+In the limit that $v_{esc} \gg v$, it can be shown that $M \propto
+M^{4/3}$, which implies a runaway scenario, in which growth
+accelerates with mass. This mode of growth was confirmed with N-body
+simulations by \citet{kokubo96} and appears necessary to construct
+protoplanets within the lifetime of a protoplanetary disk. Due to the
+velocity dependence of the gravitational focusing effect, it is not clear how ubiquitous this mode of growth is.
 In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied.
@@
 a spectrum of masses, these velocity differences become even more
-pronounced because as system evolves towards a state of quasi-equilibrium where $v \sim m^{1/2}$.
+pronounced because as the system evolves, it moves to a state of
+energy equipartition where $v \sim m^{1/2}$.
 For a system of equal mass bodies in which encounters are driven by random motions rather than Keplerian shear (dispersion dominated), the timescale for gravitational stirring is described by the two-body relaxation time \citep{ida93}
-
 \begin{equation}\label{eq:relax}
-	t_{relax} = \frac{v^3}{n \pi G^2 m_{pl} \ln \Lambda},
+	t_{relax} = \frac{v^3}{4 \pi n G^2 {m_{pl}}^2 \ln \Lambda},
 \end{equation}
-
-\noindent where $\mathrm{ln} \Lambda$ is the Coulomb logarithm,
+%TRQ: changed this to match Ida & Makino 1993.
+where $\ln \Lambda$ is the Coulomb logarithm,
 typically taken to be $\approx 10$ for a planetesimal disk. Despite
@@
 that the massive runaway bodies make up about 50 percent of the solid
-surface density (citation), a period of less vigorous ``oligarchic'' growth commences, in which the few largest bodies continue to accrete planetesimals at similar rates.
+surface density
+%TRQ: citation needed.
+(citation), a period of less vigorous ``oligarchic'' growth commences, in which the few largest bodies continue to accrete planetesimals at similar rates.
 
@@
 
-In figure \ref{fig:timescales}, we show ratio between the relaxation and collision timescale for a population of equal-mass planetesimals as a function of orbital period.
-Here, the encounter velocity is described by $v = \left( 5/8 \left< e^2 \right>^{1/2} + \left< i^2 \right>^{1/2} \right)^{1/2} v_{k}$, where $\left< e^2 \right>^{1/2}$ and $\left< i^2 \right>^{1/2}$ are the eccentricity and inclination dispersions of the planetesimal disk and $v_{k}$ is the Keplerian velocity.
-For simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2 \right>{1/2}$ \citep{ida93a} and that the eccentricity dispersion is constant with orbital period.
-The eccentricity dispersion is described in units scaled by the Hill factor $\left( m_{pl}/ 3 M_{star} \right)^{1/3}$ such that $e_{h} = 1$ corresponds to the boundary between shear and dispersion dominated encounters.
-The horizontal dashed line indicates where $t_{relax} = t_{coll}$.
-The timescale criterion for oligarchic growth is only satisfied in regions where the disk is sufficiently dynamically cold and the orbital period is sufficiently long.
-In section \ref{sec:results} we will explore the behavior and outcome of planetesimal accretion in regions where this criterion is \textit{not} satisfied.
+In figure \ref{fig:timescales}, we show ratio between the relaxation
+and collision timescale for a population of equal-mass planetesimals
+as a function of orbital period. Here, the encounter velocity is
+described by
+$$
+v = \left( 5/8 \left< e^2 \right>^{1/2} + \left< i^2 \right>^{1/2}
+\right)^{1/2} v_{k},
+$$
+(citation) where $\left< e^2 \right>^{1/2}$ and $\left< i^2
+\right>^{1/2}$ are the eccentricity and inclination dispersions of the
+planetesimal disk and $v_{k}$ is the Keplerian velocity. For
+simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2
+\right>^{1/2}$ \citep{ida93a} and that the eccentricity dispersion is
+constant with orbital period. The eccentricity dispersion is described
+in units scaled by the Hill factor $\left( m_{pl}/ 3 M_{\star}
+\right)^{1/3}$ such that $e_{h} = 1$ corresponds to the boundary
+between shear and dispersion dominated encounters. The horizontal
+dashed line indicates where $t_{relax} = t_{coll}$. The timescale
+criterion for oligarchic growth is only satisfied in regions where the
+disk is sufficiently dynamically cold and the orbital period is
+sufficiently long. In sections \ref{sec:narrow} and \ref{sec:fulldisk}
+we will explore the behavior and outcome of planetesimal accretion in regions where this criterion is \textit{not} satisfied.
 
@@
     \includegraphics[width=0.5\textwidth]{figures/timescales.png}
-    \caption{The ratio between the two-body relaxation and collision timescale for a population of equal-mass planetesimals with an internal density of 3 g cm$^{-3}$.
+    \caption{The ratio between the two-body relaxation and collision
+      timescale for a population of equal-mass planetesimals with an
+      internal density of 3 g cm$^{-3}$ and an eccentricity dispersion
+      characterized by $e_h$, where $e_h = 1$ is the boundary between
+      shear and dispersion dominated encounters.
 Only in regions where $t_{relax} \ll t_{coll}$ can the velocity distribution respond to changes in the mass of the bodies such that oligarchic growth can operate.
@@
 
-An insight into the expected behavior in this regime can be gained by defining the dimensionless parameter $\alpha$, which is the ratio between the physical size of a body and it's Hill radius
-
+An insight into the expected behavior in this regime can be gained by
+defining the dimensionless parameter $\alpha$, which is the ratio
+between the physical size of a body and it's Hill radius, $r_{h}$:
 \begin{equation}\label{eq:alpha}
-	\alpha = \frac{r_{pl}}{r_{h}} = \frac{1}{a} \left( \frac{9 M_{*}}{4 \pi \rho_{pl}} \right)^{1/3},
+	\alpha = \frac{r_{pl}}{r_{h}} = \frac{1}{a} \left( \frac{9 M_{\star}}{4 \pi \rho_{pl}} \right)^{1/3},
 \end{equation}
-
-\noindent where $a$ is the semimajor axis of the body and $\rho_{pl}$ is its bulk density.
+where $a$ is the semimajor axis of the body and $\rho_{pl}$ is its bulk density.
 Assuming a fixed bulk density as bodies collide and grow, and that no large-scale migration occurs, the scaling of both $r_{pl}$ and $r_{h}$ with $m_{pl}^{1/3}$ means that $\alpha$ will be constant with time.
@@
 We also introduce a second dimensionless quantity, which relates the physical size of the bodies to the velocity state of the system
-
 \begin{equation}\label{eq:beta}
@@
 \end{equation}
-
-\noindent where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body.
+where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body.
 Encounters between bodies inside of a distance of $r_{g}$ result in significant deflections of their trajectories.
@@
 
-Need a transition to next section here.
+These scaling considerations motivate the range of parameters in the
+following numerical experiments as explore the different regimes.
+
+% Need a transition to next section here.
 
@@
 
-We use the tree-based N-body code {\sc ChaNGa} \footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}} to model the gravitational and collisional evolution of planetesimals at short orbital periods (where $\alpha$ is large).
+We use the tree-based N-body code {\sc ChaNGa}\footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}} to model the gravitational and collisional evolution of planetesimals at short orbital periods (where $\alpha$ is large).
 {\sc ChaNGa} is written using the {\sc CHARM++} parallel programming language and has been shown to perform well on up to half a million processors \citep{menon15} and can follow the evolution of gravitationally interacting swarms of up to billions of particles.
@@
 For all of the simulations presented in this paper, we use a node opening criteria of $\theta_{BH}$ = 0.7.
-Additional information about the code is available in \citep{jetley08}.
+Additional information about the code is available in \citep{jetley08,menon15}.
 
-Using the neighbor-finding algorithm in {\sc ChaNGa}, originally designed for SPH calculations, we have recently implemented a solid body collision module in the code.This work is largely based on the solid-body collision implementation in {\sc PKDGRAV}, which is described in \citet{richardson94} and \citet{richardson00}.
-To summarize, imminent collisions are detected during the `drift' phase by extrapolating positions of bodies forward in time, using the velocity calculated at the opening `kick'.
-For each body, any neighboring particles which fall within a search ball of radius $fill in later$ are tested for an imminent collision.
-In the case that a collision is detected, the particles are merged into a single larger body, which is given the center of mass position and velocity of the two children.
-Resolving a collision can produce another imminent collision, so collisions are handled one-by-one and another full collision check is run after the previous event is resolved.
-For a more detailed description of the collision module in {\sc ChaNGa}, see \citep{wallace19}.
-(mention grav stepping here as well, since its used for all simulations)
+Using the neighbor-finding algorithm in {\sc ChaNGa}, originally
+designed for SPH calculations, we have recently implemented a solid
+body collision module in the code.  This work is largely based on the
+solid-body collision implementation in {\sc PKDGRAV}, which is
+described in \citet{richardson94} and \citet{richardson00}. To
+summarize, imminent collisions are detected during the ``drift'' phase
+by extrapolating positions of bodies forward in time, using the
+velocity calculated at the opening ``kick''. For each body, any
+neighboring particles which fall within a search ball of radius XXX
+$fill in later$ are tested for an imminent collision. In the case that
+a collision is detected, the particles are merged into a single larger
+body, which is given the center of mass position and velocity of the
+two children. Resolving a collision can produce another imminent
+collision, so collisions are handled one-by-one and another full
+collision check is run after the previous event is resolved. For a
+more detailed description of the collision module in {\sc ChaNGa}, see
+\citep{wallace19}.
+Particles are advanced in time on individual timesteps chosen as a
+power of two of a base timestep.  The timestep for an individual
+particle is based on an estimate of the gravitational dynamical time
+determined by the minimum of $\sqrt{d_{node}^3/(G(M_{node} + m_{pl}))}$
+across all nodes in the tree that are accepted by the Barnes-Hut
+opening criterion.  Here $d_{node}$ is the distance from the
+planetesimal to the center of mass of the tree node and $M_{node}$ is
+the total mass of the tree node.  For nearby particles $M_{node}$ is
+replaced with the mass of the nearby particle.
 
@@
 
-We begin by presenting a parameter study of planetesimal accretion, motivated by two questions raised in section \ref{sec:theory}.
-1.
-Does runaway growth still operate when the condition that $v \ll v_{esc}$ is not satisfied?
-2.
-How does planetesimal accretion proceed when the planetesimals themselves occupy a significant fraction of their Hill spheres?
+We begin by presenting a parameter study of planetesimal accretion,
+motivated by two questions raised in section \ref{sec:theory}. 1) Does
+runaway growth still operate when the condition that $v \ll v_{esc}$
+is not satisfied? 2) How does planetesimal accretion proceed when the planetesimals themselves occupy a significant fraction of their Hill spheres?
 
-To answer these questions, we run a series of simulations in which a narrow annulus of planetesimals orbits a star.
-The values of $\alpha$ and $\beta$ are varied individually.
-4000 planetesimals with individual masses of $5 \times 10^{23}$ g are placed with semimajor axes randomly drawn between 0.95 and 1.05 AU about a 1 $M_{\odot}$ star.
-The argument of perihelion $\omega$, longitude of ascending node $\Omega$, and mean anomaly M for each body is drawn from a uniform distribution $\in [0, 2 \pi)$.
-The inclination dispersion $\left< i^{2} \right>^{1/2}$ is chosen to be half the eccentricity dispersion $\left< e^{2} \right>^{1/2}$ \citep{ida93a}.
+To answer these questions, we run a series of simulations in which a
+narrow annulus of planetesimals orbits a star. The values of $\alpha$
+and $\beta$ are varied individually. 4000 planetesimals with
+individual masses of $5 \times 10^{23}$ g are placed with semimajor
+axes randomly drawn between 0.95 and 1.05 AU about a 1 $M_{\odot}$
+star. The argument of perihelion $\omega$, longitude of ascending node
+$\Omega$, and mean anomaly M for each body is drawn from a uniform
+distribution $\in [0, 2 \pi)$. The inclination dispersion $\left<
+i^{2} \right>^{1/2}$ is chosen to be half the eccentricity
+dispersion $\left< e^{2} \right>^{1/2}$ \citep{ida93a}.
+% Mention Rayleigh distribution: TRQ: yes!
 
-% Mention Rayleigh distribution
-In the `nominal' case, we give the bodies a bulk density of 3 g cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, where $e_{h} = e a/r_{h}$ (define this in the previous section instead) which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
+In the ``fiducial'' case, we give the bodies a bulk density of 3 g
+cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
 These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth.
@@
 
-In all cases, the simulations are evolved with a base timestep of 1.7 days, which corresponds to 3\% of an orbital dynamical time $\sqrt{a^3/G M_{*}}$.
-Due to the vastly differing growth timescales in each case, a simulation is stopped when the growth of the most massive body flattens out.
-In figure \ref{fig:alpha_beta}, we show the a-e distribution of bodies in the initial (blue) and final (orange) snapshots from each of the 4 simulations.
-The size of the points indicates the relative masses of the bodies.
-Only in the case of small $\alpha$ does a residual population of dynamically hot planetesimals develop.
-The lack of high eccentricity planetesimals in the large $\alpha$ case suggests that most encounters instead result in accretion.
-In the case of large $\beta$, the protoplanets and remaining planetesimals end up in a dynamically cool state, compared to the initial conditions.
+In all cases, the simulations are evolved with a base timestep of 1.7
+days, which corresponds to 3\% of an orbital dynamical time
+$\sqrt{a^3/G M_{*}}$. Due to the vastly differing growth timescales in
+each case, a simulation is stopped when the growth of the most massive
+body flattens out. In figure \ref{fig:alpha_beta}, we show the a-e
+distribution of bodies in the initial (blue) and final (orange)
+snapshots from each of the 4 simulations. The size of the points
+indicates the relative masses of the bodies. Only in the case of small
+$\alpha$ does a residual population of dynamically hot planetesimals
+develop. The lack of high eccentricity planetesimals in the large
+$\alpha$ case suggests that most encounters result in accretion
+instead of scattering. In the case of large $\beta$, the protoplanets
+and remaining planetesimals end up in a dynamically cool state,
+compared to the initial conditions.
+%TRQ albeit for small alpha, only slightly cooler.
 (Are the inelastic collisions playing a significant role here?)
@@
 
-To investigate whether any of these planetesimal disks underwent runaway growth, we examine the time evolution of the maximum and mean masses in each case.
-The ratio $m_{max}/\left< m \right>$ is plotted in figure \ref{fig:alpha_beta_evo}.
-On this plot, a positive slope indicates that the growth rate is accelerating with mass, which is evident in all four cases.
-Even with a large value of $\beta$, which means that the effective collision cross section is very near the geometric value, runaway growth still appears to operate.
-This seems to imply that, as bodies collide and grow, the relative increase in their gravitational focusing factors, rather than its absolute size, is what drives the system towards runaway growth.
-Although larger encounter velocities will lengthen the growth timescales, this mode of growth appears to be inevitable, so long as gravity is the dominant force in the system.
+To investigate whether any of these planetesimal disks underwent
+runaway growth, we examine the time evolution of the maximum and mean
+masses in each case. The ratio $m_{max}/\left< m \right>$ is plotted
+in figure \ref{fig:alpha_beta_evo}. On this plot, a positive slope
+indicates that the growth rate is accelerating with mass, which is
+evident at various times in all four cases. Even with a large value of
+$\beta$, which means that the effective collision cross section is
+very near the geometric value, runaway growth still appears to
+operate. This seems to imply that, as bodies collide and grow, the
+relative increase in their gravitational focusing factors, rather than
+its absolute size, is what drives the system towards runaway
+growth. Although larger encounter velocities will lengthen the growth
+timescales, this mode of growth appears to be inevitable, so long as
+gravity is the dominant force in the system.
+% TRQ: also mention the negative slope
 
@@
 
-Motivated by the apparent dependence of accretion modes on $\alpha$, we next investigate whether this highly efficient, non-oligarchic growth mode should be expected to operate in a typical planet-forming disk.
-Given the dearth of short period terrestrial planets observed around M stars (citation), we model a series of wide planetesimal disks, which span from 1 to 100 days in orbital period orbiting a late-type M star of mass 0.08 $M_{\odot}$.
+Motivated by the apparent dependence of accretion modes on $\alpha$,
+we next investigate whether this highly efficient, non-oligarchic
+growth mode should be expected to operate in a typical planet-forming
+disk.
+Given the dearth (TRQ: why is this a reason for a wide disk?) of short period terrestrial planets observed around M stars (citation), we model a series of wide planetesimal disks, which span from 1 to 100 days in orbital period orbiting a late-type M star of mass 0.08 $M_{\odot}$.
 For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this orbital period range corresponds to $\alpha \in (0.7, 0.05)$.
@@
 Four wide disk simulations are run in total (see table \ref{tab:sims}). In each case, the solid surface density follows a power law profile
-
 \begin{equation}
-	\Sigma(r) = \left( \frac{M_{*}}{M_{\odot}} \right) A \Sigma_{mmsn} \left( \frac{r}{1 AU} \right)^{-\alpha},
+	\Sigma(r) = \left( \frac{M_{*}}{M_{\odot}} \right) A \Sigma_{MMSN} \left( \frac{r}{1 AU} \right)^{-\alpha},
 \end{equation}
-
-\noindent where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g cm$^{-2}$ is surface density of the minimum-mass solar nebula \citep{hayashi81} at 1 AU, and $A$ is an enhancement factor.
+%TRQ: should we use a different greek letter for the power law index?
+where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g cm$^{-2}$ is surface density of the minimum-mass solar nebula \citep{hayashi81} at 1 AU, and $A$ is an enhancement factor.
 In the first case (fdHi), we model a disk that follows a MMSN power law slope, with the overall normalization enhanced by a factor of 100.
@@
     \includegraphics[width=0.5\textwidth]{figures/alpha_beta_mass.png}
-    \caption{The final state of the mass distribution for the simulations described in section \ref{sec:narrow}.
-For small $\alpha$, a few embryos form alongside a power law tail of planetesimals.
-For larger values of $\alpha$, the mass distribution takes on a more unimodal form.
+    \caption{The final state of the mass distribution for the
+      simulations described in section \ref{sec:narrow}. For small
+      $\alpha$, a few embryos form alongside a power law tail of
+      planetesimals. For larger values of $\alpha$, the mass
+      distribution takes on a more unimodal (TRQ: uniform?) form.
 As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.\label{fig:alpha_beta_mass}}

### 2022-08-02 makeFig.py
Add later fullDiskLo snapshot

@@ -84,7 +84,7 @@ perSh = 2*np.pi*np.sqrt((plVHiSh['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.
 snap = pb.load('data/fullDiskLoLarge.ic')
 plLoIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_lo_ic = pb.analysis.profile.Profile(plLoIC.d, bins=bins)
-snap = pb.load('data/fullDiskLoLarge.1000000')
+snap = pb.load('data/fullDiskLoLarge.2840000')
 plLo = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_lo = pb.analysis.profile.Profile(plLo.d, bins=bins)
 perICLo = 2*np.pi*np.sqrt((plLoIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
@@ -413,13 +413,14 @@ def plot_surfden_profiles():
 
 	fig, axes = plt.subplots(figsize=(8,6))
 
-	axes.scatter(per.value, plVHi['e'], s=500*plVHi['mass']/np.max(plVHiSt['mass']), label='fdHi')
-	axes.scatter(perSt.value, plVHiSt['e'], s=500*plVHiSt['mass']/np.max(plVHiSt['mass']), label='fdHiSteep')
-	axes.scatter(perSh.value, plVHiSh['e'], s=500*plVHiSh['mass']/np.max(plVHiSt['mass']), label='fdHiShallow')
-	axes.scatter(perLo.value, plLo['e'], s=500*plLo['mass']/np.max(plVHiSt['mass']), label='fdLo')
+	size = 1000
+	axes.scatter(per.value, plVHi['e'], s=size*plVHi['mass']/np.max(plVHiSt['mass']), label='fdHi', marker='o')
+	axes.scatter(perSt.value, plVHiSt['e'], s=size*plVHiSt['mass']/np.max(plVHiSt['mass']), label='fdHiSteep', marker='^')
+	axes.scatter(perSh.value, plVHiSh['e'], s=size*plVHiSh['mass']/np.max(plVHiSt['mass']), label='fdHiShallow', marker='x')
+	axes.scatter(perLo.value, plLo['e'], s=size*plLo['mass']/np.max(plVHiSt['mass']), label='fdLo', marker='p')
 
[…]

### 2022-08-02 main.tex
Add reference to childs 22
Rework intro, fill in citations

@@
 
-% TRQ: the following paragraph (particularly the last sentence could
-% use citations: probably to review articles.
-Planetesimal accretion is one of a number of stages in which micron-sized solids from the protostellar nebula coalesce to eventually build terrestrial planets.
-In the earliest stages, aerodynamic forces dominate the growth and evolution of the solids.
-Millimeter-sized bodies grow through adhesive pairwise collisions and stay well-coupled to the surrounding gas.
-Beyond this size, however, a number of growth barriers present themselves.
-Most notably, larger solids orbit the central star at Keplerian speeds as they decouple from the gas, which orbits at a sub-keplerian speed due to radial pressure support.
-This leads the solids to feel a headwind, which is maximally effective at sapping away angular momentum for objects around 1 meter in size.
-At this size, the timescale for the growing solids to fall onto the star is catastrophically short and leads to what is known as the drift barrier.
-In addition, two-body collisions between mm- to cm-sized bodies tend to result in bouncing or destruction, rather than continued growth.
-For these reasons, a number of mechanisms have been proposed which facilitate fast growth from mm to km sizes by locally concentrating solids.
-Dust traps, streaming instability, pebble piles...etc.
+Planetesimal accretion is a key phase in the terrestrial planet growth process, bridging the gap from kilometer-sized bodies up to roughly moon-sized objects known as planetary embryos.
+In the earliest stages of the planet formation process, aerodynamic forces dominate the growth and evolution of the solids and statistical models \citep{johansen14, birnstiel16} are appropriate to describe how these numerous, small bodies coagulate.
+Due to the internal pressure support of the gas disk, the gas itself orbits at sub-Keplerian speed and exerts a headwind on any solids large enough to decouple from the gas \citep{weidenschilling77}.
+Above about a meter in size, this headwind is maximally effective at sapping away angular momentum and planet-building material can fall onto the central star on catastrophically short timescales \citep{weidenschilling77, nakagawa86}.
+Additionally, laboratory experiments suggest that collisions between mm- to cm- sized solids tend to result in bouncing or destruction, rather than continued growth \citep{blum93, beitz11, colwell03}.
+For these reasons, a number of mechanisms which involve radially concentrating solids in a planet-forming disk have been proposed to facilitate fast growth from mm to km sizes \citep{johansen07, lyra08, bai10}.
+Interestingly, formation models for the short-period multiplanet systems revealed by Kepler \citep{fabrycky14} also seem to require enhanced concentrations of planet-building material to reproduce the observed architectures \citep{raymond07, hansen12}.
 
-Beyond kilometer scales, gravity begins to dominate and aerodynamic gas drag plays a smaller and smaller role.
+Regardless of how the mm- to km-sized growth barriers are surmounted, gravity begins to dominate and aerodynamic gas drag plays a less significant role beyond this size.
 During this phase, collision cross sections are enhanced as gravitational focusing \citep{safronov69} acts to bend the trajectories of bodies undergoing close encounters.
-Large bodies are most effective at focusing the trajectories of nearby planetesimals, leading to a period of runaway growth \citep{wetherill89, kokubo96, barnes09}.
+Because larger bodies are more effective at focusing the trajectories of nearby planetesimals, a period of runaway growth occurs \citep{wetherill89, kokubo96, barnes09}.
 Eventually, the largest bodies (known as oligarchs) dynamically heat the surrounding planetesimals, severely limiting further growth \citep{kokubo98}.
 The end result of this phase is a bimodal population of dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals.
-Lines of evidence suggest that the asteroid belt, kuiper belt and the oort cloud are largely composed of the leftovers of this stage of planet formation.
-(Mention more specific evidence, morbidelli 09 paper, CAIs?)
+Lines of evidence suggest that the asteroid belt, Kuiper belt and the Oort cloud are largely composed of the leftovers of this stage of planet formation.
 
-Although gas drag has a minimal influence on the Moon to Mars-sized oligarchs, it is enough to prevent these largest bodies from perturbing each other onto crossing orbits.
-Simulations show that evaporation of the gas disk is required to allow instability to trigger a phase of giant impacts (Mention that disk fraction decay timescale roughly matches timing of giant impacts in SS).
-It is during this phase that oligarchs collide to form Earth-sized planets \citep{chambers98, raymond06}.
+After a long period of quiescence, the collection of embryos and remaining planetesimals undergoes a large-scale instability \citep{chambers98}.
+Suddenly, the oligarchics are no longer on isolated, stable orbits and coalesce to form Earth-sized planets through a series of extremely energetic, giant impacts \citep{kokubo02, raymond05, raymond06}.
+Due to the relative ease of modeling the early dust coagulation phases and the final giant impact phase, these steps in the terrestrial planet formation process have received the most attention in the literature.
+The planetesimal accretion phase, which we will focus on in this paper, falls into an awkward in-between, where there are too many particles to directly track with traditional N-body codes, while the gravitational influence of the few, but massive oligarchs that form make statistical methods an inappropriate approach.
+Because of this limitation, planetesimal accretion is usually modeled in a narrow ring and the results are then scaled to suit whatever situation is being studied.
+N-body simulations of terrestrial planet formation typically begin with a series of neatly spaced oligarchs, whose mass varies smoothly with orbital period.
+As we will show in this paper, this extrapolation with orbital period is inappropriate, particularly at short ($<$ 10 day) periods.
 
-Over the last few decades, terrestrial planet formation models have largely advanced by matching properties of the solar system.
+Given that systems of tightly-packed inner planets (STIPs) appear to be a common outcome of planet formation, understanding exactly how solids accumulate at short orbital periods is crucial.
+Although gas-disk driven migration of the planets themselves is often invoked to explain the observed architectures, we will focus on an in-situ model in this paper.
+That is, once the planetesimals themselves form, they largely stay in place and any subsequent large-scale movement of the solids are the result of mutual gravitational interactions.
+The focus of this work will be to understand how the outcome of the planetesimal accretion process scales with orbital period by using a high-powered N-body code to directly follow the growth and evolution of the planetesimals across a wide range of orbital periods (1 to 100 days).
+In doing so, we will assess whether the typical `isolation mass' initial conditions used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
+In a series of follow up papers, we plan to use these results to directly track the formation of full-sized planets from planetesimals and to understand how gravitational perturbations from a nearby gas giant might affect the outcome of this process.
+
+% This stuff doesn't fit since I reworked the intro. Might be better to save some of this for paper 2 (planetesimals->planets)
+% Still deciding whether I should mention habitability and low mass stars
+% I think there are plenty of STIPs around sun like stars, but I should double check this
+
+%Over the last few decades, terrestrial planet formation models have largely advanced by matching properties of the solar system.
 Compared to exoplanetary systems, the solar system provides a rich set of constraints (isotopic ratios, cratering records, small body populations) that are mostly unmeasurable for even the closest neighboring planet forming systems.
@@
 
-Given the difficult question of whether to treat the solar system as
-an outlier, the best way forward is to use statistical samples of
-exoplanetary architectures to develop and inform formation
-models. This is generally done through the use of population synthesis
-models \citep{ida04, alibert11}, but many of the mechanisms in these
-models are informed and tuned by solar system constraints. One
-pervasive and exotic result revealed by the Kepler space telescope is the discovery of hundreds of compact multi-planet terrestrial systems, dubbed systems of tightly-packed inner planets (STIPs).
+%Given the difficult question of whether to treat the solar system as
+%an outlier, the best way forward is to use statistical samples of
+%exoplanetary architectures to develop and inform formation
+%models. This is generally done through the use of population synthesis
+%models \citep{ida04, alibert11}, but many of the mechanisms in these
+%models are informed and tuned by solar system constraints. One
+%pervasive and exotic result revealed by the Kepler space telescope is the discovery of hundreds of compact multi-planet terrestrial systems, dubbed systems of tightly-packed inner planets (STIPs).
 Although there is no formal definition of a STIP, they typically contain 3 or more Earth-sized planets with orbital periods extending between 1 and 100 days.
@@
 
-To date, a large body of work exists that has attempted to reproduce
-the architectures of STIPs, starting from planetary embryos (cite some
-examples). However, the runaway and oligarchic growth phases, which
-precede the assembly of the embryos, are assumed to be
-ubiquitous. Given that the timescales for accretion and gravitational
-scattering scale differently with encounter velocity, which itself
-scales with orbital period, it is not entirely clear that planetary
-embryos should form in the same way close to the star as they do at
-much longer, more thoroughly studied orbital periods. In this paper,
-we use direct N-body simulations to explore the outcome of the
-planetesimal accretion stage at orbital periods shorter than 100 days
-around an M star.
+%To date, a large body of work exists that has attempted to reproduce
+%the architectures of STIPs, starting from planetary embryos (cite some
+%examples). However, the runaway and oligarchic growth phases, which
+%precede the assembly of the embryos, are assumed to be
+%ubiquitous. Given that the timescales for accretion and gravitational
+%scattering scale differently with encounter velocity, which itself
+%scales with orbital period, it is not entirely clear that planetary
+%embryos should form in the same way close to the star as they do at
+%much longer, more thoroughly studied orbital periods. In this paper,
+%we use direct N-body simulations to explore the outcome of the
+%planetesimal accretion stage at orbital periods shorter than 100 days
+%around an M star.
 % TRQ perhaps mention habitable zone here.  Somewhere, a discussion of
@@
 % where STIPS are found, needs to be discussed.
-In particular, we seek to understand what the orbital and mass distributions of the embryos and residual planetesimals look like, and to assess whether the initial conditions used by late-stage simulations of STIP assembly are reasonable.
+%In particular, we seek to understand what the orbital and mass distributions of the embryos and residual planetesimals look like, and to assess whether the initial conditions used by late-stage simulations of STIP assembly are reasonable.
+%
 
@@
 
+Radial mixing appears to be enhanced by a partial collision model, along with smaller collision cross section inflation \citep{childs22}.
+
 % show alpha, beta study again with bounce vs merge model

### 2022-08-03 main.tex
Small grammar edit.

@@
 relative increase in their gravitational focusing factors, rather than
-its absolute size, is what drives the system towards runaway
+their absolute size, is what drives the system towards runaway
 growth. Although larger encounter velocities will lengthen the growth

### 2022-08-04 main.tex
Full read through.

@@
 
-Planetesimal accretion is a key phase in the terrestrial planet growth process, bridging the gap from kilometer-sized bodies up to roughly moon-sized objects known as planetary embryos.
-In the earliest stages of the planet formation process, aerodynamic forces dominate the growth and evolution of the solids and statistical models \citep{johansen14, birnstiel16} are appropriate to describe how these numerous, small bodies coagulate.
-Due to the internal pressure support of the gas disk, the gas itself orbits at sub-Keplerian speed and exerts a headwind on any solids large enough to decouple from the gas \citep{weidenschilling77}.
-Above about a meter in size, this headwind is maximally effective at sapping away angular momentum and planet-building material can fall onto the central star on catastrophically short timescales \citep{weidenschilling77, nakagawa86}.
+Planetesimal accretion is a key phase in the terrestrial planet growth
+process, bridging the gap from kilometer-sized bodies up to roughly
+moon-sized objects known as planetary embryos. In the earliest stages
+of the planet formation process, aerodynamic forces dominate the
+growth and evolution of the solids and statistical models
+\citep{johansen14, birnstiel16} are appropriate to describe how these
+numerous, small bodies coagulate. Due to the internal pressure support
+of the gas disk, the gas itself orbits at sub-Keplerian speed and
+exerts a headwind on any solids large enough to decouple from the gas
+\citep{weidenschilling77}. Above about a meter in size, this headwind
+is maximally effective at sapping away angular momentum, and planet-building material can fall onto the central star on catastrophically short timescales \citep{weidenschilling77, nakagawa86}.
 Additionally, laboratory experiments suggest that collisions between mm- to cm- sized solids tend to result in bouncing or destruction, rather than continued growth \citep{blum93, beitz11, colwell03}.
@@
 
-After a long period of quiescence, the collection of embryos and remaining planetesimals undergoes a large-scale instability \citep{chambers98}.
-Suddenly, the oligarchics are no longer on isolated, stable orbits and coalesce to form Earth-sized planets through a series of extremely energetic, giant impacts \citep{kokubo02, raymond05, raymond06}.
-Due to the relative ease of modeling the early dust coagulation phases and the final giant impact phase, these steps in the terrestrial planet formation process have received the most attention in the literature.
-The planetesimal accretion phase, which we will focus on in this paper, falls into an awkward in-between, where there are too many particles to directly track with traditional N-body codes, while the gravitational influence of the few, but massive oligarchs that form make statistical methods an inappropriate approach.
-Because of this limitation, planetesimal accretion is usually modeled in a narrow ring and the results are then scaled to suit whatever situation is being studied.
+After a long period of quiescence, the collection of embryos and
+remaining planetesimals undergoes a large-scale instability
+\citep{chambers98}.
+%TRQ "Suddenly" seems a drastic term to use here.
+Suddenly, the oligarchics are no longer on isolated, stable orbits and
+coalesce to form Earth-sized planets through a series of extremely
+energetic, giant impacts \citep{kokubo02, raymond05, raymond06}.
+%TRQ new paragraph here?
+Due to the relative ease of modeling the early dust coagulation phases
+and the final giant impact phase, these steps in the terrestrial
+planet formation process have received the most attention in the
+literature. The planetesimal accretion phase, which we will focus on
+in this paper, falls into an awkward in-between, where there are too
+many particles to directly track with traditional N-body codes, while
+the gravitational influence of the few, but massive oligarchs that
+form make statistical methods an inappropriate approach. Because of
+this limitation, planetesimal accretion is usually modeled in a narrow
+ring, and the results are then scaled to suit whatever situation is being studied.
 N-body simulations of terrestrial planet formation typically begin with a series of neatly spaced oligarchs, whose mass varies smoothly with orbital period.
@@
 
-Given that systems of tightly-packed inner planets (STIPs) appear to be a common outcome of planet formation, understanding exactly how solids accumulate at short orbital periods is crucial.
-Although gas-disk driven migration of the planets themselves is often invoked to explain the observed architectures, we will focus on an in-situ model in this paper.
-That is, once the planetesimals themselves form, they largely stay in place and any subsequent large-scale movement of the solids are the result of mutual gravitational interactions.
-The focus of this work will be to understand how the outcome of the planetesimal accretion process scales with orbital period by using a high-powered N-body code to directly follow the growth and evolution of the planetesimals across a wide range of orbital periods (1 to 100 days).
-In doing so, we will assess whether the typical `isolation mass' initial conditions used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
+Given that systems of tightly-packed inner planets (STIPs) appear to
+be a common outcome of planet formation, understanding exactly how
+solids accumulate at short orbital periods is crucial. Although
+gas-disk driven migration of the planets themselves is often invoked
+to explain the observed architectures, we will focus on an in-situ
+model in this paper. That is, once the planetesimals themselves form,
+they largely stay in place and any subsequent large-scale movement of
+the solids are the result of mutual gravitational interactions. The
+focus of this work will be to understand how the outcome of the
+planetesimal accretion process scales with orbital period by using a
+high-powered N-body code to directly follow the growth and evolution
+of the planetesimals across a wide range of orbital periods (1 to 100
+days). In doing so, we will assess whether the typical ``isolation
+mass'' initial conditions used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
 In a series of follow up papers, we plan to use these results to directly track the formation of full-sized planets from planetesimals and to understand how gravitational perturbations from a nearby gas giant might affect the outcome of this process.
@@
 % I think there are plenty of STIPs around sun like stars, but I should double check this
+% TRQ: for the discussion/conclusions: mention that the mass of the
+% star doesn't matter (caveat composition changes in the
+% planetesimals); it's the orbital period that is crucial.
 
@@
 gravity is the dominant force in the system.
-% TRQ: also mention the negative slope
+% TRQ: also mention the negative slope?
 
@@
 
-\noindent where $\Sigma_{g}$ is the gas surface density (taken to be 240x the solid surface density), $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
+\noindent where $\Sigma_{g}$ is the gas surface density (taken to be
+240 times the solid surface density), $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
 The sound speed profile is given by $c_{s} = \sqrt{k_{B} T(r) / \left( \mu m_{H} \right)}$, where $k_{B}$ is Boltzmann's constant, $T(r) = T_{0} r^{-Q}$, $\mu = 2.34$ and $m_{h}$ is the mass of a hydrogen atom.
@@
 
-\noindent where $v_{k}$ is the local Keplerian velocity.
-As in section \ref{sec:narrow}, the argument of perihelion $\omega$, longitude of ascending node $\Omega$, and mean anomaly M for the planetesimals drawn from a uniform distribution $\in [0, 2 \pi)$.
+\noindent where $v_{k}$ is the local Keplerian velocity. As in section
+\ref{sec:narrow}, the argument of perihelion $\omega$, longitude of
+ascending node $\Omega$, and mean anomaly M for the planetesimals are drawn from a uniform distribution $\in [0, 2 \pi)$.
 
@@
 
-In the case of the fdHi simulation, there are nearly 1 million particles, whose orbital periods two orders of magnitude in time.
-Due to the very short interaction timescales near the inner edge of the disk, a fixed timestep size would required a prohibitively large number of steps to follow planetesimal growth throughout the entire disk.
-For this reason, we use a multi-tiered timestepping scheme, in which particles are placed onto the nearest power of two timestep based on their most recently calculated gravitational acceleration.
-(Mention that this scheme is used in other works with ChaNGa).
+In the case of the fdHi simulation, there are nearly 1 million
+particles, whose orbital periods vary by two orders of magnitude. Due
+to the very short interaction timescales near the inner edge of the
+disk, a fixed timestep size would required a prohibitively large
+number of steps to follow planetesimal growth throughout the entire
+disk. For this reason, we use a multi-tiered timestepping scheme, in
+which particles are placed onto the nearest power of two timestep
+based on their most recently calculated gravitational
+acceleration. (This scheme is used on almost all works using ChaNGa,
+and is common among large-scale simulation codes.)
 
-This more efficient scheme, however, introduces two additional issues related to particles interacting on different timesteps.
-First, momentum is not completely conserved when bodies switch timesteps.
-The error introduced becomes particularly severe for a particle on an eccentric Keplerian orbit, whose perihelion and aphelion distances straddle a timestep boundary.
-For a large collection of particles, this problem manifests itself as a V-shaped gap in the semimajor axis-eccentricity plane, which is centered on the boundary itself.
+This more efficient scheme, however, introduces two additional issues
+related to particles interacting on different timesteps. First,
+momentum is not completely conserved when bodies switch timesteps. The
+error introduced becomes particularly severe for a particle on an
+eccentric Keplerian orbit, whose perihelion and aphelion distances
+straddle a timestep boundary. For a large collection of particles,
+this problem manifests itself as the development of a V-shaped gap in the semimajor axis-eccentricity plane, which is centered on the boundary itself.
 To correct this problem, we introduce a second timestepping criterion, which is based on the gravitational acceleration on the particle by the central star at perihelion.
@@
 \caption{Final Properties of Full Disk Simulations}
+%TRQ: the mass numbers in this table look wrong.
 \begin{tabular}{lllll} \hline \hline
@@
 
-In all four simulations, the timescales for embryo formation depend on the chosen surface density profile, along with the particular location in the disk.
-Protoplanets form first near the inner edge of the disk, where the dynamical timescales are short.
-Growth proceeds in an inside-out fashion, with the outermost regions of the disk completing the protoplanet assembly phase last.
-This fact is not typically accounted for in planet formation simulations, and appears to be an important component to forming realistic solar system analogs \citep{clement20}.
-As with the narrow annulus simulations, we stop the integration once the mass of protoplanets in the outermost region of the disk reach a steady value.
-In table \ref{tab:sim_properties}, we summarize the outcomes of the four `full disk' cases.
+In all four simulations, the timescales for embryo formation depend on
+the chosen surface density profile, along with the particular location
+in the disk. Protoplanets form first near the inner edge of the disk,
+where the dynamical timescales are short. Growth proceeds in an
+inside-out fashion, with the outermost regions of the disk completing
+the protoplanet assembly phase last. This fact is not typically
+accounted for in planet formation simulations, and appears to be an
+important component to forming realistic solar system analogs
+\citep{clement20}. As with the narrow annulus simulations, we stop the
+integration once the masses of protoplanets in the outermost region of
+the disk reach a steady value. In table \ref{tab:sim_properties}, we
+summarize the outcomes of the four ``full disk'' cases.
 
-We show the final state of the `fiHi' simulation in figure \ref{fig:fulldisk_e_m}.
+We show the final state of the ``fiHi'' simulation in figure \ref{fig:fulldisk_e_m}.
 In the top panel, the initial (contours) and final (points) state of the simulation is shown in orbital period and eccentricity.
@@
 In the bottom panel, the mass of the largest bodies is shown as a function of orbital period.
-The solid curves indicate the isolation mass
-
+The solid curves indicate the isolation mass,
 \begin{equation}\label{eq:iso}
@@
 \end{equation}
-
-\noindent where $\tilde{b}$ is the size of the feeding zone in units of Hill radii.
-For a body on a circular orbit $\tilde{b} = 2 \sqrt{3}$, while a protoplanet formed by oligarchic growth typically has $\tilde{b} = 10$ \citep{kokubo98}.
+where $\tilde{b}$ is the size of the feeding zone in units
+of Hill radii. For a body on a circular orbit $\tilde{b} = 2
+\sqrt{3}$, while a protoplanet formed by oligarchic growth typically
+has $\tilde{b} = 10$ \citep{kokubo98}.
+%TRQ there is no orange line in the figure.
 The isolation mass is plotted in blue and orange for these two values of $\tilde{b}$, respectively.
@@
 
-To ensure that the boundary seen near 60 days in orbital period is not simply a transient product of the inside out growth throughout the disk, we examine the time evolution of $\sigma/\Sigma$ at multiple locations.
-In figure \ref{fig:pl_frac_time}, the value of $\sigma/\Sigma$ is plotted as a function of time in 10 orbital period bins.
+To ensure that the boundary seen near 60 days in orbital period is not
+simply a transient product of the inside out growth throughout the
+disk, we examine the time evolution of $\sigma/\Sigma$ at multiple
+locations. In figure \ref{fig:pl_frac_time}, the value of
+$\sigma/\Sigma$ is plotted as a function of time in 10 orbital period
+bins.
+%TRQ: width of the bins?
 Bins interior to 60 days are indicated with a dashed line, while those exterior are indicated with a solid line.
@@
     \includegraphics[width=0.5\textwidth]{figures/fulldisk_e_m.png}
-    \caption{The final state of the fdHi simulation.
-In the top panel, the contours denote the initial period-eccentricity distribution of the planetesimals.
-Point sizes indicate the relative masses of bodies.
-In the bottom panel, the solid line indicates the isolation mass for $b = 2 \sqrt{3}$.
+    \caption{The final state of the fdHi simulation. In the top panel,
+      the contours denote the initial period-eccentricity distribution
+      of the planetesimals. Point sizes indicate the relative masses
+      of bodies. In the bottom panel, the solid line indicates the
+      isolation mass for $\tilde{b} = 2 \sqrt{3}$.
 The vertical dashed line marks the approximate location of the accretion mode boundary.
@@
     \includegraphics[width=0.5\textwidth]{figures/surfden_iso.png}
-    \caption{Masses of the remaining bodies from the simulations listed in table \ref{tab:sim_properties}, in units of the isolation mass for $b = 2 \sqrt{3}$.
+    \caption{Masses of the remaining bodies from the simulations
+      listed in table \ref{tab:sim_properties}, in units of the
+      isolation mass for $\tilde{b} = 2 \sqrt{3}$.
 Despite the vastly different initial solid surface density profiles, the orbital period inside of which the embryo masses exceed the isolation mass is very consistent.\label{fig:surfden_iso}}
@@
 
-Next, we compare the effect of varying the initial solid surface density profile on the resulting planetesimal and embryo distribution.
-The final orbital period-eccentricity state of the particles is shown in figure \ref{fig:surfden_profiles}, with point sizes indicating the relative masses of the bodies.
+Next, we compare the effect of varying the initial solid surface
+density profile on the resulting planetesimal and embryo
+distribution. The final orbital period-eccentricity state of the
+particles is shown in figure \ref{fig:surfden_profiles}, with colors
+and point styles indicating the different initial surface density profiles,
+and with point sizes indicating the relative masses of the bodies.
 There is a clear trend between solid surface density at a given orbital period and the eccentricities of the remaining planetesimals.
@@
 
-We begin by investigating the `smoothness' of the accretion events that give rise to each embryo.
-Drawing from a common technique used for cosmological simulations (citation?), we divide growth events for a given body into `major' and `minor' mergers.
+We begin by investigating the ``smoothness'' of the accretion events
+that give rise to each embryo. Drawing from a common technique used
+for cosmological simulations (citation?), we divide growth events for
+a given body into ``major'' and ``minor'' mergers.
 Minor events are defined as any collision involving an initial planetesimal, while major events consist of any two larger bodies.
@@
 
-The difference in slope of the short vs longer period bodies in figure \ref{fig:minor_frac} indicates a difference in how the planetesimal-embryo populations interact in each region.
+The difference in slope of the short vs.\ long period bodies in figure \ref{fig:minor_frac} indicates a difference in how the planetesimal-embryo populations interact in each region.
 In the long period oligarchic growth region, embryos continue to accrete planetesimals as they grow and the minor mass fraction stays mostly flat.
@@
 
-Further evidence for the lack of gravitational scattering events can be seen in figure \ref{fig:acc_zones}.
-Here, we have chosen the 20 most massive bodies from the fdHi simulation and arranged them in order of present orbital period.
-The vertical black line indicates the orbital period of each embryo.
-The associated histogram for each body denotes where the planetesimals used to construct that embryo originated in the disk.
-The peaks of the histograms have all been normalized to the same value, so that the distributions only show the relative widths and locations of the feeding zones.
-Beyond the 60 day boundary, the ordering of the feeding zones and the embryo locations become much less consistent.
-This suggests that scattering events between embryos are much more common beyond this accretion mode boundary.
-In the inner region of the disk, close encounters between embryos often result in a merger, which allows them to grow beyond the isolation mass while only a minor alteration to their orbital period.
+Further evidence for the lack of gravitational scattering events in
+the inner region can be seen in figure \ref{fig:acc_zones}. Here, we
+have chosen the 20 most massive bodies from the fdHi simulation and
+arranged them in order of present orbital period. The vertical black
+line indicates the orbital period of each embryo. The associated
+histogram for each body denotes where the planetesimals used to
+construct that embryo originated in the disk. The peaks of the
+histograms have all been normalized to the same value, so that the
+distributions only show the relative widths and locations of the
+feeding zones. Beyond the 60 day boundary, the ordering of the feeding
+zones and the embryo locations become much less consistent. This
+suggests that scattering events between embryos are much more common
+beyond this accretion mode boundary. In the inner region of the disk,
+close encounters between embryos often result in a merger, which
+allows them to grow beyond the isolation mass with only a minor alteration to their orbital period.
 With few close encounters resulting in a scattering event, embryos are unable to move away from their birth location.
@@
 
-In all cases shown so far, the boundary between the standard oligarchic growth and the highly-efficient short period accretion region lies around 60 days in orbital period.
-The mode of accretion is set entirely by the local value of $\alpha$, which scales with both distance from the star and the bulk density of the planetesimals (see equation \ref{eq:alpha}).
-The artificial inflation of the collision cross section of the particles in our simulations, which is meant to reduce the computational expense, has the side effect of reducing the bulk densities.
-Because $\alpha \sim \rho_{pl}^{-1/3}$, increasing the particle sizes by a factor of f=6 reduces the orbital period at which $\alpha$ has a given value by a factor of approximately 15.
+In all cases shown so far, the boundary between the standard
+oligarchic growth and the highly-efficient short period accretion
+region lies around 60 days in orbital period. The mode of accretion is
+set entirely by the local value of $\alpha$, which scales with both
+distance from the star and the bulk density of the planetesimals (see
+equation \ref{eq:alpha}). The artificial inflation of the collision
+cross section of the particles in our simulations, which is meant to
+reduce the computational expense, has the side effect of reducing the
+bulk densities. Because $\alpha \sim \rho_{pl}^{-1/3}$, increasing the
+particle sizes by a factor of $f=6$ reduces the orbital period at which $\alpha$ has a given value by a factor of approximately 15.
 Therefore, one would expect the accretion boundary to lie near 5 days in orbital period for 3 g $cm^{-3}$ bodies.
 
-Although a simulation with f=1 is not computationally tractable, we can test whether the accretion boundary moves in the way we expect by modestly changing the value of $f$.
-In figure \ref{fig:f6f4}, we compare the fdHi simulation to a nearly identical run using f=4.
-In the top panel, the embryo masses in units of the isolation mass are shown as a function of orbital period.
-In the bottom panel, the value of $\alpha$ as a function of orbital period is shown for 3 g $cm^{-3}$ bodies with an artificial radius enhancement of f=1, 4 and 6.
-The horizontal dashed line indicates the value of alpha below which the accretion mode switches to oligarchic growth.
-Comparing the top and bottom panels, the intersection of the embryo masses and local isolation mass matches well with the orbital period at which $\alpha \sim 0.1$.
-Also shown by the curved dotted lines are the $\alpha$ curves for realistic-sized bodies with $\rho_{pl}$ = 1, 5 and 10 g $cm^{-3}$.
+Although a simulation with $f=1$ is not computationally tractable, we
+can test whether the accretion boundary moves in the way we expect by
+modestly changing the value of $f$. In figure \ref{fig:f6f4}, we
+compare the fdHi simulation to a nearly identical run using $f=4$. In
+the top panel, the embryo masses in units of the isolation mass are
+shown as a function of orbital period. In the bottom panel, the value
+of $\alpha$ as a function of orbital period is shown for 3 g $cm^{-3}$
+bodies with an artificial radius enhancement of $f=1$, 4 and 6. The
+horizontal dashed line indicates the value of alpha below which the
+accretion mode switches to oligarchic growth. Comparing the top and
+bottom panels, the intersection of the embryo masses and local
+isolation mass matches well with the orbital period at which $\alpha
+\sim 0.1$.  Also shown by the shaded region are $\alpha$ values for
+realistic sized bodies with $\rho_{pl}$ between 1 and 10 g cm$^{-3}$.
+% Also shown by the curved dotted lines are the $\alpha$ curves for
+% realistic-sized bodies with $\rho_{pl}$ = 1, 5 and 10 g $cm^{-3}$.
 In all cases, the accretion boundary still lies within the part of the disk in which solids would be expected to accumulate (citation?).
@@
     \includegraphics[width=0.5\textwidth]{figures/f6f4.png}
-    \caption{In the top panel, we show the final masses of the bodies from the fdHi and fdHif4 simulations in units of the isolation mass for $b = 2\sqrt{3}$.
+    \caption{In the top panel, we show the final masses of the bodies
+      from the fdHi and fdHif4 simulations in units of the isolation
+      mass for $\tilde{b} = 2\sqrt{3}$.
 The bottom panel shows the variation of $\alpha$ with orbital period for the bodies used in each case (solid curves).
 The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of the embryo mass distribution and isolation mass.
-The shaded region in the bottom panel show the values of alpha for realistic-sized (f=1) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4}}
+The shaded region in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4}}
 \end{center}
@@
 In this case, a collision can result in one of two outcomes: if the impact velocity is smaller than the mutual escape velocity of the colliding particles, defined as
-
 %TRQ: I corrected this off the top of my head: CHECK!
@@
 \end{equation}
-
-\noindent where $m_{1}, m_{2}$ and $r_{1}, r_{2}$ are the masses and radii of colliding particles 1 and 2, then the bodies perfectly merge.
-For impact velocities larger than $v_{mut, esc}$, no mass is transferred and the bodies undergo a completely elastic bounce.
+where $m_{1}, m_{2}$ and $r_{1}, r_{2}$ are the masses and radii of
+colliding particles 1 and 2, then the bodies perfectly merge. For
+impact velocities larger than $v_{mut, esc}$, no mass is transferred, and the bodies undergo a completely elastic bounce.
 Because there is no possibility of partial accretion, this model likely restricts growth more than the model used by \citet{leinhardt12}.
@@
 
+%TRQ: expand on this?  Compare figure 10 histograms for the two runs?
 Radial mixing appears to be enhanced by a partial collision model, along with smaller collision cross section inflation \citep{childs22}.
@@
 What is the migration timescale for the embryos to move to the inner edge of the disk? Maybe this section isn't terribly important and should be excluded?
+TRQ: I agree
 
@@
 
-In this work, we have demonstrated that planetary embryo formation operates in two distinct modes in a planet-forming disk.
-In the first mode, gravitational feedback from the growing embryos heats the remaining planetesimals and results in a dynamically cold population of embryos with a significant amount of residual planetesimals.
-This corresponds to the `oligarchic growth' case revealed by \citep{kokubo98}.
+In this work, we have demonstrated that planetary embryo formation
+operates in two distinct modes in a planet-forming disk. In the first
+mode, gravitational feedback from the growing embryos heats the
+remaining planetesimals and results in a dynamically cold population
+of embryos with a significant amount of residual planetesimals. This
+corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}.
 In the second mode, the gravitational feedback does not operate, embryos quickly sweep up all planetesimals, and grow about twice as large as is predicted by oligarchic growth.
@@
 
-We have demonstrated the outcome of both accretion modes through a low resolution parameter study.
+We have demonstrated the outcome of both accretion modes through a
+sparsely sampled parameter study.
 The initial planetesimal distribution can be described in terms of two dimensionless constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) and gravitational ($r_{g}$) radii, respectively.
@@
 
-So long as the density of the bodies does not significantly change as their mass distribution evolves, this ratio, and therefore the boundary between these accretion modes is set entirely by the distance from the star.
-Because both the physical and Hill radius of the bodies grows as $M^{1/3}$, the boundary between growth remains at a fixed location in the disk during the planetesimal accretion process.
+So long as the density of the bodies does not significantly change as
+their mass distribution evolves, this ratio, and therefore the
+boundary between these accretion modes is set entirely by the distance
+from the star. Because both the physical and Hill radii of the bodies
+grows as $M^{1/3}$, the boundary between growth remains at a fixed
+location in the disk during the planetesimal accretion process.
 
-We have verified this fact by testing the outcome of the planetesimal accretion process for a variety of solid surface density profiles.
-Although altering the surface density does affect the resulting masses of the embryos, the location of the boundary separating the growth modes is remarkably similar between all of our simulations.
+We have verified this fact by testing the outcome of the planetesimal
+accretion process for a variety of solid surface density
+profiles. Although altering the surface density does affect the
+resulting masses of the embryos, the location of the boundary
+separating the growth modes is remarkably similar among all of our simulations.
 We have verified this by comparing the resulting embryo masses to the isolation mass, in addition to highlighting qualitative differences in the accretion history of embryos on both sides of the boundary.
@@
 
-To date, there have been no other studies of planetesimal accretion with such a large value of $\alpha$.
-However, a value of $\alpha = 1$ corresponds to the Roche limit of a three-body system, and so one might wonder this high-$\alpha$ accretion mode might be relevant for a circumplanetary system.
-There is a small collection of previous works which use N-body methods to examine in-situ satellitesimal accretion \citep{ida97, richardson00, ida20}.
-\citet{ida97} was able to form 1-2 large moon just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over.
+To date, there have been no other studies of planetesimal accretion
+with such a large value of $\alpha$. However, a value of $\alpha = 1$
+corresponds to the Roche limit of a three-body system, and so one
+might wonder this high-$\alpha$ accretion mode might be relevant for a
+circumplanetary system. There is a small collection of previous works
+which use N-body methods to examine in-situ satellitesimal accretion
+\citep{ida97, richardson00, ida20}. \citet{ida97} was able to form 1-2
+large moons just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over.
 The widest disk they modeled extended out to $\alpha = 0.5$.
@@
 
-To connect these accretion modes to the final orbital architecture, and to ultimate determine what implications an in situ formation model has for the growth of STIPs, we will continue to evolve the final simulation snaphots presented here with a hybrid symplectic integrator.
+To connect these accretion modes to the final orbital architecture,
+and to ultimately determine what implications an in situ formation model has for the growth of STIPs, we will continue to evolve the final simulation snaphots presented here with a hybrid symplectic integrator.
 The final distribution of planets formed, along with composition predictions generated by applying cosmochemical models to our initial planetesimal distributions and propagating compositions through the merger trees, will be examined in a follow-up paper.
+
+\section{Acknowledgements}
+
+NSF, XSEDE.
 

### 2022-08-05 main.tex
More edits through sections 1-3

@@
 \citep{chambers98}.
-%TRQ "Suddenly" seems a drastic term to use here.
-Suddenly, the oligarchics are no longer on isolated, stable orbits and
-coalesce to form Earth-sized planets through a series of extremely
-energetic, giant impacts \citep{kokubo02, raymond05, raymond06}.
-%TRQ new paragraph here?
+As a consequence of the instability, the oligarchics are no longer
+on isolated, stable orbits and coalesce to form Earth-sized planets'
+through a series of extremely energetic, giant 
+impacts \citep{kokubo02, raymond05, raymond06}.
+
 Due to the relative ease of modeling the early dust coagulation phases
@@
 by Keplerian frequency $\Omega$ can be written as $n \Gamma v$, where
-$n = \Sigma_{pl} \Omega / 2 m_{pl} v$, $\Gamma$ is the effective
+$n = \Sigma_{pl} \Omega / 2 m_{pl} v$ (where we have assumed that the scale height of the planetesimal disk goes as $\Omega/(2v)$. $\Gamma$ describes the effective
 collision cross section and $v$ is the typical encounter velocity
 between planetesimals.
-% TRQ: mention that $v$ is related to the velocity dispersion of the
-% planetesimals.  Also: mention that the scale height of the disk is
-% assumed to be \Omega/(2v)
+For a swarm of planetesimals on randomly oriented orbits, $v$ is typically
+taken to the rms velocity, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \citep{lissauer93}:
+\begin{equation}\label{eq:ecc_vel}
+	\left< v^{2} \right>^{1/2} = \left( \frac{5}{4} \left< e^{2} \right>^{1/2} + \left< i^{2} \right>^{1/2}  \right) v_{k}.
+\end{equation}
 Assuming that every collision results in a perfect merger, the growth rate of a planetesimal is given by
@@
 
-In the case where the collision cross section, $\Gamma$, depends only
+In the case where the collision cross section, depends only
 on the physical size of the planetesimals, the growth scales linearly
@@
 However, bodies larger than $\sim 100$ km in size are expected to exert a significant gravitational force on each other during encounters and the collision cross section depends on both the size of the bodies and their encounter velocities.
-In this case, $\Gamma = \Gamma_{geo} \left( 1 + v_{esc}^2 / v^2 \right)$, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
-%TRQ: reference Safranov?
+In this case, $\Gamma = \Gamma_{geo} \left( 1 + v_{esc}^2 / v^2 \right)$ \citep{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
 
@@
 \end{equation}
-%TRQ: changed this to match Ida & Makino 1993.
 where $\ln \Lambda$ is the Coulomb logarithm,
@@
 gravitational focusing and throttles the growth rate. Around the time
-that the massive runaway bodies make up about 50 percent of the solid
-surface density
-%TRQ: citation needed.
-(citation), a period of less vigorous ``oligarchic'' growth commences, in which the few largest bodies continue to accrete planetesimals at similar rates.
+that the mass of the runaway bodies exceeds the mass of the planetesimals
+by a factor of $\sim 50-100$ (depending on the orbital period)
+\citep{ida93} a phase of less vigorous ``oligarchic'' 
+growth commences, in which the few largest bodies continue to 
+accrete planetesimals at similar rates.
 
-The picture described above relies upon an important factor, which is that the mass distribution evolves slow enough for gravitational stirring to maintain energy equipartition.
+The picture described above relies upon an important assumption, which is that the mass distribution evolves slow enough for gravitational stirring to maintain energy equipartition.
 In other words, the relaxation timescale must remain short relative to the growth timescale.
@@
 $$
-(citation) where $\left< e^2 \right>^{1/2}$ and $\left< i^2
+\citep{lissauer93} where $\left< e^2 \right>^{1/2}$ and $\left< i^2
 \right>^{1/2}$ are the eccentricity and inclination dispersions of the
@@
 These scaling considerations motivate the range of parameters in the
-following numerical experiments as explore the different regimes.
-
-% Need a transition to next section here.
-
-% analytic conditions for runaway and orderly growth
-% not clear what happens as gravitational focusing factor approaches 1
-
-% mass and velocity distributions both evolve, two-body relaxation time works to describe velocity evolution when dispersion dominated
-% if relaxation time shorter than collision time, oligarchic growth operates
-% but what happens if these timescales are flipped? not clear, because the timescales themselves depend on mass and velocity, which both evolve with time
-
-% a cleaner formalism: compare planetesimal size to hill and gravitational radius (alpha, beta)
-% alpha does not evolve with time, beta will tend towards 1
-
-% motivation for n-body simulations: what do masses and orbital properties of embryos look like as we change alpha and beta?
-% at short period, alpha and beta are large
+following numerical experiments as we explore the different regimes.
 
@@
 velocity calculated at the opening ``kick''. For each body, any
-neighboring particles which fall within a search ball of radius XXX
-$fill in later$ are tested for an imminent collision. In the case that
+neighboring particles which fall within a search ball of radius
+$2 \Delta T v + 2 r_{pl}$, where $\Delta T$ is the current timestep size
+for the particle and $v$ is magnitude of its heliocentric velocity,
+ are tested for an imminent collision. In the case that
 a collision is detected, the particles are merged into a single larger
@@
 $\Omega$, and mean anomaly M for each body is drawn from a uniform
-distribution $\in [0, 2 \pi)$. The inclination dispersion $\left<
-i^{2} \right>^{1/2}$ is chosen to be half the eccentricity
-dispersion $\left< e^{2} \right>^{1/2}$ \citep{ida93a}.
-% Mention Rayleigh distribution: TRQ: yes!
+distribution $\in [0, 2 \pi)$. The inclinations and eccentricities are drawn
+from a Rayleigh distribution with
+$\left< i^{2} \right> = 1/2 \left< e^{2} \right>$ \citep{ida93a}.
 
@@
 fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &   \\
-fdLo                & $1 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &   \\ \hline
+fdLo                & $5 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &   \\ \hline
 \end{tabular}

### 2022-08-08 main.tex
More edits

@@
 and remaining planetesimals end up in a dynamically cool state,
-compared to the initial conditions.
-%TRQ albeit for small alpha, only slightly cooler.
-(Are the inelastic collisions playing a significant role here?)
+compared with the initial conditions. This is due to kinetic energy 
+being lost as particles inelastically collide. One final point to note 
+is the difference between eccentricities of the protoplanets in the 
+large $\alpha$, large $\beta$ and the small $\alpha$,
+large $\beta$ case. The dynamically cooler result of the latter case
+is likely due to the dominant role that inelastic collisions play here.
 
@@
 
-To investigate whether any of these planetesimal disks underwent
+To investigate whether any of these planetesimal rings underwent
 runaway growth, we examine the time evolution of the maximum and mean
-masses in each case. The ratio $m_{max}/\left< m \right>$ is plotted
+masses in each simulation. The ratio $m_{max}/\left< m \right>$ is plotted
 in figure \ref{fig:alpha_beta_evo}. On this plot, a positive slope
-indicates that the growth rate is accelerating with mass, which is
-evident at various times in all four cases. Even with a large value of
+indicates that the maximum and mean masses are diverging (i.e.
+the growth rate is accelerating with mass), which is
+evident for every case we have tested. Even with a large
 $\beta$, which means that the effective collision cross section is
 very near the geometric value, runaway growth still appears to
-operate. This seems to imply that, as bodies collide and grow, the
-relative increase in their gravitational focusing factors, rather than
-their absolute size, is what drives the system towards runaway
-growth. Although larger encounter velocities will lengthen the growth
+operate. The ubiquity of the early positive trends in this figure indicates
+that, as bodies collide and grow the
+relative difference in gravitational focusing factors between bodies
+is what drives the system towards runaway
+growth. Although larger encounter velocities lengthen the growth
 timescales, this mode of growth appears to be inevitable, so long as
-gravity is the dominant force in the system.
-% TRQ: also mention the negative slope?
+gravity is the dominant force in the system. For the large $\alpha$
+cases, the curves in this figure eventually turn over and begin to decline.
+Upon inspecting the simulation snapshots, we find that this trend is
+driven by an increase in the average mass as the planetesimal population
+becomes depleted. One should expect that the same thing will eventually
+occur for small $\alpha$, although many more timesteps are required to
+begin to run out of planetesimals.
 
-Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions, controls the qualitative outcome of accretion.
-Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will allow oligarchic growth to operate.
+Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions (the physical and Hill radius both scale with $M^{1/3}$, so $\alpha$ stays constant as bodies grow), controls the qualitative outcome of accretion.
+Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will facilitate oligarchic growth.
 In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and embryos \citep{weidenschilling89, ida90}.
@@
 \begin{table}
-% I'm going to replace the fdLo simulation with a lower resolution version m_pl = 5e22 for consistency
-% Originally wanted to run everything at m_pl = 1e22, which corresponds to 100km bodies, but this wasn't feasible at higher Sigma
 \caption{Summary of Full Disk Simulations Run}
@@
 
-Motivated by the apparent dependence of accretion modes on $\alpha$,
+Motivated by the dependence of accretion modes on $\alpha$,
 we next investigate whether this highly efficient, non-oligarchic
 growth mode should be expected to operate in a typical planet-forming
-disk.
-Given the dearth (TRQ: why is this a reason for a wide disk?) of short period terrestrial planets observed around M stars (citation), we model a series of wide planetesimal disks, which span from 1 to 100 days in orbital period orbiting a late-type M star of mass 0.08 $M_{\odot}$.
+disk. Given that N-body simulations of short-period terrestrial planet formation 
+typically begin with a chain of neatly-spaced, isolation mass 
+(see \citet{kokubo00} eq. 20) protoplanets, it is pertinent to determine 
+whether the high $\alpha$ growth mode we revealed
+in the previous section invalidates this choice of initial conditions.
+
+ Given the dearth of short-period terrestrial planets observed around M stars (e.g.
+TRAPPIST-1), we chose to model a series of wide planetesimal disks, which span from 1 to 100 days in orbital period orbiting a late-type M star of mass 0.08 $M_{\odot}$.
 For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this orbital period range corresponds to $\alpha \in (0.7, 0.05)$.
@@
 \begin{equation}
-	\Sigma(r) = \left( \frac{M_{*}}{M_{\odot}} \right) A \Sigma_{MMSN} \left( \frac{r}{1 AU} \right)^{-\alpha},
+	\Sigma(r) = \left( \frac{M_{*}}{M_{\odot}} \right) A \Sigma_{\mathrm{MMSN}} \left( \frac{r}{1 \mathrm{AU}} \right)^{-\delta},
 \end{equation}
-%TRQ: should we use a different greek letter for the power law index?
 where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g cm$^{-2}$ is surface density of the minimum-mass solar nebula \citep{hayashi81} at 1 AU, and $A$ is an enhancement factor.

### 2022-08-16 main.tex
More edits

@@
 we next investigate whether this highly efficient, non-oligarchic
-growth mode should be expected to operate in a typical planet-forming
+growth should be expected to operate near the innermost regions of a typical planet-forming
 disk. Given that N-body simulations of short-period terrestrial planet formation 
@@
 Given the dearth of short-period terrestrial planets observed around M stars (e.g.
-TRAPPIST-1), we chose to model a series of wide planetesimal disks, which span from 1 to 100 days in orbital period orbiting a late-type M star of mass 0.08 $M_{\odot}$.
+TRAPPIST-1), we chose to model the evolution of a series of wide planetesimal disks, which span from 1 to 100 days in orbital period, orbiting a late-type M star of mass 0.08 $M_{\odot}$.
 For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this orbital period range corresponds to $\alpha \in (0.7, 0.05)$.
@@
 
-Four wide disk simulations are run in total (see table \ref{tab:sims}). In each case, the solid surface density follows a power law profile
+Four wide-disk simulations are run in total (see table \ref{tab:sims}). In each case, the solid surface density follows a power law profile
 \begin{equation}
@@
 In the first case (fdHi), we model a disk that follows a MMSN power law slope, with the overall normalization enhanced by a factor of 100.
-This choice of parameters for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \citep{hansen12}.
-Additionally, we vary the power law index (fdHiShallow, fdHiSteep) and overall normalization (fdLo) of the solids profile.
+This choice of normalization for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \citep{hansen12}.
+Additionally, we vary the power law index (fdHiShallow, fdHiSteep) and overall normalization (fdLo) of $\Sigma(r)$.
 
@@
 In addition to the mutual gravitational forces, a Stokes drag force from to the gas disk is applied to each particle, following the prescription described in section 2.2.1 of \citet{morishima10}.
-The surface density and temperature profile are identical to those used to construct the initial conditions and the cylindrical coordinate system is centered on the host star.
 
@@
 In the case of the fdHi simulation, there are nearly 1 million
-particles, whose orbital periods vary by two orders of magnitude. Due
-to the very short interaction timescales near the inner edge of the
-disk, a fixed timestep size would required a prohibitively large
+particles, whose orbital periods vary by two orders of magnitude. Because the
+interaction timescales near the inner edge of the
+disk are exceedingly short, a fixed timestep size would required a prohibitively large
 number of steps to follow planetesimal growth throughout the entire
@@
 based on their most recently calculated gravitational
-acceleration. (This scheme is used on almost all works using ChaNGa,
-and is common among large-scale simulation codes.)
-
-This more efficient scheme, however, introduces two additional issues
-related to particles interacting on different timesteps. First,
+acceleration. \footnote{This scheme is used on almost all works using ChaNGa,
+and is common among large-scale simulation codes.}
+
+This more efficient scheme introduces two issues, however. Firstly,
 momentum is not completely conserved when bodies switch timesteps. The
@@
 this problem manifests itself as the development of a V-shaped gap in the semimajor axis-eccentricity plane, which is centered on the boundary itself.
-To correct this problem, we introduce a second timestepping criterion, which is based on the gravitational acceleration on the particle by the central star at perihelion.
+To correct this problem, we introduce a slightly modified timestepping criterion, which is based on the expected gravitational acceleration of the particle at pericenter.
 Only in the case of a close encounter with another planetesimal (in which the acceleration is no longer dominated by the star) is the timestep allowed to reduce based on the original criterion.
@@
 As in the previous case, momentum is not completely conserved because the most recent `kick' steps did not happen simultaneously for these bodies.
-Early in the simulation, we find that runaway growth tends to trigger first at the timestep boundaries.
-Unfortunately, this issue carries itself forward through the embryo formation phase and protoplanets tend to form at the boundaries.
+Early in the simulation, we find that runaway growth tends to initiate at the timestep boundaries.
+This issue carries itself forward through the embryo formation phase, and protoplanets tend to form at the boundaries.
 To correct this issue, we ignore collisions between bodies on different timesteps early in the simulation.
-We find that enabling multi-timestep collisions after the maximum mass grows by a factor of 10 prevents any artifacts from forming at the timestep boundaries, while also minimizing the number of `skipped' collisions\footnote{In the case of fdHi, only about 20 collisions out of an eventual 900,000 are ignored.}.
+We find that preventing multi-timestep collisions until after the maximum mass grows by a factor of 10 prevents any artifacts from developing at the timestep boundaries, while also minimizing the number of `skipped' collisions\footnote{In the case of fdHi, only about 20 collisions out of an eventual 900,000 are ignored.}.
 
@@
 \caption{Final Properties of Full Disk Simulations}
-%TRQ: the mass numbers in this table look wrong.
 \begin{tabular}{lllll} \hline \hline
 Name     & $M_{PP}^a$ & $T_{int}^b$ & $T_{int 1}^c$ &  \\ \hline
-fdHi                 & 100                                                         & 1.5                              & 4  &  \\
-fdHiShallow     & 100                                                        & 0.5                              & 4  &  \\
-fdHiSteep       & 100                                                         & 2.5                              & 4 &  \\
-fdLo                & 1                                                             & 1.5                              & 4 &  \\ \hline
+fdHi                 &  1.00                                                         & 456                              & 16,377  &  \\
+fdHiShallow    &  1.19                                                        & 456                              & 16,377  &  \\
+fdHiSteep       &  1.08                                                         & 456                              & 16,377 &  \\
+fdLo                &  1.77 $\times 10^{-3}$                                  & 3,713                              & 133,651 &  \\ \hline
 \end{tabular}
@@
 
-In all four simulations, the timescales for embryo formation depend on
-the chosen surface density profile, along with the particular location
-in the disk. Protoplanets form first near the inner edge of the disk,
+The timescales for embryo formation depend on
+the chosen surface density profile, along with the local orbital
+timescale. Protoplanets form first at the inner edge of the disk,
 where the dynamical timescales are short. Growth proceeds in an
 inside-out fashion, with the outermost regions of the disk completing
-the protoplanet assembly phase last. This fact is not typically
-accounted for in planet formation simulations, and appears to be an
+the protoplanet assembly phase last. This radial timescale dependence is not typically
+accounted for in planet formation simulations\footnote{Instead, the innermost protoplanets 
+patiently `wait' for this phase of evolution to complete everywhere in the disk}, and appears to be an
 important component to forming realistic solar system analogs
@@
 
-We show the final state of the ``fiHi'' simulation in figure \ref{fig:fulldisk_e_m}.
-In the top panel, the initial (contours) and final (points) state of the simulation is shown in orbital period and eccentricity.
+We show the final state of the ``fdHi'' simulation in figure \ref{fig:fulldisk_e_m}. In the top panel,
+the initial (contours) and final (points) state of the simulation is shown in the orbital period-eccentricity plane.
 The size of the points indicates the relative mass of the bodies.
@@
 where $\tilde{b}$ is the size of the feeding zone in units
-of Hill radii. For a body on a circular orbit $\tilde{b} = 2
-\sqrt{3}$, while a protoplanet formed by oligarchic growth typically
-has $\tilde{b} = 10$ \citep{kokubo98}.
-%TRQ there is no orange line in the figure.
+of Hill radii. For two bodies on circular, non-inclined orbits,  $\tilde{b} = 2
+\sqrt{3}$ is the smallest orbital separation that produces a non-negative Jacobi energy
+and permits a close encounter (see \citet{naka88}).
 The isolation mass is plotted in blue and orange for these two values of $\tilde{b}$, respectively.
@@
 Protoplanets in this region appear to closely follow the isolation mass curve for $\tilde{b} = 10$.
-Exterior to the boundary, the residual planetesimal population is much more numerous, and protoplanets more closely follow the $\tilde{b} = 2 \sqrt{3}$ curve.
-This tentatively suggests that the transition between the low $\alpha$ and high $\alpha$ accretion modes seen in section \ref{sec:narrow} happens near this location.
-
-% Also mention that no eccentricity difference between large and small alpha regions, as we saw in the narrow annulus simulations
-
-In figure (removed), we show $\alpha$ (left axis) and the fraction of remaining planetesimals (right axis) as a function of orbital period.
+Exterior to the boundary, the residual planetesimal population is much more pristine, and protoplanets more closely follow the $\tilde{b} = 2 \sqrt{3}$ curve.
+This suggests that the transition between the low $\alpha$ and high $\alpha$ accretion modes seen in section \ref{sec:narrow} happens near this location.
+
+In section \ref{sec:narrow}, we postulated that the increased importance of inelastic damping in the inner, non-oligarchic growth region of the disk should lower the overall eccentricity of the protoplanets there.
+This behavior is not immediately apparent in the top panel of figure \ref{fig:fulldisk_e_m}.
+There are, however, a couple of factors in the wide disk simulations that could make this extra dynamical cooling mechanism difficult to see.
+Firstly, the initial eccentricity distributions of the inner and outer disk are different because of the dependence of the viscous stirring and gas drag timescales on orbital period.
+Additionally, the protoplanet formation timescales for the inner and outer disk are vastly different, rendering a comparison between these regions at the same moment in time inappropriate.
+
+%In figure (removed), we show $\alpha$ (left axis) and the fraction of remaining planetesimals (right axis) as a function of orbital period.
 Here, the fraction of remaining planetesimals is measured by dividing the disk into 15 semimajor axis bins and using the profile function in {\sc pynbody} to measure the total solid surface density $\Sigma$ in each of those bins, and also the planetesimal surface density $\sigma$.
@@
 To ensure that the boundary seen near 60 days in orbital period is not
-simply a transient product of the inside out growth throughout the
+simply a transient product of the inside-out growth throughout the
 disk, we examine the time evolution of $\sigma/\Sigma$ at multiple
@@
 $\sigma/\Sigma$ is plotted as a function of time in 10 orbital period
-bins.
-%TRQ: width of the bins?
+bins, each with a width of 10 days.
 Bins interior to 60 days are indicated with a dashed line, while those exterior are indicated with a solid line.
-The planetesimal surface density fraction has decelerated and is approaching an asymptotic value in all cases.
-In the inner disk, this is driven by the near-total depletion of the planetesimal reservoir.
-In the outer disk, dynamical friction between the embryos and planetesimals throttles subsequent accretion.
-
-% Since we are using f=6, do we want to stick to plotting things in terms of timestep number, and then provide rescaled time estimates at the end?
+In all radial bins, the planetesimal surface density is approaching an asymptotic value.
+In the inner disk, this value asymptotes to zero as the planetesimal population completely depletes.
+In the outer disk, dynamical friction between the embryos and planetesimals eventually throttles subsequent accretion and leaves $\sim$ 10 to 20 percent of the mass surface density as planetesimals.
 
@@
 The transition visible near 60 days in all cases also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
-% fdLo needs to run a bit longer
 

### 2022-08-16 main.tex
Replace y values in figure 8 with b_tilde

@@
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/surfden_iso.png}
-    \caption{Masses of the remaining bodies from the simulations
-      listed in table \ref{tab:sim_properties}, in units of the
-      isolation mass for $\tilde{b} = 2 \sqrt{3}$.
-Despite the vastly different initial solid surface density profiles, the orbital period inside of which the embryo masses exceed the isolation mass is very consistent.\label{fig:surfden_iso}}
+    \includegraphics[width=0.5\textwidth]{figures/surfden_b.png}
+    \caption{Feeding zone width (see equation \ref{eq:iso} required to produce the final masses for the protoplanets from the simulations listed in table \ref{tab:sim_properties}.
+The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$.
+Despite the vastly different initial solid surface density profiles, the feeding zone width reaches the circular orbit value around $\sim$ 60 days.
+\label{fig:surfden_b}}
 \end{center}
@@
 
-In figure \ref{fig:surfden_iso}, we compare the masses of the resulting protoplanets and planetesimals in all four simulations to each other.
+In figure \ref{fig: surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $\tilde{b}$ (see equation \ref{eq:iso}).
+Here, we assume that each embryo has reached its isolation mass, and that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the size of its feeding zone, which is set by the dynamics relevant at that location in the disk.
+By plotting the derived value of $\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more clearly visible.
+As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the minimum feeding zone width that a body can have.
+In all four simulations, the feeding zone width exceeds the minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days.
+The orbital periods at which this transition occurs are remarkably similar, despite the vastly different solid surface density profiles used.
+This similarity indicates that the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
+
+%In figure \ref{fig:surfden_iso}, we compare the masses of the resulting protoplanets and planetesimals in all four simulations to each other.
 Here, the masses are scaled by the isolation mass at the given orbital distance (see equation \ref{eq:iso}).

### 2022-08-16 makeFig.py

@@ -467,6 +467,36 @@ def plot_surfden_iso():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
+def plot_surfden_b():
+	file_str = 'figures/surfden_b.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	def get_btilde(pl, prof0):
+		surf_den = (prof0['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)
+		mp = (pl['mass']*u.M_sun).to(u.g).value
+		mCeng = (mCentral*u.M_sun).to(u.g).value
+		aCm = (pl['a']*u.AU).to(u.cm).value
+		surf_den_at = np.interp(pl['a'], prof0['rbins'], surf_den)
+		return mp**(2./3.)*(3*mCeng)**(1./3.)/(2*np.pi*aCm**2*surf_den_at)
+
+	fig, axes = plt.subplots(figsize=(8,6))
+
+	axes.scatter(per.value, get_btilde(plVHi, p_vhi_ic), label='fdHi', edgecolor='black')
+	axes.scatter(perSt.value, get_btilde(plVHiSt, p_vhi_ic_st), label='fdSteep', edgecolor='black')
+	axes.scatter(perSh.value, get_btilde(plVHiSh, p_vhi_sh), label='fdShallow', edgecolor='black')
+	axes.scatter(perLo.value, get_btilde(plLo, p_lo_ic), label='fdLo', edgecolor='black')
+	axes.axhline(2*np.sqrt(3), ls='--')
+
+	axes.set_xlim(-5, 100)
+	axes.set_yscale('log')
+	axes.set_ylim(1, 200)
+	axes.set_xlabel('Orbital Period [d]')
+	axes.set_ylabel(r'Required $\tilde{b}$')
+	axes.legend()
+
+	plt.savefig(file_str, format=fmt, bbox_inches='tight')
+
 # Extract information about the 'surviving' members from a collision table
 def coll_info(df):
     mass_mask = df['m1'].values >= df['m2'].values
@@ -737,8 +767,9 @@ def plot_frag_evo():
 #plot_fulldisk_e_m()
 #plot_alpha_pl_frac()
 #plot_pl_frac_time()
-plot_surfden_profiles()
-plot_surfden_iso()
+#plot_surfden_profiles()
+#plot_surfden_iso()
+plot_surfden_b()
 #plot_smooth_acc()
 #plot_acc_zones()
 #plot_f6f4()

### 2022-08-16 makeFig.py
Update figures

@@ -28,6 +28,7 @@ clobber = True
 fmt = 'png'
 s = 0.005
 lw = 4
+refmass = (1*u.M_earth).to(u.M_sun).value
 
 num_bins = 50
 mCentral = 0.08
@@ -84,7 +85,7 @@ perSh = 2*np.pi*np.sqrt((plVHiSh['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.
 snap = pb.load('data/fullDiskLoLarge.ic')
 plLoIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_lo_ic = pb.analysis.profile.Profile(plLoIC.d, bins=bins)
-snap = pb.load('data/fullDiskLoLarge.2840000')
+snap = pb.load('data/fullDiskLoLarge.4640000')
 plLo = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_lo = pb.analysis.profile.Profile(plLo.d, bins=bins)
 perICLo = 2*np.pi*np.sqrt((plLoIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
@@ -169,7 +170,6 @@ def plot_alpha_beta():
 		pl0 = ko.orb_params(snap0, isHelio=True, mCentral=mcen)
 		snap = pb.load('data/'+prefix+'.end')
 		pl = ko.orb_params(snap, isHelio=True, mCentral=mcen)
-		print()
 		ax.scatter(pl0['a'], pl0['e'], s=pl0['mass']/np.max(pl['mass'])*500)
 		ax.scatter(pl['a'], pl['e'], s=pl['mass']/np.max(pl['mass'])*500)
 		ax.text(0.85, 0.95, title, transform=ax.transAxes, ha='center', va='center')
@@ -297,7 +297,7 @@ def plot_fulldisk_e_m():
 	l = np.logspace(np.log10(30), np.log10(np.max(H)), 10)
 	c = axes.contour(binsX, binsY, np.flipud(np.rot90(H)), colors='black', linewidths=0.2, levels=l)
 
-	axes.scatter(per.value, plVHi['e'], s=plVHi['mass']/np.max(plVHi['mass'])*500)
+	axes.scatter(per.value, plVHi['e'], s=plVHi['mass']/refmass*500)
 	axes.set_ylabel('Eccentricity')
 	axes.set_xlim(p_min, p_max)
[…]

### 2022-09-07 main.tex
Remove duplicate equation relating velocity and eccentricity

@@
 as a function of orbital period. Here, the encounter velocity is
-described by
-$$
-v = \left( 5/8 \left< e^2 \right>^{1/2} + \left< i^2 \right>^{1/2}
-\right)^{1/2} v_{k},
-$$
-\citep{lissauer93} where $\left< e^2 \right>^{1/2}$ and $\left< i^2
-\right>^{1/2}$ are the eccentricity and inclination dispersions of the
-planetesimal disk and $v_{k}$ is the Keplerian velocity. For
+described by equation \ref{eq:ecc_vel}. For
 simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2
@@
       planetesimals. For larger values of $\alpha$, the mass
-      distribution takes on a more unimodal (TRQ: uniform?) form.
-As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.\label{fig:alpha_beta_mass}}
+      distribution takes on a more uniform form. As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.\label{fig:alpha_beta_mass}}
 \end{center}

### 2022-09-07 main.tex
Fix up figure 8

@@
 
-In figure \ref{fig: surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $\tilde{b}$ (see equation \ref{eq:iso}).
+In figure \ref{fig:surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $\tilde{b}$ (see equation \ref{eq:iso}).
 Here, we assume that each embryo has reached its isolation mass, and that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the size of its feeding zone, which is set by the dynamics relevant at that location in the disk.

### 2022-09-07 makeFig.py

@@ -523,25 +523,32 @@ def plot_surfden_b():
 	axes = ax[0]
 	axes.scatter(per.value, get_btilde(plVHi, p_vhi_ic), label='fdHi', edgecolor='black')
 	axes.axhline(2*np.sqrt(3), ls='--')
+	axes.set_ylabel(r'Required $\tilde{b}$')
+	axes.set_title('fdHi')
 	axes = ax[1]
 	axes.scatter(perSt.value, get_btilde(plVHiSt, p_vhi_ic_st), label='fdSteep', edgecolor='black')
 	axes.axhline(2*np.sqrt(3), ls='--')
+	axes.set_ylabel(r'Required $\tilde{b}$')
+	axes.set_title('fdHiSteep')
 	axes = ax[2]
 	axes.scatter(perSh.value, get_btilde(plVHiSh, p_vhi_sh), label='fdShallow', edgecolor='black')
 	axes.axhline(2*np.sqrt(3), ls='--')
+	axes.set_ylabel(r'Required $\tilde{b}$')
+	axes.set_title('fdHiShallow')
 	axes = ax[3]
 	axes.scatter(perLo.value, get_btilde(plLo, p_lo_ic), label='fdLo', edgecolor='black')
 	axes.axhline(2*np.sqrt(3), ls='--')
+	axes.set_ylabel(r'Required $\tilde{b}$')
+	axes.set_title('fdLo')
 
 	axes.set_xlim(-5, 100)
 	#axes.set_yscale('log')
 	axes.set_ylim(0, 20)
 	axes.set_xlabel('Orbital Period [d]')
-	axes.set_ylabel(r'Required $\tilde{b}$')
 	#axes.legend()
 
 	plt.tight_layout()
-	plt.subplots_adjust(wspace=0, hspace=0)
+	#plt.subplots_adjust(wspace=0, hspace=0)
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 # Extract information about the 'surviving' members from a collision table
@@ -865,9 +872,9 @@ def plot_frag_evo():
 #plot_pl_frac_time()
 #plot_surfden_profiles()
 #plot_surfden_iso()
-#plot_surfden_b()
+plot_surfden_b()
 #plot_smooth_acc()
-plot_acc_zones()
+#plot_acc_zones()
 #plot_f6f4()
 #plot_frag_ecc()
 #plot_frag_evo()

### 2022-09-07 main.tex
Edits through section 5.4

@@
 and permits a close encounter (see \citet{naka88}).
+In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend to space themselves apart by $\tilde{b} = 10$ (although it should be noted that they do not consume all of the planetesimals within this distance).
 The isolation mass is plotted in blue and orange for these two values of $\tilde{b}$, respectively.
@@
 Firstly, the initial eccentricity distributions of the inner and outer disk are different because of the dependence of the viscous stirring and gas drag timescales on orbital period.
-Additionally, the protoplanet formation timescales for the inner and outer disk are vastly different, rendering a comparison between these regions at the same moment in time inappropriate.
+Additionally, the protoplanet formation timescales for the inner and outer disk are vastly different, making a comparison between these regions at the same moment in time somewhat inappropriate.
 
@@
 disk, we examine the time evolution of $\sigma/\Sigma$ at multiple
-locations. In figure \ref{fig:pl_frac_time}, the value of
+orbital periods. In figure \ref{fig:pl_frac_time}, the value of
 $\sigma/\Sigma$ is plotted as a function of time in 10 orbital period
 bins, each with a width of 10 days.
-Bins interior to 60 days are indicated with a dashed line, while those exterior are indicated with a solid line.
+Bins interior to 60 days are shown by a dashed line, while those exterior are shown as a solid line.
 In all radial bins, the planetesimal surface density is approaching an asymptotic value.
-In the inner disk, this value asymptotes to zero as the planetesimal population completely depletes.
-In the outer disk, dynamical friction between the embryos and planetesimals eventually throttles subsequent accretion and leaves $\sim$ 10 to 20 percent of the mass surface density as planetesimals.
+In the inner disk, this value asymptotes to zero as the planetesimal population entirely depletes.
+In the outer disk, dynamical friction between the embryos and planetesimals eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals.
+It should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimal mass should remain out of reach of the protoplanets.
 
@@
 
-Next, we compare the effect of varying the initial solid surface
-density profile on the resulting planetesimal and embryo
-distribution. The final orbital period-eccentricity state of the
-particles is shown in figure \ref{fig:surfden_profiles}, with colors
-and point styles indicating the different initial surface density profiles,
-and with point sizes indicating the relative masses of the bodies.
-There is a clear trend between solid surface density at a given orbital period and the eccentricities of the remaining planetesimals.
-This trend is largely set by the initial conditions, as the gravitational stirring is more vigorous when bodies are packed together closely and higher eccentricities are required to produce an equilibrating aerodynamic drag force (see equations \ref{eq:vs_timescale} and \ref{eq:ts_stokes}).
-Despite having significantly different masses, the planetary embryos formed in each case have remarkably similar eccentricities.
+Next, we investigate how the resulting planetesimal and protoplanet distribution
+changes as we vary the initial solid surface density profile.
+The final orbital period-eccentricity state of the
+particles in the fdHi, fdHiSteep, fdHiShallow and fdLo simulations are shown in figure \ref{fig:surfden_profiles}, with point sizes indicating the relative masses of the bodies.
+In all cases, the inner disk is largely depleted of planetesimals, while the outer disk contains a bimodal population of planetesimals and embryos, with a clear separation in eccentricity between the two.
+Despite having significantly different masses, the planetary embryos formed in all simulations have remarkably similar eccentricities.
 This is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which offsets the fact that the initial bodies started off in a dynamically hotter state.
@@
 In all four simulations, the feeding zone width exceeds the minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days.
-The orbital periods at which this transition occurs are remarkably similar, despite the vastly different solid surface density profiles used.
-This similarity indicates that the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
+The orbital periods at which this transition occurs are quite similar between simulations, despite the vastly different solid surface density profiles used.
+This indicates that the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
 

### 2022-09-07 makeFig.py

@@ -870,9 +870,9 @@ def plot_frag_evo():
 #plot_fulldisk_e_m()
 #plot_alpha_pl_frac()
 #plot_pl_frac_time()
-#plot_surfden_profiles()
+plot_surfden_profiles()
 #plot_surfden_iso()
-plot_surfden_b()
+#plot_surfden_b()
 #plot_smooth_acc()
 #plot_acc_zones()
 #plot_f6f4()

### 2022-10-10 main.tex
Edit section 5.5

@@
 
-Further insight into the difference between the short vs long period accretion modes can be gained by examining the merger history of the planetary embryos.
-Because all collisions are directly resolved by the N-body code, a direct lineage can be traced between each embryo and a set of initial planetesimals.
+Further insight regarding the difference between the short vs long period accretion modes can be gained by looking at the merger history of the planetary embryos.
+Because all collisions are directly resolved by the N-body code, a direct lineage can be traced between the resulting planetary embryo and the initial planetesimals.
 
@@
 that give rise to each embryo. Drawing from a common technique used
-for cosmological simulations (citation?), we divide growth events for
-a given body into ``major'' and ``minor'' mergers.
-Minor events are defined as any collision involving an initial planetesimal, while major events consist of any two larger bodies.
-In figure \ref{fig:minor_frac}, we show the total mass fraction gained by minor events as a function of mass for the 100 largest bodies at the end of fdHi.
-Blue dots represent bodies interior to the 60 day orbital period boundary, while red crosses indicate bodies exterior.
-For the outer bodies in the oligarchic growth region, we see a very weak trend between minor accretion mass fraction and total mass.
-Regardless of how much an embryo has grown, the initial mass planetesimals contribute about the same relative amount to its total mass.
-At shorter orbital periods, however, there is a somewhat stronger trend.
-The largest bodies in this region gain about an order of magnitude more of their mass fraction from major mergers, compared to the smallest bodies.
+for cosmological simulations of galaxy formation, we divide growth events for
+a given body into ``major'' and ``minor'' mergers. Here, we define minor events as any collision involving an initial mass 
+planetesimal, while major events consist of a merger between any two larger bodies. In figure \ref{fig:minor_frac}, we choose the 
+100 largest bodies at the end of the fdHi simulation, retrieve all collision events involving these bodies, and plot the total mass 
+fraction attained through minor events as a function of the final mass of the body. The bodies are then subdivided into those that 
+end up with orbital periods greater than 60 days (red x's) and less than 60 days (blue dots). For the bodies in the outer oligarchic 
+growth region, the trend between smooth accretion mass fraction and final mass is nearly flat. Regardless of how much an 
+embryo has grown, mergers with initial mass planetesimals contribute on the order of a few percent to the final mass.
+At shorter orbital periods, however, the contribution from minor mergers can be over an order of magnitude smaller as the 
+embryos mature.
 
@@
 
-The difference in slope of the short vs.\ long period bodies in figure \ref{fig:minor_frac} indicates a difference in how the planetesimal-embryo populations interact in each region.
-In the long period oligarchic growth region, embryos continue to accrete planetesimals as they grow and the minor mass fraction stays mostly flat.
-At short period, collisions mostly occur between equal mass bodies as the embryos grow and the contribution from planetesimals becomes less significant over time.
-This suggests that embryo-embryo collisions are common at short period.
-As discussed in section \ref{sec:sizeandhill}, the importance of gravitational scattering is greatly reduced here.
-Without frequent gravitational interactions between the embryos and planetesimals, orbital repulsion \citep{kokubo98} and isolation of the embryos does not occur.
-As we showed in figure \ref{fig:surfden_iso}, the embryos formed in this region exceed the isolation mass.
-
-Further evidence for the lack of gravitational scattering events in
-the inner region can be seen in figure \ref{fig:acc_zones}. Here, we
-have chosen the 20 most massive bodies from the fdHi simulation and
-arranged them in order of present orbital period. The vertical black
-line indicates the orbital period of each embryo. The associated
-histogram for each body denotes where the planetesimals used to
-construct that embryo originated in the disk. The peaks of the
-histograms have all been normalized to the same value, so that the
-distributions only show the relative widths and locations of the
-feeding zones. Beyond the 60 day boundary, the ordering of the feeding
-zones and the embryo locations become much less consistent. This
-suggests that scattering events between embryos are much more common
-beyond this accretion mode boundary. In the inner region of the disk,
-close encounters between embryos often result in a merger, which
-allows them to grow beyond the isolation mass with only a minor alteration to their orbital period.
-With few close encounters resulting in a scattering event, embryos are unable to move away from their birth location.
+The variation in smooth accretion fraction with mass for the short period bodies suggests that the planetesimal and embryo populations interact differently than those in the outer disk.
+Exterior to the 60 day accretion mode boundary, the growing embryos continue to accrete planetesimals as they near their final mass.
+Inside the boundary, however, later growth events tend to be dominated by embryo-embryo collisions, and the smooth accretion fraction drops as mergers with planetesimals play a less significant role.
+As we discussed in section \ref{sec:sizeandhill}, gravitational scattering should be very weak in the inner disk.
+Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion (see \citet{kokubo98}), and so a lack of gravitational scattering should prevent the embryos from settling onto neatly-spaced, isolated orbits.
+As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zones predicted by an oligarchic growth model.
+Figure \ref{fig:minor_frac} suggests that this extra mass here obtain comes from mergers with the other nearby embryos.
+
+%%%
+
+Another line of evidence pointing to a lack of gravitational scattering and orbital repulsion in the inner disk can be seen in figure \ref{fig:acc_zones}.
+Here, we have chosen the 20 most massive bodies from the fdHi simulation and arranged them in order of final orbital period.
+On each line, the black has mark indicates the present orbital period of an embryo and the gray histogram represents the initial orbital period distribution of the planetesimals which were used to construct the embryo.
+One should note that unlike the previous figure, this plot shows where every single bit of mass (in the form of planetesimals) originated, rather than only denoting embryo-planetesimal collisions.
+
+Qualitatively, there are a couple of differences between the initial planetesimal distributions in the inner ($<$ 60 days) and outer ($>$ 60 days) part of the disk.
+The planetesimal distributions for the outer disk are much more smooth and unimodal, while many of the distributions near the inner disk have multiple peaks.
+As we discussed when examining figure \ref{fig:minor_frac}, growth events for the inner embryos tend to be sudden and stochastic, often involving pairs of embryos.
+When an embryo-embryo collision happens, one would expect a second peak to appear in the accretion distribution as the merger tree suddenly obtains a whole other subtree from the embryo that it absorbed.
+In the outer disk, however, the increased importance of embryo-planetesimal mergers means that growth should be smooth, steady and local.
+
+In figure \ref{fig:acc_zones}, evidence of orbital repulsion can be seen for the outermost embryos.
+Beyond 60 days, the final positions of the embryos tend to be offset from the peaks of the accretion distributions.
+This suggests that gravitational scattering events between embryos occurred later on, after accretion had mostly completed.
+Although many of the inner embryos also end up shifted away from the peak of their accretion distribution, their present position is usually associated with another secondary peak.
+This suggests that most of the close encounters between embryos here resulted in a merger event, rather than a scatter.
 

### 2022-10-11 main.tex
Edit section 6

@@
     \includegraphics[width=0.5\textwidth]{figures/surfden_b.png}
-    \caption{Feeding zone width (see equation \ref{eq:iso} required to produce the final masses for the protoplanets from the simulations listed in table \ref{tab:sim_properties}.
+    \caption{Feeding zone width (see equation \ref{eq:iso}) required to produce the final masses for the protoplanets from the simulations listed in table \ref{tab:sim_properties}.
 The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$.
@@
 
-%%%
-
 Another line of evidence pointing to a lack of gravitational scattering and orbital repulsion in the inner disk can be seen in figure \ref{fig:acc_zones}.
@@
 
-% from how far do embryos accumulate material
-% do embryos migrate at all? might need to run a simulation without gas to demonstrate whether this is due to PDM
-% major vs minor mergers?
-
 \section{Simplifying Assumptions}\label{sec:assump}
@@
 
-In all cases shown so far, the boundary between the standard
+In all cases shown so far, the boundary between the
 oligarchic growth and the highly-efficient short period accretion
-region lies around 60 days in orbital period. The mode of accretion is
+region lies around 60 days in orbital period. As discussed in section \ref{sec:sizeandhill}, the mode of accretion is
 set entirely by the local value of $\alpha$, which scales with both
 distance from the star and the bulk density of the planetesimals (see
-equation \ref{eq:alpha}). The artificial inflation of the collision
-cross section of the particles in our simulations, which is meant to
-reduce the computational expense, has the side effect of reducing the
-bulk densities. Because $\alpha \sim \rho_{pl}^{-1/3}$, increasing the
-particle sizes by a factor of $f=6$ reduces the orbital period at which $\alpha$ has a given value by a factor of approximately 15.
-Therefore, one would expect the accretion boundary to lie near 5 days in orbital period for 3 g $cm^{-3}$ bodies.
+equation \ref{eq:alpha}). Because we chose to artificially inflate the
+collision cross section of the particles in our simulations, the bulk densities
+of the particles are reduced, and the accretion boundary is shifted outward.
+However,  the scaling relation between $\alpha$ and $\rho$ ($\alpha \sim \rho_{pl}^{-1/3}$) can be used
+to predict where this accretion boundary should lie in a disk with realistic-sized planetesimals. The simulations
+presented in this paper use a collision cross section enhancement factor of 6, which moves the boundary outward in orbital
+period by a factor of approximately 15. One would therefore expect the accretion boundary to lie near 5 days in orbital period
+for 3 g $cm^{-3}$ bodies.
 
@@
 can test whether the accretion boundary moves in the way we expect by
-modestly changing the value of $f$. In figure \ref{fig:f6f4}, we
+modestly changing the value of $f$. In figure \ref{fig:f6f4_b}, we
 compare the fdHi simulation to a nearly identical run using $f=4$. In
-the top panel, the embryo masses in units of the isolation mass are
-shown as a function of orbital period. In the bottom panel, the value
+the top panel, we show the feeding zone width required for each particle to
+attain its present mass. As in figure \ref{fig:surfden_b}, we indicate the feeding
+zone size predicted by oligarchic growth with a horizontal dashed line.  In the bottom panel, the value
 of $\alpha$ as a function of orbital period is shown for 3 g $cm^{-3}$
 bodies with an artificial radius enhancement of $f=1$, 4 and 6. The
-horizontal dashed line indicates the value of alpha below which the
-accretion mode switches to oligarchic growth. Comparing the top and
-bottom panels, the intersection of the embryo masses and local
-isolation mass matches well with the orbital period at which $\alpha
-\sim 0.1$.  Also shown by the shaded region are $\alpha$ values for
-realistic sized bodies with $\rho_{pl}$ between 1 and 10 g cm$^{-3}$.
-% Also shown by the curved dotted lines are the $\alpha$ curves for
-% realistic-sized bodies with $\rho_{pl}$ = 1, 5 and 10 g $cm^{-3}$.
-In all cases, the accretion boundary still lies within the part of the disk in which solids would be expected to accumulate (citation?).
+horizontal dashed line indicates the empirical value of alpha below which the
+accretion mode switches to oligarchic. Comparing the top and
+bottom panels, the intersection of the feeding zone width seen in our simulations and the
+feeding zone width predicted by oligarchic growth matches well with the orbital period at which $\alpha
+\sim 0.1$ for both values of $f$.  Also shown by the shaded region are the expected $\alpha$ values for
+realistic-sized bodies with $\rho_{pl}$ between 1 and 10 g cm$^{-3}$. Although the removal of the cross section
+enhancement greatly reduces the size of the non-oligarchic region, it still should be expected to cover a portion of the
+disk where planetesimals might be expected to form for a wide range of $\rho_{pl}$.
 
@@
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/f6f4.png}
+    \includegraphics[width=0.5\textwidth]{figures/f6f4_b.png}
     \caption{In the top panel, we show the final masses of the bodies
@@
 The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of the embryo mass distribution and isolation mass.
-The shaded region in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4}}
+The shaded region in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
 \end{center}
 \end{figure}
-
-% compare f=4 and f=6 disk. show that the mass transition moves inwards by the correct amount as alpha changes
-% how does density affect results? trappist-1 planets are 5 g/cc (agol+ 2021)
 
@@
 
-In the simulations presented in this work, all collisions result in a complete merging of a pair of bodies with no loss of mass or momentum.
-Although simple to model, this assumption of perfect accretion may result in overly efficient growth, particularly at the innermost region of the disk where encounter velocities are the largest.
-To handle this issue properly, semianalytic collision resolution models have been developed and implemented in N-body codes (see \citet{leinhardt12}).
-However, resolving collisional debris fragments using a direct approach as we have done with {\sc ChaNGa} would result in an intractably large number of particles.
+For the simulations presented in this work, every collision results in a perfect merger between pairs of bodies, with no loss
+of mass or momentum. Although simpler and less computationally expensive to model, allowing every collision to produce a
+merger might result in overly efficient growth, particularly in the innermost region of the disk where the encounter velocities are largest.
+A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic model (see \citet{leinhardt12}).
+However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of bodies to bounce is too expensive to model, even with {\sc ChaNGa}.
 
-To test whether a more restrictive collision model should modify our results, we present a smaller scale test using a slightly more sophisticated collision model.
+To test whether a more restrictive collision model should alter the growth mode of the inner disk, we ran a smaller scale test using a slightly more restrictive collision model.
 In this case, a collision can result in one of two outcomes: if the impact velocity is smaller than the mutual escape velocity of the colliding particles, defined as
-%TRQ: I corrected this off the top of my head: CHECK!
 \begin{equation}\label{eq:v_mut}
-	v_{mut, esc} = \sqrt{\frac{G (m_{1} + m_{2})}{r_{1} + r_{2}}},
+	v_{mut, esc} = \sqrt{\frac{2 G (m_{1} + m_{2})}{r_{1} + r_{2}}},
 \end{equation}
 where $m_{1}, m_{2}$ and $r_{1}, r_{2}$ are the masses and radii of
-colliding particles 1 and 2, then the bodies perfectly merge. For
+colliding particles 1 and 2, then the bodies merge. For
 impact velocities larger than $v_{mut, esc}$, no mass is transferred, and the bodies undergo a completely elastic bounce.
-Because there is no possibility of partial accretion, this model likely restricts growth more than the model used by \citet{leinhardt12}.
-However, we will show below that the bounce-merge model does not meaningfully affect the outcome of the planetesimal accretion phase, and so a partial accretion model should do the same.
+Because the accretion outcome is all or nothing, this model should restrict growth more than a partial accretion model \citep{leinhardt12}.
+Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner disk's planetesimal accretion phase, and so a partial accretion model should do the same.
 
-For the configuration of initial conditions we have chosen, the typical encounter velocity (defined by $v_{enc} = \left< e^{2} \right>^{1/2} v_{k}$, where $v_{k}$ is the local Keplerian velocity) is about 25 percent larger than $v_{mut, esc}$.
-Because the encounter velocities follow a Gaussian distribution, there should be some small subset of collisions that still meet the merger criteria.
-In addition, $v_{mut, esc}$ becomes larger as the bodies grow and the merger criteria should become easier to meet as the system evolves.
+To compare the outcome of the two collision models, we have chosen to use the initial conditions from the fdLo simulation, but 
+have truncated the disk beyond 3 days in orbital period. We truncate the outer disk because the particle count with the bounce-
+merge model declines much more slowly, while also requiring many more timesteps overall.
+For the initial conditions we have chosen, the typical encounter velocity (defined by $v_{enc} = \left< e^{2} \right>^{1/2} v_{k}$, 
+where $v_{k}$ is the local Keplerian velocity) is about 25 percent larger than $v_{mut, esc}$. Because the encounter velocities 
+follow a Gaussian distribution, there should still be a small subset of collisions that still meet the merger criteria to occur early on. 
+In addition, $v_{mut, esc}$ becomes larger as the bodies grow and the merger criteria should become easier to meet as the 
+system evolves. For these reasons, one would expect the inhibition of growth due to the more restrictive collision model to be temporary.
 
-In figure \ref{fig:frag_ecc}, we show the results of two versions of the fdLo simulation, one with mergers only (shown in orange) and one with the bounce-merge model (shown in green).
+In figure \ref{fig:frag_ecc}, we compare the outcomes of the simulations, one with mergers only (shown in orange) and one with the bounce-merge model (shown in green).
 The blue points in the top panel show the initial conditions used for both cases.
-Because the bounce-merge model greatly increases the number of timesteps required, we choose to model only the innermost part of the disk to reduce the computational cost.
-Although the bounce-merge simulation takes much longer to reach the same phase of evolution, the resulting orbits and masses of the embryos are indistinguishable from the merger-only case.
+Although the bounce-merge simulation takes much longer to reach the same phase of evolution, the resulting orbital properties and mass distribution of the embryos are indistinguishable from the merger-only case.
 
-To investigate the differences between the two collision models early in the simulations, we show the time evolution of the ratio between the maximum and mean mass in figure \ref{fig:frag_evo}.
-In both cases, this ratio grows at early times, which indicates that runaway growth still operates, regardless of the collision model used.
+To investigate the differences in growth between the two collision models early on, we show the time evolution of the ratio between the maximum and mean mass in figure \ref{fig:frag_evo}.
+In both cases, this ratio first increases, which indicates that runaway growth still operates, regardless of the collision model used.
 In the bounce-merge case, the mass ratio peaks at a higher value, while also undergoing a longer runaway growth phase.
@@
 Radial mixing appears to be enhanced by a partial collision model, along with smaller collision cross section inflation \citep{childs22}.
-
-% show alpha, beta study again with bounce vs merge model
-% mergers still happen for 'lo' simulations but not 'hi'
-% this is because the eccentricity dispersion is significantly higher in the 'hi' case
-% mostly because stirring rate increases with surface density
-% criteria should get less restrictive as larger bodies grow, what if we turn on bounces partway thru growth process?
-
-\subsection{Type I Migration}
-
-What is the migration timescale for the embryos to move to the inner edge of the disk? Maybe this section isn't terribly important and should be excluded?
-TRQ: I agree
 

### 2022-10-11 makeFig.py

@@ -107,6 +107,16 @@ def prev_iorder(new_iord, num_original, del_iord):
 def p_orbit(sma):
 	return (2*np.pi*np.sqrt(sma**3/mCentral)*simT).to(u.d).value
 
+# Determine the feeding zone widths required for a set of particles
+# to obtain their current mass, based on an initial surface density profile
+def get_btilde(pl, prof0):
+	surf_den = (prof0['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)
+	mp = (pl['mass']*u.M_sun).to(u.g).value
+	mCeng = (mCentral*u.M_sun).to(u.g).value
+	aCm = (pl['a']*u.AU).to(u.cm).value
+	surf_den_at = np.interp(pl['a'], prof0['rbins'], surf_den)
+	return mp**(2./3.)*(3*mCeng)**(1./3.)/(2*np.pi*aCm**2*surf_den_at)
+
 # For a given snapshot, find a given property of the 'roots' of the particles
 def get_root_property(pl0, pl, root, time, prop):
 	def find(node, iord):
@@ -510,14 +520,6 @@ def plot_surfden_b():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	def get_btilde(pl, prof0):
-		surf_den = (prof0['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)
-		mp = (pl['mass']*u.M_sun).to(u.g).value
-		mCeng = (mCentral*u.M_sun).to(u.g).value
-		aCm = (pl['a']*u.AU).to(u.cm).value
-		surf_den_at = np.interp(pl['a'], prof0['rbins'], surf_den)
-		return mp**(2./3.)*(3*mCeng)**(1./3.)/(2*np.pi*aCm**2*surf_den_at)
-
 	fig, ax = plt.subplots(figsize=(8,12), nrows=4, sharex=True, sharey=True)
 
 	axes = ax[0]
@@ -792,6 +794,76 @@ def plot_f6f4():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
+def plot_f6f4_b():
+	file_str = 'figures/f6f4_b.' + fmt
[…]

### 2022-10-12 main.tex
Edit summary + discussion

@@
 
-In this work, we have demonstrated that planetary embryo formation
-operates in two distinct modes in a planet-forming disk. In the first
+In this work, we have demonstrated that planetary embryo growth
+can operate in two distinct modes in a planet-forming disk. In the first
 mode, gravitational feedback from the growing embryos heats the
 remaining planetesimals and results in a dynamically cold population
-of embryos with a significant amount of residual planetesimals. This
-corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}.
-In the second mode, the gravitational feedback does not operate, embryos quickly sweep up all planetesimals, and grow about twice as large as is predicted by oligarchic growth.
-The distinction between these modes is determined by ratio between the physical size of the bodies and their Hill radius.
+of embryos with a modest amount of residual planetesimals. This
+corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}, which is often used as a starting point for late-stage accretion models (e.g.
+\citet{kokubo02, raymond05, raymond06}).
+In the second mode, the gravitational feedback does not operate, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by oligarchic growth.
+The distinction between these modes is determined by ratio between the physical size of the bodies and their Hill radius, which sets the relative contribution of close gravitational encounters and collisions to the dynamical evolution of the disk.
 
@@
 sparsely sampled parameter study.
-The initial planetesimal distribution can be described in terms of two dimensionless constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) and gravitational ($r_{g}$) radii, respectively.
-For a fixed planetesimal mass and radius, $\alpha$ scales with the orbital period and $\beta$ scales with the level of dynamical excitation of the disk.
-We showed that $\alpha \ll 1$ leads to oligarchic growth, while a non-negligible $\alpha$ produces this new non-oligarchic growth mode.
-We find that the resulting mass distribution, along with the final eccentricities of the embryos and residual planetesimals, ends up the same, regardless of the initial value of $\beta$.
+The initial planetesimal distribution can be described in terms of two dimensionless constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) and gravitational ($r_{g}$) radius, respectively.
+For a fixed planetesimal composition, $\alpha$ scales with the orbital period and $\beta$ scales with the level of dynamical excitation of the disk.
+We showed that $\alpha \ll 1$ leads to oligarchic growth, while a non-negligible $\alpha$ produces this newly revealed non-oligarchic growth mode.
+Within this non-oligarchic mode, we find that the resulting masses and eccentricities of the embryos come out the same, regardless of the initial value of $\beta$.
 
@@
 from the star. Because both the physical and Hill radii of the bodies
-grows as $M^{1/3}$, the boundary between growth remains at a fixed
-location in the disk during the planetesimal accretion process.
+grows as $M^{1/3}$, the growth mode boundary remains stationary
+ in the disk during the planetesimal accretion process.
 
-We have verified this fact by testing the outcome of the planetesimal
-accretion process for a variety of solid surface density
+We have verified that the growth boundary location is independent of the
+solid surface density distribution by testing the outcome of the planetesimal
+accretion process for a variety of solid
 profiles. Although altering the surface density does affect the
@@
 separating the growth modes is remarkably similar among all of our simulations.
-We have verified this by comparing the resulting embryo masses to the isolation mass, in addition to highlighting qualitative differences in the accretion history of embryos on both sides of the boundary.
+In addition, the sizes of the feeding zones, along with qualitative differences in the
+accretion history of embryos on both sides of the boundary provide further evidence to
+suggest that oligarchy is not operating in the inner disk.
 
-Lastly, we quantified the way in which our use of perfect accretion and an inflated collision cross section, both meant to make the simulations more computationally tractable, affect the non-oligarchic growth mode and the location of the accretion boundary.
-We showed that although the use of perfect accretion speeds up the growth of the embryos, it does not affect the masses or orbital properties of the resulting bodies.
-Because the inflated collision cross sections artificially reduce the density of the planetesimals, this shortcut does shift the accretion boundary outward.
-However, it moves in a predictable fashion and we verified this by running an extra simulation with a modestly smaller collision cross section.
-In a real planet-forming disk, one would expect this boundary to lie somewhere between 2 and 10 days, depending on the composition of the planetesimals.
+Finally, we examined the way in which our simplifying assumption of perfect accretion, along with the enhancement of the 
+collision cross sections to speed up the simulations might alter the emergence and location of the non-oligarchic growth region. 
+We showed that a much more restrictive collision model, in which only low-velocity collisions produce a merger, still allows for 
+this growth mode to occur at the innermost part of the disk, where encounter speeds are most vigorous. In a real planet-forming 
+disk, partial accretion events should allow growth to happen more quickly than what was seen in this test case, so this growth 
+mode should certainly still occur. We also showed that the collision cross section enhancement moves the accretion boundary 
+outward. We verified this by deriving a scaling relation between the boundary location and the bulk density of the planetesimals, 
+and showing that the boundary moves to the predicted location when running a simulation with a slightly smaller inflation factor. 
+For planetesimals with a realistic bulk density, this boundary should lie around 5 days in orbital period.
 
@@
 which use N-body methods to examine in-situ satellitesimal accretion
-\citep{ida97, richardson00, ida20}. \citet{ida97} was able to form 1-2
+\citep{ida97, richardson00, kokubo00b, ida20}, although some of these simulations involve a complex interaction between spiral density waves formed inside of the Roche limit and the material exterior to it.
+\citet{ida97} was able to form 1-2
 large moons just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over.
@@
 Inside to the $\alpha = 0.1$ accretion boundary (which lies near $15 R_{U}$ in figure 1 of \citet{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary.
-In addition, a residual population of satellitesimals is still present beyond the boundary, which suggests that oligarchic growth is indeed operating on the far side.
+In addition, a residual population of satellitesimals is still present beyond the boundary, which suggests that oligarchic growth is indeed operating only on the far side.
 
-Presently, the implications that this non-oligarchic accretion mode has for the formation of short-period terrestrial planets, and whether the accretion boundary would leave any lasting imprint on the final orbital architecture, is unclear.
-One point that our results do highlight is that the initial conditions used for most late stage planet formation simulations are overly simplistic.
-\citet{clement20} recently simulated planetesimal accretion in a disk extending from the orbit of Mercury to the asteroid belt and found that the disk never reaches a state in which equally-spaced, isolation mass embryos are present everywhere simultaneously.
-Instead, different annuli reach a `giant impact' phase at different times, preventing the onset of a global instability throughout the entire disk, as is common in classic terrestrial planet formation models \citep{chambers01, raymond09}.
-
-% Any examples of studies of STIPs that use these simplistic ICs? Could the accretion boundary help reconcile differences with kepler systems?
+Presently, the implications that this non-oligarchic accretion mode has for the formation of short-period terrestrial planets, and 
+whether the accretion boundary would leave any lasting imprint on the final orbital architecture, is unclear. One point that our 
+results do highlight is that the initial conditions used for most late-stage planet formation simulations are overly simplistic. 
+\citet{clement20} recently simulated planetesimal accretion in a disk extending from the orbit of Mercury to the asteroid belt and 
+found that the disk never reaches a state in which equally-spaced, isolation mass embryos are present everywhere 
+simultaneously. Instead, different annuli reach a `giant impact' phase at different times, preventing the onset of a global instability 
+throughout the entire disk, as is common in classic terrestrial planet formation models \citep{chambers01, raymond09}.
 
 To connect these accretion modes to the final orbital architecture,
-and to ultimately determine what implications an in situ formation model has for the growth of STIPs, we will continue to evolve the final simulation snaphots presented here with a hybrid symplectic integrator.
-The final distribution of planets formed, along with composition predictions generated by applying cosmochemical models to our initial planetesimal distributions and propagating compositions through the merger trees, will be examined in a follow-up paper.
+and to ultimately determine what implications an in-situ formation model has for the growth of STIPs, we will evolve the final 
+simulation snapshots presented here with a hybrid-symplectic integrator for Myr timescales. The final distribution of planets 
+formed, along with composition predictions generated by applying cosmochemical models to our initial planetesimal distributions 
+and propagating compositions through the collision trees, will be examined in a follow-up paper.
 

### 2022-10-18 main.tex
Clean up figures, make sure captions and text match current version of figures

@@
 \end{abstract}
-
-%\begin{list}
-%\item Explain $\alpha$ controls importance of scattering vs accretion
-%\item Also mention $\beta$. Introduces another relevant size scale, but we seem to get runaway growth no matter how large or small this is (is this true?)
-%\item Show full disk vhi f6 and f4 simulations. Boundary of efficient accretion moves with density of bodies. Roughly lies where $\alpha = 0.1$.
-%\item Eccentricities reach v = vesc regardless of alpha. Show narrow annulus simulations in which embryo 'cools' in planetesimal disk with varying $\alpha$.
-%\item Show collision tree plot for full disk vhi f6. Do planetesimals move around much? How does motion of condensation fronts (due to pre-MS evolution of M stars) affect this?
-%\item What about fragmentation?
-%\item Planetesimals get completely consumed in inner disk. May have implications for planetesimal driven migration (outward, counteract type I migration)?
-%\item Embryos form first in the inner disk. What are the implications of this? Might make outward planetesimal driven migration easier
-%\end{list}
 
@@
 In a series of follow up papers, we plan to use these results to directly track the formation of full-sized planets from planetesimals and to understand how gravitational perturbations from a nearby gas giant might affect the outcome of this process.
-
-% This stuff doesn't fit since I reworked the intro. Might be better to save some of this for paper 2 (planetesimals->planets)
-% Still deciding whether I should mention habitability and low mass stars
-% I think there are plenty of STIPs around sun like stars, but I should double check this
-% TRQ: for the discussion/conclusions: mention that the mass of the
-% star doesn't matter (caveat composition changes in the
-% planetesimals); it's the orbital period that is crucial.
-
-%Over the last few decades, terrestrial planet formation models have largely advanced by matching properties of the solar system.
-Compared to exoplanetary systems, the solar system provides a rich set of constraints (isotopic ratios, cratering records, small body populations) that are mostly unmeasurable for even the closest neighboring planet forming systems.
-However, the system architectures discovered by spaced-based missions in the last decade reveal that the solar system could very well be an outlier in terms of what a typical planet-forming disk produces.
-In addition, the sizes and compositions of the terrestrial planets likely rely on a series of finely-tuned events to play out that involve truncation of the primordial planetesimal disk \citep{raymond17}, inward, followed by outward migration of an outer giant planet \citep{walsh11}, or a large-scale instability triggered by a pair of convergently migrating giant planets \citep{tsiganis05, levison11, nesvorny11}.
-Given qualitatively similar initial conditions, solar system formation models can even occasionally reproduce the correct masses and orbital periods of the terrestrial planets without invoking any of the aforementioned scenarios, given the right random number seed \citep{fischer14}.
-
-%Given the difficult question of whether to treat the solar system as
-%an outlier, the best way forward is to use statistical samples of
-%exoplanetary architectures to develop and inform formation
-%models. This is generally done through the use of population synthesis
-%models \citep{ida04, alibert11}, but many of the mechanisms in these
-%models are informed and tuned by solar system constraints. One
-%pervasive and exotic result revealed by the Kepler space telescope is the discovery of hundreds of compact multi-planet terrestrial systems, dubbed systems of tightly-packed inner planets (STIPs).
-Although there is no formal definition of a STIP, they typically contain 3 or more Earth-sized planets with orbital periods extending between 1 and 100 days.
-Reconciling the structural differences between the solar system (devoid of large bodies interior to 88 days) and STIPs is going to be an important step in building a general, widely-applicable planet formation model.
-
-%To date, a large body of work exists that has attempted to reproduce
-%the architectures of STIPs, starting from planetary embryos (cite some
-%examples). However, the runaway and oligarchic growth phases, which
-%precede the assembly of the embryos, are assumed to be
-%ubiquitous. Given that the timescales for accretion and gravitational
-%scattering scale differently with encounter velocity, which itself
-%scales with orbital period, it is not entirely clear that planetary
-%embryos should form in the same way close to the star as they do at
-%much longer, more thoroughly studied orbital periods. In this paper,
-%we use direct N-body simulations to explore the outcome of the
-%planetesimal accretion stage at orbital periods shorter than 100 days
-%around an M star.
-% TRQ perhaps mention habitable zone here.  Somewhere, a discussion of
-% the importance of understanding habitable zones around M-stars,
-% where STIPS are found, needs to be discussed.
-%In particular, we seek to understand what the orbital and mass distributions of the embryos and residual planetesimals look like, and to assess whether the initial conditions used by late-stage simulations of STIP assembly are reasonable.
-%
 
@@
       internal density of 3 g cm$^{-3}$ and an eccentricity dispersion
-      characterized by $e_h$, where $e_h = 1$ is the boundary between
-      shear and dispersion dominated encounters.
-Only in regions where $t_{relax} \ll t_{coll}$ can the velocity distribution respond to changes in the mass of the bodies such that oligarchic growth can operate.
-This condition is no longer satisfied for a dynamically hot disk at sufficiently short orbital periods.\label{fig:timescales}}
+      characterized by $e_h$. Only in regions where $t_{relax} \ll t_{coll}$ can 
+      the velocity distribution respond to changes in the mass of the bodies such
+      that oligarchic growth can operate. This condition is no longer satisfied for a dynamically hot disk at sufficiently short orbital periods.\label{fig:timescales}}
 \end{center}
@@
 runaway growth still operate when the condition that $v \ll v_{esc}$
-is not satisfied? 2) How does planetesimal accretion proceed when the planetesimals themselves occupy a significant fraction of their Hill spheres?
+is not satisfied? 2) How does planetesimal accretion proceed when the planetesimals themselves occupy a significant fraction of 
+their Hill spheres?
 
@@
 In the ``fiducial'' case, we give the bodies a bulk density of 3 g
-cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
-These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth.
-To vary the value of $\alpha$, we alter the bulk density of the particles.
-In the high-$\alpha$ case, the bulk density is reduced by a factor of $\sim$ 7100, which produces $\alpha = 1$.
-To vary $\beta$, the eccentricity dispersion is increased.
-For the high-$\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
+cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 
+10^{-3}$. These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth. 
+To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by 
+a factor of $\sim$ 7100, which produces $\alpha = 1$. To vary $\beta$, the eccentricity dispersion is increased. For the high-$
+\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
 
@@
 
-Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions (the physical and Hill radius both scale with $M^{1/3}$, so $\alpha$ stays constant as bodies grow), controls the qualitative outcome of accretion.
-Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will facilitate oligarchic growth.
-In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and embryos \citep{weidenschilling89, ida90}.
-When $\alpha$ is large, the Hill sphere of a body is no longer mostly empty space, and close encounters that would otherwise result in stirring instead result in accretion.
-In this regime, we observe that runaway growth still commences, but nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of planet formation \citep{kokubo98, kokubo00}.
+Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions (the physical and 
+Hill radius both scale with $M^{1/3}$, so $\alpha$ stays constant as bodies grow), controls the qualitative outcome of accretion. 
+Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will 
+facilitate oligarchic growth. In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and 
+embryos \citep{weidenschilling89, ida90}. When $\alpha$ is large, the Hill sphere of a body is no longer mostly empty space, 
+and close encounters that would otherwise result in stirring instead result in accretion. In this regime, we observe that runaway 
+growth still commences, but nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered 
+onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of planet formation 
+\citep{kokubo98, kokubo00}.
 
@@
 \end{table}
+
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/alpha_beta.png}
+    \caption{The initial (blue) and final (orange) states of the narrow annulus simulations described in section \ref{sec:narrow}. 
+    Relative masses of the bodies are indicated by point size. In the case of large $\alpha$, almost no residual planetesimal 
+    population remains. Regardless of the initial choice of $\beta$, the protoplanets that form attain similar eccentricities. 
+    \label{fig:alpha_beta}}
+\end{center}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_mass.png}
+    \caption{The final state of the mass distributions for the
+      narrow annulussimulations described in section \ref{sec:narrow}. For small
+      $\alpha$, a few embryos form alongside a power law tail of
+      planetesimals. For larger values of $\alpha$, the mass distribution stops becoming bimodal. 
+      As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.
+      \label{fig:alpha_beta_mass}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
+    \caption{The evolution of the ratio between the maximum and mean mass for the four simulations presented in section 
+    \ref{sec:narrow}. The runaway growth phase can be identified by a positive slope in this ratio. For all values of $\alpha$, an 
+    increase in $\beta$ has the effect of delaying growth.\label{fig:alpha_beta_evo}}
+\end{center}
+\end{figure}
 
@@
 The size of the points indicates the relative mass of the bodies.
-In the bottom panel, the mass of the largest bodies is shown as a function of orbital period.
-The solid curves indicate the isolation mass,
+In the bottom panel, the final masses of the bodies (in units of feeding zone size) are shown as a function of orbital period.
+The feeding zone size $\tilde{b}$ is calculated according to
+
 \begin{equation}\label{eq:iso}
-	M_{iso} = \left[ \frac{\left( 2 \pi a^2 \Sigma \tilde{b} \right)^3}{3 M_{*}} \right]^{1/2},
+	M = \left[ \frac{\left( 2 \pi a^2 \Sigma \tilde{b} \right)^3}{3 M_{*}} \right]^{1/2},
 \end{equation}
-where $\tilde{b}$ is the size of the feeding zone in units
-of Hill radii. For two bodies on circular, non-inclined orbits,  $\tilde{b} = 2
-\sqrt{3}$ is the smallest orbital separation that produces a non-negative Jacobi energy
-and permits a close encounter (see \citet{naka88}).
-In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend to space themselves apart by $\tilde{b} = 10$ (although it should be noted that they do not consume all of the planetesimals within this distance).
-The isolation mass is plotted in blue and orange for these two values of $\tilde{b}$, respectively.
 
-A qualitative shift in the protoplanet and planetesimal distribution is visible at $\sim$ 60 days.
-Interior to this location, there are very few remaining planetesimals and the embryos formed are noticeably more massive.
-Protoplanets in this region appear to closely follow the isolation mass curve for $\tilde{b} = 10$.
-Exterior to the boundary, the residual planetesimal population is much more pristine, and protoplanets more closely follow the $\tilde{b} = 2 \sqrt{3}$ curve.
-This suggests that the transition between the low $\alpha$ and high $\alpha$ accretion modes seen in section \ref{sec:narrow} happens near this location.
+where $M$ is taken to be the final mass of each body. Here, we assume that each embryo has reached its isolation mass, and 
+that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 
+size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $
+\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
+clearly visible. For two bodies on circular, non-inclined orbits,  $\tilde{b} = 2
+\sqrt{3}$ (indicated by the horizontal dashed line) is the smallest orbital separation that produces a non-negative Jacobi energy
+and permits a close encounter (see \citet{naka88}). In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
+to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
+within this distance.
 
-In section \ref{sec:narrow}, we postulated that the increased importance of inelastic damping in the inner, non-oligarchic growth region of the disk should lower the overall eccentricity of the protoplanets there.
-This behavior is not immediately apparent in the top panel of figure \ref{fig:fulldisk_e_m}.
-There are, however, a couple of factors in the wide disk simulations that could make this extra dynamical cooling mechanism difficult to see.
-Firstly, the initial eccentricity distributions of the inner and outer disk are different because of the dependence of the viscous stirring and gas drag timescales on orbital period.
-Additionally, the protoplanet formation timescales for the inner and outer disk are vastly different, making a comparison between these regions at the same moment in time somewhat inappropriate.
+A qualitative shift in the protoplanet and planetesimal distribution is visible at $\sim$ 60 days. Interior to this location, there are 
+very few remaining planetesimals and the embryos formed have larger feeding zones. Exterior to the boundary, the residual 
+planetesimal population is much more unmodified, and protoplanets more closely follow the $\tilde{b} = 2 \sqrt{3}$ line. This 
+suggests that the transition between the low $\alpha$ and high $\alpha$ accretion modes seen in section \ref{sec:narrow} 
+happens near this location.
 
-%In figure (removed), we show $\alpha$ (left axis) and the fraction of remaining planetesimals (right axis) as a function of orbital period.
-Here, the fraction of remaining planetesimals is measured by dividing the disk into 15 semimajor axis bins and using the profile function in {\sc pynbody} to measure the total solid surface density $\Sigma$ in each of those bins, and also the planetesimal surface density $\sigma$.
-Here, a planetesimal is defined to any body with $m < 10 m_{pl}$.
-Exterior to 60 days in orbital period, $\sigma/\Sigma$ sharply increases, indicating that the highly efficient accretion mode seen previously does not operate here.
-As can be seen from the plot, the accretion boundary roughly corresponds to $\alpha = 0.1$.
-% This figure could be turned into a few sentences in the text.
-
-% A mystery: what's so special about alpha = 0.1?
+In section \ref{sec:narrow}, we postulated that the increased importance of inelastic damping in the inner, non-oligarchic growth 
+region of the disk should lower the overall eccentricity of the protoplanets there. This behavior is not immediately apparent in the 
+top panel of figure \ref{fig:fulldisk_e_m}. There are, however, a couple of factors in the wide disk simulations that could make this 
+extra dynamical cooling mechanism difficult to see. Firstly, the initial eccentricity distributions of the inner and outer disk are 
+different because of the dependence of the viscous stirring and gas drag timescales on orbital period. Additionally, the 
+protoplanet formation timescales for the inner and outer disk are vastly different, making a comparison between these regions at 
+the same moment in time somewhat inappropriate.
 
@@
 bins, each with a width of 10 days.
-Bins interior to 60 days are shown by a dashed line, while those exterior are shown as a solid line.
-In all radial bins, the planetesimal surface density is approaching an asymptotic value.
-In the inner disk, this value asymptotes to zero as the planetesimal population entirely depletes.
-In the outer disk, dynamical friction between the embryos and planetesimals eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals.
-It should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimal mass should remain out of reach of the protoplanets.
+Bins interior to 60 days are shown by a dashed line, while those exterior are shown as a solid line. In all radial bins, the 
+planetesimal surface density is approaching an asymptotic value. In the inner disk, this value asymptotes to zero as the 
+planetesimal population entirely depletes. In the outer disk, dynamical friction between the embryos and planetesimals 
+eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals. It 
+should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle 
+onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimal mass should remain out of reach of the 
+protoplanets.
 
@@
 
-\begin{figure*}
-\begin{center}
-    \includegraphics[width=\textwidth]{figures/alpha_beta.png}
-    \caption{The initial (blue) and final (orange) states of the simulations described in section \ref{sec:narrow}.
-Relative masses of the bodies are indicated by point size.
-In the case of large $\alpha$, almost no residual planetesimal population remains.
-Regardless of the initial choice of $\beta$, the protoplanets that form attain similar eccentricities.
-\label{fig:alpha_beta}}
-\end{center}
-\end{figure*}
-
 \begin{figure}
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_mass.png}
-    \caption{The final state of the mass distribution for the
-      simulations described in section \ref{sec:narrow}. For small
-      $\alpha$, a few embryos form alongside a power law tail of
-      planetesimals. For larger values of $\alpha$, the mass
-      distribution takes on a more uniform form. As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.\label{fig:alpha_beta_mass}}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
-    \caption{The evolution of the ratio between the maximum and mean mass for the four simulations presented in section \ref{sec:narrow}.
-The runaway growth phase can be identified by a positive slope in this ratio.
-For all values of $\alpha$, an increase in $\beta$ has the effect of delaying the growth of the embryos.\label{fig:alpha_beta_evo}}
-\end{center}
-\end{figure}
-
-% show 4 panel plot of period-e distribution for large, small alpha and beta
-% show that runaway growth still operates for large beta
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/fulldisk_e_m.png}
+    \includegraphics[width=0.5\textwidth]{figures/fulldisk_e_m_b.png}
     \caption{The final state of the fdHi simulation. In the top panel,
@@
       of the planetesimals. Point sizes indicate the relative masses
-      of bodies. In the bottom panel, the solid line indicates the
-      isolation mass for $\tilde{b} = 2 \sqrt{3}$.
-The vertical dashed line marks the approximate location of the accretion mode boundary.
-For $P_{orb} < 60$ days, the high $\alpha$ accretion mode produces embryos that exceed the isolation mass.\label{fig:fulldisk_e_m}}
+      of bodies at the end of the simulation. In the bottom panel, we show the
+      feeding zone width (see equation \ref{eq:iso}) required to produce
+      the final masses of the bodies. The lower dashed line indicates the feeding
+      zone size ($\tilde{b} = 2 \sqrt{3}$) expected for bodies on circular orbits. Interior to the oligarchc
+      growth region (around 60 d), the feeding zone sizes exceed this value.\label{fig:fulldisk_e_m}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/pl_frac_time.png}
-    \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi simulation.
-Each curve represents a radial slice of the disk.
-The innermost region evolves the quickest, and is therefore represented by the lowest curve.
-The dashed lines indicate radial zones interior to the 60 day orbital period boundary.\label{fig:pl_frac_time}}
+    \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi 
+    simulation. Each curve represents a radial slice of the disk. The innermost region evolves the quickest, and is therefore 
+    represented by the lowest curve. The dashed lines indicate radial zones interior to the 60 day orbital period boundary.\label{fig:pl_frac_time}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/surfden_profiles.png}
-    \caption{The final state of all simulations listed in table \ref{tab:sim_properties}. Point sizes indicate mass relative to the largest body in the fdHi simulation.\label{fig:surfden_profiles}}
+    \caption{The final state of the full disk simulations listed in table \ref{tab:sim_properties}. 
+    Point sizes indicate mass relative to the largest body in each simulation.\label{fig:surfden_profiles}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/surfden_b.png}
-    \caption{Feeding zone width (see equation \ref{eq:iso}) required to produce the final masses for the protoplanets from the simulations listed in table \ref{tab:sim_properties}.
-The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$.
-Despite the vastly different initial solid surface density profiles, the feeding zone width reaches the circular orbit value around $\sim$ 60 days.
-\label{fig:surfden_b}}
+    \caption{Feeding zone width (see equation \ref{eq:iso}) required to produce the final masses for the protoplanets from the 
+    simulations listed in table \ref{tab:sim_properties}. The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$. Despite the 
+    vastly different initial solid surface density profiles, the feeding zone width reaches the circular orbit value around $\sim$ 60 
+    days. \label{fig:surfden_b}}
 \end{center}
 \end{figure}
-
-% show period-e distribution
-% show show period-mass distribution, with isolation mass curve overlaid
-% what about 'maximum planetary mass' from Schlichting 2014?
-% show plot of period vs alpha, mass. drop in embryo mass occurs where alpha = 0.1
-% also plot period vs sigma/Sigma and mass with alpha=0.1 location marked. residual planetesimal population missing interior to alpha=0.1
-
-% does the accretion boundary always fall somewhere within the PPD, or can it lie inside the magnetic truncation radius sometimes?
-how does this depend on spectral type?
-(this is complicated, depends on radius + magnetic field strength of star, plus accretion rate of PPD)
 
@@
 The final orbital period-eccentricity state of the
-particles in the fdHi, fdHiSteep, fdHiShallow and fdLo simulations are shown in figure \ref{fig:surfden_profiles}, with point sizes indicating the relative masses of the bodies.
-In all cases, the inner disk is largely depleted of planetesimals, while the outer disk contains a bimodal population of planetesimals and embryos, with a clear separation in eccentricity between the two.
-Despite having significantly different masses, the planetary embryos formed in all simulations have remarkably similar eccentricities.
-This is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which offsets the fact that the initial bodies started off in a dynamically hotter state.
+particles in the fdHi, fdHiSteep, fdHiShallow and fdLo simulations are shown in figure \ref{fig:surfden_profiles}, with point sizes 
+indicating the relative masses of the bodies. In all cases, the inner disk is largely depleted of planetesimals, while the outer disk 
+contains a bimodal population of planetesimals and embryos, with a clear separation in eccentricity between the two. Despite 
+having significantly different masses, the planetary embryos formed in all simulations have remarkably similar eccentricities. This 
+is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which 
+offsets the fact that the initial bodies started off in a dynamically hotter state. The only exception to this is the fdLo simulation, 
+where the resulting eccentricities are a couple orders of magnitude smaller. Inelastic damping likely plays an even more 
+significant role here, due to the much larger masses of the initial planetesimals.
 
-% Period vs mass for each model?
-% Positive trend for trappist-1 planets, excluding a,b
+In figure \ref{fig:surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $
+\tilde{b}$ (see equation \ref{eq:iso}).
 
-In figure \ref{fig:surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $\tilde{b}$ (see equation \ref{eq:iso}).
-Here, we assume that each embryo has reached its isolation mass, and that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the size of its feeding zone, which is set by the dynamics relevant at that location in the disk.
-By plotting the derived value of $\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more clearly visible.
-As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the minimum feeding zone width that a body can have.
-In all four simulations, the feeding zone width exceeds the minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days.
-The orbital periods at which this transition occurs are quite similar between simulations, despite the vastly different solid surface density profiles used.
-This indicates that the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
-
-%In figure \ref{fig:surfden_iso}, we compare the masses of the resulting protoplanets and planetesimals in all four simulations to each other.
-Here, the masses are scaled by the isolation mass at the given orbital distance (see equation \ref{eq:iso}).
-In all four cases, the masses follow a similar trend: interior to about 60 days in orbital period, protoplanets grow to a factor of a few larger than $M_{iso}$.
-Exterior to this point, the protoplanet masses roughly stay near the isolation mass.
-Despite the drastically different solid surface density profiles used, the masses of the largest bodies in all four cases follow a similar trend with orbital period.
-This indicates that the highly efficient accretion mode seen at shorter orbital periods is dependent on the sizes of the individual bodies themselves, rather than how they are distributed.
-The transition visible near 60 days in all cases also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
+As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the  
+feeding zone width that a body on a circular orbit should have. In all four simulations, the feeding zone width exceeds the 
+minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days. The orbital periods at which this transition 
+occurs are quite similar between simulations, despite the vastly different solid surface density profiles used. This indicates that 
+the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our 
+conclusion that planetesimal accretion is largely complete everywhere in the disk.
 
@@
 
-Further insight regarding the difference between the short vs long period accretion modes can be gained by looking at the merger history of the planetary embryos.
-Because all collisions are directly resolved by the N-body code, a direct lineage can be traced between the resulting planetary embryo and the initial planetesimals.
+Further insight regarding the difference between the short vs long period accretion modes can be gained by looking at the 
+merger history of the planetary embryos. Because all collisions are directly resolved by the N-body code, a direct lineage can be 
+traced between the resulting planetary embryo and the initial planetesimals.
 
@@
     \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown.
-The black hash marks indicate the present position of the body.
+The hash marks indicate the present position of the body.
 The accretion distributions indicate the initial locations of the planetesimals that were used to assemble a body, rather than the locations at which collisions with the massive body occurred.\label{fig:acc_zones}}
@@
 attain its present mass. As in figure \ref{fig:surfden_b}, we indicate the feeding
-zone size predicted by oligarchic growth with a horizontal dashed line.  In the bottom panel, the value
+zone size expected for oligarchic growth with a horizontal dashed line. In the bottom panel, the value
 of $\alpha$ as a function of orbital period is shown for 3 g $cm^{-3}$
@@
     \includegraphics[width=0.5\textwidth]{figures/f6f4_b.png}
-    \caption{In the top panel, we show the final masses of the bodies
-      from the fdHi and fdHif4 simulations in units of the isolation
-      mass for $\tilde{b} = 2\sqrt{3}$.
-The bottom panel shows the variation of $\alpha$ with orbital period for the bodies used in each case (solid curves).
-The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of the embryo mass distribution and isolation mass.
-The shaded region in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
+    \caption{In the top panel, we show the required feeding zone sizes to produce the masses of the bodies seen
+    at the end of the fdHi and fdHif4 simulations.The bottom panel shows the variation of $\alpha$ with orbital period for the 
+    bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of 
+    the embryo mass distribution and isolation mass. The shaded region in the bottom panel show the values of alpha for realistic-
+    sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/frag_ecc.png}
-    \caption{A comparison between the innermost regions of the fdLo (orange) simulation, and a second version using a bounce-merge collision model (green).
-In the top panel, the period-eccentricity state of the particles is shown, with marker sizes indicating relative mass.
-The blue points represent the initial state of the simulations.
-The bottom panel compares the final masses of the bodies.
-\label{fig:frag_ecc}}
+    \caption{A comparison between the innermost region of the fdLo (orange) simulation, and a second version using a bounce-
+    merge collision model (green). In the top panel, the period-eccentricity state of the particles is shown, with marker sizes 
+    indicating relative mass. The blue points represent the initial state of the simulations. The bottom panel compares the final 
+    mass distributions of the bodies. \label{fig:frag_ecc}}
 \end{center}
@@
     \caption{The evolution of the ratio between the maximum and mean mass of the simulations shown in figure \ref{fig:frag_ecc}. 
-In both cases, the system first evolves through a phase of runaway growth, before the massive bodies consume the smaller bodies, driving down the mean mass.
-With the bounce-merge model, the mass ratio decreases later because not all collisions result in growth.\label{fig:frag_evo}}
+    In both cases, the system first evolves through a phase of runaway growth, before the massive bodies consume the smaller 
+    bodies, driving down the mean mass. With the bounce-merge model, the mass ratio decreases later because not all collisions 
+    result in growth.\label{fig:frag_evo}}
 \end{center}
@@
 of mass or momentum. Although simpler and less computationally expensive to model, allowing every collision to produce a
-merger might result in overly efficient growth, particularly in the innermost region of the disk where the encounter velocities are largest.
-A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic model (see \citet{leinhardt12}).
-However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of bodies to bounce is too expensive to model, even with {\sc ChaNGa}.
+merger might result in overly efficient growth, particularly in the innermost region of the disk where the encounter velocities are 
+largest. A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic model (see 
+\citet{leinhardt12}). However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of bodies to 
+bounce is too expensive to model, even with {\sc ChaNGa}.
 
-To test whether a more restrictive collision model should alter the growth mode of the inner disk, we ran a smaller scale test using a slightly more restrictive collision model.
-In this case, a collision can result in one of two outcomes: if the impact velocity is smaller than the mutual escape velocity of the colliding particles, defined as
+To test whether a more restrictive collision model should alter the growth mode of the inner disk, we ran a smaller scale test 
+using a slightly more restrictive collision model. In this case, a collision can result in one of two outcomes: if the impact velocity is 
+smaller than the mutual escape velocity of the colliding particles, defined as
+
 \begin{equation}\label{eq:v_mut}
@@
 \end{equation}
+
 where $m_{1}, m_{2}$ and $r_{1}, r_{2}$ are the masses and radii of
@@
 impact velocities larger than $v_{mut, esc}$, no mass is transferred, and the bodies undergo a completely elastic bounce. 
-Because the accretion outcome is all or nothing, this model should restrict growth more than a partial accretion model \citep{leinhardt12}.
-Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner disk's planetesimal accretion phase, and so a partial accretion model should do the same.
+Because the accretion outcome is all or nothing, this model should restrict growth more than a partial accretion model 
+\citep{leinhardt12}. Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner 
+disk's planetesimal accretion phase, and so a partial accretion model should do the same.
 
@@
 In addition, $v_{mut, esc}$ becomes larger as the bodies grow and the merger criteria should become easier to meet as the 
-system evolves. For these reasons, one would expect the inhibition of growth due to the more restrictive collision model to be temporary.
+system evolves. For these reasons, one would expect the inhibition of growth due to the more restrictive collision model to be 
+temporary.
 
-In figure \ref{fig:frag_ecc}, we compare the outcomes of the simulations, one with mergers only (shown in orange) and one with the bounce-merge model (shown in green).
-The blue points in the top panel show the initial conditions used for both cases.
-Although the bounce-merge simulation takes much longer to reach the same phase of evolution, the resulting orbital properties and mass distribution of the embryos are indistinguishable from the merger-only case.
+In figure \ref{fig:frag_ecc}, we compare the outcomes of the simulations, one with mergers only (shown in orange) and one with 
+the bounce-merge model (shown in green). The blue points in the top panel show the initial conditions used for both cases. 
+Although the bounce-merge simulation takes much longer to reach the same phase of evolution, the resulting orbital properties 
+and mass distribution (with the exception of some extra residual planetesimals) are indistinguishable from the merger-only case.
 
-To investigate the differences in growth between the two collision models early on, we show the time evolution of the ratio between the maximum and mean mass in figure \ref{fig:frag_evo}.
-In both cases, this ratio first increases, which indicates that runaway growth still operates, regardless of the collision model used.
-In the bounce-merge case, the mass ratio peaks at a higher value, while also undergoing a longer runaway growth phase.
-This suggests that the mass distribution becomes much less unimodal during this growth process, but as figure \ref{fig:frag_ecc} shows, this does not affect the resulting embryos or allow for a residual planetesimal population.
+To investigate the differences in growth between the two collision models early on, we show the time evolution of the ratio 
+between the maximum and mean mass in figure \ref{fig:frag_evo}. In both cases, this ratio first increases, which indicates that 
+runaway growth still operates, regardless of the collision model used. In the bounce-merge case, the mass ratio peaks at a 
+higher value, while also undergoing a longer runaway growth phase. This suggests that the mass distribution becomes much 
+less unimodal during this growth process, but as figure \ref{fig:frag_ecc} shows, this does not affect the resulting embryos or 
+allow for a residual planetesimal population.
 
-%TRQ: expand on this?  Compare figure 10 histograms for the two runs?
-Radial mixing appears to be enhanced by a partial collision model, along with smaller collision cross section inflation \citep{childs22}.
+As a final note, \citet{childs22} found that a more realistic collision model also enhanced radial mixing in their simulations. Upon 
+calculating the planetesimal accretion zones using the same method as was done to produce figure \ref{fig:acc_zones}, we find 
+that the embryos in the bounce-merge simulation annulus do have modestly wider accretion zones than those produced in the 
+merger-only simulation.
 
@@
 of embryos with a modest amount of residual planetesimals. This
-corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}, which is often used as a starting point for late-stage accretion models (e.g.
-\citet{kokubo02, raymond05, raymond06}).
-In the second mode, the gravitational feedback does not operate, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by oligarchic growth.
-The distinction between these modes is determined by ratio between the physical size of the bodies and their Hill radius, which sets the relative contribution of close gravitational encounters and collisions to the dynamical evolution of the disk.
+corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}, which is often used as a starting point for late-stage 
+accretion models (e.g. \citet{kokubo02, raymond05, raymond06}). In the second mode, the gravitational feedback does not 
+operate, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
+oligarchic growth. The distinction between these modes is determined by ratio between the physical size of the bodies and their 
+Hill radius, which sets the relative contribution of close gravitational encounters and collisions to the dynamical evolution of the 
+disk.
 
 We have demonstrated the outcome of both accretion modes through a
-sparsely sampled parameter study.
-The initial planetesimal distribution can be described in terms of two dimensionless constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) and gravitational ($r_{g}$) radius, respectively.
-For a fixed planetesimal composition, $\alpha$ scales with the orbital period and $\beta$ scales with the level of dynamical excitation of the disk.
-We showed that $\alpha \ll 1$ leads to oligarchic growth, while a non-negligible $\alpha$ produces this newly revealed non-oligarchic growth mode.
-Within this non-oligarchic mode, we find that the resulting masses and eccentricities of the embryos come out the same, regardless of the initial value of $\beta$.
+sparsely sampled parameter study. The initial planetesimal distribution can be described in terms of two dimensionless 
+constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) 
+and gravitational ($r_{g}$) radius, respectively. For a fixed planetesimal composition, $\alpha$ scales with the orbital period and 
+$\beta$ scales with the level of dynamical excitation of the disk. We showed that $\alpha \ll 1$ leads to oligarchic growth, while a 
+non-negligible $\alpha$ produces this newly revealed non-oligarchic growth mode. Within this non-oligarchic mode, we find that 
+the resulting masses and eccentricities of the embryos come out the same, regardless of the initial value of $\beta$.
 
@@
 which use N-body methods to examine in-situ satellitesimal accretion
-\citep{ida97, richardson00, kokubo00b, ida20}, although some of these simulations involve a complex interaction between spiral density waves formed inside of the Roche limit and the material exterior to it.
-\citet{ida97} was able to form 1-2
+\citep{ida97, richardson00, kokubo00b, ida20}, although some of these simulations involve a complex interaction between spiral 
+density waves formed inside of the Roche limit and the material exterior to it. \citet{ida97} was able to form 1-2
 large moons just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over. 
-The widest disk they modeled extended out to $\alpha = 0.5$.
-Qualitatively, this result is very similar to the short period planetesimal accretion mode observed in our simulations.
-\citet{ida20} modeled a much wider satellitesimal disk, which extends out to about $\alpha \approx 0.05$.
-Inside to the $\alpha = 0.1$ accretion boundary (which lies near $15 R_{U}$ in figure 1 of \citet{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary.
-In addition, a residual population of satellitesimals is still present beyond the boundary, which suggests that oligarchic growth is indeed operating only on the far side.
+The widest disk they modeled extended out to $\alpha = 0.5$. Qualitatively, this result is very similar to the short period 
+planetesimal accretion mode observed in our simulations. \citet{ida20} modeled a much wider satellitesimal disk, which extends 
+out to about $\alpha \approx 0.05$. Inside to the $\alpha = 0.1$ accretion boundary (which lies near $15 R_{U}$ in figure 1 of 
+\citet{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary. In addition, a 
+residual population of satellitesimals is still present beyond the boundary, which suggests that oligarchic growth is indeed 
+operating only on the far side.
 

### 2022-10-18 makeFig.py

@@ -40,10 +40,10 @@ bins = np.linspace(0.01, 0.3, num_bins)
 
 snap = pb.load('data/fullDiskVHi.ic')
 plVHiIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
-p_vhi_ic = pb.analysis.profile.Profile(plVHiIC.d, bins=bins)
+p_vhi_ic = pb.analysis.profile.Profile(plVHiIC.d, bins=bins, calc_x = lambda x: x['a'])
 snap = pb.load('data/fullDiskVHi1.250000')
 plVHi = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
-p_vhi = pb.analysis.profile.Profile(plVHi.d, bins=bins)
+p_vhi = pb.analysis.profile.Profile(plVHi.d, bins=bins, calc_x = lambda x: x['a'])
 perIC = 2*np.pi*np.sqrt((plVHiIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 prof_perIC = 2*np.pi*np.sqrt((p_vhi_ic['rbins']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 per = 2*np.pi*np.sqrt((plVHi['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
@@ -56,40 +56,40 @@ r_pl = ((3*(m_pl*u.M_sun).to(u.g).value/(4*np.pi*rho))**(1/3)*u.cm).to(u.AU).val
 
 snap = pb.load('data/fullDiskVHif4.ic')
 plVHif4IC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
-p_vhif4_ic = pb.analysis.profile.Profile(plVHif4IC.d, bins=bins)
+p_vhif4_ic = pb.analysis.profile.Profile(plVHif4IC.d, bins=bins, calc_x = lambda x: x['a'])
 snap = pb.load('data/fullDiskVHif41.152000')
 plVHif4 = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
-p_vhif4 = pb.analysis.profile.Profile(plVHif4.d, bins=bins)
+p_vhif4 = pb.analysis.profile.Profile(plVHif4.d, bins=bins, calc_x = lambda x: x['a'])
[…]

### 2022-10-26 main.tex
Changes into annulus simulations.
Look for "TRQ" comments.

--- 2022-10-12 main.tex
@@
 As a consequence of the instability, the oligarchics are no longer
-on isolated, stable orbits and coalesce to form Earth-sized planets'
+on isolated, stable orbits and coalesce to form Earth-sized planets
 through a series of extremely energetic, giant 
@@
 model in this paper. That is, once the planetesimals themselves form,
-they largely stay in place and any subsequent large-scale movement of
+they largely stay in place, and any subsequent large-scale movement of
 the solids are the result of mutual gravitational interactions. The
@@
 by Keplerian frequency $\Omega$ can be written as $n \Gamma v$, where
-$n = \Sigma_{pl} \Omega / 2 m_{pl} v$ (where we have assumed that the scale height of the planetesimal disk goes as $\Omega/(2v)$. $\Gamma$ describes the effective
+$n = \Sigma_{pl} \Omega / 2 m_{pl} v$ (where we have assumed that the scale height of the planetesimal disk goes as $2v/\Omega$. $\Gamma$ describes the effective
 collision cross section and $v$ is the typical encounter velocity
@@
 \begin{equation}\label{eq:growth}
-	\frac{dM}{dt} = \frac{\Sigma \Omega}{2 m_{pl}} \Gamma.
+	\frac{dM}{dt} = \frac{\Sigma \Omega}{2}} \Gamma.
 \end{equation}
@@
 In the case where the collision cross section, depends only
+% TRQ: perhaps "sub-linearly"?  I see dMdt ~ M^{2/3}
 on the physical size of the planetesimals, the growth scales linearly
@@
 
-In the limit that $v_{esc} \gg v$, it can be shown that $M \propto
+In the limit that $v_{esc} \gg v$, it can be shown that $dM/dt \propto
 M^{4/3}$, which implies a runaway scenario, in which growth
@@
 
-The picture described above relies upon an important assumption, which is that the mass distribution evolves slow enough for gravitational stirring to maintain energy equipartition.
+The picture described above relies upon an important assumption, which
+is that the mass distribution evolves slowly enough for gravitational stirring to maintain energy equipartition.
 In other words, the relaxation timescale must remain short relative to the growth timescale.
@@
 
-In figure \ref{fig:timescales}, we show ratio between the relaxation
+In figure \ref{fig:timescales}, we show the ratio between the relaxation
 and collision timescale for a population of equal-mass planetesimals
@@
 
-In the formalism described above, the mass and velocity distribution of the bodies are both a function of time.
-Due to the interdependence of these quantities, it is not clear whether the timescales for gravitational scattering and growth will remain proportional as the oligarchs develop.
-In the case of many studies of planetesimal accretion in the solar system (cite examples), the $t_{relax} \ll t_{coll}$ condition must remain true, otherwise runaway growth would have continued until all of the planetesimals were consumed.
+In the formalism described above, the mass and velocity distribution
+of the bodies are both a function of time. Due to the interdependence
+of these quantities, it is not clear whether the timescales for
+gravitational scattering and growth will remain proportional as the
+oligarchs develop. In the case of many studies of planetesimal
+accretion in the solar system
+%TRQ: citations needed
+{\bf(cite examples)}, the $t_{relax} \ll t_{coll}$ condition must remain true, otherwise runaway growth would have continued until all of the planetesimals were consumed.
 However, it isn't immediately clear what will happen if the system begins in a state where $t_{coll} \ll t_{relax}$.
@@
 An insight into the expected behavior in this regime can be gained by
-defining the dimensionless parameter $\alpha$, which is the ratio
-between the physical size of a body and it's Hill radius, $r_{h}$:
+defining the dimensionless parameter, $\alpha$, which is the ratio
+between the physical size of a body and its Hill radius, $r_{h}$:
 \begin{equation}\label{eq:alpha}
@@
 \end{equation}
-where $a$ is the semimajor axis of the body and $\rho_{pl}$ is its bulk density.
-Assuming a fixed bulk density as bodies collide and grow, and that no large-scale migration occurs, the scaling of both $r_{pl}$ and $r_{h}$ with $m_{pl}^{1/3}$ means that $\alpha$ will be constant with time.
-For a composition of ice and rock, $\alpha$ is small for any populated region of the solar system ($\alpha \sim 10^{-2}$ for Earth and $\alpha \sim 10^{-4}$ in the Kuiper belt).
-As one moves close to the star $\alpha$ becomes larger than 1, which implies that the physical extent of a body exceeds its Hill sphere.
-(also mention that hill sphere size independent of velocity for small eccentricity)
+where $a$ is the semimajor axis of the body and $\rho_{pl}$ is its
+bulk density. Assuming a fixed bulk density as bodies collide and
+grow, and that no large-scale migration occurs, the scaling of both
+$r_{pl}$ and $r_{h}$ with $m_{pl}^{1/3}$ means that $\alpha$ will be
+constant with time. For a composition of ice and rock, $\alpha$ is
+small for any populated region of the solar system ($\alpha \sim
+10^{-2}$ for Earth and $\alpha \sim 10^{-4}$ in the Kuiper belt). As
+one moves close to the star $\alpha$ becomes larger than 1, which
+implies that the physical extent of a body exceeds its Hill sphere.
+{\bf(also mention that hill sphere size independent of velocity for small eccentricity)}
 
@@
 axes randomly drawn between 0.95 and 1.05 AU about a 1 $M_{\odot}$
-star. The argument of perihelion $\omega$, longitude of ascending node
-$\Omega$, and mean anomaly M for each body is drawn from a uniform
+star. The argument of perihelion, $\omega$, longitude of ascending node,
+$\Omega$, and mean anomaly, M, for each body is drawn from a uniform
 distribution $\in [0, 2 \pi)$. The inclinations and eccentricities are drawn
@@
 large $\alpha$, large $\beta$ and the small $\alpha$,
+%TRQ large alpha (former) is cooler!?!
 large $\beta$ case. The dynamically cooler result of the latter case
 is likely due to the dominant role that inelastic collisions play here.
+%TRQ Moving figure 2 up in the paper would help keep this discussion straight.
 
@@
       planetesimals. For larger values of $\alpha$, the mass
-      distribution takes on a more uniform form. As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.\label{fig:alpha_beta_mass}}
+      distribution is more uniform.  As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.\label{fig:alpha_beta_mass}}
 \end{center}

### 2022-11-17 main.tex
Redid eq. 2.  (planetesimal growth rate) Check this.
Updates to full disk section.

@@
 \begin{equation}\label{eq:growth}
-	\frac{dM}{dt} = \frac{\Sigma \Omega}{2}} \Gamma.
+	\frac{1}{M}\frac{dM}{dt} = \frac{\Sigma \Omega}{2 m_{pl}} \Gamma.
 \end{equation}
@@
 
+%TRQ: switched to delta for power law index
 \begin{table}
@@
 \begin{tabular}{llllll} \hline \hline
-Name    & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\alpha^{d}$ &  \\ \hline
+Name    & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\delta^{d}$ &  \\ \hline
 fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &   \\
@@
 \end{equation}
-where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g cm$^{-2}$ is surface density of the minimum-mass solar nebula \citep{hayashi81} at 1 AU, and $A$ is an enhancement factor.
+where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g
+cm$^{-2}$ is the surface density of the minimum-mass solar nebula
+\citep{hayashi81} at 1 AU, and $A$ is an enhancement factor.
+%TRQ: \delta = ???
 In the first case (fdHi), we model a disk that follows a MMSN power law slope, with the overall normalization enhanced by a factor of 100.
@@
 \end{equation}
-
-\noindent where $\Omega$, $a$ and $e$ are the orbital frequencies, semimajor axes and eccentricities of the individual planetesimals.
-In the Stokes regime, the gas drag timescale is given by \citet{adachi76} as
-
+where $\Omega$, $a$ and $e$ are the orbital frequencies, semimajor axes and eccentricities of the individual planetesimals. In the Stokes regime, the gas drag timescale is given by \citet{adachi76} as
 \begin{equation}\label{eq:ts_stokes}
@@
 \end{equation}
-
-\noindent where $C_{D}$ is a drag coefficient of order unity, $\rho_{g}$ is the local gas volume density and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal.
+where $C_{D}$ is a drag coefficient of order unity, $\rho_{g}$ is the local gas volume density and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal.
 The local gas volume density is given by
-
+%TRQ check this
 \begin{equation}\label{eq:rho_gas}
-	\rho_{g} = \frac{\Sigma_{g}}{\sqrt{2 \pi} h_{g} \exp\left[ -z^{2} / \left( 2 h_{g}^{2} \right) \right]},
+	\rho_{g} = \frac{\Sigma_{g}}{\sqrt{2 \pi} h_{g}} \exp\left[ -z^{2} / \left( 2 h_{g}^{2} \right) \right],
 \end{equation}
-
-\noindent where $\Sigma_{g}$ is the gas surface density (taken to be
-240 times the solid surface density), $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
+where $\Sigma_{g}$ is the gas surface density (taken to be
+240 times the solid surface density ({\bf citation for this number}), $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
 The sound speed profile is given by $c_{s} = \sqrt{k_{B} T(r) / \left( \mu m_{H} \right)}$, where $k_{B}$ is Boltzmann's constant, $T(r) = T_{0} r^{-Q}$, $\mu = 2.34$ and $m_{h}$ is the mass of a hydrogen atom.
@@
 In addition to the mutual gravitational forces, a Stokes drag force from to the gas disk is applied to each particle, following the prescription described in section 2.2.1 of \citet{morishima10}.
+%TRQ: add a qualitative description of the effect of this, e.g. what
+%is the drift timescale caused by this drag.
 
@@
 based on their most recently calculated gravitational
-acceleration. \footnote{This scheme is used on almost all works using ChaNGa,
+acceleration.\footnote{This scheme is used on almost all works using ChaNGa,
 and is common among large-scale simulation codes.}
@@
 
-A second issue is introduced when two particles on different timesteps undergo a collision.
-As in the previous case, momentum is not completely conserved because the most recent `kick' steps did not happen simultaneously for these bodies.
-Early in the simulation, we find that runaway growth tends to initiate at the timestep boundaries.
-This issue carries itself forward through the embryo formation phase, and protoplanets tend to form at the boundaries.
-To correct this issue, we ignore collisions between bodies on different timesteps early in the simulation.
-We find that preventing multi-timestep collisions until after the maximum mass grows by a factor of 10 prevents any artifacts from developing at the timestep boundaries, while also minimizing the number of `skipped' collisions\footnote{In the case of fdHi, only about 20 collisions out of an eventual 900,000 are ignored.}.
+A second issue is introduced when two particles on different timesteps
+undergo a collision. As in the previous case, momentum is not
+completely conserved because the most recent `kick' steps did not
+happen simultaneously for these bodies. Early in the simulation, we
+find that runaway growth tends to initiate at the timestep
+boundaries. This issue carries itself forward through the embryo
+formation phase, and protoplanets tend to form at the boundaries. To
+correct this issue, we ignore collisions between bodies on different
+timesteps early in the simulation. We find that preventing
+multi-timestep collisions until after the maximum mass grows by a
+factor of 10 prevents any artifacts from developing at the timestep
+boundaries, while also minimizing the number of `skipped' collisions.\footnote{In the case of fdHi, only about 20 collisions out of an eventual 900,000 are ignored.}
 
@@
 We show the final state of the ``fdHi'' simulation in figure \ref{fig:fulldisk_e_m}. In the top panel,
-the initial (contours) and final (points) state of the simulation is shown in the orbital period-eccentricity plane.
-The size of the points indicates the relative mass of the bodies.
-In the bottom panel, the final masses of the bodies (in units of feeding zone size) are shown as a function of orbital period.
-The feeding zone size $\tilde{b}$ is calculated according to
-
+the initial (contours) and final (points) state of the simulation is
+shown in the orbital period-eccentricity plane. The size of the points
+indicates the relative mass of the bodies. In the bottom panel, the
+final masses of the bodies (in units of feeding zone size) are shown
+as a function of orbital period. The feeding zone size $\tilde{b}$ is
+calculated according to ({\bf citation})
 \begin{equation}\label{eq:iso}
@@
 \end{equation}
-
 where $M$ is taken to be the final mass of each body. Here, we assume that each embryo has reached its isolation mass, and 
@@
 clearly visible. For two bodies on circular, non-inclined orbits,  $\tilde{b} = 2
-\sqrt{3}$ (indicated by the horizontal dashed line) is the smallest orbital separation that produces a non-negative Jacobi energy
+\sqrt{3}$ (indicated by the lower horizontal dashed line) is the smallest orbital separation that produces a non-negative Jacobi energy
 and permits a close encounter (see \citet{naka88}). In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
-to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
+to space themselves apart by $\tilde{b} = 10$, (top horizontial line in
+figure \ref{fig:fulldisk_e_m}, bottom panel) although it should be noted that they do not consume all of the planetesimals 
 within this distance.
@@
 
+%TRQ: \sigma is not defined.
 To ensure that the boundary seen near 60 days in orbital period is not
@@
       the final masses of the bodies. The lower dashed line indicates the feeding
-      zone size ($\tilde{b} = 2 \sqrt{3}$) expected for bodies on circular orbits. Interior to the oligarchc
+      zone size ($\tilde{b} = 2 \sqrt{3}$) expected for bodies on
+      circular orbits.
+%TRQ: upper horizontal line ....
+      Interior to the oligarchic
       growth region (around 60 d), the feeding zone sizes exceed this value.\label{fig:fulldisk_e_m}}

### 2022-11-26 main.tex
Changes to end of paper.

@@
 onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimal mass should remain out of reach of the 
-protoplanets.
+protoplanets.({\bf citation here})
 
@@
 where the resulting eccentricities are a couple orders of magnitude smaller. Inelastic damping likely plays an even more 
+% TRQ: ??? the masses of the initial planetesimals are the same in all
+% simulations according to table 1.
 significant role here, due to the much larger masses of the initial planetesimals.
@@
 \tilde{b}$ (see equation \ref{eq:iso}). 
-
 As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the  
@@
 
+%TRQ: perhaps use a logarithmic horizontal axis for better comparison
 \begin{figure*}
@@
 
-Another line of evidence pointing to a lack of gravitational scattering and orbital repulsion in the inner disk can be seen in figure \ref{fig:acc_zones}.
-Here, we have chosen the 20 most massive bodies from the fdHi simulation and arranged them in order of final orbital period.
-On each line, the black has mark indicates the present orbital period of an embryo and the gray histogram represents the initial orbital period distribution of the planetesimals which were used to construct the embryo.
+Another line of evidence pointing to a lack of gravitational
+scattering and orbital repulsion in the inner disk can be seen in
+figure \ref{fig:acc_zones}. Here, we have chosen the 20 most massive
+bodies from the fdHi simulation and arranged them in order of final
+orbital period. On each line, the black
+%TRQ: the mark is dark blue, not black.
+hash mark indicates the present orbital period of an embryo and the gray histogram represents the initial orbital period distribution of the planetesimals which were used to construct the embryo.
 One should note that unlike the previous figure, this plot shows where every single bit of mass (in the form of planetesimals) originated, rather than only denoting embryo-planetesimal collisions.
@@
     \caption{In the top panel, we show the required feeding zone sizes to produce the masses of the bodies seen
-    at the end of the fdHi and fdHif4 simulations.The bottom panel shows the variation of $\alpha$ with orbital period for the 
+    at the end of the fdHi and fdHif4 simulations.  The bottom panel shows the variation of $\alpha$ with orbital period for the 
     bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of 
-    the embryo mass distribution and isolation mass. The shaded region in the bottom panel show the values of alpha for realistic-
-    sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
+    the embryo mass distribution and isolation mass. The shaded region
+    in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
 \end{center}
@@
 smaller than the mutual escape velocity of the colliding particles, defined as
-
 \begin{equation}\label{eq:v_mut}
@@
 \end{equation}
-
 where $m_{1}, m_{2}$ and $r_{1}, r_{2}$ are the masses and radii of
@@
 operate, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
-oligarchic growth. The distinction between these modes is determined by ratio between the physical size of the bodies and their 
+oligarchic growth. The distinction between these modes is determined
+by the ratio between the physical size of the bodies and their 
 Hill radius, which sets the relative contribution of close gravitational encounters and collisions to the dynamical evolution of the 

### 2023-01-04 main.tex
Fill in acknowledgements

@@
-\documentclass[twocolumn]{aastex63}
+\documentclass[twocolumn,linenumbers]{aastex63}
 \usepackage{natbib}
@@
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
+The simulations presented in this work were run on XSEDE/SDSC Comet and Expanse under allocation MCA94P018.
+SCW and TRQ were were supported by NSF award 62-2684.
+We acknowledge the people of the Dkhw’Duw’Absh, the Duwamish Tribe, the Muckleshoot Tribe, and other tribes on whose traditional lands we have performed this work.
 
-NSF, XSEDE.
+\textit{Software:} Astropy \citep{astropy13}, {\sc ChaNGa} \citep{jetley08, menon15}, Matplotlib 
+\citep{matplotlib07}, NumPy \citep{numpy11}, Pandas \citep{pandas10}, {\sc PYNBODY} \citep{pynbody13}
+
+\section*{Data Availability}
+The data presented in this article are available on our GitHub repository, at \url{https://github.com/spencerw/stip_planetesimal_paper}.
 

### 2023-01-17 main.tex
Fix grant number in acknowledgements

@@
 \section*{Acknowledgements}
-The simulations presented in this work were run on XSEDE/SDSC Comet and Expanse under allocation MCA94P018.
-SCW and TRQ were were supported by NSF award 62-2684.
+This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number ACI-1548562.
+SCW and TRQ were were supported by National Science Foundation grant number AST-2006752.
 We acknowledge the people of the Dkhw’Duw’Absh, the Duwamish Tribe, the Muckleshoot Tribe, and other tribes on whose traditional lands we have performed this work.

### 2023-01-19 main.tex
Final edits before submission

@@
 becomes nearly 100 percent efficient at short orbital periods, leading
-to embryo masses that are roughly twice as large as the classical
+to embryo masses that are much larger than the classical
 isolation mass. For rocky bodies, the physical size of the object
-begins to occupy a significant fraction of its Hill sphere at orbital
-periods less than about 50 days. In this regime, most close encounters
-result in collisions, rather than scattering, and the system cannot
-bifurcate into a collection of dynamically hot planetesimals and
-dynamically cold oligarchs, like is seen in previous work. The highly
+begins to occupy a significant fraction of its Hill sphere towards the inner edge of the disk. In this regime, most close encounters
+result in collisions, rather than scattering, and the system does not
+develop a bimodal population dynamically hot planetesimals and
+dynamically cold oligarchs, like is seen in previous studies. The highly
 efficient accretion seen at short orbital periods implies that systems
@@
 results to assumptions about the initial disk model, and also
-investigate how far material can radially mix across the boundary
-between modes.
+investigate that our simplified collision model has on the emergence
+of this non-oligarchic growth mode in a planet forming disk.
 \end{abstract}
@@
 \citep{johansen14, birnstiel16} are appropriate to describe how these
-numerous, small bodies coagulate. Due to the internal pressure support
+numerous, small bodies coagulate.
+
+Due to the internal pressure support
 of the gas disk, the gas itself orbits at sub-Keplerian speed and
 exerts a headwind on any solids large enough to decouple from the gas
-\citep{weidenschilling77}. Above about a meter in size, this headwind
-is maximally effective at sapping away angular momentum, and planet-building material can fall onto the central star on catastrophically short timescales \citep{weidenschilling77, nakagawa86}.
-Additionally, laboratory experiments suggest that collisions between mm- to cm- sized solids tend to result in bouncing or destruction, rather than continued growth \citep{blum93, beitz11, colwell03}.
-For these reasons, a number of mechanisms which involve radially concentrating solids in a planet-forming disk have been proposed to facilitate fast growth from mm to km sizes \citep{johansen07, lyra08, bai10}.
-Interestingly, formation models for the short-period multiplanet systems revealed by Kepler \citep{fabrycky14} also seem to require enhanced concentrations of planet-building material to reproduce the observed architectures \citep{raymond07, hansen12}.
+\citep{weidenschilling77}. Around a meter in size, this headwind
+is maximally effective at sapping away orbital angular momentum, and planet-building material can fall onto the central star on 
+catastrophically short timescales \citep{weidenschilling77, nakagawa86}. Additionally, laboratory experiments suggest that 
+collisions between mm- to cm- sized solids tend to result in bounces or destruction, rather than continued growth
+\citep{blum93, colwell03, beitz11}.
 
-Regardless of how the mm- to km-sized growth barriers are surmounted, gravity begins to dominate and aerodynamic gas drag plays a less significant role beyond this size.
-During this phase, collision cross sections are enhanced as gravitational focusing \citep{safronov69} acts to bend the trajectories of bodies undergoing close encounters.
-Because larger bodies are more effective at focusing the trajectories of nearby planetesimals, a period of runaway growth occurs \citep{wetherill89, kokubo96, barnes09}.
-Eventually, the largest bodies (known as oligarchs) dynamically heat the surrounding planetesimals, severely limiting further growth \citep{kokubo98}.
-The end result of this phase is a bimodal population of dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals.
-Lines of evidence suggest that the asteroid belt, Kuiper belt and the Oort cloud are largely composed of the leftovers of this stage of planet formation.
+For these reasons, a number of mechanisms to radially concentrate solids in a planet-forming disk have been proposed to 
+facilitate fast growth from mm to km sizes \citep{johansen07, lyra08, bai10} in order to surmount these barriers. Interestingly, 
+formation models for the short-period multiplanet systems revealed by Kepler \citep{fabrycky14} also seem to require enhanced 
+concentrations of planet-building material to reproduce the observed architectures \citep{raymond07, hansen12}.
+
+Regardless of how the mm- to km-sized growth barriers are surmounted, gravity begins to dominate and aerodynamic gas drag 
+plays an increasingly unimportant role beyond this size. During this phase, collision cross sections are enhanced as gravitational 
+focusing \citep{safronov69} acts to bend the trajectories of bodies undergoing close encounters. Because gravitational focusing 
+becomes more effective as bodies grow larger, a period of runaway growth occurs \citep{wetherill89, kokubo96, barnes09} and a 
+power law spectrum of masses develop. Eventually, the largest bodies (known as oligarchs) dynamically heat the remaining 
+planetesimals, severely limiting further growth \citep{kokubo98}. The final outcome of this phase is a bimodal population of 
+dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals. Lines of evidence suggest 
+that the asteroid belt, Kuiper belt and the Oort cloud are largely composed of the leftovers of this stage of planet formation.
 
 After a long period of quiescence, the collection of embryos and
-remaining planetesimals undergoes a large-scale instability
+remaining planetesimals undergo a large-scale instability
 \citep{chambers98}.
@@
 on isolated, stable orbits and coalesce to form Earth-sized planets
-through a series of extremely energetic, giant 
+through a series of extremely energetic giant 
 impacts \citep{kokubo02, raymond05, raymond06}.
@@
 and the final giant impact phase, these steps in the terrestrial
-planet formation process have received the most attention in the
+planet formation process have received most of the attention in the
 literature. The planetesimal accretion phase, which we will focus on
-in this paper, falls into an awkward in-between, where there are too
+in this paper, is more difficult and expensive to model because there are too
 many particles to directly track with traditional N-body codes, while
-the gravitational influence of the few, but massive oligarchs that
-form make statistical methods an inappropriate approach. Because of
-this limitation, planetesimal accretion is usually modeled in a narrow
-ring, and the results are then scaled to suit whatever situation is being studied.
-N-body simulations of terrestrial planet formation typically begin with a series of neatly spaced oligarchs, whose mass varies smoothly with orbital period.
-As we will show in this paper, this extrapolation with orbital period is inappropriate, particularly at short ($<$ 10 day) periods.
+the gravitational influence of the few massive oligarchs that
+form make statistical methods inappropriate. Due to computational expense, N-body simulations of
+planetesimal accretion are usually modeled in a narrow
+ring \citep{kokubo96, kokubo98}, and the results and timescales are then scaled to suit whatever relevant orbital period is being 
+studied. N-body simulations of terrestrial planet assembly typically begin with a series of neatly spaced oligarchs, whose mass 
+varies smoothly with orbital period. As we will show in this paper, oligarchic growth does not scale to arbitrarily short
+orbital periods.
 
 Given that systems of tightly-packed inner planets (STIPs) appear to
-be a common outcome of planet formation, understanding exactly how
+be a common outcome of planet formation \citep{lantham11, lissauer11, rowe14}, understanding exactly how
 solids accumulate at short orbital periods is crucial. Although
@@
 section \ref{sec:narrow}, we present a parameter study of planetesimal
-accretion using a series of simulations of narrow annuli at various
-orbital periods.
-In section \ref{sec:fulldisk} we present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods.
-Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}.
-In section \ref{sec:discuss}, we discuss the implications of this multimodal accretion behavior throughout the disk for planet formation models and conclude.
+accretion using a series of simulations of narrow annuli that exhibit both oligarchic and non-oligarchic growth. In section 
+\ref{sec:fulldisk} we present a set of simulations starting with a  wide planetesimal disk and demonstrate that a transition 
+between accretion modes occurs at moderately small orbital periods. Next, we assess the impact of 
+simplifications made to our collision model on this result in section \ref{sec:assump}. In section \ref{sec:discuss}, we discuss the 
+implications of this multimodal accretion behavior throughout the disk for planet formation models and conclude.
 
@@
 
-We begin our analysis by considering a disk of equal planetesimals
+We begin our analysis by considering a disk of equal mass planetesimals
 with radius $r_{pl}$, mass $m_{pl}$ and surface density
@@
 by Keplerian frequency $\Omega$ can be written as $n \Gamma v$, where
-$n = \Sigma_{pl} \Omega / 2 m_{pl} v$ (where we have assumed that the scale height of the planetesimal disk goes as $2v/\Omega$. $\Gamma$ describes the effective
+$n = \Sigma_{pl} \Omega / 2 m_{pl} v$ (where we have assumed that the scale height of the planetesimal disk goes as $2v/\Omega$). $\Gamma$ describes the effective
 collision cross section and $v$ is the typical encounter velocity
@@
 
-In the case where the collision cross section, depends only
-% TRQ: perhaps "sub-linearly"?  I see dMdt ~ M^{2/3}
-on the physical size of the planetesimals, the growth scales linearly
+In the case where the collision cross section depends only
+on the physical size of the planetesimals, the growth scales sub-linearly
 with mass and the mass distribution is expected to evolve in an
@@
 However, bodies larger than $\sim 100$ km in size are expected to exert a significant gravitational force on each other during encounters and the collision cross section depends on both the size of the bodies and their encounter velocities.
-In this case, $\Gamma = \Gamma_{geo} \left( 1 + v_{esc}^2 / v^2 \right)$ \citep{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
+In this case, $\Gamma = \pi r_{pl}^2 \left( 1 + v_{esc}^2 / v^2 \right)$ \citep{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
 
 In the limit that $v_{esc} \gg v$, it can be shown that $dM/dt \propto
-M^{4/3}$, which implies a runaway scenario, in which growth
+M^{4/3}$, which implies a runaway scenario where growth
 accelerates with mass. This mode of growth was confirmed with N-body
@@
 An important feature is missing from the model described above, which
-limits its applicability at late times. Encounters between
-planetesimals that do not result in a collision play a crucial role
-over long timescales. These close encounters act to convert energy
-from Keplerian shear into random motion. Over time, this gravitational
-stirring effect will raise the typical encounter velocities between
-bodies and diminish the effectiveness of gravitational focusing. With
-a spectrum of masses, these velocity differences become even more
-pronounced because as the system evolves, it moves to a state of
-energy equipartition where $v \sim m^{1/2}$.
-For a system of equal mass bodies in which encounters are driven by random motions rather than Keplerian shear (dispersion dominated), the timescale for gravitational stirring is described by the two-body relaxation time \citep{ida93}
+limits its applicability at late times. Gravitational stirring, which converts
+Keplerian shear into random motion, raises the typical encounter velocity
+between planetesimals over time \citep{weidenschilling89, ida90} and diminishes the effectiveness of gravitational
+focusing. As the mass spectrum of the system evolves away from uniformity, these velocity differences become even more
+pronounced. As the system evolves, it tends toward a state of
+energy equipartition where $v \sim m^{1/2}$. For a system of equal mass bodies in which encounters are driven by random 
+motions rather than Keplerian shear (dispersion dominated), the timescale for gravitational stirring is described by the two-body 
+relaxation time \citep{ida93}
 \begin{equation}\label{eq:relax}
@@
 the fact that the behavior of gravitational stirring is well-described
-by the two-body formalism, \citep{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters.
-As we will show in section \ref{sec:narrow}, gravitational stirring effectively shuts off when the Hill sphere of a body becomes comparable to its physical size.
-In this case, close encounters tend to result in collisions, and the main pathway for energy exchange between planetesimals is unable to operate.
+by a two-body formula, \citep{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters, which 
+requires a three-body formalism. As we will show in section \ref{sec:narrow}, gravitational stirring effectively shuts off when the 
+Hill sphere of a body becomes comparable to its physical size. In this case, close encounters tend to result in collisions, and the 
+main pathway for energy exchange between planetesimals and growing protoplanets is unable to operate.
 
@@
 showed that runaway growth is actually self-limiting. As the runaway
-bodies grow larger, they become more effective at heating the
-remaining planetesimals, which diminishes the effectiveness of
-gravitational focusing and throttles the growth rate. Around the time
+bodies develop, they become increasingly effective at heating the
+remaining planetesimals, which diminishes the
+gravitational focusing cross sections and throttles the growth rate. Around the time
 that the mass of the runaway bodies exceeds the mass of the planetesimals
-by a factor of $\sim 50-100$ (depending on the orbital period)
+by a factor of $\sim 50-100$
 \citep{ida93} a phase of less vigorous ``oligarchic'' 
-growth commences, in which the few largest bodies continue to 
-accrete planetesimals at similar rates.
+growth commences, in which the largest bodies continue to 
+accrete planetesimals at similar rates, independent of mass.
 
-The picture described above relies upon an important assumption, which
+The picture described above relies upon an crucial assumption, which
 is that the mass distribution evolves slowly enough for gravitational stirring to maintain energy equipartition.
 In other words, the relaxation timescale must remain short relative to the growth timescale.
-For typical conditions near the terrestrial planet forming region of the solar system, this timescale condition is satisfied.
-Due to the steep dependence of the relaxation time on encounter velocity, this condition can easily be violated at shorter orbital periods.
+For typical conditions near the terrestrial region of the solar system, this timescale condition is satisfied.
+Due to the steep dependence of the relaxation time on encounter velocity, however, this condition can easily be violated at shorter orbital periods.
 
@@
 \right>^{1/2}$ \citep{ida93a} and that the eccentricity dispersion is
-constant with orbital period. The eccentricity dispersion is described
-in units scaled by the Hill factor $\left( m_{pl}/ 3 M_{\star}
+constant with orbital period. The eccentricity dispersion is 
+scaled by the Hill factor $\left( m_{pl}/ 3 M_{\star}
 \right)^{1/3}$ such that $e_{h} = 1$ corresponds to the boundary
@@
 gravitational scattering and growth will remain proportional as the
-oligarchs develop. In the case of many studies of planetesimal
-accretion in the solar system
-%TRQ: citations needed
-{\bf(cite examples)}, the $t_{relax} \ll t_{coll}$ condition must remain true, otherwise runaway growth would have continued until all of the planetesimals were consumed.
-However, it isn't immediately clear what will happen if the system begins in a state where $t_{coll} \ll t_{relax}$.
+oligarchs develop. In the case of the solar system, $t_{relax} \ll t_{coll}$ likely continued to remain true, otherwise runaway 
+growth would have consumed all of the small bodies and there would be nothing left to populate the asteroid or Kuiper belt. In 
+the case where $t_{coll} \ll t_{relax}$, however, it is not clear how the system might evolve.
 
 An insight into the expected behavior in this regime can be gained by
-defining the dimensionless parameter, $\alpha$, which is the ratio
-between the physical size of a body and its Hill radius, $r_{h}$:
+defining a dimensionless parameter, $\alpha$, which is the ratio
+between the physical size of a body and its Hill radius, $r_{h}$
 \begin{equation}\label{eq:alpha}
@@
 where $a$ is the semimajor axis of the body and $\rho_{pl}$ is its
-bulk density. Assuming a fixed bulk density as bodies collide and
+bulk density. Assuming that the bulk density stays constant as bodies collide and
 grow, and that no large-scale migration occurs, the scaling of both
-$r_{pl}$ and $r_{h}$ with $m_{pl}^{1/3}$ means that $\alpha$ will be
+$r_{pl}$ and $r_{h}$ as $m_{pl}^{1/3}$ means that $\alpha$ will be
 constant with time. For a composition of ice and rock, $\alpha$ is
-small for any populated region of the solar system ($\alpha \sim
-10^{-2}$ for Earth and $\alpha \sim 10^{-4}$ in the Kuiper belt). As
-one moves close to the star $\alpha$ becomes larger than 1, which
-implies that the physical extent of a body exceeds its Hill sphere.
-{\bf(also mention that hill sphere size independent of velocity for small eccentricity)}
+small for any presently populated region of the solar system ($\alpha \sim
+10^{-2}$ near Earth and $\alpha \sim 10^{-4}$ in the Kuiper belt). As
+one moves closer to the sun, $\alpha$ becomes larger than 1, which
+implies that the Hill sphere of a body becomes smaller than its physical size.
 
-The size of $\alpha$ controls the relative importance of gravitational scattering and collisions in driving the evolution of the planetesimal disk.
-In the case that $\alpha$ is small, most close encounters will result in a gravitational interaction only, moving the system toward a state of relaxation.
-If, however, the Hill sphere is largely filled by the body itself, these same encounters will instead drive evolution of the masses.
-Because $\alpha$ is independent of time, the innermost region of the planetesimal disk, where collisions dominate over scattering events, should remain that way.
+The magnitude of $\alpha$ controls the relative importance of gravitational scattering and collisions in driving the evolution of the planetesimal disk.
+When $\alpha$ is small, most close encounters will result in a gravitational interaction, moving the system toward a state of relaxation.
+If, however, the Hill sphere is largely filled by the body itself, these same encounters will instead drive evolution of the mass spectrum.
+Because $\alpha$ stays constant with mass, the boundary in the disk where collisions or gravitational encounters dominate, will stay static with time.
 
@@
 It should be noted that the gravitational focusing enhancement factor $v^{2}/v_{esc}^{2}$ is equal to 1 for $\beta = 1$.
-In the case where $r_{g}$ is smaller than the size of a planetesimal, the gravitational focusing enhancement factor will be between 0 and 1.
+In the case where $r_{g}$ is smaller than the size of a planetesimal, the gravitational focusing enhancement factor will be between 0 and 1 and the collision cross section is mostly set by the geometric value.
 
-These scaling considerations motivate the range of parameters in the
-following numerical experiments as we explore the different regimes.
+These scaling considerations motivate the range of parameters we choose for the numerical experiments presented in the next section, where we aim to understand where and when runaway and oligarchic growth can operate.
+
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/alpha_beta.png}
+    \caption{The initial (blue) and final (orange) states of the narrow annulus simulations described in section \ref{sec:narrow}. 
+    Relative masses of the bodies are indicated by point size. In the case of large $\alpha$, almost no residual planetesimal 
+    population remains. Regardless of the initial choice of $\beta$, the protoplanets that form attain similar eccentricities. 
+    \label{fig:alpha_beta}}
+\end{center}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_mass.png}
+    \caption{The final state of the mass distributions for the
+      narrow annulus simulations described in section \ref{sec:narrow}. For small
+      $\alpha$, a few embryos form alongside a power law tail of
+      planetesimals. For larger values of $\alpha$, the mass distribution stops being bimodal. 
+      As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.
+      \label{fig:alpha_beta_mass}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
+    \caption{The evolution of the ratio between the maximum and mean mass for the four simulations presented in section 
+    \ref{sec:narrow}. The runaway growth phase can be identified by a positive trend in this ratio. For all values of $\alpha$, an 
+    increase in $\beta$ has the effect of delaying runaway growth.\label{fig:alpha_beta_evo}}
+\end{center}
+\end{figure}
 
@@
 
-We use the tree-based N-body code {\sc ChaNGa}\footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}} to model the gravitational and collisional evolution of planetesimals at short orbital periods (where $\alpha$ is large).
-{\sc ChaNGa} is written using the {\sc CHARM++} parallel programming language and has been shown to perform well on up to half a million processors \citep{menon15} and can follow the evolution of gravitationally interacting swarms of up to billions of particles.
+We use the tree-based N-body code {\sc ChaNGa}\footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}} to model the gravitational and collisional evolution of a swarm of planetesimals.
+{\sc ChaNGa} is written using the {\sc CHARM++} parallel programming language and has been shown to perform well on up to half a million processors \citep{menon15} and can follow the evolution of gravitationally interacting collections of up to billions of particles.
 Using a modified Barnes-Hut tree with hexadecapole expansions of the moments to approximate forces, {\sc ChaNGa} integrates the equations of motion using a kick-drift-kick leapfrog scheme.
@@
 \citep{wallace19}.
-Particles are advanced in time on individual timesteps chosen as a
+Particles are advanced on individual timesteps chosen as a
 power of two of a base timestep.  The timestep for an individual
@@
 $\alpha$ case suggests that most encounters result in accretion
-instead of scattering. In the case of large $\beta$, the protoplanets
+rather than scattering. In the case of large $\beta$, the protoplanets
 and remaining planetesimals end up in a dynamically cool state,
 compared with the initial conditions. This is due to kinetic energy 
-being lost as particles inelastically collide. One final point to note 
-is the difference between eccentricities of the protoplanets in the 
+being lost as particles inelastically collide. One last point we note
+is the difference between the eccentricities of protoplanets in the 
 large $\alpha$, large $\beta$ and the small $\alpha$,
-%TRQ large alpha (former) is cooler!?!
 large $\beta$ case. The dynamically cooler result of the latter case
 is likely due to the dominant role that inelastic collisions play here.
-%TRQ Moving figure 2 up in the paper would help keep this discussion straight.
 
@@
 in figure \ref{fig:alpha_beta_evo}. On this plot, a positive slope
-indicates that the maximum and mean masses are diverging (i.e.
-the growth rate is accelerating with mass), which is
-evident for every case we have tested. Even with a large
-$\beta$, which means that the effective collision cross section is
-very near the geometric value, runaway growth still appears to
-operate. The ubiquity of the early positive trends in this figure indicates
-that, as bodies collide and grow the
+indicates that the quantities are diverging (i.e.
+the growth rate is accelerating with mass). This behavior is
+evident in all four cases. Even with a large
+$\beta$, where the effective collision cross section is
+ nearly equal to the geometric value, runaway growth still appears to
+operate. The ubiquity of the early positive trends in this figure suggests
+that as bodies collide and grow, the
 relative difference in gravitational focusing factors between bodies
 is what drives the system towards runaway
-growth. Although larger encounter velocities lengthen the growth
-timescales, this mode of growth appears to be inevitable, so long as
+growth, no matter how close the collision cross sections lie to the geometric value.
+Although larger encounter velocities lengthen the growth
+timescales, runaway growth appears to be inevitable, so long as
 gravity is the dominant force in the system. For the large $\alpha$
@@
 
-Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions (the physical and 
-Hill radius both scale with $M^{1/3}$, so $\alpha$ stays constant as bodies grow), controls the qualitative outcome of accretion. 
+Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions, controls the qualitative outcome of accretion. 
 Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will 
 facilitate oligarchic growth. In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and 
-embryos \citep{weidenschilling89, ida90}. When $\alpha$ is large, the Hill sphere of a body is no longer mostly empty space, 
-and close encounters that would otherwise result in stirring instead result in accretion. In this regime, we observe that runaway 
-growth still commences, but nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered 
-onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of planet formation 
-\citep{kokubo98, kokubo00}.
-
-% Additional idea: run a simulation with an oligarch embedded in a disk of planetesimals for large and small alpha.
-Allow oligarch and planetesimals to collide.
-What does the eccentricity evolution of the oligarch look like in each case?
-
-% One thing im still not clear on: In dispersion dominated regime, distant encounters are what drive VS + DF.
-These encounters happen well outside of the Hill sphere.
-Why does it appear to matter if the geometric cross section fills a significant chunk of the hill sphere?
-And why doesn't the velocity dispersion (beta large or small) appear to matter?
-
-% According to Ida 1990, 'distant encounters are not important' (but viscous stirring timescale can be described by Chandresehkar time).
-Also Weidenschilling 1989.
-This is also consistent with Goldreich 2004.
-So then why does the Armitage book describe viscous stirring in terms of distant encounters (b > b_min)?
-
-% Wetherill + Stewart 1989, Ohtsuki 1990, Spaute 1991 find that runaway growth happens when velocity decreases with mass. Is that what we're seeing at high alpha?
-
-%TRQ: switched to delta for power law index
+embryos \citep{weidenschilling89, ida90}. When $\alpha$ is non-negligible, the Hill sphere of a body is no longer mostly 
+empty space, and close encounters that would otherwise result in viscous stirring instead result in accretion. In this regime, we 
+observe that runaway growth still occurs, but nearly all of the planetesimals are consumed by the forming protoplanets, rather 
+than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of 
+planet formation \citep{kokubo98, kokubo00}.
 \begin{table}
@@
 
-\begin{figure*}
-\begin{center}
-    \includegraphics[width=\textwidth]{figures/alpha_beta.png}
-    \caption{The initial (blue) and final (orange) states of the narrow annulus simulations described in section \ref{sec:narrow}. 
-    Relative masses of the bodies are indicated by point size. In the case of large $\alpha$, almost no residual planetesimal 
-    population remains. Regardless of the initial choice of $\beta$, the protoplanets that form attain similar eccentricities. 
-    \label{fig:alpha_beta}}
-\end{center}
-\end{figure*}
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_mass.png}
-    \caption{The final state of the mass distributions for the
-      narrow annulussimulations described in section \ref{sec:narrow}. For small
-      $\alpha$, a few embryos form alongside a power law tail of
-      planetesimals. For larger values of $\alpha$, the mass distribution stops becoming bimodal. 
-      As in the previous figure, the initial choice of $\beta$ does not appear to have any meaningful impact on the end result.
-      \label{fig:alpha_beta_mass}}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
-    \caption{The evolution of the ratio between the maximum and mean mass for the four simulations presented in section 
-    \ref{sec:narrow}. The runaway growth phase can be identified by a positive slope in this ratio. For all values of $\alpha$, an 
-    increase in $\beta$ has the effect of delaying growth.\label{fig:alpha_beta_evo}}
-\end{center}
-\end{figure}
-
 \section{Full Disk Simulation}\label{sec:fulldisk}
@@
 
-Motivated by the dependence of accretion modes on $\alpha$,
+Motivated by the qualitative dependence of accretion on $\alpha$,
 we next investigate whether this highly efficient, non-oligarchic
@@
 cm$^{-2}$ is the surface density of the minimum-mass solar nebula
-\citep{hayashi81} at 1 AU, and $A$ is an enhancement factor.
-%TRQ: \delta = ???
-In the first case (fdHi), we model a disk that follows a MMSN power law slope, with the overall normalization enhanced by a factor of 100.
+\citep{hayashi81} at 1 AU, $A$ is an enhancement factor and $\delta$ is the power law index.
+In the first case (fdHi), we model a disk that follows a MMSN power law slope ($\delta$ = 1.5), with the overall normalization enhanced by a factor of 100.
 This choice of normalization for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \citep{hansen12}.
@@
 
-In all cases, the eccentricities and inclinations of the bodies are randomly drawn from a Rayleigh distribution, with $\left< e^{2} \right>^{1/2} = 2\left<i^{2} \right>^{1/2} = e_{eq}$.
+In all cases, the eccentricities and inclinations of the bodies are randomly drawn from a Rayleigh distribution, with $\left< e^{2} \right>^{1/2} = 2\left<i^{2} \right>^{1/2} = e_{eq}$ \citep{ida93}.
 The value of $e_{eq}$ is chosen such that the timescales for viscous stirring and aerodynamic gas drag on the planetesimals are in equilibrium.
@@
 The local gas volume density is given by
-%TRQ check this
 \begin{equation}\label{eq:rho_gas}
@@
 where $\Sigma_{g}$ is the gas surface density (taken to be
-240 times the solid surface density ({\bf citation for this number}), $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
+240 times the solid surface density \citep{hayashi81}, $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
 The sound speed profile is given by $c_{s} = \sqrt{k_{B} T(r) / \left( \mu m_{H} \right)}$, where $k_{B}$ is Boltzmann's constant, $T(r) = T_{0} r^{-Q}$, $\mu = 2.34$ and $m_{h}$ is the mass of a hydrogen atom.
@@
 
-In addition to the mutual gravitational forces, a Stokes drag force from to the gas disk is applied to each particle, following the prescription described in section 2.2.1 of \citet{morishima10}.
-%TRQ: add a qualitative description of the effect of this, e.g. what
-%is the drift timescale caused by this drag.
+In addition to the mutual gravitational forces, a Stokes drag force due to the the gas disk is applied to each particle, following the prescription described in section 2.2.1 of \citet{morishima10}.
+For the initial mass planetesimals, the stopping time (see equation \ref{eq:ts_stokes}) at the inner edge of the disk is roughly 100 yr.
+Although this is a few orders of magnitude shorter than the integration time of the simulations, the Stokes drag force plays a fairly insignificant role as the bodies grow via mutual collisions.
+By the time the bodies reach isolation mass (roughly a tenth of an Earth mass), the stopping time at the inner disk edge exceeds 50,000 years.
+Although the aerodynamic gas drag is not expected to significantly alter the final protoplanet distribution, we include its effects here to be self-consistent with the initial conditions, which were constructed by balancing the effects of viscous stirring with gas drag.
 
@@
 This more efficient scheme introduces two issues, however. Firstly,
-momentum is not completely conserved when bodies switch timesteps. The
+momentum is not completely conserved when bodies switch timestep tiers. The
 error introduced becomes particularly severe for a particle on an
-eccentric Keplerian orbit, whose perihelion and aphelion distances
+eccentric orbit, whose perihelion and aphelion distances
 straddle a timestep boundary. For a large collection of particles,
-this problem manifests itself as the development of a V-shaped gap in the semimajor axis-eccentricity plane, which is centered on the boundary itself.
+this problem manifests itself as the development of a V-shaped gap in the a-e plane, centered on the boundary itself.
 To correct this problem, we introduce a slightly modified timestepping criterion, which is based on the expected gravitational acceleration of the particle at pericenter.
-Only in the case of a close encounter with another planetesimal (in which the acceleration is no longer dominated by the star) is the timestep allowed to reduce based on the original criterion.
+Only in the case of a close encounter with another planetesimal (in which the acceleration is no longer dominated by the star) is the timestep allowed to reduce based on the original instantaneous criterion.
 
@@
 happen simultaneously for these bodies. Early in the simulation, we
-find that runaway growth tends to initiate at the timestep
-boundaries. This issue carries itself forward through the embryo
+find that this problem tends to trigger runaway growth at the timestep
+boundaries first. This issue carries itself forward through the embryo
 formation phase, and protoplanets tend to form at the boundaries. To
@@
 boundaries, while also minimizing the number of `skipped' collisions.\footnote{In the case of fdHi, only about 20 collisions out of an eventual 900,000 are ignored.}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/fulldisk_e_m_b.png}
+    \caption{The final state of the fdHi simulation. In the top panel,
+      the contours denote the initial period-eccentricity distribution
+      of the planetesimals. Point sizes indicate the relative masses
+      of bodies at the end of the simulation. In the bottom panel, we show the
+      feeding zone width (see equation \ref{eq:iso}) required to produce
+      the final masses of the bodies. The dashed line indicates the feeding
+      zone size ($\tilde{b} = 2 \sqrt{3}$) expected for bodies on
+      circular orbits.
+      Interior to the oligarchic
+      growth region (around 60 d), the feeding zone sizes exceed this value.\label{fig:fulldisk_e_m}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/pl_frac_time.png}
+    \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi 
+    simulation. Each curve represents a radial slice of the disk. The outermost region evolves the slowest, and is therefore 
+    represented by the top curve. The dashed lines indicate radial zones interior to the 60 day orbital period boundary.\label{fig:pl_frac_time}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/surfden_profiles.png}
+    \caption{The final state of the full disk simulations listed in table \ref{tab:sim_properties}. 
+    Point sizes indicate mass relative to the largest body in each simulation.\label{fig:surfden_profiles}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/surfden_b.png}
+    \caption{Feeding zone width (see equation \ref{eq:iso}) required to produce the final masses for the protoplanets from the 
+    simulations listed in table \ref{tab:sim_properties}. The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$. Despite the 
+    vastly different initial solid surface density profiles, the feeding zone width reaches the circular orbit value around $\sim$ 60 
+    days in all cases. \label{fig:surfden_b}}
+\end{center}
+\end{figure}
 
@@
 as a function of orbital period. The feeding zone size $\tilde{b}$ is
-calculated according to ({\bf citation})
+calculated according to \citet{kokubo02}
 \begin{equation}\label{eq:iso}
@@
 clearly visible. For two bodies on circular, non-inclined orbits,  $\tilde{b} = 2
-\sqrt{3}$ (indicated by the lower horizontal dashed line) is the smallest orbital separation that produces a non-negative Jacobi energy
+\sqrt{3}$ (indicated by the horizontal dashed line) is the smallest orbital separation that produces a non-negative Jacobi energy
 and permits a close encounter (see \citet{naka88}). In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
-to space themselves apart by $\tilde{b} = 10$, (top horizontial line in
-figure \ref{fig:fulldisk_e_m}, bottom panel) although it should be noted that they do not consume all of the planetesimals 
+to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
 within this distance.
@@
 very few remaining planetesimals and the embryos formed have larger feeding zones. Exterior to the boundary, the residual 
-planetesimal population is much more unmodified, and protoplanets more closely follow the $\tilde{b} = 2 \sqrt{3}$ line. This 
+planetesimal population is much more visible, and protoplanets more closely follow the $\tilde{b} = 2 \sqrt{3}$ line. This 
 suggests that the transition between the low $\alpha$ and high $\alpha$ accretion modes seen in section \ref{sec:narrow} 
-happens near this location.
+is happening near this location.
 
@@
 
-%TRQ: \sigma is not defined.
 To ensure that the boundary seen near 60 days in orbital period is not
 simply a transient product of the inside-out growth throughout the
-disk, we examine the time evolution of $\sigma/\Sigma$ at multiple
-orbital periods. In figure \ref{fig:pl_frac_time}, the value of
+disk, we examine the time evolution of $\sigma/\Sigma$, which compares the planetesimal and total solid surface density at 
+multiple orbital periods. In figure \ref{fig:pl_frac_time}, the value of
 $\sigma/\Sigma$ is plotted as a function of time in 10 orbital period
@@
 should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle 
-onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimal mass should remain out of reach of the 
-protoplanets.({\bf citation here})
-
-% Another important point: the accretion boundary doesn't move as we change surface density (how does t_relax and t_coll scale with sigma?). More evidence that it just depends on alpha(r)
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/fulldisk_e_m_b.png}
-    \caption{The final state of the fdHi simulation. In the top panel,
-      the contours denote the initial period-eccentricity distribution
-      of the planetesimals. Point sizes indicate the relative masses
-      of bodies at the end of the simulation. In the bottom panel, we show the
-      feeding zone width (see equation \ref{eq:iso}) required to produce
-      the final masses of the bodies. The lower dashed line indicates the feeding
-      zone size ($\tilde{b} = 2 \sqrt{3}$) expected for bodies on
-      circular orbits.
-%TRQ: upper horizontal line ....
-      Interior to the oligarchic
-      growth region (around 60 d), the feeding zone sizes exceed this value.\label{fig:fulldisk_e_m}}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/pl_frac_time.png}
-    \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi 
-    simulation. Each curve represents a radial slice of the disk. The innermost region evolves the quickest, and is therefore 
-    represented by the lowest curve. The dashed lines indicate radial zones interior to the 60 day orbital period boundary.\label{fig:pl_frac_time}}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/surfden_profiles.png}
-    \caption{The final state of the full disk simulations listed in table \ref{tab:sim_properties}. 
-    Point sizes indicate mass relative to the largest body in each simulation.\label{fig:surfden_profiles}}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/surfden_b.png}
-    \caption{Feeding zone width (see equation \ref{eq:iso}) required to produce the final masses for the protoplanets from the 
-    simulations listed in table \ref{tab:sim_properties}. The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$. Despite the 
-    vastly different initial solid surface density profiles, the feeding zone width reaches the circular orbit value around $\sim$ 60 
-    days. \label{fig:surfden_b}}
-\end{center}
-\end{figure}
+onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimals should remain out of reach of the 
+protoplanets\footnote{A feeding zone width of $ \tilde{b} = 2 \sqrt{3}$ covers roughly 70 percent of the 10 $r_{h}$ space between the protoplanets.}.
 
@@
 is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which 
-offsets the fact that the initial bodies started off in a dynamically hotter state. The only exception to this is the fdLo simulation, 
+offsets the fact that the initial bodies started off in a dynamically hotter state (due to the increased effectiveness of viscous stirring). The only exception to this is the fdLo simulation, 
 where the resulting eccentricities are a couple orders of magnitude smaller. Inelastic damping likely plays an even more 
-% TRQ: ??? the masses of the initial planetesimals are the same in all
-% simulations according to table 1.
 significant role here, due to the much larger masses of the initial planetesimals.
@@
 \tilde{b}$ (see equation \ref{eq:iso}). 
-As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the  
-feeding zone width that a body on a circular orbit should have. In all four simulations, the feeding zone width exceeds the 
+As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) is the  
+feeding zone width that a body on a circular orbit will have. In all four simulations, the feeding zone width exceeds the 
 minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days. The orbital periods at which this transition 
 occurs are quite similar between simulations, despite the vastly different solid surface density profiles used. This indicates that 
-the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our 
+the boundary between accretion modes is driven entirely by the local value of $\alpha$, and also supports our 
 conclusion that planetesimal accretion is largely complete everywhere in the disk.
@@
 Further insight regarding the difference between the short vs long period accretion modes can be gained by looking at the 
-merger history of the planetary embryos. Because all collisions are directly resolved by the N-body code, a direct lineage can be 
-traced between the resulting planetary embryo and the initial planetesimals.
+growth history of the planetary embryos. Because all collisions are directly resolved by the N-body code, a lineage can be 
+traced between each planetary embryo and the initial planetesimals.
 
@@
 For the short period bodies, there is a decreasing correlation between smooth accretion fraction and mass, which suggests that most growth occurs between equal mass bodies.
-For the longer period bodies in the oligarchic growth region, this trend is flat, indicating that accretion of planetesimals is important during all phases of evolution.\label{fig:minor_frac}}
+For the bodies in the outer disk, this trend is flat, indicating that accretion of planetesimals is important during all phases of evolution.\label{fig:minor_frac}}
 \end{center}
@@
 
-%TRQ: perhaps use a logarithmic horizontal axis for better comparison
 \begin{figure*}
@@
 The hash marks indicate the present position of the body.
-The accretion distributions indicate the initial locations of the planetesimals that were used to assemble a body, rather than the locations at which collisions with the massive body occurred.\label{fig:acc_zones}}
+The histograms indicate the initial locations of the planetesimals that were used to assemble a body.\label{fig:acc_zones}}
 \end{center}
@@
 Inside the boundary, however, later growth events tend to be dominated by embryo-embryo collisions, and the smooth accretion fraction drops as mergers with planetesimals play a less significant role.
-As we discussed in section \ref{sec:sizeandhill}, gravitational scattering should be very weak in the inner disk.
-Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion (see \citet{kokubo98}), and so a lack of gravitational scattering should prevent the embryos from settling onto neatly-spaced, isolated orbits.
-As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zones predicted by an oligarchic growth model.
-Figure \ref{fig:minor_frac} suggests that this extra mass here obtain comes from mergers with the other nearby embryos.
+Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion (see \citet{kokubo98}), and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
+As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zone size predicted by an oligarchic growth model.
+Figure \ref{fig:minor_frac} suggests that the extra mass here obtain comes from mergers with the other nearby embryos.
 
@@
 bodies from the fdHi simulation and arranged them in order of final
-orbital period. On each line, the black
-%TRQ: the mark is dark blue, not black.
-hash mark indicates the present orbital period of an embryo and the gray histogram represents the initial orbital period distribution of the planetesimals which were used to construct the embryo.
-One should note that unlike the previous figure, this plot shows where every single bit of mass (in the form of planetesimals) originated, rather than only denoting embryo-planetesimal collisions.
+orbital period. On each line, the blue
+hash mark indicates the present orbital period of an embryo and the histogram represents the initial orbital period distribution of the planetesimals used to construct the embryo.
+One should note that unlike the previous figure, this plot shows where every single bit of mass (in the form of planetesimals) originated, rather than only indicating the result of direct collisions with the embryos.
 
-Qualitatively, there are a couple of differences between the initial planetesimal distributions in the inner ($<$ 60 days) and outer ($>$ 60 days) part of the disk.
-The planetesimal distributions for the outer disk are much more smooth and unimodal, while many of the distributions near the inner disk have multiple peaks.
-As we discussed when examining figure \ref{fig:minor_frac}, growth events for the inner embryos tend to be sudden and stochastic, often involving pairs of embryos.
+Qualitatively, there are a couple of key differences between the initial planetesimal distributions in the inner ($<$ 60 days) and outer ($>$ 60 days) part of the disk.
+The planetesimal distributions for the outer disk are much more smooth and unimodal, while many of the distributions near the inner disk rather disjoint.
+As discussed when examining figure \ref{fig:minor_frac}, growth events for the inner embryos tend to be sudden and stochastic, often involving mergers with other embryos.
 When an embryo-embryo collision happens, one would expect a second peak to appear in the accretion distribution as the merger tree suddenly obtains a whole other subtree from the embryo that it absorbed.
@@
     at the end of the fdHi and fdHif4 simulations.  The bottom panel shows the variation of $\alpha$ with orbital period for the 
-    bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of 
-    the embryo mass distribution and isolation mass. The shaded region
+    bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the location at 
+    which $\tilde{b}$ exceeds $2 \sqrt{3}$. The shaded region
     in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
@@
     indicating relative mass. The blue points represent the initial state of the simulations. The bottom panel compares the final 
-    mass distributions of the bodies. \label{fig:frag_ecc}}
+    cumulative mass distributions of the bodies. \label{fig:frag_ecc}}
 \end{center}
@@
     In both cases, the system first evolves through a phase of runaway growth, before the massive bodies consume the smaller 
-    bodies, driving down the mean mass. With the bounce-merge model, the mass ratio decreases later because not all collisions 
-    result in growth.\label{fig:frag_evo}}
+    bodies, driving down the mean mass. With the bounce-merge model, the mass ratio takes much longer to begin decreasing.\label{fig:frag_evo}}
 \end{center}
@@
 For the simulations presented in this work, every collision results in a perfect merger between pairs of bodies, with no loss
-of mass or momentum. Although simpler and less computationally expensive to model, allowing every collision to produce a
-merger might result in overly efficient growth, particularly in the innermost region of the disk where the encounter velocities are 
-largest. A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic model (see 
-\citet{leinhardt12}). However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of bodies to 
-bounce is too expensive to model, even with {\sc ChaNGa}.
+of mass or energy. Although simpler and less computationally expensive to model, allowing every collision to produce a
+perfect merger might result in overly efficient growth, particularly in the innermost region of the disk where the encounter 
+velocities are largest. A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic 
+model (see \citet{leinhardt12}). However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of 
+bodies to bounce is too expensive to model, even with {\sc ChaNGa}.
 
 To test whether a more restrictive collision model should alter the growth mode of the inner disk, we ran a smaller scale test 
-using a slightly more restrictive collision model. In this case, a collision can result in one of two outcomes: if the impact velocity is 
+using a more restrictive collision model. In this case, a collision can result in one of two outcomes: if the impact velocity is 
 smaller than the mutual escape velocity of the colliding particles, defined as
@@
 \citep{leinhardt12}. Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner 
-disk's planetesimal accretion phase, and so a partial accretion model should do the same.
+disk's planetesimal accretion phase, and so a more realistic partial accretion model should do the same.
 
 To compare the outcome of the two collision models, we have chosen to use the initial conditions from the fdLo simulation, but 
-have truncated the disk beyond 3 days in orbital period. We truncate the outer disk because the particle count with the bounce-
-merge model declines much more slowly, while also requiring many more timesteps overall.
+have truncated the disk beyond 3 days in orbital period.
+This offsets the increased computational cost of the more restrictive collision model, while still allowing the disk to evolve in the region where mergers would be most difficult to achieve.
 For the initial conditions we have chosen, the typical encounter velocity (defined by $v_{enc} = \left< e^{2} \right>^{1/2} v_{k}$, 
@@
 In this work, we have demonstrated that planetary embryo growth
-can operate in two distinct modes in a planet-forming disk. In the first
+can simultaneously operate in two distinct modes in a planet-forming disk. In the first
 mode, gravitational feedback from the growing embryos heats the
@@
 We have demonstrated the outcome of both accretion modes through a
-sparsely sampled parameter study. The initial planetesimal distribution can be described in terms of two dimensionless 
+simple parameter study using a narrow annulus of planetesimals. The initial planetesimal distribution can be described in terms of two dimensionless 
 constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) 
@@
 
-So long as the density of the bodies does not significantly change as
+So long as the density of the bodies do not significantly change as
 their mass distribution evolves, this ratio, and therefore the
-boundary between these accretion modes is set entirely by the distance
+location of the boundary between these accretion modes is set entirely by the distance
 from the star. Because both the physical and Hill radii of the bodies
@@
 accretion history of embryos on both sides of the boundary provide further evidence to
-suggest that oligarchy is not operating in the inner disk.
+suggest that oligarchic growth is not operating in the inner disk.
 
@@
 and showing that the boundary moves to the predicted location when running a simulation with a slightly smaller inflation factor. 
-For planetesimals with a realistic bulk density, this boundary should lie around 5 days in orbital period.
+For rocky planetesimals with a realistic bulk density, this boundary should lie around 5 days in orbital period.
 
@@
 might wonder this high-$\alpha$ accretion mode might be relevant for a
-circumplanetary system. There is a small collection of previous works
+circumplanetary accretion. There is a small collection of previous works
 which use N-body methods to examine in-situ satellitesimal accretion
@@
 Presently, the implications that this non-oligarchic accretion mode has for the formation of short-period terrestrial planets, and 
-whether the accretion boundary would leave any lasting imprint on the final orbital architecture, is unclear. One point that our 
+whether the accretion boundary would leave any lasting imprint on the final orbital architecture, is unclear.
+The extreme efficiency of planetesimal accretion at the inner edge of the disk suggests that no residual populations of small bodies should be expected to exist here.
+A crucial point that our
 results do highlight is that the initial conditions used for most late-stage planet formation simulations are overly simplistic. 

### 2023-01-19 makeFig.py

@@ -400,7 +400,7 @@ def plot_fulldisk_e_m_b():
 	axes = ax[1]
 	axes.scatter(per.value, get_btilde(plVHi, p_vhi_ic), edgecolor='black', linewidth=0.4)
 	axes.axhline(2.*np.sqrt(3.), ls='--', color='gray')
-	axes.axhline(10., ls='--', color='gray')
+	#axes.axhline(10., ls='--', color='gray')
 	axes.set_ylim(0, 20)
 	axes.set_xlabel('Orbital Period [d]')
 	axes.set_ylabel(r'Required $\tilde{b}$')
@@ -704,14 +704,14 @@ def plot_acc_zones():
 
 	s = 1000
 	amin, amax = 0.05, 0.2
-	histbins = np.linspace(0, 100, 200)
+	histbins = np.logspace(0, 2, 200)#np.linspace(0, 100, 200)
 
 	def p_orbit(a):
 		return ((np.sqrt(a**3/mCentral))*u.yr).to(u.d).value
 
 	def oli_plot(i, idx):
 		child_p = p_orbit(a_init[i])
-		hist, bins = np.histogram(child_p, bins=histbins, normed=True)
+		hist, bins = np.histogram(child_p, bins=histbins, density=True)
 		bins = 0.5*(bins[1:] + bins[:-1])
 		hist /= np.max(hist)/0.1
 		axes.plot(bins, hist+0.2*idx, drawstyle='steps-mid', lw=0.5)
@@ -722,6 +722,7 @@ def plot_acc_zones():
 		axes.set_xlabel('Orbital Period [d]')
 		axes.set_ylabel('Fraction of Planetesimals Accreted')
 		axes.set_yticks([])
+		axes.set_xscale('log')
 
 	# Sort by semimajor axis beore plotting
 	indices = np.arange(0, 20)
@@ -963,7 +964,7 @@ def plot_frag_evo():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	fig, axes = plt.subplots(figsize=(8,8))
+	fig, axes = plt.subplots(figsize=(8,6))
 
 	axes.plot([], [])
 
@@ -1051,7 +1052,7 @@ def plot_frag_acc_zones():
 #plot_alpha_beta()
 #plot_alpha_beta_evo()
 #plot_alpha_beta_mass()
-plot_fulldisk_e_m_b()
[…]

### 2023-03-01 refereeResponse.txt
Add multiple simulations to figure 8, rescale x axis in figure 6 to units of accretion time

cript at hand presents a numerical study of planetesimal accretion. The authors identify a novel mode of accretion that operates if the primary's radius is a significant fraction of its hill-radius - a criterion the authors find to be met at short orbital periods in circumstellar disks. This new accretion mode is shown to be highly efficient, resulting in several large planetary embryos and a depletion of the primordial planetesimal formation, and is therefore distinct from bimodal planetesimal distribution that is the end product of an oligarchic growth phase.

I find the presented research to be innovative, interesting, and valuable for the scientific community. However, before I can recommend the manuscript for publication, I believe there are several areas that require improvement. Specifically, I suggest that the authors address the five major comments outlined below to ensure that the findings are properly supported and effectively communicated. I also include a detailed list of specific notes, comments and questions that I suggest the authors consider when revising the manuscript. I appreciate the authors' work and look forward to seeing the progress on the manuscript.

Major Comments

1) I am unconvinced that the orbital period of P = 60 days is such a clear-cut, and universal boundary between oligarchic accretion mode and the new 'high-alpha' accretion mode. As far as I understand, the authors motivate this value mainly from their fdHi simulation e.g. Fig. 5, when the value for tilde b of the largest bodies falls below the critical value of 2sqrt(3). I would naively argue that for fdHiShallow and for fdLow, this is happening at ~40 and ~70 days respectively (Fig. 8). A key feature of the oligarchic growth mode seems to be the production of a bimodal distribution of bodies. Even for fdHi, this is the case up to an inner orbit of P = 10 d. Next, in Fig.6 which plots the evolution of the primordial planetesimal surface density, I do not see a clear qualitatively different behavior between the curves for 50 and 60 orbits, vs the curves for 60 or 70 orbits. Yes, the depletion of planetesimals becomes more rapid the more one moves towards the star, but to first order, I would imagine this is just due to dynamical timescales becoming shorter. In addition, the authors argue that the shape of the accretion zone changes outside vs inside of P=60d. I agree that there is a qualitative change, but to me, this change happens only at 10-20 orbits. Lastly, it seems to me that the value for the boundary could be quite sensitive to the random seed. If for example in the fdHi simulation the body at ~ 55d had a tilde b of less than 2sqrt(3), then one could immediately argue that that P~40d-50d is a more appropriate value for the location of the accretion mode transition.
In summary, to me it seems like the presented simulations are much more indicative of the mode of accretion somewhat smoothly changing from oligarchic to 'high-alpha' as alpha is increased, and that it is therefore challenging defining a clear boundary between the two modes.
I suggest that the authors either soften their statements on this, or present additional, quantitative arguments supporting their claims about the universality of this sharp boundary.

	Update figure 6 to show the time evolution in units of the local collision timescale. After doing so, the oligarchic curves lie on top of each other, and the inner non-oligarchic ones don't. This implies two qualitatively different accretion modes.

	Update figure 8 to show multiple versions of each simulation. Gives a much clearer estimate of the error bars on the P=60d estimate.

2) Related to my first point, I think a very interesting, yet somewhat unanswered question is what alpha exactly corresponds to the transition between accretion modes. The authors allude to alpha = 0.1 being of importance, but this choice currently feels somewhat arbitrary. For example, in Figure 11, the authors show the alpha profile for their simulations and show that alpha falling below 0.1 approximately corresponds to tilde b of the largest bodies falling below the critical value of 2sqrt(3). Is there a specific reason for this? Or is this what motivates the choice of alpha = 0.1 in the first place? If so, I think this is an interesting finding, because it allows for a direct prediction of the dominant mode of accretion given the size and location of a planetesimal. Also, how consistent is this alpha = 0.1 value with the simulations with different surface density power laws listed in Table 2?
I recommend that this, in my opinion, quite interesting point is discussed in more detail in the manuscript.
The authors utilize a simplified collision model in which each collision results in a merger. They also perform a test with a merge-bounce model in which some collisions result in an inelastic bounce rather than a merger. They argue that physical collisions are somewhere in-between, and, given that there is little qualitative difference between only-mergers and bounce-merger models, the model outcome should well represent the outcome of physical collisions.

	alpha = 0.1 entirely comes from looking at figure 11. It is simply the location in the disk where the feeding zones settle down to 2*sqrt(3). alpha < 0.1 roughly corresponds to "alpha << 1". Show the b_tilde plots alongsize the alpha curve for the other simulations.

3) I am unconvinced that the test of the collision model indeed is an extreme case. In particular, I'm imagining a very destructive, inelastic collision such that all fragments are smaller than the original bodies. Say the fragments follow a power law distribution assuming a collisional cascade (see Dohnanyi 1969, Zvyagina et al 1974). It's not obvious to me that resupplying smaller bodies to the planetesimal population this way would not impact the merger history. In the extreme case, the entire embryo population would be grinded down by destructive collisions. The authors' bounce-merge model, is essentially equivalent to less efficient, but ultimately constructive planetesimal accretion (thus leading to a prolonged runaway growth phase as shown in Fig. 13). If smaller collisional fragments are re-supplied this could have for example consequences for orbital repulsion and gravitational scattering, which as the authors argue in Sect. 5 requires the presence of smaller planetesimals.
Could the authors comment on this? Maybe the authors can argue why collisions are not expected to be destructive, and clarify why resupplying smaller bodies does not affect the subsequent evolution of the system.

	Accretion mode is size independent (only depends on density and orbital period), so the growth for smaller bodies should behave exactly the same. No chance of enhanced orbital repulsion or scattering with smaller bodies. The other concern to adress would be whether material gets ground down and removed faster than the embryos can grow. Need to compare the growth timescale and calculate some sort of mass removal timescale (look into this).

	Mass removal mechanisms: grinding to meter sizes, radial drift
							 grinding to dust size, pr drag

4) I think the introduction of several physical concepts warrants additional clarification for accessibility and clarity of the manuscript, and sometimes also lack concrete definitions. In particular, this includes isolation mass, the concepts of tidal stability and Hill radius, the eccentricity dispersion e_h, and the exact definition of tilde b. See my specific comments below.

5) I have some suggestions for improving the presentation of the results in Figures, to make the science result more clear and intuitively obtainable. In my specific comments below, I included suggestions for the figures.

Specific comments, notes and suggestions.

Abstract
7: Are short period planets that exotic in the broader context of exoplanets?
14: "[...] population OF dynamically [...]"
17-18: something is missing in the second part of this sentence.

1.Introduction
26: How large are these solids? I assume this is referencing micron sized dust-grains?
68: Add reference
72: Maybe elaborate on this. How long is the period of quiescence? How does this instability work?
88: Add reference maybe.
99: Capitalize "Systems of Tightly-packed Inner Planets"
104: Gas-Disk driven migration → reference?
116: What is the "isolation mass" initial condition? Maybe isolation mass can be defined
118: I'm not sure if this belongs in the introduction. I think the mention of future work at the end of the discussion is sufficient.

2. Overview of planetesimal accretion
2.1 Oligarchic and Runaway Growth
144 onwards: indices in math upright
152: Define rms velocity
161: What does "orderly" fashion mean exactly?
174: Add reference.
198: Ln Lambda approx 10 missing could use a reference.
204: I suggest more formally introducing the concept of Hill sphere and hill factor.
209: This sentence seems not necessary.
213: add "dynamically" heating
222: add "a" crucial assumption
226: Maybe clarify that growth timescale equals collision time scale.
238: The eccentricity dispersion e_h is never defined anywhere. It is unclear to me what scaling e_h with the Hill-factor means physically.
Figure .1:
Since this is an analytical plot, I think one could color the entire parameter space according to the ratio t_relax/t_coll. Currently, it may suggest that the plotted values for e_h are chosen for a particular reason.
Also, I think it would be nice to have a reference for what values of e_h are standard for certain disk conditions, i.e. how outrageous would it be to have a e_h = 16? Are all disks like that? Or do we expect e_h = 1 as the standard?
Also, I recommend adjusting the x-limits of the plot to correspond to the limits of the orbital period.

2.2 Planetesimal Size and Extent of Hill Sphere
253: "will remain proportional" - Proportional to what?
254: but this doesn't have to be the case at all orbital periods, right? Given Fig.1 it seems clear that outside of 1AU, and especially for the Kuiper Belt this condition seems to be fulfilled.
263: Again, I think the concept of Hill radius and tidal stability needs to be formally introduced earlier.
273: Wouldn't these bodies then be tidally disrupted, and therefore not exist? Alpha > 1 is certainly not true for any solar system bodies that I am aware of. I understand that the scaling of alpha predicts alpha >1 at some radius (which I would explicitly mention), but this just implies that inside this radius, bodies must have greater densities to not be disrupted.
289: gravitational radius: is this physically motivated? Maybe reference
296: beta > 1 means collision cross section > geometric and small gravitational focusing. I recommend explicitly stating what the physical intuition for beta < 1 is.

I think this section could be improved by having a schematic of the three sizes, for two different sets of alpha and beta, that highlights the physical meaning of both. This would communicate intuition for the two dimensionless parameters, and thus allow for a smoother read-through of the N-body results.

3. Numerical Methods
335: children: Would those not be the parent particles?

4. Narrow Annulus Simulations
352: I think it's somewhat ambitious calling four simulations a parameter study.
362: Regarding the initial condition, I recommend adding some more intuitive mass units, i.e. approx 0.5 Ceres masses, as well as the corresponding radius 341 km. Also, to what is the bulk density reduced to? Is this still physical? What is the corresponding radius? Maybe motivate the initial planetesimal masses / radii (e.g., Morbidelli 2009, Hartlep & Cuzzi 2020, Gerbig & Li, 2023). Also, maybe put the total mass of the planetesimals into context. I think this is 0.33 Earth masses, within 0.1 AU of Earth, the feeding zone of Earth.
367: I'm assuming the semi-major axis is also drawn from a uniform distribution?
377: is alpha=1 chosen because it is the highest stable alpha? If so I would write that. Why is beta = 15000 chosen?

Figure.2: Some suggestions to improve this figure are:
A reference planetesimal size that shows what mass a circle has
Horizontal lines in each panel showing where e_h is
Maybe consider having beta value as a column label and alpha value as a row label. I would also explicitly state the values for alpha.
I would also probably label the four panels / cases a,b,c,d and then refer as such in the text body

391: Why would this because there are no high eccentricity planetesimals. Isn't the fact that there is no residual population not already evidence that encounters are accreting rather than scattering? Also, isn't this also not just very expected since alpha exactly quantifies the relative importance of scattering vs accretion?
394: small alpha, large beta doesn't look dynamically cool to me.
400: Small alpha large beta does not look dynamically cooler than large alpha large beta to me. In fact, the opposite.
402: I don't really understand why small alpha small beta leads to so many dynamically hot bodies, both planetesimals and protoplanets. Maybe the authors can elaborate.
Figure 3:
Again, I really think labeling the cases would be helpful.
I would express the mass in units of e.g. Ceres
406: I'm not sure about "significantly" larger. The biggest body in large alpha, small beta is about a factor 3 more massive than in small alpha, small beta. This is only a factor of 1.4 in size.
415: the y-label in Fig.6 does not match the description in the text
Figure 4:
Why don't the simulations start all with m_max/m = 1?
I'd be interested in also having another panel that shows the evolution of just M_max and <m> (maybe in solid and dashed lines) for the four simulations. That would also underscore that the turnover is driven by an increase in <m> rather than m_max.

418: I would specifically state that for the large alpha cases runaway growth only occurs at the start, to avoid initial confusion that the slope turns around when the planetesimal supply is depleted.
435: Is this true? I was under the impression that the residual planetesimal population remains? I think this does not seem consistent with the rest of the work...?
446: What exactly does alpha being non-negligible mean? Given that alpha is always less than unity, what alpha value marks the transition of the oligarchic growth regime vs, consumption regime? See major comment.

5. Full disk Simulation
5.1 Initial Conditions
470: Reference of TRAPPIST-1
483 I recommend writing Eq. (6) along the lines of 10 g/cm^2 \times A (M_*/M_\odot)(r/1AU)^(-delta) for readability. The Sigma_MMSN is never used so it's not necessary.
Table 1.
I don't think the notes are necessary
I would probably put the planetesimal masses in units of Ceres
I think Table 1 and Table 2 could be combined

490: How could such an enhancement in planetesimal surface density be achieved initially? Is this initial condition consistent with planetesimal formation models, e.g. Dra̧żkowska & Dullemond 2018, Lenz et al 2019.
493: What is the motivation behind variation in the power-law index? Is there significant uncertainty in the MMSN power law index?
499: Maybe elaborate on why this equilibrium is physical? Are there other works which use the same balance to inform initial conditions?
504: missing respectively. And semi-major axes.
505: When is the Stokes regime valid, and what does it mean?
506: The letter tau is used for a timescale just above, but now it says t. I would recommend staying consistent. Tau tends to be used for dimensionless timescales, so I would probably go with t_s and t_vs.
511: Solid-to-gas surface density ratio of 1/240 seems very small, especially given that the authors are considering the solid surface density to already be enhanced by a factor of 100. Also, if the planetesimals are already formed, it is conceivable that the gas disk is already dissipating (especially so close in). I think the authors could be over-estimating the gas density by up to a factor of a 100, which means the stopping time would be a factor of 100 longer.
516: I suggest using another symbol for the temperature power law, since Q is associated with the Toomre value of the disk, for example q. Also, this equation should read T(r) = T_0(r/1AU)^-q, right?
521: Where is that equation coming from? Maybe add reference.

5.2. Gas Drag Force
512: I think it would be very informative to calculate the dimensionless stopping time, i.e. the Stokes number of the planetesimals, I'm assuming that they are substantially above unity, which means that the bodies are essentially decoupled from the gas.
536: Isolation mass lacks definition

5.3 Time-stepping Criterion
554: footnote 2 can just go in the main text body.
584: footnote 3 can also go in the main text body.
584: Are there any works on the numerical robustness of this more efficient time-stepping scheme. While I'm inclined to believe that the error is only marginal, I think having some sort of test (or a reference to one) would make the results more steadfast.

5.4 Results
586: Maybe include reference to figure where this is shown
592: Is this really always true? Counterexample e.g. Emsenhuber et al 2021 and others.
Table 2:
What is the rescaled integration time?
Figure 5:
I think the bottom panel should have a log y-axis
I would make the color of the dots consistent with Fig.2, where the final outcome is orange
There could be numbers on the contours indicating the density of the initial condition.
The meaning of the dashed line in the bottom panel could be indicated inside the figure itself.
I'm confused by the statement "interior to the oligarchic growth region (around 60d)". Where does this definition come from? Is this defined by bodies exceeding the critical feeding size? If so the statement should be rephrased to make the causal connection clear.
606: How can a mass be expressed in units of feeding zone size?
620: What is the intuition behind tilde b, how exactly is it defined? Since it is a dimensionless quantity, calling it an orbital separation is not intuitive to me. Can tilde b be converted to a physical size? Also, I struggle to interpret the critical tilde be of 2*sqrt(3). Do I understand correctly that a body with tilde b less than 2 sqrt(3) is associated with a feeding zone so small that close encounters are not possible, and thus are not expected to grow further?
632: Why are the bodies expected to follow the tilde b = 2sqrt(3) from a theoretical perspective? Also, I'm unconvinced that the bodies do that at all in the presented simulations - they fall below this value but don't follow it.
640: If anything the opposite seems to be true, no? Maybe have a specific value for the expected eccentricity of protoplanets with and without inelastic damping.
644: If I look at the contour map by eye, the eccentricity distribution doesn't seem all that different in the inner vs outer disk. Maybe the difference can be quantified?
647: This is an interesting point. I'd be interested in seeing a comparison between inner and outer disk accounting for that difference in time scales. Is it possible to include such a comparison maybe with a figure?
Figure 6:
This figure could be improved if each line was colored by the semi-major axis of the radius bin, and if there was a corresponding colorbar. The difference between the 60 day boundary could still be indicated with an additional line.
665: I struggle to see that there is a significant qualitative difference in the behavior in the lines just inside and just outside the boundary of 60 orbits. The first dashed line also seems to converge to a sigma/Sigma \sim 5 %, not much below the first solid line.
668: add reference. Also footnote 5 can probably go in the main text. Can the authors provide an equation that converts tilde b to units of r_h?
682: This statement seems only to be true for fdshallow. The others have a spread in eccentricity that covers two orders of magnitude...
685: It is not clear to me why more inelastic collisions lead to a more sharply peaked eccentricity distribution, and not just more damping like the authors argue for the fdLo simulation.
701: Again, I don't see that the value for tilde b approaches 2sqrt(3) beyond P=60d orbits. The bodies have smaller feeding zones than tilde b = 2sqrt(3)
702: Are they that similar? Maybe this statement can be more quantitative? To me it looks like the values fall below 2sqrt(3) at 40 days for fdHiShallow and at 70 days for fdLo. The interpretation that the boundary is only driven by the local value for alpha seems somewhat speculative. I'd also be interested how randomness affects this, i.e. if the simulation is initialized with a different random seed, by how much does the final distribution change?

5.5. Assembly History of Embryos
719: add references.
721: Does this distinction have analogies in galaxy formation? Also isn't this overly strict? I would expect that the initial population has quickly collided at least once, so most of the collisions will be major mergers under this definition. This seems to be supported by Fig. 9 where the smooth accretion fraction is always <10%.
724: Why are only the 100 largest bodies chosen? It seems more natural to me to choose a mass cut-off. Also, given that in Fig9 is plotting mass on a log-scale, I suggest just plotting the entire population including those planetesimals that remained relatively small and pristine. Also, why is the fdHi simulation chosen?
726: I think it could be explicitly stated that smooth accretion = minor mergers.
730 & onwards: Can the authors quantify this trend? E.g., by making three linear fits (with error bars) for > 60d, < 60d and the full population. I'm in particular unconvinced that the trend for P > 60 days truly is flat, given the small sample size for larger bodies.
Figure 9:
Given that I'm skeptical about the 60 day boundary being clear and universal, I think this plot would be stronger if the bodies were colored by orbital period (in addition to the marker style indicating this boundary), and the plot would include a corresponding colorbar.
The authors state "there is a decreasing correlation between smooth accretion fraction and mass, which suggests that most growth occurs between equal mass bodies". As far as I understand, this doesn't have to be the case. I would argue that more massive bodies require more time to build up and during later stages there are simply less primordial planetesimals left so collisions are just more likely to be major mergers.
The authors state "indicating that accretion of planetesimals is important during all phases of the evolution", yet the smooth accreting fraction is only between 1-10% for all these bodies. Seems to me that for all bodies, regardless of mass and orbital period, major mergers are significantly more important - that is at least with the author's definition of major and minor merger.
In the legend, I think "orbit" should be put in the subscript instead of P_orbit
746: This is just because in the inner disk there are no primordial planetesimals left to build the more massive bodies, right?
750: use /citep[see][]{Kokubo}
756: I agree that the large bodies must've originated due to mergers with other embryos, but this is not really an explanation for why the feeding zone size doesn't match the theoretical value, no? Instead it's the lack of gravitational scattering, as the authors write above. Maybe the authors can clarify specifically why oligarchic growth models predict this feeding zone size, and also why gravitational scattering is suppressed in the inner disk (due to the lack of primordial planetesimals in the inner disk?).
766: "One should note that [...]." This sentence can be deleted in my opinion.
Figure 10:
I suggest indicating the boundary between accretion modes in this figure. >60d orbits only include 4-5 bodies. However, to me it seems like the shape of the accretion zone is qualitatively the same until ~ 20 orbits, which strengthens my view that the 60d orbit boundary is not very clear at all.
I suggest matching the x-axis limits the shown xdata.
I think "Fraction of planetesimals accreted" is a somewhat misleading description of what the plot is showing. What about: "Distribution of accreted planetesimals"?
775: The transition between smooth and unimodal seems to be happening at about 20 days to me.
Figure 11
The y-axis label overlap
I think the finding that the crossing of alpha = 0.1 in the bottom panel well matches the crossing of tilde b = 2 sqrt(3) is interesting and worth highlighting more, maybe with some vertical lines? Is there a meaning behind alpha = 0.1, i.e., is this coming from some analytical consideration? See my major comments

6. Simplifying assumptions
6.1 Collision cross section
802: As I argued above, I'm unconvinced in this clear-cut boundary at 60 days. Maybe the authors could put a quantitative uncertainty to this number?
816: I'm not following where the factor of 15 comes from. Maybe the authors can write down the explicit proportionality used to obtain this value.
821: How is this expected to change with f?
843: Maybe add reference to such short period planets.
868: I'm not sure I fully follow this statement of the collision model. See my major comment above.

Figure 12:
Add a description of what green and orange means to the plot.

901: Are the populations really indistinguishable? The authors could perform for example a Kolmogorov-Smirnov test to underline this statement. If not, I would suggest softening this statement.
912: The authors perform this collisional model test very close-in where residual planetesimal populations are suppressed anyways. Maybe the authors can comment on what would change (if anything) if this test was performed in the outer parts of the disks.

7. Summary and Discussion
933: I would think the gravitational feedback still operates, just on a timescale that is much longer than the planetesimal accretion timescale that depletes the planetesimal supply.
942: Refer to the section where this is discussed.
946: alpha is already reviewed in the paragraph above
952: non-negligible is not very precise . Maybe change to while "alpha close to unity"
954: Refer to figure where this is shown. I think Fig.2? Also "the same" is very strong. Maybe "very similar" instead.
959: Sentence is currently implying that the boundary location is set by the distance to the star which doesn't really work in my opinion. Maybe just delete "and therefore the location of the boundary between these accretion modes" as this becomes clear with the subsequent sentence anyways.
965: I think this is too strong a statement. See my previous comments. I think the subsequent sentence "Although [...]" is more appropriate.
972: Refer to Fig. 10.
978: Missing a verb, maybe "differs" ? Also the second part of the sentence "along with [...]" seems odd to me. Maybe rephrase it in two sentences?
986: Is there a reference for this? It does not seem obvious to me. See my previous comments.
996: what bulk density? Maybe also rephrase to a less strong statement, e.g., "[...] bulk density, our results suggest that the boundary is located around 5 days in orbital period."
998: I recommend introducing a subsection heading here, for clarity.
999: Maybe add references of what values for alpha typically were used?
1000: This sentence is somewhat odd to me. Yes, alpha = 1 are the largest bodies stable under tidal gravity, however, this applies not just to circumplanetary disks but also for the circumstellar planetesimals the authors investigated in their work. Because of this, it doesn't seem like this statement is an appropriate segue to circumplanetary disks. I suggest separating this paragraph as a subsection under a heading such as "high-alpha accretion in circumplanetary disks".
1003: delete "small"
1007: Can the authors clarify the relevance of the inclusion of spiral density wave interactions?
1018: I recommend defining R_U for readers unfamiliar with Ida et al 2020, e.g., by summarizing that Ida et al 2020 considered a circumplanetary disk around Uranus.

### 2023-03-01 makeFig.py

@@ -38,10 +38,10 @@ mCentralg = (mCentral*u.M_sun).to(u.g)
 
 bins = np.linspace(0.01, 0.3, num_bins)
 
-snap = pb.load('data/fullDiskVHi.ic')
+snap = pb.load('data/fullDiskVHia.ic')
 plVHiIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi_ic = pb.analysis.profile.Profile(plVHiIC.d, bins=bins, calc_x = lambda x: x['a'])
-snap = pb.load('data/fullDiskVHi1.250000')
+snap = pb.load('data/fullDiskVHi1a.250000')
 plVHi = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi = pb.analysis.profile.Profile(plVHi.d, bins=bins, calc_x = lambda x: x['a'])
 perIC = 2*np.pi*np.sqrt((plVHiIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
@@ -458,6 +458,7 @@ def plot_pl_frac_time():
 
 	pbins = (np.linspace(1, 100, 10)*u.d).value
 	bins1 = ((((pbins*u.d).to(u.s)/(2*np.pi))**2*G.cgs*(mCentral*u.M_sun).to(u.g))**(1/3)).to(u.AU).value
+	prof_ic = pb.analysis.profile.Profile(plVHiIC.d, bins=bins1, calc_x = lambda x: x['a'])
 
 	files_sub = files
 
@@ -484,10 +485,27 @@ def plot_pl_frac_time():
 		else:
 			ls = '-'
 			lw1 = lw
-		axes.plot(time_arr, prof_arr[idx], color='black', linestyle=ls, lw=lw1)
+		tdyn_loc = pbins[idx]/(2*np.pi)
+
+		e_disp = prof_ic['e_disp'][idx]
+		vk = np.sqrt(mCentral/prof_ic['rbins'][idx])
+		v = np.sqrt(e_disp)*vk
+
+		sigma_geo = np.pi*(6*r_pl)**2
+		v_esc = np.sqrt(2*m_pl/(6*r_pl))
+		sigma = sigma_geo*(1 + (v_esc**2/v**2))
+
+		omega = np.sqrt(mCentral/prof_ic['rbins'][idx]**3)
+		n = prof_ic['density'][idx]*omega/(2*m_pl*v)
+
+		tacc_loc = 1/(n*sigma*v)
+
[…]

### 2023-03-01 refereeResponse.txt
Address referee comments for abstract and introduction

@@
 	Mass removal mechanisms: grinding to meter sizes, radial drift
-							 grinding to dust size, pr drag
+							 grinding to cm size, pr drag
+							 grinding to micron size, dust blowout
 
@@
 7: Are short period planets that exotic in the broader context of exoplanets?
+	Hard to say! We have replaced 'exotic' with 'wide variety'.
 14: "[...] population OF dynamically [...]"
+	Fixed
 17-18: something is missing in the second part of this sentence.
+	Missing words at the end of L17: 'investigate *the effects*'
 
@@
 26: How large are these solids? I assume this is referencing micron sized dust-grains?
+	Correct, some text was added to clarify this.
 68: Add reference
+	Need to find a reference for this
 72: Maybe elaborate on this. How long is the period of quiescence? How does this instability work?
+	We intentionally left this part vague as someone really needs to look into this more! There are three relevant timescales here:
+	1. The timescale for the instability itself (depends on the orbital properties of the embryos, see Chambers 98)
+	2.
+Dynamical friction between protoplanets and planetesimals.
+This will shut off once the planetesimals are either scattered away, or slowly accreted onto the embryos.
+Not sure what the timescale for this would be.
+Note that this shouldn't operate at short period according to this work!
+	3. Tidal eccentricity damping of the embryos due to the gas disk. Should shut off once the gas disk disperses on ~Myr timescales.
+	TODO: decide what to add to the text here.
 88: Add reference maybe.
+	I don't know of any references to add, but we added some text to clarify why this is the case (for particle-in-a-box methods, oligarchic growth results in only a few bodies in the highest mass bins)
 99: Capitalize "Systems of Tightly-packed Inner Planets"
+	Fixed
 104: Gas-Disk driven migration → reference?
+	Added reference to Izidoro 17 and 21, which invokes gas disk driven migration, followed by resonant trapping and an possible orbital instability to explain the observed architectures of STIPs
 116: What is the "isolation mass" initial condition? Maybe isolation mass can be defined
+	We will define isolation mass later in the paper. For now, we removed this term and replaced it with 'fully-formed, evenly spaced protoplanets'.
 118: I'm not sure if this belongs in the introduction. I think the mention of future work at the end of the discussion is sufficient.
+	Agreed. Removed the last sentence of this paragraph.
 

### 2023-03-01 main.tex
Address referee comments for abstract and introduction

@@
 small body populations. However, planetesimal accretion has not yet
-been fully explored in the context of more exotic terrestrial systems,
-particularly those that host short-period planets. In this work, we
+been fully explored in the context of the wide variety of recently discovered extrasolar planetary systems,
+particularly those that host short-period terrestrial planets. In this work, we
 use direct N-body simulations to explore and understand the growth of
@@
 result in collisions, rather than scattering, and the system does not
-develop a bimodal population dynamically hot planetesimals and
+develop a bimodal population of dynamically hot planetesimals and
 dynamically cold oligarchs, like is seen in previous studies. The highly
@@
 results to assumptions about the initial disk model, and also
-investigate that our simplified collision model has on the emergence
+investigate the effects that our simplified collision model has on the emergence
 of this non-oligarchic growth mode in a planet forming disk.
@@
 moon-sized objects known as planetary embryos. In the earliest stages
-of the planet formation process, aerodynamic forces dominate the
+of the planet formation process, beginning from $\mu$m sizes, aerodynamic forces dominate the
 growth and evolution of the solids and statistical models
@@
 dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals. Lines of evidence suggest 
-that the asteroid belt, Kuiper belt and the Oort cloud are largely composed of the leftovers of this stage of planet formation.
+that the asteroid belt, Kuiper belt and the Oort cloud are largely composed of the leftovers of this stage of planet formation (add reference).
 
@@
 the gravitational influence of the few massive oligarchs that
-form make statistical methods inappropriate. Due to computational expense, N-body simulations of
+form make statistical methods inappropriate because the highest mass bins contain only a few bodies. Due to computational expense, N-body simulations of
 planetesimal accretion are usually modeled in a narrow
@@
 
-Given that systems of tightly-packed inner planets (STIPs) appear to
+Given that Systems of Tightly-packed Inner Planets (STIPs) appear to
 be a common outcome of planet formation \citep{lantham11, lissauer11, rowe14}, understanding exactly how
@@
 gas-disk driven migration of the planets themselves is often invoked
-to explain the observed architectures, we will focus on an in-situ
+to explain the observed architectures \citep{izidoro17, izidoro21}, we will focus on an in-situ
 model in this paper. That is, once the planetesimals themselves form,
@@
 of the planetesimals across a wide range of orbital periods (1 to 100
-days). In doing so, we will assess whether the typical ``isolation
-mass'' initial conditions used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
-In a series of follow up papers, we plan to use these results to directly track the formation of full-sized planets from planetesimals and to understand how gravitational perturbations from a nearby gas giant might affect the outcome of this process.
+days).
+In doing so, we will assess whether the typical initial conditions (fully formed, evenly spaced protoplanets, e.g.
+\citet{raymond06}) used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
 

### 2023-03-02 refereeResponse.txt
Address more comments in section 2

@@
 
+Where should I put these?
+
 5) I have some suggestions for improving the presentation of the results in Figures, to make the science result more clear and intuitively obtainable.
@@
 Specific comments, notes and suggestions.
+
+TODO: First few edits need to be highlighted in manuscript with strikethroughs and bold face.
 
@@
 Note that this shouldn't operate at short period according to this work!
-	3. Tidal eccentricity damping of the embryos due to the gas disk. Should shut off once the gas disk disperses on ~Myr timescales.
+	3. Tidal eccentricity damping of the embryos due to the gas disk. Should shut off once the gas disk disperses on ~Myr timescales (Beckwith + Sargent 1996).
 	TODO: decide what to add to the text here.
@@
 144 onwards: indices in math upright
+	Fixed
 152: Define rms velocity
+	TODO: not sure what the referee wants? Its defined in equation 1?
 161: What does "orderly" fashion mean exactly?
+	This means the mass ratios between bodies tend toward unity. This has been clarified in the text.
 174: Add reference.
+	TODO: Section 5.2.1 of the Armitage book calculates this. Is there also a paper to reference? (runaway growth required to build planets in a reasonable amount of time)
 198: Ln Lambda approx 10 missing could use a reference.
+	TODO: This is also in the armitage book, but lets look for a paper that calculates it
 204: I suggest more formally introducing the concept of Hill sphere and hill factor.
+	TODO: Where to put this?
 209: This sentence seems not necessary.
+	Agreed, removed
 213: add "dynamically" heating
+	Added
 222: add "a" crucial assumption
+	Fixed
 226: Maybe clarify that growth timescale equals collision time scale.
+	We have replaced 'growth' with 'collision' here
 238: The eccentricity dispersion e_h is never defined anywhere. It is unclear to me what scaling e_h with the Hill-factor means physically.
+	TODO: Clarify
 Figure .1:
@@
 While I'm inclined to believe that the error is only marginal, I think having some sort of test (or a reference to one) would make the results more steadfast.
+	No there arent. I'm going to create an appendix which shows the fdHi simulations from 1 to 4 days in p_orbit with fixed steps and multi stepping. The results should be the same.
 

### 2023-03-02 main.tex
Address more comments in section 2

@@
 \usepackage{natbib}
+\usepackage[LGRgreek]{mathastext}
 %\definecolor{orcidlogocol}{HTML}{A6CE39}
@@
 with mass and the mass distribution is expected to evolve in an
-``orderly'' fashion.
+``orderly'' fashion, in which mass ratios between bodies tend toward unity.
 However, bodies larger than $\sim 100$ km in size are expected to exert a significant gravitational force on each other during encounters and the collision cross section depends on both the size of the bodies and their encounter velocities.
@@
 
-As mentioned above, the system will tend toward a state of energy
-equipartition for a non-uniform mass distribution. \citet{kokubo98}
-showed that runaway growth is actually self-limiting. As the runaway
-bodies develop, they become increasingly effective at heating the
+\citet{kokubo98} showed that \textbf{the runaway growth process described above} is actually self-limiting. As the runaway
+bodies develop, they become increasingly effective at \textbf{dynamically} heating the
 remaining planetesimals, which diminishes the
@@
 
-The picture described above relies upon an crucial assumption, which
+The picture described above relies upon \textbf{a} crucial assumption, which
 is that the mass distribution evolves slowly enough for gravitational stirring to maintain energy equipartition.
-In other words, the relaxation timescale must remain short relative to the growth timescale.
+In other words, the relaxation timescale must remain short relative to the \textbf{collision} timescale.
 For typical conditions near the terrestrial region of the solar system, this timescale condition is satisfied.

### 2023-03-02 makeFig.py

@@ -1122,7 +1122,7 @@ def plot_frag_acc_zones():
 #plot_alpha_beta_mass()
 #plot_fulldisk_e_m_b()
 #plot_alpha_pl_frac()
-plot_pl_frac_time()
+#plot_pl_frac_time()
 #plot_surfden_profiles()
 #plot_surfden_iso()
 #plot_surfden_b()

### 2023-03-03 refereeResponse.txt
Edits through section 2

@@
 226: Maybe clarify that growth timescale equals collision time scale.
-	We have replaced 'growth' with 'collision' here
+	We have replaced 'growth' with 'collision' here, and done the same elsewhere in the paper for consistency
 238: The eccentricity dispersion e_h is never defined anywhere. It is unclear to me what scaling e_h with the Hill-factor means physically.
-	TODO: Clarify
+	e_h can be thought of as the radial excursion of the body's orbit in units of its Hill radius.
+For e_h > 1, encounters between bodies can be treated with a two-body formalism.
+We have decided to remove any mention of e_h here, and instead save this definition for section 4 (TODO: define in section 4), where it is next mentioned.
 Figure .1:
@@
 Currently, it may suggest that the plotted values for e_h are chosen for a particular reason.
+	Get rid of the legend, explain that e_h values increase from bottom to top.
 Also, I think it would be nice to have a reference for what values of e_h are standard for certain disk conditions, i.e.
@@
 Or do we expect e_h = 1 as the standard?
+	Not sure if there is going to be a reference for this. Equilibrium e_h depends on particle mass and gas density. Could try to plot things in terms of that instead. (Maybe fix rho_gas and vary mass?)
 Also, I recommend adjusting the x-limits of the plot to correspond to the limits of the orbital period.
+	Done
 
@@
 253: "will remain proportional" - Proportional to what?
+	Changed the wording to 'ratio between the relaxation and collision timescale remains constant' to clarify this.
 254: but this doesn't have to be the case at all orbital periods, right? Given Fig.1 it seems clear that outside of 1AU, and especially for the Kuiper Belt this condition seems to be fulfilled.
+	Exactly! That's the point we're getting at here. (TODO: do I need to clarify something in the paper here?)
 263: Again, I think the concept of Hill radius and tidal stability needs to be formally introduced earlier.
+	TODO: Introduct this formally earlier
 273: Wouldn't these bodies then be tidally disrupted, and therefore not exist?
@@
 I understand that the scaling of alpha predicts alpha >1 at some radius (which I would explicitly mention), but this just implies that inside this radius, bodies must have greater densities to not be disrupted.
+	Alpha = 1 doesn't correspond  to the roche limit (although they are close)! TODO: Maybe add a calculation here explaining this.
 289: gravitational radius: is this physically motivated? Maybe reference
+	Yes, it is explained just below the equation. TODO: Do I need to clarify something?
 296: beta > 1 means collision cross section > geometric and small gravitational focusing. I recommend explicitly stating what the physical intuition for beta < 1 is.
+	Done.
 

### 2023-03-03 main.tex
Edits through section 2

@@
 of the bodies are both a function of time. Due to the interdependence
-of these quantities, it is not clear whether the timescales for
-gravitational scattering and growth will remain proportional as the
+of these quantities, it is not clear whether the \textbf{ratio between the relaxation and collision timescales will remain constant} as the
 oligarchs develop. In the case of the solar system, $t_{relax} \ll t_{coll}$ likely continued to remain true, otherwise runaway 
@@
 In the case where $r_{g}$ is smaller than the size of a planetesimal, the gravitational focusing enhancement factor will be between 0 and 1 and the collision cross section is mostly set by the geometric value.
+\textbf{For very large values of $r_{g}$ ($\beta \gg 1$), the effective collision cross section is almost entirely set by gravitational scattering.}
 

### 2023-03-03 makeFig.py

@@ -162,7 +162,7 @@ def plot_timescales():
 	mp = 4/3*np.pi*rhop*rp**3
 
 	mstar = (1*u.M_sun).to(u.g)
-	p_bins = (np.logspace(-4, 0)*u.yr).to(u.s)
+	p_bins = (np.logspace(0, 2)*u.d).to(u.s)
 	r_bins = ((p_bins/(2*np.pi))**2*G.cgs*mstar)**(1/3)
 
 	def timescale_ratio(eh):
@@ -188,11 +188,9 @@ def plot_timescales():
 
 	fig, axes = plt.subplots(figsize=(8,6))
 	ehvals = [16, 8, 4, 2, 1]
-	colors = plt.cm.viridis(np.linspace(0, 1, len(ehvals)))
 	for idx, eh in enumerate(ehvals):
-		axes.plot(p_bins.to(u.d), timescale_ratio(eh), c=colors[idx], label=r'e$_{h}$ = '+str(eh), lw=lw)
+		axes.plot(p_bins.to(u.d), timescale_ratio(eh), c='black', label=r'e$_{h}$ = '+str(eh), lw=lw)
 	axes.axhline(1, ls='--', color='gray')
-	axes.legend()
 	axes.set_xscale('log')
 	axes.set_yscale('log')
 	axes.set_xlabel('Orbital Period [d]')
@@ -1116,7 +1114,7 @@ def plot_frag_acc_zones():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
-#plot_timescales()
+plot_timescales()
 #plot_alpha_beta()
 #plot_alpha_beta_evo()
 #plot_alpha_beta_mass()

### 2023-03-07 refereeResponse.txt
Add appendix comparing timestepping scheme to fixed steps

@@
 While I'm inclined to believe that the error is only marginal, I think having some sort of test (or a reference to one) would make the results more steadfast.
-	No there arent. I'm going to create an appendix which shows the fdHi simulations from 1 to 4 days in p_orbit with fixed steps and multi stepping. The results should be the same.
+	No there arent.
+I've added an appendix that compares this timestepping scheme against a fixed timestep case.
+There appear to be no meaningful differences.
+TODO: Show mass distribution as differential or cumulative?
+Finish running sims
 

### 2023-03-07 main.tex
Add appendix comparing timestepping scheme to fixed steps

@@
 
+\appendix
+\section{Robustness of Timestepping Scheme}\label{sec:rung_ecc}
+
+As described in section \ref{sec:methods}, {\sc ChaNGa} evolves the motions of the particles in the planetesimal disk using a multi-tiered timestepping scheme.
+Due to the extremely short dynamical timescale at the inner edge of the disk, the outer disk would require a prohibitive number of timesteps to reach the protoplanet phase using a fixed timestep scheme.To circumvent this, particles are evolved in discrete power-of-two timestep groups.
+In the event that a collision occurs between two particles on different timesteps, a slight error is introduced to the energy and angular momentum of the merged particle.
+Due to the nonlinear nature of the runaway growth phase, this slight error tends to trigger more subsequent collisions at the timestep boundary in the disk, and causes protoplanets to preferentially form at the boundaries.
+
+To circumvent this issue, we prohibit particles on different timesteps from merging until the runaway growth phase is well underway.
+For the fdHi simulation, multi-tiered mergers are not allowed during the first thousand steps.
+To verify that this technique does not alter the resulting protoplanet distribution in any meaningful way, we ran two test simulations of the inner part (1 to 4 days in orbital period) of the disk from the fdHi simulation.
+In the first case, the aforementioned timestepping scheme is used.
+In the second case, all particles are evolved on the timestep appropriate for the inner edge of the disk.
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/rung_ecc.png}
+    \caption{A comparison between the innermost region of the fdHi (orange) simulation, and a second version using a fixed timestep appropriate for the inner edge of the disk (green).
+In the top panel, the period-eccentricity state of the particles is shown, with marker sizes indicating relative mass.
+The blue points represent the initial state of the simulations.
+The bottom panel compares the final mass distributions of the bodies (diff or cumulative?).\label{fig:rung_ecc}}
+\end{center}
+\end{figure}
+
+In figure \ref{fig:rung_ecc}, we compare the final period-eccentricity state and final mass distributions to each other.
+There do not appear to be any differences between the two protoplanet distributions, particularly near the timestep boundary at 2 days.
+In addition, the masses of both the protoplanets and the remaining growing planetesimals are indistinguishable.
+We therefore safely conclude that the timestepping scheme used in this work does not alter the growth of the protoplanets in any meaningful way.
+
 \bibliography{references}

### 2023-03-07 makeFig.py

@@ -1114,7 +1114,62 @@ def plot_frag_acc_zones():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
-plot_timescales()
+def plot_rung_ecc():
+	file_str = 'figures/rung_ecc.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	snap0 = pb.load('data/rungTest/rungTest.ic')
+	pl0 = ko.orb_params(snap0, isHelio=True, mCentral=mCentral)
+	per0 = 2*np.pi*np.sqrt((pl0['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+	snap = pb.load('data/rungTest/fullDiskVHi1.054000')
+	plNf = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+	perNf = 2*np.pi*np.sqrt((plNf['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+	snap = pb.load('data/rungTestSingle/fullDiskVHi.216000')
+	plF = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+	perF = 2*np.pi*np.sqrt((plF['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
+
+	fig, ax = plt.subplots(figsize=(8,8), nrows=2)
+	axes = ax[0]
+	axes.scatter(per0, pl0['e'], s=pl0['mass']/np.min(pl0['mass'])*0.1)
+	axes.scatter(perNf, plNf['e'], s=plNf['mass']/np.min(pl0['mass'])*0.1, edgecolor='black', linewidth=0.4)
+	axes.scatter(perF, plF['e'], s=plF['mass']/np.min(pl0['mass'])*0.1, edgecolor='black', linewidth=0.4)
+	axes.set_yscale('log')
+	axes.set_ylim(5e-5, 5e-2)
+	axes.set_xlabel('Orbital Period [d]')
+	axes.set_ylabel('Eccentricity')
+
+	axes = ax[1]
+	axes.plot([], [])
+	axes.fill_between([], [], [], step='mid', alpha=0.5)
+
+	q1 = (plNf['mass']*u.M_sun).to(u.g).value
+	hist, bins = np.histogram(q1, bins=np.logspace(np.min(np.log10(q1)), np.max(np.log10(q1))))
[…]

### 2023-03-10 refereeResponse.txt
Add references requested by referee

@@
 68: Add reference
-	Need to find a reference for this
+	Added a handful of references arguing that the asteroids, KBOs and Oort cloud bodies are leftover planetesimals.
 72: Maybe elaborate on this. How long is the period of quiescence? How does this instability work?
@@
 88: Add reference maybe.
-	I don't know of any references to add, but we added some text to clarify why this is the case (for particle-in-a-box methods, oligarchic growth results in only a few bodies in the highest mass bins)
+	I don't know of any references which have tested the applicability of statistical methods during the oligarchic growth phase, but maybe some clarification would help.
+The runaway growth phase produces a small number of large bodies, which eventually interact and terminate runaway growth (Ida + Makino 1993, Kokubo + Ida 1995).
+Given how few oligarchs are produced, one would not expect particle-in-a-box methods to be a good approach here.
+We've clarified this in the text as well.
 99: Capitalize "Systems of Tightly-packed Inner Planets"
@@
 174: Add reference.
-	TODO: Section 5.2.1 of the Armitage book calculates this. Is there also a paper to reference? (runaway growth required to build planets in a reasonable amount of time)
+	Added reference to Lissauer 1987. Also mentioned that pebble accretion is a viable alternative.
 198: Ln Lambda approx 10 missing could use a reference.
-	TODO: This is also in the armitage book, but lets look for a paper that calculates it
+	Typo in the text, Ln Lambda ~ 3 is typically used. Added references to Ida 1990, Stewart and Ida 1993). Ln Lambda = 3 was used to construct figure 1, so no changes to the figure needed.
 204: I suggest more formally introducing the concept of Hill sphere and hill factor.
@@
 	e_h can be thought of as the radial excursion of the body's orbit in units of its Hill radius.
-For e_h > 1, encounters between bodies can be treated with a two-body formalism.
+For e_h > 1, the random velocity of a body dominates over the velocity difference due to the shearing of the disk (over a separation of 1 r_h) and encounters between bodies can be treated with a two-body formalism.
 We have decided to remove any mention of e_h here, and instead save this definition for section 4 (TODO: define in section 4), where it is next mentioned.
@@
 263: Again, I think the concept of Hill radius and tidal stability needs to be formally introduced earlier.
-	TODO: Introduct this formally earlier
+	TODO: Introduce this formally earlier
 273: Wouldn't these bodies then be tidally disrupted, and therefore not exist?
@@
 289: gravitational radius: is this physically motivated? Maybe reference
-	Yes, it is explained just below the equation. TODO: Do I need to clarify something?
+	There is a physical explanation of r_g immediately below equation 5 in the text. Also added a reference to Ida 1990.
 296: beta > 1 means collision cross section > geometric and small gravitational focusing. I recommend explicitly stating what the physical intuition for beta < 1 is.
@@
 Also, isn't this also not just very expected since alpha exactly quantifies the relative importance of scattering vs accretion?
+	There are two possible outcomes from an encounter:
+		Scattering, eccentricity increases, subsequent encounters more unlikely
+		Collision -> merger -> eccentricity decreases due to collisional damping
+	No high eccentricity particles suggests there are very few scattering events
 394: small alpha, large beta doesn't look dynamically cool to me.
+	TODO: Change the text to only reference the dynamical state of the protoplanets
 400: Small alpha large beta does not look dynamically cooler than large alpha large beta to me. In fact, the opposite.
+	You are correct! This is a mistake in the text. TODO: Fix
 402: I don't really understand why small alpha small beta leads to so many dynamically hot bodies, both planetesimals and protoplanets. Maybe the authors can elaborate.
+
 Figure 3:
@@
 435: Is this true? I was under the impression that the residual planetesimal population remains? I think this does not seem consistent with the rest of the work...?
+	TODO: Change the wording here. Maybe this isnt true. Would the growth mode simply 'flatten' out here?
 446: What exactly does alpha being non-negligible mean?

### 2023-03-10 main.tex
Add references requested by referee

@@
 dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals. Lines of evidence suggest 
-that the asteroid belt, Kuiper belt and the Oort cloud are largely composed of the leftovers of this stage of planet formation (add reference).
+that the asteroid belt \textbf{\citep{bottke05, morbidelli09}}, Kuiper belt \textbf{\citep{levison08, sheppard10}} and the Oort cloud \textbf{\citep{levison11}} are largely composed of the leftovers of this stage of planet formation.
 
@@
 many particles to directly track with traditional N-body codes, while
-the gravitational influence of the few massive oligarchs that
-form make statistical methods inappropriate because the highest mass bins contain only a few bodies. Due to computational expense, N-body simulations of
+the gravitational interactions between the \textbf{few massive bodies produced by the runaway growth phase \citep{ida93, kokubo95, kokubo98} render statistical methods inappropriate}.
+Due to computational expense, N-body simulations of
 planetesimal accretion are usually modeled in a narrow
@@
 gas-disk driven migration of the planets themselves is often invoked
-to explain the observed architectures \citep{izidoro17, izidoro21}, we will focus on an in-situ
+to explain the observed architectures \textbf{\citep{izidoro17, izidoro21}}, we will focus on an in-situ
 model in this paper. That is, once the planetesimals themselves form,
@@
 simulations by \citet{kokubo96} and appears necessary to construct
-protoplanets within the lifetime of a protoplanetary disk. Due to the
+protoplanets within the lifetime of a protoplanetary disk \textbf{\citep{lissauer87}, although one should note that pebble accretion \citep{lambrechts12, lambrechts14, bitsch15} is a viable alternative scenario}.
+Due to the
 velocity dependence of the gravitational focusing effect, it is not clear how ubiquitous this mode of growth is.
@@
 where $\ln \Lambda$ is the Coulomb logarithm,
-typically taken to be $\approx 10$ for a planetesimal disk. Despite
+typically taken to be \textbf{$\approx 3$ for a planetesimal disk \citep{ida90, stewart00}}. Despite
 the fact that the behavior of gravitational stirring is well-described
@@
 \end{equation}
-where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body.
+where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body (see eq 4.1 of \citet{ida90}).
 Encounters between bodies inside of a distance of $r_{g}$ result in significant deflections of their trajectories.

### 2023-03-28 refereeResponse.txt
Address referee comments in section 4

@@
 335: children: Would those not be the parent particles?
+	We've been representing the collision history of a particle with a tree structure.
+Following computer science convention, our tree is flipped upside down, with the original planetesimals at the bottom (hence calling them children).
+I agree that calling them 'parents' is probably more intuitive for most readers, however.
+We have changed 'children' to 'parents' here.
 
@@
 352: I think it's somewhat ambitious calling four simulations a parameter study.
+	Agreed. This has been changed to 'an exploration of the (alpha, beta) parameter space'.
 362: Regarding the initial condition, I recommend adding some more intuitive mass units, i.e.
@@
 I think this is 0.33 Earth masses, within 0.1 AU of Earth, the feeding zone of Earth.
+	I don't think I like the idea of providing more physical motivation here.
+This was meant to be a study of the effects of varying alpha and beta.
+I think some of these points should be saved for the full disk section.
+Perhaps it would be better if I described everything in dimensionless units?
+TODO
+
 367: I'm assuming the semi-major axis is also drawn from a uniform distribution?
+	Yes, this is now clarified.
+
 377: is alpha=1 chosen because it is the highest stable alpha? If so I would write that. Why is beta = 15000 chosen?
+	Alpha = 1 corresponds to r_pl = r_hill.
+One would expect that gravitational scattering should completely shut off for alpha >= 1.
+The 'large beta' value is chosen to be as large as possible while still allowing the simulation to finish in a reasonable amount of time (collisions become more infrequent as we turn up the eccentricity dispersion).
+This is not explained in the text.
+Beta is also probably limited by r_apo-r_peri < delta_a (TODO: calculate this)
 
@@
 A reference planetesimal size that shows what mass a circle has
+	Might skip this, want to keep everything in dimensionless units here TODO: decide
 Horizontal lines in each panel showing where e_h is
+	Might skip this, depending on whether I remove the e_h lines from figure 1. TODO
 Maybe consider having beta value as a column label and alpha value as a row label. I would also explicitly state the values for alpha.
+
 I would also probably label the four panels / cases a,b,c,d and then refer as such in the text body
+	Done
 
@@
 Also, isn't this also not just very expected since alpha exactly quantifies the relative importance of scattering vs accretion?
-	There are two possible outcomes from an encounter:
-		Scattering, eccentricity increases, subsequent encounters more unlikely
-		Collision -> merger -> eccentricity decreases due to collisional damping
-	No high eccentricity particles suggests there are very few scattering events
+	I'm assuming this is referring to the statement that begins with 'The lack of high eccentricity planetesimals...'.
+I think you must be misinterpreting what we said in the text here, because it sounds like we are both making the same point.
+When we turn up alpha, the high eccentricity planetesimals dissapear.
+This is expected, because large alpha makes gravitational scattering difficult, so those bodies that undergo close encounters end up being accreted by the protoplanets, rather than getting kicked onto high eccentricity orbits.
+If there is something that needs to be clarified in the text, please let us know!
+
 394: small alpha, large beta doesn't look dynamically cool to me.
-	TODO: Change the text to only reference the dynamical state of the protoplanets
+	This should have been referring to the dynamical state of the growing protoplanets, relative to the initial eccentricities of the planetesimals. This has now been clarified in the text.
 400: Small alpha large beta does not look dynamically cooler than large alpha large beta to me. In fact, the opposite.
-	You are correct! This is a mistake in the text. TODO: Fix
+	You are correct! This is a mistake in the text (replaced 'latter' with 'former').
 402: I don't really understand why small alpha small beta leads to so many dynamically hot bodies, both planetesimals and protoplanets. Maybe the authors can elaborate.
+	When alpha and beta are both small, the gravitational stirring timescale is very short and the disk quickly heats up.
+Because the stirring timescale goes as v^{1/4} (TODO: reference), the scattering slows down as the disk gets hotter.
+So runaway growth doesn't really kick in until after the eccentricities have grown enough that stirring slows down.
+I think this is why the initial choice of beta doesn't really seem to affect the final dynamical state of the disk in figure 2.
+This is also why the initial choice of e_h isn't very consistent across planetesimal accretion studies (cite some examples).
+TODO: Let's add another paragraph discussing this here.
 

### 2023-03-28 main.tex
Address referee comments in section 4

@@
 body, which is given the center of mass position and velocity of the
-two children. Resolving a collision can produce another imminent
+two \textbf{parents}. Resolving a collision can produce another imminent
 collision, so collisions are handled one-by-one and another full
@@
 
-We begin by presenting a parameter study of planetesimal accretion,
-motivated by two questions raised in section \ref{sec:theory}. 1) Does
+We begin by 
+\textbf{exploring the outcome of planetesimal accretion in different parts of the $\left( \alpha, \beta \right)$
+parameter space.} The choices of $\alpha$ and $\beta$ are motivated by two questions raised in section \ref{sec:theory}. 1) Does
 runaway growth still operate when the condition that $v \ll v_{esc}$
@@
 individual masses of $5 \times 10^{23}$ g are placed with semimajor
-axes randomly drawn between 0.95 and 1.05 AU about a 1 $M_{\odot}$
+axes drawn \textbf{from a uniform distribution} between 0.95 and 1.05 AU about a 1 $M_{\odot}$
 star. The argument of perihelion, $\omega$, longitude of ascending node,
@@
 To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by 
-a factor of $\sim$ 7100, which produces $\alpha = 1$. To vary $\beta$, the eccentricity dispersion is increased. For the high-$
+a factor of $\sim$ 7100, which produces $\alpha = 1$.
+\textbf{In this case, a planetesimal completely fills its Hill sphere, and one should expect no strong gravitational scattering to occur.} To vary $\beta$, the eccentricity dispersion is increased.
+For the high-$
 \beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
+\textbf{This choice of $\beta$ places the system firmly in the $v > v_{esc}$ regime, while still allowing growth to occur in a reasonable number of timesteps.}
 
@@
 snapshots from each of the 4 simulations. The size of the points
-indicates the relative masses of the bodies. Only in the case of small
-$\alpha$ does a residual population of dynamically hot planetesimals
+indicates the relative masses of the bodies. Only \textbf{with small
+$\alpha$ (case c, d)} does a residual population of dynamically hot planetesimals
 develop. The lack of high eccentricity planetesimals in the large
-$\alpha$ case suggests that most encounters result in accretion
-rather than scattering. In the case of large $\beta$, the protoplanets
-and remaining planetesimals end up in a dynamically cool state,
-compared with the initial conditions. This is due to kinetic energy 
+$\alpha$ \textbf{(case a, b) simulation} suggests that most encounters result in accretion
+rather than scattering. \textbf{For} large $\beta$ \textbf{(case b, d)}, the \textbf{growing} protoplanets
+and end up in a dynamically cool state,
+\textbf{relative} with the initial conditions. This is due to kinetic energy 
 being lost as particles inelastically collide. One last point we note
 is the difference between the eccentricities of protoplanets in the 
-large $\alpha$, large $\beta$ and the small $\alpha$,
-large $\beta$ case. The dynamically cooler result of the latter case
+large $\alpha$, large $\beta$ \textbf{(case b)} and the small $\alpha$,
+large $\beta$ \textbf{(case d) simulation}. The dynamically cooler result of the \textbf{former} case
 is likely due to the dominant role that inelastic collisions play here.
 
-In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four cases.
-In addition to leaving fewer residual planetesimals, the large $\alpha$ simulations produce significantly larger embryos.
+In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}.
+In addition to leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce significantly larger embryos.
 Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) appears to have no significant effect on the final distribution of masses.
@@
 timescales, runaway growth appears to be inevitable, so long as
-gravity is the dominant force in the system. For the large $\alpha$
-cases, the curves in this figure eventually turn over and begin to decline.
+gravity is the dominant force in the system. For large $\alpha$
+\textbf{(case a, b)}, the curves in this figure eventually turn over and begin to decline.
 Upon inspecting the simulation snapshots, we find that this trend is

### 2023-03-28 makeFig.py

@@ -169,7 +169,7 @@ def plot_timescales():
 		Sigma = surf_den(r_bins.to(u.AU))
 
 		vk = np.sqrt(G.cgs*mstar/r_bins)
-		lnLam = 5
+		lnLam = 3
 		omega = 2*np.pi/p_bins
 		vesc = np.sqrt(G.cgs*mp/rp)
 
@@ -214,13 +214,13 @@ def plot_alpha_beta():
 		ax.text(0.85, 0.95, title, transform=ax.transAxes, ha='center', va='center')
 
 	fig, ax = plt.subplots(figsize=(16,12), nrows=2, ncols=2, sharex=True, sharey=True)
-	subplot(ax[0][0], 'ki_fluffy', r'Large $\alpha$, Small $\beta$')
+	subplot(ax[0][0], 'ki_fluffy', r'Case a: Large $\alpha$, Small $\beta$')
 	ax[0][0].set_ylabel('Eccentricity')
-	subplot(ax[0][1], 'ki_fluffy_hot', r'Large $\alpha$, Large $\beta$')
-	subplot(ax[1][0], 'ki', r'Small $\alpha$, Small $\beta$')
+	subplot(ax[0][1], 'ki_fluffy_hot', r'Case b: Large $\alpha$, Large $\beta$')
+	subplot(ax[1][0], 'ki', r'Case c: Small $\alpha$, Small $\beta$')
 	ax[1][0].get_xticklabels()[0].set_visible(False)
 	ax[1][0].get_xticklabels()[-1].set_visible(False)
-	subplot(ax[1][1], 'ki_hot', r'Small $\alpha$, Large $\beta$')
+	subplot(ax[1][1], 'ki_hot', r'Case d: Small $\alpha$, Large $\beta$')
 	ax[1][1].get_xticklabels()[0].set_visible(False)
 	ax[1][1].get_xticklabels()[-1].set_visible(False)
 
@@ -228,7 +228,7 @@ def plot_alpha_beta():
 	ax[1][1].set_xlim(0.9, 1.1)
 	ax[1][1].set_ylim(1e-5, 0.3)
 
-	fig.supslabel('Semimajor Axis [AU]')
+	fig.supxlabel('Semimajor Axis [AU]')
 	fig.supylabel('Eccentricity')
 
 	plt.subplots_adjust(wspace=0, hspace=0)
@@ -243,18 +243,18 @@ def plot_alpha_beta_evo():
 	fig, axes = plt.subplots(figsize=(8,6))
 
[…]

### 2023-03-29 refereeResponse.txt
Referee changes through update to fig 4

@@
 I would express the mass in units of e.g. Ceres
+	Todo: Push back on this? Use dimensionless units for this section.
 406: I'm not sure about "significantly" larger. The biggest body in large alpha, small beta is about a factor 3 more massive than in small alpha, small beta. This is only a factor of 1.4 in size.
+	The text now says 'a factor of a few larger'
 415: the y-label in Fig.6 does not match the description in the text
+	This comment must be referring to figure 4? If so, 'm_max' in the text has been changed to 'M'.
 Figure 4:
@@
 That would also underscore that the turnover is driven by an increase in <m> rather than m_max.
+	We have now added a second panel to figure 4 which shows the evolution of these quantities separately. Todo: Units? Why does the max mass decrease for case a?
 

### 2023-03-29 main.tex
Referee changes through update to fig 4

@@
     \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
-    \caption{The evolution of the ratio between the maximum and mean mass for the four simulations presented in section 
-    \ref{sec:narrow}. The runaway growth phase can be identified by a positive trend in this ratio. For all values of $\alpha$, an 
-    increase in $\beta$ has the effect of delaying runaway growth.\label{fig:alpha_beta_evo}}
+    \caption{\textbf{Top:} The evolution of the ratio between the maximum and mean mass for the four simulations presented
+    in section \ref{sec:narrow}. The runaway growth phase can be identified by a positive trend in this ratio. For all values of 
+    $\alpha$, an increase in $\beta$ has the effect of delaying runaway growth. \textbf{Bottom: The evolution of the maximum
+    (solid lines) and mean (dashed lines) shown individually.}\label{fig:alpha_beta_evo}}
 \end{center}
@@
 In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}.
-In addition to leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce significantly larger embryos.
+In addition to leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce \textbf{embryos that are a factor of a few larger}.
 Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) appears to have no significant effect on the final distribution of masses.
@@
 runaway growth, we examine the time evolution of the maximum and mean
-masses in each simulation. The ratio $m_{max}/\left< m \right>$ is plotted
-in figure \ref{fig:alpha_beta_evo}. On this plot, a positive slope
+masses in each simulation. The ratio $M/\left< m \right>$ is plotted
+in \textbf{the top panel of} figure \ref{fig:alpha_beta_evo}. \textbf{Here}, a positive slope
 indicates that the quantities are diverging (i.e.
@@
 \textbf{(case a, b)}, the curves in this figure eventually turn over and begin to decline.
-Upon inspecting the simulation snapshots, we find that this trend is
+\textbf{In the bottom panel of figure \ref{fig:alpha_beta_evo}, we separately show the evolution of
+the maximum (solid lines) and mean (dashed lines) mass for each case. Here, it is evident}
+that \textbf{the turnover in $M/\left< m \right>$} is
 driven by an increase in the average mass as the planetesimal population

### 2023-03-29 makeFig.py

@@ -240,25 +240,38 @@ def plot_alpha_beta_evo():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	fig, axes = plt.subplots(figsize=(8,6))
+	fig, axes = plt.subplots(figsize=(8,12), nrows=2)
 
 	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_fluffy.txt')
-	axes.loglog(stepnumber, max_mass/mean_mass, label=r'Case a: Large $\alpha$, Small $\beta$', lw=lw)
+	c=next(axes[0]._get_lines.prop_cycler)['color']
+	axes[0].loglog(stepnumber, max_mass/mean_mass, label=r'Case a: Large $\alpha$, Small $\beta$', lw=lw, color=c)
+	axes[1].loglog(stepnumber, max_mass, lw=lw, color=c)
+	axes[1].loglog(stepnumber, mean_mass, lw=lw, ls='--', color=c)
 
 	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_fluffy_hot.txt')
-	axes.loglog(stepnumber, max_mass/mean_mass, label=r'Case b: Large $\alpha$, Large $\beta$', lw=lw)
+	c=next(axes[0]._get_lines.prop_cycler)['color']
+	axes[0].loglog(stepnumber, max_mass/mean_mass, label=r'Case b: Large $\alpha$, Large $\beta$', lw=lw, color=c)
+	axes[1].loglog(stepnumber, max_mass, lw=lw, color=c)
+	axes[1].loglog(stepnumber, mean_mass, lw=lw, ls='--', color=c)
 
 	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki.txt')
-	axes.loglog(stepnumber, max_mass/mean_mass, label=r'Case c: Small $\alpha$, Small $\beta$', lw=lw)
+	c=next(axes[0]._get_lines.prop_cycler)['color']
+	axes[0].loglog(stepnumber, max_mass/mean_mass, label=r'Case c: Small $\alpha$, Small $\beta$', lw=lw, color=c)
+	axes[1].loglog(stepnumber, max_mass, lw=lw, color=c)
+	axes[1].loglog(stepnumber, mean_mass, lw=lw, ls='--', color=c)
 
 	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_hot.txt')
[…]

### 2023-03-29 refereeResponse.txt
Changes into sec 5

@@
 See major comment.
+	This is a good point, and I'm not sure if we have a definitive answer.
+Inspecting figure 11, theh transition seems to occur near alpha ~ 0.1.
+I think the best thing to do here is to state the converse: for alpha << 1, most encounters result in scattering and you get oligarchic growth.
+The key finding from this section is that oligarchic growth does not occur when alpha is not << 1.
+The text has been updated to reflect this.
 
@@
 470: Reference of TRAPPIST-1
+	Added reference to Gillon 2016 + 2017, Agol 2021
 483 I recommend writing Eq. (6) along the lines of 10 g/cm^2 \times A (M_*/M_\odot)(r/1AU)^(-delta) for readability. The Sigma_MMSN is never used so it's not necessary.
+
 Table 1.

### 2023-03-29 main.tex
Changes into sec 5

@@
 facilitate oligarchic growth. In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and 
-embryos \citep{weidenschilling89, ida90}. When $\alpha$ is non-negligible, the Hill sphere of a body is no longer mostly 
-empty space, and close encounters that would otherwise result in viscous stirring instead result in accretion. In this regime, we 
+embryos \citep{weidenschilling89, ida90}.
+\textbf{When $\alpha \ll 1$, the Hill sphere of a body is mostly empty space and the majority of close encounters result in viscous stirring, rather than accretion.
+In the opposite regime,} we
 observe that runaway growth still occurs, but nearly all of the planetesimals are consumed by the forming protoplanets, rather 
@@
 Given the dearth of short-period terrestrial planets observed around M stars (e.g.
-TRAPPIST-1), we chose to model the evolution of a series of wide planetesimal disks, which span from 1 to 100 days in orbital period, orbiting a late-type M star of mass 0.08 $M_{\odot}$.
+TRAPPIST-1 \textbf{\citep{gillon16, gillon17, agol21}}), we chose to model the evolution of a series of wide planetesimal disks, which span from 1 to 100 days in orbital period, orbiting a late-type M star of mass 0.08 $M_{\odot}$.
 For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this orbital period range corresponds to $\alpha \in (0.7, 0.05)$.
@@
 \begin{equation}
-	\Sigma(r) = \left( \frac{M_{*}}{M_{\odot}} \right) A \Sigma_{\mathrm{MMSN}} \left( \frac{r}{1 \mathrm{AU}} \right)^{-\delta},
-\end{equation}
+	\Sigma(r) = \textrm{10 g cm}^{-2} \times A \left( \frac{M_{*}}{M_{\odot}} \right) \left( \frac{r}{\textrm{1 AU}} \right)^{-\delta}
+\end{equation}
+%\begin{equation}
+%	\Sigma(r) = \left( \frac{M_{*}}{M_{\odot}} \right) A \Sigma_{\mathrm{MMSN}} \left( \frac{r}{1 \mathrm{AU}} \right)^{-\delta},
+%\end{equation}
 where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g

### 2023-03-30 refereeResponse.txt
Referee edits into section 5

@@
 One would expect that gravitational scattering should completely shut off for alpha >= 1.
-The 'large beta' value is chosen to be as large as possible while still allowing the simulation to finish in a reasonable amount of time (collisions become more infrequent as we turn up the eccentricity dispersion).
-This is not explained in the text.
-Beta is also probably limited by r_apo-r_peri < delta_a (TODO: calculate this)
+Beta = 15,000 corresponds to <e^{1/2}>^2 = 0.05, which is the largest eccentricity for which a particle at 1 AU will an apo and pericenter distance that is still within the boundaries of the disk.
+For an eccentricity dispersion this large, the stirring timescale is much longer than the simulation time, so we can be confident that the boundary effects do not get worse.
+An explanation of the large beta value has been added to the text.
 
@@
 483 I recommend writing Eq. (6) along the lines of 10 g/cm^2 \times A (M_*/M_\odot)(r/1AU)^(-delta) for readability. The Sigma_MMSN is never used so it's not necessary.
-
+	Done
 Table 1.
@@
 I would probably put the planetesimal masses in units of Ceres
+	Where should I put the units?
 I think Table 1 and Table 2 could be combined
+	Table 1 has been merged into table 2.
 
@@
 Dra̧żkowska & Dullemond 2018, Lenz et al 2019.
+	Most planetesimal formation models invoke some sort of localized surface density enhancement to trigger the streaming instability.
+However, as the drazkowska paper shows, these preferential locations (in their case the snowline) can move, this spreading out super MMSN density planetesimals over a rather wide area.
+	TODO: What to mention in the paper about this?
+
 493: What is the motivation behind variation in the power-law index? Is there significant uncertainty in the MMSN power law index?
+	Chiang and Laughlin 2013 found that the MMEN power law varies between 1.6 and 1.8
+	Sub-mm observations of cold outer disks finds power law slopes as low as 0.5 (Mundy 2000, Andrews 2009, 2010).
+Alpha = 2.5 is chosen to increase the power law slope by the same interval in the other direction.
+TODO: Incorporate this into text
 499: Maybe elaborate on why this equilibrium is physical? Are there other works which use the same balance to inform initial conditions?
+	t_vs = t_gas is more of an upper limit on the eccentricity, although this is the same technique that Kokubo + Ida 1998 use to set up their initial conditions.
+It's certainly possible that the disk could have started out dynamically colder, although as we showed in figure 2, this doesn't seem to affect the resulting protoplanets.
+We have added a short discussion of these points to the text.
 504: missing respectively. And semi-major axes.
+	Fixed
 505: When is the Stokes regime valid, and what does it mean?
+	In the Stokes regime, the mean free path of the gas is much smaller than the size of the bodies and the gas can be treated as a fluid.
+For conditions in a typical protoplanetary disk, Stokes drag is relevant for cm-sized bodies and larger.
+This has been added to the text.
 506: The letter tau is used for a timescale just above, but now it says t.

### 2023-03-30 main.tex
Referee edits into section 5

@@
 \beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
+\textbf{This is the largest value of $\beta$ that permits a particle at 1 AU to still an apocenter and pericenter distance that lies within the boundaries of the disk.}
+
 \textbf{This choice of $\beta$ places the system firmly in the $v > v_{esc}$ regime, while still allowing growth to occur in a reasonable number of timesteps.}
@@
 planet formation \citep{kokubo98, kokubo00}.
-\begin{table}
-\caption{Summary of Full Disk Simulations Run}
-\begin{tabular}{llllll} \hline \hline
-Name    & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\delta^{d}$ &  \\ \hline
-fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &   \\
-fdHiShallow    & $5 \times 10^{22}$ & 903,687 & 100                                                        & 0.5                              &   \\
-fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &   \\
-fdLo                & $5 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &   \\ \hline
-\end{tabular}
-\begin{flushleft}
-\textsc{Note} \\ {$^a$ Planetesimal mass [g] \\
-		       $^b$ Number of planetesimals \\
-		       $^c$ Solid surface density normalization (relative to MMSN) \\
-		       $^d$ Solid surface density power law index } \\
-\end{flushleft}
-\label{tab:sims}
-\end{table}
 
@@
 
-Four wide-disk simulations are run in total (see table \ref{tab:sims}). In each case, the solid surface density follows a power law profile
+Four wide-disk simulations are run in total (see table \ref{tab:sim_properties}). In each case, the solid surface density follows a power law profile
 \begin{equation}
@@
 \end{equation}
-%\begin{equation}
-%	\Sigma(r) = \left( \frac{M_{*}}{M_{\odot}} \right) A \Sigma_{\mathrm{MMSN}} \left( \frac{r}{1 \mathrm{AU}} \right)^{-\delta},
-%\end{equation}
+
 where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g
@@
 In all cases, the eccentricities and inclinations of the bodies are randomly drawn from a Rayleigh distribution, with $\left< e^{2} \right>^{1/2} = 2\left<i^{2} \right>^{1/2} = e_{eq}$ \citep{ida93}.
-The value of $e_{eq}$ is chosen such that the timescales for viscous stirring and aerodynamic gas drag on the planetesimals are in equilibrium.
-The viscous stirring timescale is given by \citet{ida93} as
+\textbf{Following \citet{kokubo98},} the value of $e_{eq}$ is chosen such that the timescales for viscous stirring and aerodynamic gas drag on the planetesimals are in equilibrium.
+\textbf{Although this approach assumes that these two mechanisms are in balance, there is nothing preventing planetesimal accretion from getting underway before the disk is sufficiently hot to be limited by gas drag.
+However, as we showed in the previous section, the initial dynamical state of the planetesimals does not seem to affect the outcome of accretion, so it is safe to assume that the resulting distribution of protoplanets would remain unchanged had we started with a colder disk.} The viscous stirring timescale is given by \citet{ida93} as
 
@@
 \end{equation}
-where $\Omega$, $a$ and $e$ are the orbital frequencies, semimajor axes and eccentricities of the individual planetesimals. In the Stokes regime, the gas drag timescale is given by \citet{adachi76} as
+where $\Omega$, $a$ and $e$ are the orbital frequencies, semi-major axes and eccentricities of the individual planetesimals, \textbf{respectively}.
+In the Stokes regime, \textbf{where the mean-free path of the gas is much smaller than the solid particles, the gas can be treated as a fluid and} the drag timescale is given by \citet{adachi76} as
 \begin{equation}\label{eq:ts_stokes}
@@
 
-\begin{table}
-\caption{Final Properties of Full Disk Simulations}
-\begin{tabular}{lllll} \hline \hline
-Name     & $M_{PP}^a$ & $T_{int}^b$ & $T_{int 1}^c$ &  \\ \hline
-fdHi                 &  1.00                                                         & 456                              & 16,377  &  \\
-fdHiShallow    &  1.19                                                        & 456                              & 16,377  &  \\
-fdHiSteep       &  1.08                                                         & 456                              & 16,377 &  \\
-fdLo                &  1.77 $\times 10^{-3}$                                  & 3,713                              & 133,651 &  \\ \hline
+\begin{table*}
+\caption{Summary of Full Disk Simulations}
+\begin{tabular}{llllllllll} \hline \hline
+Name     & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\delta^{d}$ & $M_{PP}^a$ & $T_{int}^b$ & $T_{int 1}^c$ &  \\ \hline
+fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &  1.00                                                         & 456                              & 16,377  &  \\
+fdHiShallow    & $5 \times 10^{22}$ & 903,687 & 100                                                        & 0.5                              &  1.19                                                        & 456                              & 16,377  &  \\
+fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &  1.08                                                         & 456                              & 16,377 &  \\
+fdLo                & $5 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &  1.77 $\times 10^{-3}$                                  & 3,713                              & 133,651 &  \\ \hline
 \end{tabular}
@@
 \end{flushleft}
-\end{table}
+\end{table*}
 

### 2023-03-31 refereeResponse.txt
Referee edits up to sec 5.2

@@
 Dra̧żkowska & Dullemond 2018, Lenz et al 2019.
-	Most planetesimal formation models invoke some sort of localized surface density enhancement to trigger the streaming instability.
-However, as the drazkowska paper shows, these preferential locations (in their case the snowline) can move, this spreading out super MMSN density planetesimals over a rather wide area.
-	TODO: What to mention in the paper about this?
+	This is briefly discussed in the introduction but we will expand upon it here.
+Most mechanisms involve dust traps or pressure bumps occuring at some preferential location in the disk which trigger the streaming instability.
+Dra̧żkowska & Dullemond 2018 show that a migrating snow line can actually trigger planetesimal formation over a fairly wide area, and also produce surface density enhancements at least as large as the ones we use.
+Given that low-mass stars have particularly extreme luminosity changes during the pre-main sequence (see Baraffe 2015), one can imagine that it might not be hard to trigger planetesimal formation over a wide area.
+This particular paragraph in the text has been expanded to discuss this.
 
 493: What is the motivation behind variation in the power-law index? Is there significant uncertainty in the MMSN power law index?
-	Chiang and Laughlin 2013 found that the MMEN power law varies between 1.6 and 1.8
+	Chiang and Laughlin 2013 applied a similar analysis to Kepler multis and found that delta varies between 1.6 and 1.8.
 Sub-mm observations of cold outer disks finds power law slopes as low as 0.5 (Mundy 2000, Andrews 2009, 2010).
-Alpha = 2.5 is chosen to increase the power law slope by the same interval in the other direction.
-TODO: Incorporate this into text
+Therefore, we vary delta by +/- 1.0 from the MMSN value.
+There is now a separate paragraph in the text explaining this
 499: Maybe elaborate on why this equilibrium is physical? Are there other works which use the same balance to inform initial conditions?
@@
 Tau tends to be used for dimensionless timescales, so I would probably go with t_s and t_vs.
+	tau_vs has been changed to t_vs in equation 7.
 511: Solid-to-gas surface density ratio of 1/240 seems very small, especially given that the authors are considering the solid surface density to already be enhanced by a factor of 100.
@@
 I think the authors could be over-estimating the gas density by up to a factor of a 100, which means the stopping time would be a factor of 100 longer.
+	TODO: Fix
 516: I suggest using another symbol for the temperature power law, since Q is associated with the Toomre value of the disk, for example q. Also, this equation should read T(r) = T_0(r/1AU)^-q, right?
+	Q was changed to q to be consistent with the Andrews + Williams paper. the '/1AU' has been added to the T(r) equation.
 521: Where is that equation coming from? Maybe add reference.
+	This is equation 4.30 from Phil Armitage's 'Astrophysics of Planet Formation'. A reference has been added to the text.
 

### 2023-03-31 main.tex
Referee edits up to sec 5.2

@@
 This choice of normalization for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \citep{hansen12}.
+\textbf{The most current planetesimal formation models all involve streaming instabilities triggered by solid material concentrating at preferential locations in the disk.
+This can occur via zonal flows \citep{johansen2009b, simon12}, vortices \citep{klahr03}, or through mechanisms that produce a pressure bump in the gas disk, such as an ionization \citep{lyra08} or condensation front \citep{brauer08b, drkazowska13}, or even the perturbations from an existing planet \citep{shibaike20}.
+\citet{drkazowska18} showed that evolution of the snow line boundary can cause planetesimal formation over a significant area of the disk, producing mass concentrations at least as large as the ones we use here.
+We argue that this is a particularly attractive mechanism for widespread planetesimal formation around low-mass stars, as their extreme pre-main sequence evolution is particularly conducive to significant movement of the condensation fronts \citep{baraffe15}.}
+
 Additionally, we vary the power law index (fdHiShallow, fdHiSteep) and overall normalization (fdLo) of $\Sigma(r)$.
+\textbf{Although there is no way to reliably measure the uncertainty on the MMSN power law slope, \citet{chiang13} applied a similar analysis to a sample of Kepler multiplanet systems and found a variation of $\sim 0.2$.
+Sub-millimeter observations of the outer regions of cold protoplanetary disks find that $\delta$ can be as low as 0.5 \citep{mundy00, andrews09, andrews10}.
+Therefore, we vary $\delta$ by a value of $1.0$ relative to the MMSN value for the fdHiShallow and fdHiSteep simulations.}
 
@@
 \begin{equation}\label{eq:vs_timescale}
-    \tau_{vs}  = \frac{\left< e^2 \right>}{d \left< e^2 \right> / dt} \approx \frac{1}{40}\left(\frac{\Omega^{2} a^{3}}{2 G m_{pl}}\right)^{2} \frac{4 m_{pl} \langle e^{2} \rangle^{2}}{\Sigma a^{2} \Omega},
+    t_{vs}  = \frac{\left< e^2 \right>}{d \left< e^2 \right> / dt} \approx \frac{1}{40}\left(\frac{\Omega^{2} a^{3}}{2 G m_{pl}}\right)^{2} \frac{4 m_{pl} \langle e^{2} \rangle^{2}}{\Sigma a^{2} \Omega},
 \end{equation}
@@
 240 times the solid surface density \citep{hayashi81}, $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
-The sound speed profile is given by $c_{s} = \sqrt{k_{B} T(r) / \left( \mu m_{H} \right)}$, where $k_{B}$ is Boltzmann's constant, $T(r) = T_{0} r^{-Q}$, $\mu = 2.34$ and $m_{h}$ is the mass of a hydrogen atom.
-For a protoplanetary disk around a typical M star, $T_{0} = 148$ K and $Q$ = 0.58 \citep{andrews05}.
+The sound speed profile is given by $c_{s} = \sqrt{k_{B} T(r) / \left( \mu m_{H} \right)}$, where $k_{B}$ is Boltzmann's constant, $T(r) = T_{0} \left( r / 1 \textrm{AU} \right)^{-q}$, $\mu = 2.34$ and $m_{h}$ is the mass of a hydrogen atom.
+For a protoplanetary disk around a typical M star, $T_{0} = 148$ K and $q$ = 0.58 \citep{andrews05}.
 
@@
 \begin{equation}\label{eq:v_gas}
-	v_{g} = v_{k} \left[ 1 - \sqrt{ Q c_{s}^2 / v_{k}^2} \right],
+	v_{g} = v_{k} \left[ 1 - \sqrt{ q c_{s}^2 / v_{k}^2} \right],
 \end{equation}
 
-\noindent where $v_{k}$ is the local Keplerian velocity. As in section
+\noindent where $v_{k}$ is the local Keplerian velocity \textbf{(see eq. 4.30 of \citet{armitage20})}. As in section
 \ref{sec:narrow}, the argument of perihelion $\omega$, longitude of

### 2023-04-03 refereeResponse.txt
Address comment about roche limit

@@
 	Added a handful of references arguing that the asteroids, KBOs and Oort cloud bodies are leftover planetesimals.
+	See Duncan, Tremaine Quinn papers (particularly 1988 one + references?)
 72: Maybe elaborate on this. How long is the period of quiescence? How does this instability work?
@@
 I understand that the scaling of alpha predicts alpha >1 at some radius (which I would explicitly mention), but this just implies that inside this radius, bodies must have greater densities to not be disrupted.
-	Alpha = 1 doesn't correspond  to the roche limit (although they are close)! TODO: Maybe add a calculation here explaining this.
+	The distance at which alpha = 1 (a_alpha) and the Roche (a_roche) limit are similar, but not identical.
+For a rigid spherical body, a_roche ~ 0.88 a_alpha.
+Applying the hydrostatic correction, a_roche ~ 0.6 a_alpha.
+This is important, because it implies that the new growth mode presented in this paper should be relevant for ring systems!
+We will add a note of this in the text.
+I think some of the confusion comes from the fact that the Roche limit and the Hill sphere size are not derived using the same formalism.
 289: gravitational radius: is this physically motivated? Maybe reference

### 2023-04-04 refereeResponse.txt
More referee edits in section 5

@@
 the Stokes number of the planetesimals, I'm assuming that they are substantially above unity, which means that the bodies are essentially decoupled from the gas.
+	Agreed.
+Describing things in terms of the Stokes number allows us to simplify this section a bit.
+For the initial planetesimals, St >> 1 at both the inner and outer disk edge Because St ~ m^1/3, we can guarantee that bodies will remain decoupled from the gas throughout the simulation.
+By discussing the Stokes number, we can also avoid having to compare the stopping time with the integration time of the simulations.
+These points are now all discussed in the text.
 536: Isolation mass lacks definition
+	We have removed any mention of the isolation mass here. The fact that St ~ m^1/3 is enough to guarantee that the gas and solids remain decoupled.
 
@@
 554: footnote 2 can just go in the main text body.
+	Done
 584: footnote 3 can also go in the main text body.
+	Done
 584: Are there any works on the numerical robustness of this more efficient time-stepping scheme.
 While I'm inclined to believe that the error is only marginal, I think having some sort of test (or a reference to one) would make the results more steadfast.
-	No there arent.
+	I'm fairly certain that we are the first ones to try this.
 I've added an appendix that compares this timestepping scheme against a fixed timestep case.
@@
 TODO: Show mass distribution as differential or cumulative?
-Finish running sims
 
@@
 586: Maybe include reference to figure where this is shown
+	Figure 1 of Kokbubo 2002 shows this clearly. A reference to the paper has been added in the text.
 592: Is this really always true? Counterexample e.g. Emsenhuber et al 2021 and others.
+	The NGPPS models (along with the Clement 2020 paper) seem to be a couple of notable exceptions to this, although the embryo growth is not treated self-consistently leading up to the giant impact phase.
+We have added a mention of the Emsenhuber papers to the text.
 Table 2:
 What is the rescaled integration time?
+	TODO: Not sure where to explain table columns now?
+
 Figure 5:
@@
 If so the statement should be rephrased to make the causal connection clear.
+
 606: How can a mass be expressed in units of feeding zone size?

### 2023-04-04 main.tex
Address comment about roche limit
More referee edits in section 5

@@
 implies that the Hill sphere of a body becomes smaller than its physical size.
+\textbf{As an additional note, the Roche limit of the central body and the distance at which $\alpha = 1$ are
+similar, but not identical.
+For a rigid spherical body, $a_{Roche} \simeq 0.88 a_{\alpha = 1}$.
+Applying a hydrostatic correction to the Roche limit, $a_{Roche} \simeq 0.6 a_{\alpha = 1}$.
+This accretion mode should
+therefore be relevant for ring systems.}
 
@@
 In addition to the mutual gravitational forces, a Stokes drag force due to the the gas disk is applied to each particle, following the prescription described in section 2.2.1 of \citet{morishima10}.
-For the initial mass planetesimals, the stopping time (see equation \ref{eq:ts_stokes}) at the inner edge of the disk is roughly 100 yr.
-Although this is a few orders of magnitude shorter than the integration time of the simulations, the Stokes drag force plays a fairly insignificant role as the bodies grow via mutual collisions.
-By the time the bodies reach isolation mass (roughly a tenth of an Earth mass), the stopping time at the inner disk edge exceeds 50,000 years.
-Although the aerodynamic gas drag is not expected to significantly alter the final protoplanet distribution, we include its effects here to be self-consistent with the initial conditions, which were constructed by balancing the effects of viscous stirring with gas drag.
+For the initial mass planetesimals, the \textbf{Stokes number ($\textrm{St} = t_{s} \Omega$) at the inner and outer disk edge is roughly $2 \times 10^{5}$ and $10^{7}$, respectively.
+For $\tau_{s} \gg 1$, bodies are decoupled from the gas and are only weakly affected by it.
+Because $\tau_{s} \sim m^{1/3}$, the Stokes number grows as planetesimal accretion proceeds, and the drag force plays an increasingly minor role.} Although the aerodynamic gas drag is not expected to significantly alter the final protoplanet distribution, we include its effects here to be self-consistent with the initial conditions, which were constructed by balancing the effects of viscous stirring with gas drag.
 
@@
 based on their most recently calculated gravitational
-acceleration.\footnote{This scheme is used on almost all works using ChaNGa,
+acceleration. \textbf{This scheme is used on almost all works using ChaNGa,
 and is common among large-scale simulation codes.}
@@
 factor of 10 prevents any artifacts from developing at the timestep
-boundaries, while also minimizing the number of `skipped' collisions.\footnote{In the case of fdHi, only about 20 collisions out of an eventual 900,000 are ignored.}
+boundaries, while also minimizing the number of `skipped' collisions.
+\textbf{In the case of the fdHi simulation, only about 20 collisions out of an eventual 900,000 are ignored.
+To verify that this timestepping scheme does not affect protoplanet growth, we tested an annulus of growing planetesimals with both fixed steps and our two-phase variable timestepping scheme.
+The results of these tests are shown in appendix \ref{sec:rung_egg}.}
 
@@
 inside-out fashion, with the outermost regions of the disk completing
-the protoplanet assembly phase last. This radial timescale dependence is not typically
+the protoplanet assembly phase last \textbf{((as an example, see figure 1 of \citet{kokubo02)}. This radial timescale dependence is not typically
 accounted for in planet formation simulations\footnote{Instead, the innermost protoplanets 
-patiently `wait' for this phase of evolution to complete everywhere in the disk}, and appears to be an
+patiently `wait' for this phase of evolution to complete everywhere in the disk} \textbf{(a notable exception being \citet{emsenhuber21a, emsenhuber21b})}, and appears to be an
 important component to forming realistic solar system analogs

### 2023-04-05 refereeResponse.txt
Update figure 5

@@
 If so the statement should be rephrased to make the causal connection clear.
-
+	The y axis on the bottom panel of figure 5 is now log-scaled.
+Point colors in both panels have been changed to orange, to be consistent with figure 2.
+The dashed line in the bottom panel is now labeled.
+Yes, we are defining the oligarchic growth region to be the region where \tilde{b}_required <= 2\sqrt{3}.
+The last sentence in the figure caption has been rephrased to make this clearer.
 606: How can a mass be expressed in units of feeding zone size?
+	We are solving equation 11 for \tilde{b} and using the initial local surface density, along with the final particle mass to calculate the feeding zone size.
+We tried to explain this starting on line 611, but it sounds like some further clarification is needed.
+Some additional text has been added to the paragraph following equation 11 to explain where the value for \tilde{b} comes from.
 620: What is the intuition behind tilde b, how exactly is it defined?

### 2023-04-05 main.tex
Update figure 5

@@
 To verify that this timestepping scheme does not affect protoplanet growth, we tested an annulus of growing planetesimals with both fixed steps and our two-phase variable timestepping scheme.
-The results of these tests are shown in appendix \ref{sec:rung_egg}.}
+The results of these tests are shown in appendix \ref{sec:rung_ecc}.}
 
@@
       the final masses of the bodies. The dashed line indicates the feeding
-      zone size ($\tilde{b} = 2 \sqrt{3}$) expected for bodies on
-      circular orbits.
-      Interior to the oligarchic
-      growth region (around 60 d), the feeding zone sizes exceed this value.\label{fig:fulldisk_e_m}}
+      zone size expected for bodies on circular orbits. \textbf{For the shorter period bodies,
+      the feeding zone size exceeds this expected value, which indicates that oligarchic growth is
+      not operating here. This boundary occurs near roughly 60 d in orbital period.}\label{fig:fulldisk_e_m}}
 \end{center}
@@
 inside-out fashion, with the outermost regions of the disk completing
-the protoplanet assembly phase last \textbf{((as an example, see figure 1 of \citet{kokubo02)}. This radial timescale dependence is not typically
+the protoplanet assembly phase last \textbf{(as an example, see figure 1 of \citet{kokubo02)}}. This radial timescale dependence is not typically
 accounted for in planet formation simulations\footnote{Instead, the innermost protoplanets 
@@
 \end{equation}
-where $M$ is taken to be the final mass of each body. Here, we assume that each embryo has reached its isolation mass, and 
+where $M$ is taken to be the final mass of each body.
+\textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and
 that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 

### 2023-04-05 makeFig.py

@@ -395,7 +395,7 @@ def plot_fulldisk_e_m_b():
 	l = np.logspace(np.log10(30), np.log10(np.max(H)), 10)
 	c = axes.contour(binsX, binsY, np.flipud(np.rot90(H)), colors='black', linewidths=0.2, levels=l)
 
-	axes.scatter(per.value, plVHi['e'], s=plVHi['mass']/refmass*1000, edgecolor='black', linewidth=0.4)
+	axes.scatter(per.value, plVHi['e'], s=plVHi['mass']/refmass*1000, edgecolor='black', linewidth=0.4, color='#ff7f0e')
 	axes.set_ylabel('Eccentricity')
 	axes.set_xlim(p_min, p_max)
 	axes.set_ylim(e_min, e_max)
@@ -409,10 +409,12 @@ def plot_fulldisk_e_m_b():
 	#m_iso_vhi1 = np.sqrt((2*np.pi*a_vals**2*btilde*surf_den)**3/(3*mCentralg))
 
 	axes = ax[1]
-	axes.scatter(per.value, get_btilde(plVHi, p_vhi_ic), edgecolor='black', linewidth=0.4)
+	axes.scatter(per.value, get_btilde(plVHi, p_vhi_ic), edgecolor='black', linewidth=0.4, color='#ff7f0e')
 	axes.axhline(2.*np.sqrt(3.), ls='--', color='gray')
 	#axes.axhline(10., ls='--', color='gray')
-	axes.set_ylim(0, 20)
+	axes.set_yscale('log')
+	axes.set_ylim(1, 20)
+	axes.text(70, 2*np.sqrt(3)*1.05, r'$\tilde{b} = 2 \sqrt{3}$ (Circular Orbit)', fontsize=12)
 	axes.set_xlabel('Orbital Period [d]')
 	axes.set_ylabel(r'Required $\tilde{b}$')
 
@@ -1187,9 +1189,9 @@ def plot_rung_ecc():
 
 #plot_timescales()
 #plot_alpha_beta()
-plot_alpha_beta_evo()
+#plot_alpha_beta_evo()
 #plot_alpha_beta_mass()
-#plot_fulldisk_e_m_b()
+plot_fulldisk_e_m_b()
 #plot_alpha_pl_frac()
 #plot_pl_frac_time()
 #plot_surfden_profiles()

### 2023-04-07 refereeResponse.txt
Changes through section 5.4

@@
 Do I understand correctly that a body with tilde b less than 2 sqrt(3) is associated with a feeding zone so small that close encounters are not possible, and thus are not expected to grow further?
+	This is buried in some of the references in this section (Nazakawa + Ida 1988, Kokubo 1998, Kokubo 2002), but I'm realizing this is not stated explicitly anywhere in the paper so I will do so: \tilde{b} is a length in units of the local Hill radius.
+	The \tilde{b} = 2\sqrt{3} value is important because this is the smallest possible feeding zone size that a body can have.
+As eccentricity decreases, the feeding zone size decreases, but has a minimum value of 2\sqrt{3} for (e,i) = (0,0) (See section 6 of Nazakawa + Ida 1988 for an explanation as to why).
+Therefore, a protoplanet undergoing oligarchic growth (in which gravitational scattering events are frequent and keeps the largest bodies on circular orbits) will not accrete more than 2\sqrt{3}*r_h*Sigma worth of material from its surroundings.
+The key takeaway from the bottom panel of figure 5 is that there are bodies interior to 60d that must have accreted material from a much wider annulus than this, and so oligarchic growth is not operating here.
+	TODO: Update text somewhere?
 632: Why are the bodies expected to follow the tilde b = 2sqrt(3) from a theoretical perspective?
 Also, I'm unconvinced that the bodies do that at all in the presented simulations - they fall below this value but don't follow it.
+	See response to 620.
+You are right that the outer disk bodies do not all reach \tilde{b} = 2\sqrt{3}.
+TODO: Should probably mention that this should be interpreted as a maximum.
+Not feasible to run the outer disk to completetion (especially in the fdSteep case).
 640: If anything the opposite seems to be true, no? Maybe have a specific value for the expected eccentricity of protoplanets with and without inelastic damping.
+	TODO
 644: If I look at the contour map by eye, the eccentricity distribution doesn't seem all that different in the inner vs outer disk. Maybe the difference can be quantified?
+	You are right that the variation in eccentricity is not huge.
+For the model used by our initial condition generator, the mean eccentricity is a factor of 4x larger at the outer disk edge, compared to the inner disk edge.
+This is now stated in the text.
 647: This is an interesting point.
@@
 Is it possible to include such a comparison maybe with a figure?
+	Yes!
+See our updated version of figure 6.
+The time is now shown in units of the local accretion timescale, and it is now apparent that the planetesimal surface density curves all follow the same trajectory exterior of 60d.
 Figure 6:
@@
 The difference between the 60 day boundary could still be indicated with an additional line.
+	See our response to the previous concern, along with our response to major comment #1.
+	TODO: Update text to reflect changes to figure 6.
+	TODO: Run fdhi for a thousand steps at higher output cadence, so the innermost curve starts sooner
 665: I struggle to see that there is a significant qualitative difference in the behavior in the lines just inside and just outside the boundary of 60 orbits.
 The first dashed line also seems to converge to a sigma/Sigma \sim 5 %, not much below the first solid line.
+	See our response to the previous concern, along with our response to major comment #1.
 668: add reference. Also footnote 5 can probably go in the main text. Can the authors provide an equation that converts tilde b to units of r_h?
+	\tilde{b} is already in units of r_h.
+This is now clarified near line 620 in the text.
+The 30 percent value simply comes from removing the size of the feeding zone (2\sqrt{3}) from the spacing between oligarchs (10).
+This is now clarified in the text here.
+I think the footnote text can be removed after adding this clarification.
 682: This statement seems only to be true for fdshallow. The others have a spread in eccentricity that covers two orders of magnitude...
+	I think we need to change the wording here.
+What we were trying to say is: the resulting a-e distributions for the embryos between all of the simulations are quite similar (with the exception of fdLo), despite the fact that the a-e distributions of the initial conditions are different.
 685: It is not clear to me why more inelastic collisions lead to a more sharply peaked eccentricity distribution, and not just more damping like the authors argue for the fdLo simulation.
+	I'm not sure what you mean by 'more shaply peaked'?
+The argument we're trying to make here is this: In the case that the initial surface density is large (e.g.
+the inner part of the fdSteep simulation), the initial eccentricity dispersion is larger (because the viscous stirring timescale is shorter and so we start out with a larger <e^2>^1/2 to make t_vs = t_gas).
+The increased surface density leads to more collisions, which leads to more inelastic damping.
+So the larger eccentricity dispersion that we started with quickly damps out.
 701: Again, I don't see that the value for tilde b approaches 2sqrt(3) beyond P=60d orbits. The bodies have smaller feeding zones than tilde b = 2sqrt(3)
+	Perhaps if we ran some of these simulations for longer, the embryos beyond 60d would all reach \tilde{b} = 2\sqrt{3}.
+But this requires an intractible number of timesteps, particularly for the fdSteep simulation, where the surface density in the outer disk is quite low.
+I think the best we can say here is that none of the embryos exceed \tilde{b} = 2\sqrt{3} which is consistent with the oligarchic growth model.
 702: Are they that similar?
@@
 if the simulation is initialized with a different random seed, by how much does the final distribution change?
+	We were saving these for the follow up paper, but we do have multiple versions of fdHi, fdSteep and fdShallow!
+These have now been added to figure 8.
+The added data does make it clear that the boundary is quite fuzzy.
+I've also plotted the mean and standard deviation of the \tilde{b} in a number of orbital period bins.
+I think this makes the accretion boundary a little more apparent.
+With the exception of maybe the fdShallow simulation, the locations in the disk where \tilde{b} drops below 2\sqrt{3} are broadly consistent, which supports our claim that the boundary location is driven by the local value of alpha.
 

### 2023-04-07 main.tex
Changes through section 5.4

@@
 final masses of the bodies (in units of feeding zone size) are shown
-as a function of orbital period. The feeding zone size $\tilde{b}$ is
-calculated according to \citet{kokubo02}
+as a function of orbital period. The feeding zone size $\tilde{b}$ \textbf{is described in units of the local Hill radius and is} calculated according to \citet{kokubo02}
 \begin{equation}\label{eq:iso}
@@
 extra dynamical cooling mechanism difficult to see. Firstly, the initial eccentricity distributions of the inner and outer disk are 
-different because of the dependence of the viscous stirring and gas drag timescales on orbital period. Additionally, the 
+different because of the dependence of the viscous stirring and gas drag timescales on orbital period.
+\textbf{The mean eccentricity at the outer disk edge is 4x larger than at the inner disk edge.} Additionally, the
 protoplanet formation timescales for the inner and outer disk are vastly different, making a comparison between these regions at 
@@
 should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle 
-onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimals should remain out of reach of the 
-protoplanets\footnote{A feeding zone width of $ \tilde{b} = 2 \sqrt{3}$ covers roughly 70 percent of the 10 $r_{h}$ space between the protoplanets.}.
+onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent \textbf{($2\sqrt{3}/10 \simeq 0.3$)} of the planetesimals
+should remain out of reach of the protoplanets.
 
@@
 contains a bimodal population of planetesimals and embryos, with a clear separation in eccentricity between the two. Despite 
-having significantly different masses, the planetary embryos formed in all simulations have remarkably similar eccentricities. This 
+having significantly different masses, the \textbf{semimajor axis-eccentricity} distributions of the planetary embryos formed in all simulations \textbf{are} remarkably similar. This 
 is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which 

### 2023-04-07 makeFig.py

@@ -37,6 +37,7 @@ mCentral = 0.08
 mCentralg = (mCentral*u.M_sun).to(u.g)
 
 bins = np.linspace(0.01, 0.3, num_bins)
+perbins = 2*np.pi*np.sqrt((bins*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 
 snap = pb.load('data/fullDiskVHia.ic')
 plVHiIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
@@ -640,35 +641,77 @@ def plot_surfden_b():
 	plVHiShe = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 	perShe = 2*np.pi*np.sqrt((plVHiShe['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 
+	perbins1 = np.linspace(1, 100, 6)
+	perbincents = 0.5*(perbins1[1:] + perbins1[:-1])
+
+	periods = np.concatenate([per.value, perb.value, perc.value, perd.value, pere.value])
+	btildes = np.concatenate([get_btilde(plVHi, p_vhi_ic), get_btilde(plVHib, p_vhi_ic),
+		get_btilde(plVHic, p_vhi_ic), get_btilde(plVHid, p_vhi_ic), get_btilde(plVHie, p_vhi_ic)])
+	mass_mask = btildes > 1
+	fdhi_means, edges, binnumber, = stats.binned_statistic(periods[mass_mask], btildes[mass_mask], statistic='mean', bins=perbins1)
+	fdhi_std, edges, binnumber, = stats.binned_statistic(periods[mass_mask], btildes[mass_mask], statistic='std', bins=perbins1)
+
+	periodsSt = np.concatenate([perSt.value, perStb.value, perStc.value, perStd.value, perSte.value])
+	btildesSt = np.concatenate([get_btilde(plVHiSt, p_vhi_ic_st), get_btilde(plVHiStb, p_vhi_ic_st),
+		get_btilde(plVHiStc, p_vhi_ic_st), get_btilde(plVHiStd, p_vhi_ic_st), get_btilde(plVHiSte, p_vhi_ic_st)])
+	mass_mask = btildesSt > 1
+	fdhiSt_means, edges, binnumber, = stats.binned_statistic(periodsSt[mass_mask], btildesSt[mass_mask], statistic='mean', bins=perbins1)
[…]

### 2023-04-11 refereeResponse.txt
Edits up to fig 10

@@
 With the exception of maybe the fdShallow simulation, the locations in the disk where \tilde{b} drops below 2\sqrt{3} are broadly consistent, which supports our claim that the boundary location is driven by the local value of alpha.
+	TODO: Update text to recflect changes to figure.
 
@@
 719: add references.
+	Done
 721: Does this distinction have analogies in galaxy formation?
@@
 9 where the smooth accretion fraction is always <10%.
+	TODO: Ask tom about this?
 724: Why are only the 100 largest bodies chosen?
@@
 Also, why is the fdHi simulation chosen?
+	TODO: What else to include here? Everything?
 726: I think it could be explicitly stated that smooth accretion = minor mergers.
@@
 Seems to me that for all bodies, regardless of mass and orbital period, major mergers are significantly more important - that is at least with the author's definition of major and minor merger.
+	I agree that 1-10% is a small fraction. The mass cutoff should definitely be larger. TODO: Change mass cutoff and hopefully the same scaling with mass remains.
 In the legend, I think "orbit" should be put in the subscript instead of P_orbit
 746: This is just because in the inner disk there are no primordial planetesimals left to build the more massive bodies, right?
+	No, the accretion mode should be qualitatively different, even before the planetesimals run out.
+TODO: Hopefully including more data in the plot and maybe increasing the mass cutoff for 'smooth' accretion will make this more obvious.
 750: use /citep[see][]{Kokubo}
+	Fixed
 756: I agree that the large bodies must've originated due to mergers with other embryos, but this is not really an explanation for why the feeding zone size doesn't match the theoretical value, no?
@@
 766: "One should note that [...]." This sentence can be deleted in my opinion.
+	Removed
 Figure 10:

### 2023-04-11 main.tex
Edits up to fig 10

@@
 for cosmological simulations of galaxy formation, we divide growth events for
-a given body into ``major'' and ``minor'' mergers. Here, we define minor events as any collision involving an initial mass 
+a given body into ``major'' and ``minor'' mergers \citep{kauffmann93, murali02, lhullier12}. 
+Here, we define minor events as any collision involving an initial mass 
 planetesimal, while major events consist of a merger between any two larger bodies. In figure \ref{fig:minor_frac}, we choose the 
@@
 Inside the boundary, however, later growth events tend to be dominated by embryo-embryo collisions, and the smooth accretion fraction drops as mergers with planetesimals play a less significant role.
-Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion (see \citet{kokubo98}), and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
+Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion \citep{kokubo98}, and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
 As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zone size predicted by an oligarchic growth model.
@@
 hash mark indicates the present orbital period of an embryo and the histogram represents the initial orbital period distribution of the planetesimals used to construct the embryo.
-One should note that unlike the previous figure, this plot shows where every single bit of mass (in the form of planetesimals) originated, rather than only indicating the result of direct collisions with the embryos.
 

### 2023-04-11 makeFig.py

@@ -42,7 +42,7 @@ perbins = 2*np.pi*np.sqrt((bins*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 snap = pb.load('data/fullDiskVHia.ic')
 plVHiIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi_ic = pb.analysis.profile.Profile(plVHiIC.d, bins=bins, calc_x = lambda x: x['a'])
-snap = pb.load('data/fullDiskVHi1a.250000')
+snap = pb.load('data/fullDiskVHi1.250000')
 plVHi = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi = pb.analysis.profile.Profile(plVHi.d, bins=bins, calc_x = lambda x: x['a'])
 perIC = 2*np.pi*np.sqrt((plVHiIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
@@ -772,12 +772,17 @@ def plot_smooth_acc():
 
 	nam = ['time', 'collType', 'iorder1', 'iorder2', 'm1', 'm2', 'r1', 'r2', 'x1x', 'x1y', 'x1z', 'x2x', 'x2y', 'x2z',  'v1x', 'v1y', 'v1z', \
 	'v2x', 'v2y', 'v2z', 'w1x', 'w1y', 'w1z', 'w2x', 'w2y', 'w2z']
-	df1 = pd.read_csv('data/fullDiskVHi.coll', names=nam, sep=' ', index_col=False)
-	df2 = pd.read_csv('data/fullDiskVHi1.coll', names=nam, sep=' ', index_col=False)
+	time = 0.05*248000/(2*np.pi)
+	df1 = pd.read_csv('data/fdvhia/fullDiskVHi.coll', names=nam, sep=' ', index_col=False)
+	df2 = pd.read_csv('data/fdvhia/fullDiskVHi1.coll', names=nam, sep=' ', index_col=False)
 	df = pd.concat([df1, df2])
-	df1_s, df1_d = np.loadtxt('data/fullDiskVHi_delete1', dtype='int', unpack=True)
-	massive_ind = np.argsort(np.array(plVHi['mass']))[::-1][:num_oli]
-	a_iord_orig = plVHi['iord'][massive_ind]#prev_iorder(plVHi['iord'][massive_ind], len(plVHiIC), df1_d)
+	df = df[df['time'] <= time]
+
[…]

### 2023-04-11 refereeResponse.txt
Edits to section 5 and 6

--- 2023-04-07 refereeResponse.txt
@@
 Also, why is the fdHi simulation chosen?
+	The 100 body cutoff was chosen because the analysis script we were using the construct the collision history was rather slow when asked to include all ~10,000 particle in the snapshot.
+This has been optimized and all bodies are now included in figure 9.
+fdHi is chosen to be the 'fiducial' simulation for most of this paper.
+The initial conditions for fdHi require the least assumptions (MMSN profile with enough extra mass included to construct ~1 M_earth planets).
 726: I think it could be explicitly stated that smooth accretion = minor mergers.
@@
 I'm in particular unconvinced that the trend for P > 60 days truly is flat, given the small sample size for larger bodies.
+	As with figure 8, we have now included data from the other fdHi runs (using a different random seed). The P > 60d trend is now much more clearly flat.
 Figure 9:
 Given that I'm skeptical about the 60 day boundary being clear and universal, I think this plot would be stronger if the bodies were colored by orbital period (in addition to the marker style indicating this boundary), and the plot would include a corresponding colorbar.
+	TODO: Get rid of different marker types, apply diverging color map to points, with white centered at 60d
 The authors state "there is a decreasing correlation between smooth accretion fraction and mass, which suggests that most growth occurs between equal mass bodies".
@@
 I would argue that more massive bodies require more time to build up and during later stages there are simply less primordial planetesimals left so collisions are just more likely to be major mergers.
+
 The authors state "indicating that accretion of planetesimals is important during all phases of the evolution", yet the smooth accreting fraction is only between 1-10% for all these bodies.
 Seems to me that for all bodies, regardless of mass and orbital period, major mergers are significantly more important - that is at least with the author's definition of major and minor merger.
+	I agree that 1-10% is a small fraction. The mass cutoff should definitely be larger. TODO: Change mass cutoff and hopefully the same scaling with mass remains.
 In the legend, I think "orbit" should be put in the subscript instead of P_orbit
 746: This is just because in the inner disk there are no primordial planetesimals left to build the more massive bodies, right?
+	No, the accretion mode should be qualitatively different, even before the planetesimals run out.
+TODO: Hopefully including more data in the plot and maybe increasing the mass cutoff for 'smooth' accretion will make this more obvious.
 750: use /citep[see][]{Kokubo}
+	Fixed
 756: I agree that the large bodies must've originated due to mergers with other embryos, but this is not really an explanation for why the feeding zone size doesn't match the theoretical value, no?
@@
 See my major comments
+	TODO: Include more sims in top panel of figure 11?
 
@@
 802: As I argued above, I'm unconvinced in this clear-cut boundary at 60 days. Maybe the authors could put a quantitative uncertainty to this number?
+	TODO
 816: I'm not following where the factor of 15 comes from. Maybe the authors can write down the explicit proportionality used to obtain this value.
+	For a fixed value of alpha, equation 4 gives a ~ r_pl ~ f. Therefore, P_orbit ~ f^{-3/2}.  This is now clarified in the text.
 821: How is this expected to change with f?
+	See previous comment.
 843: Maybe add reference to such short period planets.
+	TODO: What to reference here? Magnetic truncation radius?
 868: I'm not sure I fully follow this statement of the collision model. See my major comment above.
-
+	We have added a note here discussing the outcome of a potentially destructive collision model.
+As we mention in response to major comment #3, the local value of alpha is independent of particle size.
+So long as the solid mass is not ground down and removed from the system (radial drift, dust blowout, PR drag), the non-oligarchic growth mode should persist.
 Figure 12:
 Add a description of what green and orange means to the plot.
-
+	TODO
 901: Are the populations really indistinguishable? The authors could perform for example a Kolmogorov-Smirnov test to underline this statement. If not, I would suggest softening this statement.
+	KS value is large because of the extra planetesimals in the bounce-merge sim. TODO: Should I exclude these?
 912: The authors perform this collisional model test very close-in where residual planetesimal populations are suppressed anyways.
 Maybe the authors can comment on what would change (if anything) if this test was performed in the outer parts of the disks.
+	The purpose of testing the collision model at the inner part of the disk was to ensure that the delay in growth would not cause the gravitational scattering timescale to catch back up with the collision timescale (and thus cause oligarchic growth).
+In the outer part of the disk t_scatter >> t_collide, so a more realistic collision model would simply lengthen the timescale for embryo formation (see Wetherill + Stewart 1993, Leinhardt + Richardson 2005).
+We have added this discussion to the beginning of section 6.2 in the text.
 

### 2023-04-11 main.tex
Edits to section 5 and 6

@@
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/minor_frac.png}
+    \includegraphics[width=0.5\textwidth]{figures/minor_frac_100m.png}
     \caption{For the 100 most massive bodies at the end of the fdHi simulation, the fraction of their total mass attained through mergers with initial mass planetesimals (smooth accretion) as a function of total mass.
@@
 equation \ref{eq:alpha}). Because we chose to artificially inflate the
-collision cross section of the particles in our simulations, the bulk densities
+collision cross section of the particles in our simulations \textbf{by a factor of $f$}, the bulk densities
 of the particles are reduced, and the accretion boundary is shifted outward.
@@
 presented in this paper use a collision cross section enhancement factor of 6, which moves the boundary outward in orbital
-period by a factor of approximately 15. One would therefore expect the accretion boundary to lie near 5 days in orbital period
+period by a factor of approximately 15 \textbf{(For a fixed value of $\alpha$, equation \ref{eq:alpha} gives $a \sim r_{pl} \sim f$ and therefore $P_{orbit} \sim f^{-3/2}$)}.
+One would therefore expect the accretion boundary to lie near 5 days in orbital period
 for 3 g $cm^{-3}$ bodies.
@@
 perfect merger might result in overly efficient growth, particularly in the innermost region of the disk where the encounter 
-velocities are largest. A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic 
+velocities are largest. \textbf{Given that we have just shown that a distinctly non-oligarchic growth mode emerges in the inner disk when the 
+collision timescale is short relative to the gravitational scattering timescale, one might be concerned that a more realistic collision model would act 
+to lengthen the growth timescale enough for this condition to no longer be true. In the outer regions of the disk where oligarchic growth still 
+operates, more realistic collision models have been shown to simply lengthen the timescale for planetary embryos to form 
+\citep{wetherill93, leinhardt05}.} A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic 
 model (see \citet{leinhardt12}). However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of 

### 2023-04-11 makeFig.py

@@ -1,6 +1,7 @@
 #/bin/bash
 import matplotlib.pylab as plt
 import matplotlib as mpl
+from matplotlib import colors
 import numpy as np
 import pandas as pd
 import pynbody as pb
@@ -729,92 +730,110 @@ def plot_surfden_b():
 
 # Extract information about the 'surviving' members from a collision table
 def coll_info(df):
-    mass_mask = df['m1'].values >= df['m2'].values
+	mass_mask = df['m1'].values >= df['m2'].values
     
-    del_x = df['x1x'].values
-    del_x[mass_mask] = df['x2x'].values[mass_mask]
+	del_x = df['x1x'].values
+	del_x[mass_mask] = df['x2x'].values[mass_mask]
+
+	del_y = df['x1y'].values
+	del_y[mass_mask] = df['x2y'].values[mass_mask]
+
+	del_z = df['x1z'].values
+	del_z[mass_mask] = df['x2z'].values[mass_mask]
+
+	del_vx = df['v1x'].values
+	del_vx[mass_mask] = df['v2x'].values[mass_mask]
+
+	del_vy = df['v1y'].values
+	del_vy[mass_mask] = df['v2y'].values[mass_mask]
+
+	del_vz = df['v1z'].values
+	del_vz[mass_mask] = df['v2z'].values[mass_mask]
     
-    del_y = df['x1y'].values
-    del_y[mass_mask] = df['x2y'].values[mass_mask]
+	del_a, del_e, del_inc, del_omega, del_Omega, del_M = ko.cart2kep(del_x, del_y, del_z, del_vx, del_vy, del_vz, 0.08, 1e-20)
+
+	del_r = np.sqrt(del_x**2 + del_y**2, del_z**2)
+
+	del_mass = df['m1'].values
+	del_mass[mass_mask] = df['m2'].values[mass_mask]
     
-    del_z = df['x1z'].values
-    del_z[mass_mask] = df['x2z'].values[mass_mask]
-    
-    del_vx = df['v1x'].values
-    del_vx[mass_mask] = df['v2x'].values[mass_mask]
-    
-    del_vy = df['v1y'].values
-    del_vy[mass_mask] = df['v2y'].values[mass_mask]
-    
-    del_vz = df['v1z'].values
[…]

### 2023-04-14 refereeResponse.txt
Modify table 1

@@
 I don't think the notes are necessary
+	Content from the notes has been added to the column headers in the table.
 I would probably put the planetesimal masses in units of Ceres
-	Where should I put the units?
+	As discussed above, we feel that Ceres masses are too asteroid-belt specific. Instead, we have chosen to display the planetesimal masses in M_earth.
 I think Table 1 and Table 2 could be combined

### 2023-04-14 main.tex
Modify table 1

@@
 
+% tablesgenerator.com
 \begin{table*}
 \caption{Summary of Full Disk Simulations}
-\begin{tabular}{llllllllll} \hline \hline
-Name     & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\delta^{d}$ & $M_{PP}^a$ & $T_{int}^b$ & $T_{int 1}^c$ &  \\ \hline
-fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &  1.00                                                         & 456                              & 16,377  &  \\
-fdHiShallow    & $5 \times 10^{22}$ & 903,687 & 100                                                        & 0.5                              &  1.19                                                        & 456                              & 16,377  &  \\
-fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &  1.08                                                         & 456                              & 16,377 &  \\
-fdLo                & $5 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &  1.77 $\times 10^{-3}$                                  & 3,713                              & 133,651 &  \\ \hline
+\begin{tabular}{lccccccc} \hline \hline
+Simulation Name & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Initial Planetesimal \\ Mass ($M_{\odot}$)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Initial Planetesimal \\ Count\end{tabular}} & A   & d   & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Maximum Protoplanet\\ Mass ($M_{\odot}$)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Integration Time\\ (yr)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Rescaled Integration\\ Time (yr)\end{tabular}} \\
+\hline
+fdHi            & $8.37 \times 10^{-6}$                                                                                & 903,687                                                                                   & 100 & 1.5 & 1.0                                                                                              & 456                                                                                 & 16,377                                                                                       \\
+fdHiSteep       & $8.37 \times 10^{-6}$                                                                                & 903,687                                                                                   & 100 & 2.5 & 1.19                                                                                             & 456                                                                                 & 16,377                                                                                       \\
+fdHiShallow     & $8.37 \times 10^{-6}$                                                                                & 903,687                                                                                   & 100 & 0.5 & 1.08                                                                                             & 456                                                                                 & 16,377                                                                                       \\
+fdLo            & $8.37 \times 10^{-6}$                                                                                & 45,185                                                                                    & 1   & 1.5 & $1.77 \times 10^{-3}$                                                                              & 3,713                                                                               & 133,651                                  \\ \hline
 \end{tabular}
 \label{tab:sim_properties}
-\begin{flushleft}
-\textsc{Note} \\ {$^a$ Maximum protoplanet mass [$M_{earth}$] \\
-		       $^b$ Integration time [yr] \\
-		       $^c$ Rescaled integration time [yr]} \\
-\end{flushleft}
 \end{table*}

### 2023-04-19 makeFig.py
Update figures

@@ -2,6 +2,7 @@
 import matplotlib.pylab as plt
 import matplotlib as mpl
 from matplotlib import colors
+import matplotlib.cm as cm
 import numpy as np
 import pandas as pd
 import pynbody as pb
@@ -19,6 +20,7 @@ simV = u.AU / simT
 
 from scipy import stats, optimize
 import KeplerOrbit as ko
+from profileTools import e_eq, rho_gas, v_gas, soundspeed, sma
 
 mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
                             'image.cmap': 'viridis'})
@@ -153,7 +155,13 @@ def plot_timescales():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	# r in AU
+	# Values for M stars from Backus + Quinn 2016
+	q = 0.59
+	T0 = 130
+	mu = 2.34 # Hayashi 1981
+
+	C_D = 1
+
 	def surf_den(r):
 		sigma0 = 10 # g/cm^2
 		alpha = 3/2
@@ -162,21 +170,36 @@ def plot_timescales():
 	rhop = 3*u.g/u.cm**3
 	rp = (100*u.km).to(u.cm) # Timescale ratio is independent of size at fixed density
 	mp = 4/3*np.pi*rhop*rp**3
-
 	mstar = (1*u.M_sun).to(u.g)
-	p_bins = (np.logspace(0, 2)*u.d).to(u.s)
-	r_bins = ((p_bins/(2*np.pi))**2*G.cgs*mstar)**(1/3)
 
-	def timescale_ratio(eh):
-		Sigma = surf_den(r_bins.to(u.AU))
+	pvals = np.logspace(0, 2)
+	pvals_s = (pvals*u.d).to(u.s)
+	avals = sma(pvals_s.value, mstar.value)
+	avals_au = (avals*u.cm).to(u.AU).value
 
-		vk = np.sqrt(G.cgs*mstar/r_bins)
-		lnLam = 3
-		omega = 2*np.pi/p_bins
+	omega = 2*np.pi/pvals_s
+	Sigma = surf_den(avals_au*u.AU)
+
+	def calc_eqh(d_g):
+		cs = soundspeed(T0, mu, q, avals_au)
+		vgas = v_gas((mstar).to(u.M_sun).value, avals, cs, q)
+		rhogas = rho_gas(cs, omega, Sigma, d_g)
[…]

### 2023-04-21 refereeResponse.txt
Add definition of hill sphere and hill eccentricity

@@
 Currently, it may suggest that the plotted values for e_h are chosen for a particular reason.
-	Get rid of the legend, explain that e_h values increase from bottom to top.
+	The y axis now represents e_h, and the space on the plot is colored by t_relax/t_coll.
 Also, I think it would be nice to have a reference for what values of e_h are standard for certain disk conditions, i.e.
@@
 Or do we expect e_h = 1 as the standard?
-	Not sure if there is going to be a reference for this. Equilibrium e_h depends on particle mass and gas density. Could try to plot things in terms of that instead. (Maybe fix rho_gas and vary mass?)
+	e_h of order ~10 is pretty standard.
+Following Kokubo 2002, we choose e_h so that the viscous stirring and gas drag timescales are equal.
+The equilibirum value of e_h then depends on the local solid and gas density, and will vary a bit with orbital period.
+In all of the simulations presented in this paper, the equilibrium value for e_h ranges between ~5 and ~50.
+We have overplotted some curves in figure 1 to show the equilibrium value of e_h as a function of orbital period for various values of the dust-gas ratio (assuming a MMSN solid surface density profile).
+TODO: Center white on colormap at 1
 Also, I recommend adjusting the x-limits of the plot to correspond to the limits of the orbital period.
@@
 9 where the smooth accretion fraction is always <10%.
-	TODO: Ask tom about this?
+	In galaxy formation simulations, 'smooth' accretion is considered to be anything at or below the resolution limit.
+Your point about the smooth accretion fraction always being small due to this overly strict cutoff is a good one.
+We have reconstructed figure 9 using a mass cutoff of 100 m_0 for major/minor collisions.
 724: Why are only the 100 largest bodies chosen?
@@
 Also, why is the fdHi simulation chosen?
-	The 100 body cutoff was chosen because the analysis script we were using the construct the collision history was rather slow when asked to include all ~10,000 particle in the snapshot.
-This has been optimized and all bodies are now included in figure 9.
+	The 100 body cutoff was chosen because the analysis script we were using the construct the collision history was rather slow when asked to include all ~10,000 particles in the snapshot.
+This has been optimized and all bodies larger than 100 m_0 are now included in figure 9.
 fdHi is chosen to be the 'fiducial' simulation for most of this paper.
@@
 726: I think it could be explicitly stated that smooth accretion = minor mergers.
+	TODO: How to address this?
 730 & onwards: Can the authors quantify this trend?
@@
 Given that I'm skeptical about the 60 day boundary being clear and universal, I think this plot would be stronger if the bodies were colored by orbital period (in addition to the marker style indicating this boundary), and the plot would include a corresponding colorbar.
-	TODO: Get rid of different marker types, apply diverging color map to points, with white centered at 60d
+	The mass cut has been increased (100 m_0), points are now colored by orbital period and the 60d boundary is indicated by a different marker style. 
 The authors state "there is a decreasing correlation between smooth accretion fraction and mass, which suggests that most growth occurs between equal mass bodies".
@@
 I would argue that more massive bodies require more time to build up and during later stages there are simply less primordial planetesimals left so collisions are just more likely to be major mergers.
+	See updated version of figure 9.
+After including data from more simulations and coloring the points by orbital period, it is clear that there is a difference between the smooth accretion fraction of bodies in the inner disk, compared to the outer disk.
+In particular, outer disk bodies all have fairly large mass fractions, which implies that they grow in isolation.
 
@@
 Seems to me that for all bodies, regardless of mass and orbital period, major mergers are significantly more important - that is at least with the author's definition of major and minor merger.
+	I think we need to loosen our definition what a 'planetesimal' is here. 
 	I agree that 1-10% is a small fraction. The mass cutoff should definitely be larger. TODO: Change mass cutoff and hopefully the same scaling with mass remains.

### 2023-04-21 main.tex
Add definition of hill sphere and hill eccentricity

@@
 \end{equation}
+
+\textbf{The dynamical interactions between growing planetesimals can be somewhat simplified by scaling the orbital elements of the bodies by
+a Hill factor}
+
+\begin{equation}\label{eq:hillfac}
+	h = \left(\frac{m_{pl}}{3 M_{*}}\right)^{1/3}, 
+\end{equation}
+
+\textbf{\noindent where $M_{*}$ is the mass of the central star.
+With this definition, $r_{h} = h a$ is the Hill radius of a body, which is the distance where the gravity of the growing planetesimal dominates over the gravity of the star.
+Using equation \ref{eq:hillfac}, the eccentricity, inclination and separation between orbiting bodies can be defined as}
+
+\begin{equation}\label{eq:hillorb}
+	e_{h} = \frac{a e}{h}, \: i_{h} = \frac{a i}{h}, \: b = \frac{a_{2} - a_{1}}{h}.
+\end{equation}
+
+\textbf{Using this formalism, $e_{h}$ and $i_{h}$ describe the radial and vertical excursions of an orbiting body in units of its Hill radius.
+For $e_{h} > 1$, the random velocity dispersion dominates over the shearing motion over a separation of $1 r_{h}$ and encounters can be treated with a two-body formalism.}
+
 Assuming that every collision results in a perfect merger, the growth rate of a planetesimal is given by
@@
 \right>^{1/2}$ \citep{ida93a} and that the eccentricity dispersion is
-constant with orbital period. The eccentricity dispersion is 
-scaled by the Hill factor $\left( m_{pl}/ 3 M_{\star}
-\right)^{1/3}$ such that $e_{h} = 1$ corresponds to the boundary
-between shear and dispersion dominated encounters. The horizontal
+constant with orbital period. The horizontal
 dashed line indicates where $t_{relax} = t_{coll}$. The timescale
@@
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/minor_frac_100m.png}
+    \includegraphics[width=0.5\textwidth]{figures/minor_frac.png}
     \caption{For the 100 most massive bodies at the end of the fdHi simulation, the fraction of their total mass attained through mergers with initial mass planetesimals (smooth accretion) as a function of total mass.

### 2023-04-21 refereeResponse.txt
Referee edits through end of paper

@@
 Why don't the simulations start all with m_max/m = 1?
+	This is because m_max/m = 1 at T=0 and we have time plotted on a log scale.
+We have modified the x window of this figure so that the phase before the first snapshot (where the m_max/m values appear flat) is not visible.
 I'd be interested in also having another panel that shows the evolution of just M_max and <m> (maybe in solid and dashed lines) for the four simulations.
@@
 I think the bottom panel should have a log y-axis
+	Can you elaborate on why the bottom panel needs a log y-axis? The way \tilde_b is defined, a linear scale on this plot translates to a non-linear scale for mass already.
 I would make the color of the dots consistent with Fig.2, where the final outcome is orange
+	Done
 There could be numbers on the contours indicating the density of the initial condition.
@@
 933: I would think the gravitational feedback still operates, just on a timescale that is much longer than the planetesimal accretion timescale that depletes the planetesimal supply.
+	Agreed. We have changed 'does not operate' to 'does not a play a significant role'.
 942: Refer to the section where this is discussed.
+	Done
 946: alpha is already reviewed in the paragraph above
+	The last sentence of the previous paragraph (which mentions alpha) has been removed.
 952: non-negligible is not very precise . Maybe change to while "alpha close to unity"
+	'Non-negligible' has been changed to 'alpha close to unity'
 954: Refer to figure where this is shown. I think Fig.2? Also "the same" is very strong. Maybe "very similar" instead.
+	A reference to figure 2 has been added here. 'The same' has been has been changed to 'very similar'.
 959: Sentence is currently implying that the boundary location is set by the distance to the star which doesn't really work in my opinion.
 Maybe just delete "and therefore the location of the boundary between these accretion modes" as this becomes clear with the subsequent sentence anyways.
+	Done
 965: I think this is too strong a statement. See my previous comments. I think the subsequent sentence "Although [...]" is more appropriate.
+	We have changed 'is independent' to 'does not strongly depend'.
 972: Refer to Fig. 10.
+	TODO: Fig 9 and 10 have been changed
 978: Missing a verb, maybe "differs" ? Also the second part of the sentence "along with [...]" seems odd to me. Maybe rephrase it in two sentences?
+	The first sentence of this paragraph has been split into two parts.
 986: Is there a reference for this? It does not seem obvious to me. See my previous comments.
+	See figure 8 of Leinhardt 2015. The majority of constructive collisions are partial accretion events. A reference has been added to this in the text.
 996: what bulk density? Maybe also rephrase to a less strong statement, e.g., "[...] bulk density, our results suggest that the boundary is located around 5 days in orbital period."
+	Rocky material should have a bulk density of 3 g/cc. This is now specified in the text. The statement about the boundary location has been made less strong as per the referee's suggestion.
 998: I recommend introducing a subsection heading here, for clarity.
+	A subsection heading referencing satellitesimal accretion has been added
 999: Maybe add references of what values for alpha typically were used?
+	There aren't many planetesimal accretion papers that mention \alpha, but Lithwick 2014 is one that specifically assumes that \alpha << 1 for their calculations. We have mentioned that here.
 1000: This sentence is somewhat odd to me.
@@
 1003: delete "small"
+	Done
 1007: Can the authors clarify the relevance of the inclusion of spiral density wave interactions?
+	The point here is that there are some additional dynamical mechanisms at play in these moon formation simulations.
+At least near the Roche limit, this is a distinctly non-local process, unlike the accretion modes that we demonstrated in this paper.
+Some extra clarification has been added to the text here.
 1018: I recommend defining R_U for readers unfamiliar with Ida et al 2020, e.g., by summarizing that Ida et al 2020 considered a circumplanetary disk around Uranus.
+	Since it is only mentioned in one place, we have replaced R_U with 'planetary radii'.

### 2023-04-21 main.tex
Referee edits through end of paper

@@
 
-\begin{figure*}
-\begin{center}
-    \includegraphics[width=\textwidth]{figures/acc_zones.png}
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
     \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown.
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
@@
 accretion models (e.g. \citet{kokubo02, raymond05, raymond06}). In the second mode, the gravitational feedback does not 
-operate, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
-oligarchic growth. The distinction between these modes is determined
-by the ratio between the physical size of the bodies and their 
-Hill radius, which sets the relative contribution of close gravitational encounters and collisions to the dynamical evolution of the 
-disk.
+\textbf{play a significant role}, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
+oligarchic growth.
 
 We have demonstrated the outcome of both accretion modes through a
-simple parameter study using a narrow annulus of planetesimals. The initial planetesimal distribution can be described in terms of two dimensionless 
+simple parameter study using a narrow annulus of planetesimals \textbf{(section \ref{sec:narrow})}. The initial planetesimal distribution can be described in terms of two dimensionless 
 constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) 
 and gravitational ($r_{g}$) radius, respectively. For a fixed planetesimal composition, $\alpha$ scales with the orbital period and 
-$\beta$ scales with the level of dynamical excitation of the disk. We showed that $\alpha \ll 1$ leads to oligarchic growth, while a 
-non-negligible $\alpha$ produces this newly revealed non-oligarchic growth mode. Within this non-oligarchic mode, we find that 
-the resulting masses and eccentricities of the embryos come out the same, regardless of the initial value of $\beta$.
+$\beta$ scales with the level of dynamical excitation of the disk.
+We showed that $\alpha \ll 1$ leads to oligarchic growth, while \textbf{an $\alpha$ close to unity} produces this newly revealed non-oligarchic growth mode \textbf{(see figure \ref{fig:alpha_beta})}.
+Within this non-oligarchic mode, we find that
+the resulting masses and eccentricities of the embryos come out \textbf{very similar}, regardless of the initial value of $\beta$.
 
 So long as the density of the bodies do not significantly change as
-their mass distribution evolves, this ratio, and therefore the
-location of the boundary between these accretion modes is set entirely by the distance
+their mass distribution evolves, this ratio is set entirely by the distance
 from the star. Because both the physical and Hill radii of the bodies
@@
 
-We have verified that the growth boundary location is independent of the
+We have verified that the growth boundary location \textbf{does not strongly depend} of the
 solid surface density distribution by testing the outcome of the planetesimal
@@
 
-Finally, we examined the way in which our simplifying assumption of perfect accretion, along with the enhancement of the 
-collision cross sections to speed up the simulations might alter the emergence and location of the non-oligarchic growth region. 
+\textbf{Finally, we have examined how our assumption of perfect accretion, along with the collision cross section enhancement used, might alter our results. 
+We verified that these modifications, meant to make the simulations less computationally expensive, would still allow for the emergence of this 
+non-oligarchic growth mode.}
 We showed that a much more restrictive collision model, in which only low-velocity collisions produce a merger, still allows for 
 this growth mode to occur at the innermost part of the disk, where encounter speeds are most vigorous. In a real planet-forming 
-disk, partial accretion events should allow growth to happen more quickly than what was seen in this test case, so this growth 
+disk, partial accretion events should allow growth to happen more quickly than what was seen in this test case \textbf{(see figure 8 of \citet{leinhardt15})}, so this growth 
 mode should certainly still occur. We also showed that the collision cross section enhancement moves the accretion boundary 
@@
 and showing that the boundary moves to the predicted location when running a simulation with a slightly smaller inflation factor. 
-For rocky planetesimals with a realistic bulk density, this boundary should lie around 5 days in orbital period.
+For rocky planetesimals with a realistic bulk density \textbf{3 g $cm^{-3}$}, \textbf{our results suggest that} this boundary should lie around 5 days in orbital period.
+
+\subsection{Connections to Satellitesimal Accretion}
 
 To date, there have been no other studies of planetesimal accretion
-with such a large value of $\alpha$. However, a value of $\alpha = 1$
+with such a large value of $\alpha$.
+\textbf{Typically, it is assumed that $\alpha \ll 1$ (e.g.
+\citet{lithwick14}), which is certainly true for material at and beyond the Earth's orbit.} However, a value of $\alpha = 1$
 corresponds to the Roche limit of a three-body system, and so one
 might wonder this high-$\alpha$ accretion mode might be relevant for a
-circumplanetary accretion. There is a small collection of previous works
+circumplanetary accretion. There is a collection of previous works
 which use N-body methods to examine in-situ satellitesimal accretion
 \citep{ida97, richardson00, kokubo00b, ida20}, although some of these simulations involve a complex interaction between spiral 
-density waves formed inside of the Roche limit and the material exterior to it. \citet{ida97} was able to form 1-2
+density waves formed inside of the Roche limit and the material exterior to it\textbf{, making the dynamics driving accretion distinctly non-local, in contrast to what we have presented in this work}.
+\citet{ida97} was able to form 1-2
 large moons just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over. 
@@
 planetesimal accretion mode observed in our simulations. \citet{ida20} modeled a much wider satellitesimal disk, which extends 
-out to about $\alpha \approx 0.05$. Inside to the $\alpha = 0.1$ accretion boundary (which lies near $15 R_{U}$ in figure 1 of 
+out to about $\alpha \approx 0.05$. Inside to the $\alpha = 0.1$ accretion boundary (which lies near 15 \textbf{planetary radii} in figure 1 of 
 \citet{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary. In addition, a 

### 2023-04-21 makeFig.py
Updates to figures

@@ -32,6 +32,8 @@ clobber = True
 fmt = 'png'
 s = 0.005
 lw = 4
+blue = '#1f77b4'
+orange = '#ff7f0e'
 refmass = (1*u.M_earth).to(u.M_sun).value
 
 num_bins = 50
@@ -251,11 +253,10 @@ def plot_alpha_beta():
 		pl = ko.orb_params(snap, isHelio=True, mCentral=mcen)
 		ax.scatter(pl0['a'], pl0['e'], s=pl0['mass']/np.max(pl['mass'])*500)
 		ax.scatter(pl['a'], pl['e'], s=pl['mass']/np.max(pl['mass'])*500, edgecolor='black')
-		ax.text(0.85, 0.95, title, transform=ax.transAxes, ha='center', va='center')
+		ax.text(0.7, 0.95, title, transform=ax.transAxes, ha='center', va='center')
 
 	fig, ax = plt.subplots(figsize=(16,12), nrows=2, ncols=2, sharex=True, sharey=True)
 	subplot(ax[0][0], 'ki_fluffy', r'Case a: Large $\alpha$, Small $\beta$')
-	ax[0][0].set_ylabel('Eccentricity')
 	subplot(ax[0][1], 'ki_fluffy_hot', r'Case b: Large $\alpha$, Large $\beta$')
 	subplot(ax[1][0], 'ki', r'Case c: Small $\alpha$, Small $\beta$')
 	ax[1][0].get_xticklabels()[0].set_visible(False)
@@ -280,7 +281,7 @@ def plot_alpha_beta_evo():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	fig, axes = plt.subplots(figsize=(8,12), nrows=2)
+	fig, axes = plt.subplots(figsize=(8,12), nrows=2, sharex=True)
 
 	stepnumber, max_mass, mean_mass = np.loadtxt('data/ki_fluffy.txt')
 	c=next(axes[0]._get_lines.prop_cycler)['color']
@@ -311,6 +312,8 @@ def plot_alpha_beta_evo():
 	axes[1].set_xlabel('Time Steps')
 	axes[0].set_ylabel(r'M / $\langle$ m $\rangle$')
 	axes[1].set_ylabel(r'M, $\langle$ m $\rangle$')
+	axes[0].set_xlim(5e3,8e7)
+	axes[0].set_ylim(0.5, 300)
 	axes[0].legend()
 
 	plt.tight_layout()
[…]

### 2023-04-25 refereeResponse.txt
Update text to reflect changes to figures

@@
 
-	Update figure 6 to show the time evolution in units of the local collision timescale.
-After doing so, the oligarchic curves lie on top of each other, and the inner non-oligarchic ones don't.
-This implies two qualitatively different accretion modes.
+	To address this concern, we have run four more versions of the fdHi, fdHiSteep and fdHiShallow simulations using different random number seeds.
+These are first shown in figure 8 and it is now much more clear that the accretion bounary (defined by the orbital period at which \tilde{b} crosses 2\sqrt{3}) is quite fuzzy and lies somewhere between ~40 and ~70 days, like the referee suggests.
 
-	Update figure 8 to show multiple versions of each simulation. Gives a much clearer estimate of the error bars on the P=60d estimate.
+	We have also modified figure 6 to address the referee's concern that differences in the evolution of the planetesimal surface density as a function of orbital period are simply driven by the local dynamical time.
+We have rescaled the x-axis to be in units of the local accretion timescale (measured at the beginning of the simulation).
+We have also colored the curves by orbital period, rather than applying a hard cut at 60 days.
+Upon doing so, it is now apparent that all of the orbital period bins exterior to ~40 days follow a self-similar trajectory in this space.
+Interior to 40 days, the planetesimal surface density actually depletes slower, relative to the initial local accretion time (why?)
+
+	We have also modified figure 9 to include all 5 iterations of the fdHi, fdHiSteep and fdHiShallow simulations, in addition to removing the hard cut at 60 days and instead coloring the points by final orbital period.
+In all cases, there is a clear qualitative shift in the behavior of accretion interior to ~40 days.
+
+	I think these changes all support the referee's feeling that the accretion mode boundary is not as sharply defined as we had originally suggested.
+Instead, the accretion seems to behave in a fully non-oligarchic way interior to ~40 days, and the transition between non-oligarcic and oligarchic growth seems to happen between ~40-70 days.
+We have softened some of our statements about the accretion mode boundary in the revised version of the paper.
 
@@
 I recommend that this, in my opinion, quite interesting point is discussed in more detail in the manuscript.
+
+	As we discussed above, it is now more clear that the accretion mode transition happens between 40-70 days.
+This corresponds to alpha = 0.2-0.1 and appears to be true for all of the initial solid surface density profiles we have chosen A detailed study of three-body encounters with different values of alpha would help elucidate why alpha ~ 1e-1 is so special, but is definitely beyond the scope of this paper.
+At the very least, the derived scaling relation between alpha and bulk density is useful for predicting how this 40-70 boundary moves after the artifical enhancement to the collision cross sections are removed.
+
 The authors utilize a simplified collision model in which each collision results in a merger.
@@
 They argue that physical collisions are somewhere in-between, and, given that there is little qualitative difference between only-mergers and bounce-merger models, the model outcome should well represent the outcome of physical collisions.
-
-	alpha = 0.1 entirely comes from looking at figure 11.
-It is simply the location in the disk where the feeding zones settle down to 2*sqrt(3).
-alpha < 0.1 roughly corresponds to "alpha << 1".
-Show the b_tilde plots alongsize the alpha curve for the other simulations.
 
@@
 
-	Accretion mode is size independent (only depends on density and orbital period), so the growth for smaller bodies should behave exactly the same.
-No chance of enhanced orbital repulsion or scattering with smaller bodies.
-The other concern to adress would be whether material gets ground down and removed faster than the embryos can grow.
-Need to compare the growth timescale and calculate some sort of mass removal timescale (look into this).
-
-	Mass removal mechanisms: grinding to meter sizes, radial drift
-							 grinding to cm size, pr drag
-							 grinding to micron size, dust blowout
+	Assuming the embryos are able to eventually grow to full size, the size of the fragments being fed shouldn't matter.
+This is because the alpha value of a body is completely independent of its size (r_pl and r_hill both scale with M^1/3).
+Therefore, a 1m body will fill the same fraction of its Hill sphere as a 100km body, so long as they are made of the same material.
+I would expect that this non-oligarchic accretion mode would behave very similarly had we used a collision model that allowed for destructive interactions.
+So long as radial drift does not start removing a significant amount of these smaller bodies, destructive collisions should only act to lengthen the growth timescale.
+TODO: Discusss this in the paper?
+Do we need to worry about inelastic damping here?
 
@@
 
-Where should I put these?
+	Hill radius, along with hill eccentricity and inclination, are now formally defined in section 2.1
+	TODO: Formally introduce isolation mass and b_tilde in section 2.1.
 
@@
 68: Add reference
-	Added a handful of references arguing that the asteroids, KBOs and Oort cloud bodies are leftover planetesimals.
-	See Duncan, Tremaine Quinn papers (particularly 1988 one + references?)
+	Added a handful of references arguing that the asteroids, KBOs and Oort cloud bodies are leftover planetesimals, based on dynamical arguments.
 72: Maybe elaborate on this. How long is the period of quiescence? How does this instability work?
-	We intentionally left this part vague as someone really needs to look into this more! There are three relevant timescales here:
-	1. The timescale for the instability itself (depends on the orbital properties of the embryos, see Chambers 98)
-	2.
-Dynamical friction between protoplanets and planetesimals.
-This will shut off once the planetesimals are either scattered away, or slowly accreted onto the embryos.
-Not sure what the timescale for this would be.
-Note that this shouldn't operate at short period according to this work!
-	3. Tidal eccentricity damping of the embryos due to the gas disk. Should shut off once the gas disk disperses on ~Myr timescales (Beckwith + Sargent 1996).
-	TODO: decide what to add to the text here.
+	Initially, tidal interactions between the gas disk and the protoplanets keep eccentricities and inclinations low.
+As the gas disk dissipates, this damping mechanism goes away and secular resonances drive large-scale oscillations in the orbital parameters of the protoplanets.
+The gas disk dissipates on ~Myr timescales, and the gravitational perturbations operate on 10^5 yr timescales, so the total period of quiescence lasts a few Myr.
+This is now described in the text and a few references have been added.
 88: Add reference maybe.
@@
 238: The eccentricity dispersion e_h is never defined anywhere. It is unclear to me what scaling e_h with the Hill-factor means physically.
-	e_h can be thought of as the radial excursion of the body's orbit in units of its Hill radius.
-For e_h > 1, the random velocity of a body dominates over the velocity difference due to the shearing of the disk (over a separation of 1 r_h) and encounters between bodies can be treated with a two-body formalism.
-We have decided to remove any mention of e_h here, and instead save this definition for section 4 (TODO: define in section 4), where it is next mentioned.
+	e_h and i_h are now defined immediately after equation 1.
 Figure .1:
@@
 	The y axis now represents e_h, and the space on the plot is colored by t_relax/t_coll.
+Rather than choosing arbitrary values of e_h, we have overplotted curves which represent the equilibirum eccentricity (setting the viscous stirring timescale equal to the gas drag timescale) of solids as a function of orbital period.
+Here, the free parameter plotted is now the dust to gas ratio, which shortens the viscous stirring time as it is increased.
 Also, I think it would be nice to have a reference for what values of e_h are standard for certain disk conditions, i.e.
@@
 Or do we expect e_h = 1 as the standard?
-	e_h of order ~10 is pretty standard.
-Following Kokubo 2002, we choose e_h so that the viscous stirring and gas drag timescales are equal.
-The equilibirum value of e_h then depends on the local solid and gas density, and will vary a bit with orbital period.
-In all of the simulations presented in this paper, the equilibrium value for e_h ranges between ~5 and ~50.
-We have overplotted some curves in figure 1 to show the equilibrium value of e_h as a function of orbital period for various values of the dust-gas ratio (assuming a MMSN solid surface density profile).
-TODO: Center white on colormap at 1
+	See previous comment
 Also, I recommend adjusting the x-limits of the plot to correspond to the limits of the orbital period.
@@
 254: but this doesn't have to be the case at all orbital periods, right? Given Fig.1 it seems clear that outside of 1AU, and especially for the Kuiper Belt this condition seems to be fulfilled.
-	Exactly! That's the point we're getting at here. (TODO: do I need to clarify something in the paper here?)
+	Exactly!
+Unless you are modeling planetesimal accretion at orbital periods shorter than that of Mercury, t_coll >> t_relax is going to be true.
+Please let us know if something needs to be clarified here.
 263: Again, I think the concept of Hill radius and tidal stability needs to be formally introduced earlier.
-	TODO: Introduce this formally earlier
+	These concepts are now formally discussed in section 2.1
 273: Wouldn't these bodies then be tidally disrupted, and therefore not exist?
@@
 I understand that the scaling of alpha predicts alpha >1 at some radius (which I would explicitly mention), but this just implies that inside this radius, bodies must have greater densities to not be disrupted.
-	The distance at which alpha = 1 (a_alpha) and the Roche (a_roche) limit are similar, but not identical.
-For a rigid spherical body, a_roche ~ 0.88 a_alpha.
-Applying the hydrostatic correction, a_roche ~ 0.6 a_alpha.
-This is important, because it implies that the new growth mode presented in this paper should be relevant for ring systems!
-We will add a note of this in the text.
-I think some of the confusion comes from the fact that the Roche limit and the Hill sphere size are not derived using the same formalism.
+	Yes, the rigid body Roche limit corresponds to alpha = 1, although applying the hydrostatic correction moves a_roche inwards by about 60%.
+This is interesting because this accretion mode could potentially be relevant for ring systems!
+(TODO: Is this worth discussing in the text?)
 289: gravitational radius: is this physically motivated? Maybe reference
@@
 A reference planetesimal size that shows what mass a circle has
-	Might skip this, want to keep everything in dimensionless units here TODO: decide
+	Added
 Horizontal lines in each panel showing where e_h is
@@
 Maybe consider having beta value as a column label and alpha value as a row label. I would also explicitly state the values for alpha.
-
+	Added
 I would also probably label the four panels / cases a,b,c,d and then refer as such in the text body
@@
 402: I don't really understand why small alpha small beta leads to so many dynamically hot bodies, both planetesimals and protoplanets. Maybe the authors can elaborate.
-	When alpha and beta are both small, the gravitational stirring timescale is very short and the disk quickly heats up.
-Because the stirring timescale goes as v^{1/4} (TODO: reference), the scattering slows down as the disk gets hotter.
-So runaway growth doesn't really kick in until after the eccentricities have grown enough that stirring slows down.
-I think this is why the initial choice of beta doesn't really seem to affect the final dynamical state of the disk in figure 2.
-This is also why the initial choice of e_h isn't very consistent across planetesimal accretion studies (cite some examples).
-TODO: Let's add another paragraph discussing this here.
+	TODO: Is this not talking about small alpha, large beta as well? They look about the same to me
+	The small alpha disks ends up the hottest because of two effects:
+		1. Less collisions overall, so less inelastic damping to remove energy
+		2. Physically smaller bodies, so close encounters are more likely to result in gravitational
+		scattering, which converts the overall shearing motion of the disk into random motion
 
@@
 I would express the mass in units of e.g. Ceres
-	Todo: Push back on this? Use dimensionless units for this section.
+	Todo: Lets use Earth units. Ceres is too asteroid-belt specific.
 406: I'm not sure about "significantly" larger. The biggest body in large alpha, small beta is about a factor 3 more massive than in small alpha, small beta. This is only a factor of 1.4 in size.
@@
 418: I would specifically state that for the large alpha cases runaway growth only occurs at the start, to avoid initial confusion that the slope turns around when the planetesimal supply is depleted.
+
 435: Is this true? I was under the impression that the residual planetesimal population remains? I think this does not seem consistent with the rest of the work...?
-	TODO: Change the wording here. Maybe this isnt true. Would the growth mode simply 'flatten' out here?
+	'Depleted' is maybe not the right phrase to use here.
+Through a combination of depletion and scattering onto high eccentricity orbits (in which gravitational focusing is almost completely supressed), the planetesimal accretion timescale should eventually become longer than the age of the system, so the rest of the population is effectively frozen out.
+This is now explained in the text.
 446: What exactly does alpha being non-negligible mean?
@@
 	This is a good point, and I'm not sure if we have a definitive answer.
-Inspecting figure 11, theh transition seems to occur near alpha ~ 0.1.
 I think the best thing to do here is to state the converse: for alpha << 1, most encounters result in scattering and you get oligarchic growth.
@@
 843: Maybe add reference to such short period planets.
-	TODO: What to reference here? Magnetic truncation radius?
+	A reference has been added to Mulders 2018.
 868: I'm not sure I fully follow this statement of the collision model. See my major comment above.

### 2023-04-25 main.tex
Update text to reflect changes to figures

@@
 dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals. Lines of evidence suggest 
-that the asteroid belt \textbf{\citep{bottke05, morbidelli09}}, Kuiper belt \textbf{\citep{levison08, sheppard10}} and the Oort cloud \textbf{\citep{levison11}} are largely composed of the leftovers of this stage of planet formation.
-
-After a long period of quiescence, the collection of embryos and
-remaining planetesimals undergo a large-scale instability
-\citep{chambers98}.
+that the asteroid belt \textbf{\citep{bottke05, morbidelli09}}, Kuiper belt \textbf{\citep{duncan89, levison08, sheppard10}} and the Oort cloud \textbf{\citep{levison11}} are largely composed of the leftovers of this stage of planet formation.
+
+\textbf{Tidal interactions between protoplanets and the gaseous disk keep eccentricities and inclinations low until the gas disk dissipates (typically over the course of a few Myr \citep{mamajek09}).
+Eventually, gravitational perturbations eventually trigger an instability which drives bodies onto crossing orbits.
+This instability occurs on a timescale of $\sim 10^{5}$ years and involves large scale oscillations of the eccentricity and inclinations of the bodies as they strongly interact through secular resonances \citep{chambers98}.}
 As a consequence of the instability, the oligarchics are no longer
@@
       internal density of 3 g cm$^{-3}$ and an eccentricity dispersion
-      characterized by $e_h$. Only in regions where $t_{relax} \ll t_{coll}$ can 
+      characterized by $e_h$. \textbf{The dashed curves show the equilibirum eccentricity ($t_{vs} = t_{gas}$) for various values of the gas to dust ratio $\epsilon$.}
+      Only in regions where $t_{relax} \gg t_{coll}$ can 
       the velocity distribution respond to changes in the mass of the bodies such
@@
 \beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
-\textbf{This is the largest value of $\beta$ that permits a particle at 1 AU to still an apocenter and pericenter distance that lies within the boundaries of the disk.}
+\textbf{This is the largest value of $\beta$ that permits a particle at 1 AU to still have an apocenter and pericenter distance that lies within the boundaries of the disk.}
 
@@
 driven by an increase in the average mass as the planetesimal population
-becomes depleted. One should expect that the same thing will eventually
-occur for small $\alpha$, although many more timesteps are required to
-begin to run out of planetesimals.
+becomes depleted. \textbf{For small $\alpha$, one would expect that planetesimal accretion should also eventually come to a halt as
+the growth timescale lengthens due to the planetesimal surface density decreasing and the residual bodies being scattered onto high
+eccentricity orbits with negligible gravitational focusing factors. Many more timesteps, however, would be required to reach this point.}
 
@@
     \caption{Feeding zone width (see equation \ref{eq:iso}) required to produce the final masses for the protoplanets from the 
-    simulations listed in table \ref{tab:sim_properties}. The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$. Despite the 
+    simulations listed in table \ref{tab:sim_properties}.
+\textbf{For the fdHi, fdHiSteep and fdHiShallow simulations, we have included the results from five separate iterations of the simulations, each using a different random number seed.} The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$.
+Despite the
     vastly different initial solid surface density profiles, the feeding zone width reaches the circular orbit value around $\sim$ 60 
@@
 
-A qualitative shift in the protoplanet and planetesimal distribution is visible at $\sim$ 60 days. Interior to this location, there are 
+A qualitative shift in the protoplanet and planetesimal distribution is visible \textbf{inside of} $\sim$ 60 days. Interior to this location, there are 
 very few remaining planetesimals and the embryos formed have larger feeding zones. Exterior to the boundary, the residual 
@@
 
-To ensure that the boundary seen near 60 days in orbital period is not
+To ensure that the boundary seen \textbf{around} 60 days in orbital period is not
 simply a transient product of the inside-out growth throughout the
@@
 $\sigma/\Sigma$ is plotted as a function of time in 10 orbital period
-bins, each with a width of 10 days.
-Bins interior to 60 days are shown by a dashed line, while those exterior are shown as a solid line. In all radial bins, the 
-planetesimal surface density is approaching an asymptotic value. In the inner disk, this value asymptotes to zero as the 
+bins, each with a width of 10 days. \textbf{To determine whether the evolution of the planetesimal surface density behaves self-similarly across the disk,
+we normalize the time values in each bin by the local accretion timescale at the beginning of the simulation, which is given by}
+
+\begin{equation}\ref{eq:acctime}
+	t_{acc} = \frac{1}{n \sigma_0 v} = (calculate the rest of this on paper to simplify).
+\end{equation}
+
+\textbf{The color of the curves indicate the orbital period bin which is being measured. From about 40 to 100 days in orbital period, the planetesimal surface density 
+follows a similar trajectory as accretion proceeds. Interior to about 40 days, however, the rate at which $\sigma$ decays actually beings to decrease for the shortest 
+period orbits. In other words, growth is actually fueled less vigorously by planetesimals in this region. In the next section, the accretion history of bodies in this region is 
+qualitatively different than the outer disk as well.} In the inner disk, this value asymptotes to zero as the 
 planetesimal population entirely depletes. In the outer disk, dynamical friction between the embryos and planetesimals 
-eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals. It 
+eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals. \textbf{It 
 should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle 
 onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent \textbf{($2\sqrt{3}/10 \simeq 0.3$)} of the planetesimals
-should remain out of reach of the protoplanets.
+should remain out of reach of the protoplanets.}
 
@@
 \tilde{b}$ (see equation \ref{eq:iso}).
+\textbf{To make the trend between $\tilde{b}$ and orbital period more clear, we ran four more versions of the fdHi, fdHiSteep and fdHiShallow simulations using different random number seeds and included these in the figure as well.}
 As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) is the  
 feeding zone width that a body on a circular orbit will have. In all four simulations, the feeding zone width exceeds the 
-minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days. The orbital periods at which this transition 
+minimum value in the inner disk and approaches $2 \sqrt{3}$ \textbf{around $\sim$ 40 to 60 days}. The orbital periods at which this transition 
 occurs are quite similar between simulations, despite the vastly different solid surface density profiles used. This indicates that 
@@
 Here, we define minor events as any collision involving an initial mass 
-planetesimal, while major events consist of a merger between any two larger bodies. In figure \ref{fig:minor_frac}, we choose the 
-100 largest bodies at the end of the fdHi simulation, retrieve all collision events involving these bodies, and plot the total mass 
-fraction attained through minor events as a function of the final mass of the body. The bodies are then subdivided into those that 
-end up with orbital periods greater than 60 days (red x's) and less than 60 days (blue dots). For the bodies in the outer oligarchic 
-growth region, the trend between smooth accretion mass fraction and final mass is nearly flat. Regardless of how much an 
-embryo has grown, mergers with initial mass planetesimals contribute on the order of a few percent to the final mass.
-At shorter orbital periods, however, the contribution from minor mergers can be over an order of magnitude smaller as the 
-embryos mature.
+planetesimal, while major events consist of a merger between any two larger bodies.
+\textbf{In figure \ref{fig:minor_frac}, we retrieve the collision events for all bodies in all five iterations of the fdHi, fdHiSteep and fdHiShallow
+simulations and plot the total mass fraction attained through minor merger events as a function of the final mass of the body. Here, we define a minor merger
+to be any collision involving a planetesimal with $m < 100 m_{0}$. The color of the
+points indicates the final orbital period of the body.
+Beyond $\sim$ 20 to 30 days in orbital period, minor mergers make up a significant fraction of the final mass of a body.
+Interior to this, the smooth accretion fraction drops significantly and the mass contribution to minor mergers can vary by over an order of magnitude.}
 
@@
     \includegraphics[width=0.5\textwidth]{figures/minor_frac.png}
-    \caption{For the 100 most massive bodies at the end of the fdHi simulation, the fraction of their total mass attained through mergers with initial mass planetesimals (smooth accretion) as a function of total mass.
-Bodies that reside beyond the 60 day accretion boundary are shown with red crosses, while bodies interior to the boundary are shown with blue dots.
-For the short period bodies, there is a decreasing correlation between smooth accretion fraction and mass, which suggests that most growth occurs between equal mass bodies.
-For the bodies in the outer disk, this trend is flat, indicating that accretion of planetesimals is important during all phases of evolution.\label{fig:minor_frac}}
+    \caption{\textbf{For all bodies with $m > 100 m_{0}$ at the end of the high surface density simulations}, the fraction of their total mass attained through mergers with initial mass planetesimals (smooth accretion) as a function of total mass.
+\textbf{Colors indicate the orbital periods of the bodies in the final simulation snapshot.
+Bodies interior to $\sim$ 20 to 30 days attain up to an order of magnitude less of their mass through minor merger events, while accretion of planetesimals plays a much more significant role at longer orbital periods.}\label{fig:minor_frac}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
-    \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown.
-The hash marks indicate the present position of the body.
-The histograms indicate the initial locations of the planetesimals that were used to assemble a body.\label{fig:acc_zones}}
+    \caption{\textbf{The relative separation between a body the mean orbital periods of its accretion zone at the end of the fdHi, fdHiSteep and fdHiShallow simulations.
+The marker type and color denotes the simulation used, while the marker sizes indicate the relative masses of bodies.
+In each case, all five iterations of the simulations are plotted simultaneously.}\label{fig:acc_zones}}
 \end{center}
@@
 The variation in smooth accretion fraction with mass for the short period bodies suggests that the planetesimal and embryo populations interact differently than those in the outer disk.
-Exterior to the 60 day accretion mode boundary, the growing embryos continue to accrete planetesimals as they near their final mass.
+Exterior to the accretion mode boundary, the growing embryos continue to accrete planetesimals as they near their final mass.
 Inside the boundary, however, later growth events tend to be dominated by embryo-embryo collisions, and the smooth accretion fraction drops as mergers with planetesimals play a less significant role.
@@
 scattering and orbital repulsion in the inner disk can be seen in
-figure \ref{fig:acc_zones}. Here, we have chosen the 20 most massive
-bodies from the fdHi simulation and arranged them in order of final
-orbital period. On each line, the blue
-hash mark indicates the present orbital period of an embryo and the histogram represents the initial orbital period distribution of the planetesimals used to construct the embryo.
-
-Qualitatively, there are a couple of key differences between the initial planetesimal distributions in the inner ($<$ 60 days) and outer ($>$ 60 days) part of the disk.
-The planetesimal distributions for the outer disk are much more smooth and unimodal, while many of the distributions near the inner disk rather disjoint.
-As discussed when examining figure \ref{fig:minor_frac}, growth events for the inner embryos tend to be sudden and stochastic, often involving mergers with other embryos.
-When an embryo-embryo collision happens, one would expect a second peak to appear in the accretion distribution as the merger tree suddenly obtains a whole other subtree from the embryo that it absorbed.
-In the outer disk, however, the increased importance of embryo-planetesimal mergers means that growth should be smooth, steady and local.
-
-In figure \ref{fig:acc_zones}, evidence of orbital repulsion can be seen for the outermost embryos.
-Beyond 60 days, the final positions of the embryos tend to be offset from the peaks of the accretion distributions.
-This suggests that gravitational scattering events between embryos occurred later on, after accretion had mostly completed.
-Although many of the inner embryos also end up shifted away from the peak of their accretion distribution, their present position is usually associated with another secondary peak.
-This suggests that most of the close encounters between embryos here resulted in a merger event, rather than a scatter.
+figure \ref{fig:acc_zones}.
+\textbf{Here, we measure the initial orbital period distribution of bodies used to construct each embryo and calculate its mean $\left<  P_{acc} \right>$.
+Point sizes indicate the relative final masses of bodies.
+As in the previous figure, we have included data from all five versions of the fdHi, fdHiSteep and fdHiShallow simulations.
+For each body, this quantity is then compared with its final orbital period.
+In this figure, bodies that closely follow the gray dashed line still reside close to their initial feeding zones.
+On the other hand, bodies further from the dashed line must have experienced a strong gravitational scattering event during or after their accretion has completed.
+For all of the high surface density simulations, the accretion zones and present positions of the embryos appear to diverge beyond $\sim$ 20 days in orbital period.}
+
+\textbf{Coupled with the strong decrease in smooth accretion fraction for bodies in this region (seen in figure \ref{fig:minor_frac}), it appears as if the relative importance of collisions and gravitational scattering seems to shift around $\sim$ 20 days.
+For the shortest period bodies, growth events are sudden and stochastic, often involving collisions between bodies of comparable mass.
+For longer period bodies, a significant amount of growth is driven by accretion of smaller planetesimals.
+We postulate that this qualitative difference is driven by the role that embryo-embryo close encounters play in the inner and outer disk.
+In the inner disk, these encounters tend to result in a merger, which drives down the smooth accretion fraction.
+In the outer disk, these encounters tend to result in a scattering event which moves bodies away from their initial feeding zones.
+We find that the accretion zone shapes for the longer period bodies are also much more smooth and unimodal, which suggests that scattering tends to occur after accretion has largely completed.}
 
@@
 oligarchic growth and the highly-efficient short period accretion
-region lies around 60 days in orbital period. As discussed in section \ref{sec:sizeandhill}, the mode of accretion is
+region lies \textbf{between 40 and 70} days in orbital period. As discussed in section \ref{sec:sizeandhill}, the mode of accretion is
 set entirely by the local value of $\alpha$, which scales with both
@@
 period by a factor of approximately 15 \textbf{(For a fixed value of $\alpha$, equation \ref{eq:alpha} gives $a \sim r_{pl} \sim f$ and therefore $P_{orbit} \sim f^{-3/2}$)}.
-One would therefore expect the accretion boundary to lie near 5 days in orbital period
+One would therefore expect the accretion boundary to lie \textbf{between 3 and 5} days in orbital period
 for 3 g $cm^{-3}$ bodies.
@@
 enhancement greatly reduces the size of the non-oligarchic region, it still should be expected to cover a portion of the
-disk where planetesimals might be expected to form for a wide range of $\rho_{pl}$.
+disk where planetesimals might be expected to form \textbf{\citep{mulders18}} for a wide range of $\rho_{pl}$.
 

### 2023-04-25 makeFig.py

@@ -24,6 +24,7 @@ from profileTools import e_eq, rho_gas, v_gas, soundspeed, sma
 
 mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
                             'image.cmap': 'viridis'})
+mpl.rcParams['mathtext.default'] = 'regular'
 
 simT = u.year/(2*np.pi)
 simV = u.AU/simT
@@ -228,15 +229,19 @@ def plot_timescales():
 	axes.set_xscale('log')
 	axes.set_yscale('log')
 
+	#cb = plt.colorbar(cm.ScalarMappable(norm=norm, cmap=cmap), ax=axes)
 	cb = plt.colorbar(cax, ax=axes)
 	cb.set_label(r'$t_{relax}/t_{collision}$')
 	axes.set_xlabel('Orbital Period [d]')
 	axes.set_ylabel(r'$e_{h}$')
 
 	dust_to_gas = [1e-4, 1e-3, 1e-2, 1e-1, 1]
-	for dg in dust_to_gas:
+	labels = [r'$\epsilon = 10^{-4}$', '$\epsilon = 10^{-3}$', '$\epsilon = 10^{-2}$',\
+	'$\epsilon = 10^{-1}$', '$\epsilon = 1$']
+	for idx, dg in enumerate(dust_to_gas):
 		yval = calc_eqh(dg).value
 		axes.plot(pvals, yval, color='white', lw=4, ls='--')
+		axes.text(1.5, yval[0]*0.9, labels[idx], rotation=15, color='white', ha='center', va='center')
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
@@ -251,8 +256,8 @@ def plot_alpha_beta():
 		pl0 = ko.orb_params(snap0, isHelio=True, mCentral=mcen)
 		snap = pb.load('data/'+prefix+'.end')
 		pl = ko.orb_params(snap, isHelio=True, mCentral=mcen)
-		ax.scatter(pl0['a'], pl0['e'], s=pl0['mass']/np.max(pl['mass'])*500)
-		ax.scatter(pl['a'], pl['e'], s=pl['mass']/np.max(pl['mass'])*500, edgecolor='black')
+		ax.scatter(pl0['a'], pl0['e'], s=pl0['mass']/refmass*1e4)
[…]

### 2023-04-27 main.tex
Fix up table, update text for figure 1

@@
 \textbf{The dynamical interactions between growing planetesimals can be somewhat simplified by scaling the orbital elements of the bodies by
-a Hill factor}
+the Hill radius}
 
 \begin{equation}\label{eq:hillfac}
-	h = \left(\frac{m_{pl}}{3 M_{*}}\right)^{1/3}, 
+	r_{h} = \left(\frac{m_{pl}}{3 M_{*}}\right)^{1/3}, 
 \end{equation}
@@
 \textbf{\noindent where $M_{*}$ is the mass of the central star.
-With this definition, $r_{h} = h a$ is the Hill radius of a body, which is the distance where the gravity of the growing planetesimal dominates over the gravity of the star.
+The Hill radius of a body gives distance where the gravity of the growing planetesimal dominates over the gravity of the star.
 Using equation \ref{eq:hillfac}, the eccentricity, inclination and separation between orbiting bodies can be defined as}
@@
 \begin{equation}\label{eq:hillorb}
-	e_{h} = \frac{a e}{h}, \: i_{h} = \frac{a i}{h}, \: b = \frac{a_{2} - a_{1}}{h}.
+	e_{h} = \frac{a e}{r_{h}}, \: i_{h} = \frac{a i}{r_{h}}, \: b = \frac{a_{2} - a_{1}}{r_{h}}.
 \end{equation}
@@
 However, bodies larger than $\sim 100$ km in size are expected to exert a significant gravitational force on each other during encounters and the collision cross section depends on both the size of the bodies and their encounter velocities.
-In this case, $\Gamma = \pi r_{pl}^2 \left( 1 + v_{esc}^2 / v^2 \right)$ \citep{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
+In this case,
+
+\begin{equation}\label{eq:gravfocus}
+	\Gamma = \pi r_{pl}^2 \left( 1 + v_{esc}^2 / v^2 \right)
+\end{equation}
+
+\citep{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
 
@@
 \right>^{1/2}$ \citep{ida93a} and that the eccentricity dispersion is
-constant with orbital period. The horizontal
-dashed line indicates where $t_{relax} = t_{coll}$. The timescale
-criterion for oligarchic growth is only satisfied in regions where the
+constant with orbital period. \textbf{The coloring indicates the ratio between
+$t_{relax}$ and $t_{coll}$. The dashed lines denote the eccentricity at which the
+random encounter velocity (calculated according to equation \ref{eq:ecc_vel}) is
+equal to the mutual escape velocity of the bodies. This is shown for planetesimals
+with an internal density of $3 g cm^{-3}$ ranging from 10 to 200km in size.}
+
+\textbf{A physically realistic value of $e_{h}$ for a population of planetesimals is going to depend on the structure
+of the gaseous disk (which we will address in section \ref{sec:fulldisk}). However, the eccentricity
+dispersion will typically increase over time until $\left< v^{2} \right>^{1/2} = v_{esc}$ and this is
+often used to construct the initial conditions (e.g. \citet{barnes09}). Therefore, the curves in this figure
+should be interpreted as upper limits.}
+
+The timescale criterion for oligarchic growth is only satisfied in regions where the
 disk is sufficiently dynamically cold and the orbital period is
@@
       timescale for a population of equal-mass planetesimals with an
-      internal density of 3 g cm$^{-3}$ and an eccentricity dispersion
-      characterized by $e_h$. \textbf{The dashed curves show the equilibirum eccentricity ($t_{vs} = t_{gas}$) for various values of the gas to dust ratio $\epsilon$.}
-      Only in regions where $t_{relax} \gg t_{coll}$ can 
-      the velocity distribution respond to changes in the mass of the bodies such
-      that oligarchic growth can operate. This condition is no longer satisfied for a dynamically hot disk at sufficiently short orbital periods.\label{fig:timescales}}
+      internal density of 3 g cm$^{-3}$. \textbf{The dashed curves show 
+      the value of $e_{h}$ for which the random velocity dispersion is equal
+      to the escape velocity of the planetesimals for a range of sizes.} Only
+      in regions where $t_{relax} \gg t_{coll}$ can the velocity distribution 
+      respond to changes in the mass of the bodies such that oligarchic 
+      growth can operate. This condition is no longer satisfied for a 
+      dynamically hot disk at sufficiently short orbital periods.\label{fig:timescales}}
 \end{center}
@@
 
-% tablesgenerator.com
 \begin{table*}
+\begin{center}
 \caption{Summary of Full Disk Simulations}
 \begin{tabular}{lccccccc} \hline \hline
-Simulation Name & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Initial Planetesimal \\ Mass ($M_{\odot}$)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Initial Planetesimal \\ Count\end{tabular}} & A   & d   & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Maximum Protoplanet\\ Mass ($M_{\odot}$)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Integration Time\\ (yr)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Rescaled Integration\\ Time (yr)\end{tabular}} \\
-\hline
-fdHi            & $8.37 \times 10^{-6}$                                                                                & 903,687                                                                                   & 100 & 1.5 & 1.0                                                                                              & 456                                                                                 & 16,377                                                                                       \\
+Simulation Name & $m_{pl} [M_{\earth}]$ &$N_{pl}$ & A & d & $M_{PP}  [M_{\earth}]$ & $T_{int} [yr]$ & $T_{int, 1} [yr]$ \\ \hline
+fdHi              & $8.37 \times 10^{-6}$ & 903,687 & 100 & 1.5 & 1.00 & 456 & 16,377  \\
 fdHiSteep    & $8.37 \times 10^{-6}$ & 903,687 & 100 & 2.5 & 1.19 & 456 & 16,377  \\
@@
 fdLo             & $8.37 \times 10^{-6}$ & 45,185  & 1      & 1.5 & $1.77 \times 10^{-3}$ & 3,713 & 133,651 \\ \hline
-\end{tabular}
+\end{tabular}\\
+A summary of the four `full disk' simulations presented in section \ref{sec:fulldisk}.
+$m_{pl}$ and $N_{pl}$ are the initial masses and number of planetesimals.
+$A$ and $d$ is the initial power law normalization and slope of the solids in the disk.
+$M_{PP}$ is the maximum protoplanet mass at the end of the simulation and $T_{int}$ is the amount of time each simulation was integrated.
+$T_{int, 1}$ is the integration time scaled by a factor of $f^{2}$, which accounts for the fact that the accretion timescale has been shortened by the inflated collision cross sections.
 \label{tab:sim_properties}
+\end{center}
+Text goes here
 \end{table*}
@@
 
-\begin{equation}\ref{eq:acctime}
-	t_{acc} = \frac{1}{n \sigma_0 v} = (calculate the rest of this on paper to simplify).
-\end{equation}
+\begin{equation}\label{eq:acctime}
+	t_{acc} = \left( n \Gamma v \right)^{-1} = \left( \frac{\Sigma_{0} \Omega}{2 m_{pl}} \Gamma \right)^{-1},
+\end{equation}
+
+\noindent \textbf{where we have assumed the local number density of particles n is set by the surface density and the local scale height of the disk.
+The effective collision cross section is set by gravitational focusing and is given by equation \ref{eq:gravfocus}.}
 

### 2023-04-27 main.tex
Add explanation of isolation mass in section 2

@@
 \begin{equation}\label{eq:hillorb}
-	e_{h} = \frac{a e}{r_{h}}, \: i_{h} = \frac{a i}{r_{h}}, \: b = \frac{a_{2} - a_{1}}{r_{h}}.
+	e_{h} = \frac{a e}{r_{h}}, \: i_{h} = \frac{a i}{r_{h}}, \: \tilde{b} = \frac{a_{2} - a_{1}}{r_{h}}.
 \end{equation}
@@
 accrete planetesimals at similar rates, independent of mass.
+
+\textbf{Regardless of the mechanism that eventually limits the growth of the planetary embryos, a maximum estimate for the masses produced during this 
+stage of accretion can be obtained using the initial solid surface density profile. A growing protoplanet will eventually accrete material within a distance
+$b = \tilde{b} r_{h}$ of its orbit.
+The total mass of planetesimals within this feeding zone is then $2 \pi a \left(2 \tilde{b} r_{h} \right) \Sigma_{pl}$, where a is the semimajor axis of the growing protoplanet and $\Sigma_{pl}$ is the initial local planetesimal surface density.
+The ``'isolation mass'' of the protoplanet can then be obtained by setting the protoplanet mass equal to the total mass of planetesimals within the feeding zone such that}
+
+\begin{equation}\label{eq:iso_mass1}
+	M_{iso} = 4 \pi a^{2} \tilde{b} \left(\frac{M_{iso}}{3 M_{*}} \right)^{1/3} \Sigma_{pl}.
+\end{equation}
+
+\noindent \textbf{Solving for $M_{iso}$ gives}
+
+\begin{equation}\label{eq:iso}
+	M_{iso} = \left[ \frac{\left( 2 \pi a^2 \Sigma \tilde{b} \right)^3}{3 M_{*}} \right]^{1/2}.
+\end{equation}
+
+\noindent \textbf{For bodies on circular, non-inclined orbits, $\tilde{b} = 2 \sqrt{3}$ is the smallest orbital separation that produces a non-negative
+Jacobi energy and permits a close encounter \citep{nakazawa88}.
+This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet, as oligarchic growth tends to ensure that embryos stay on near-circular orbits as they grow.}
 
@@
 the protoplanet assembly phase last \textbf{(as an example, see figure 1 of \citet{kokubo02)}}. This radial timescale dependence is not typically
-accounted for in planet formation simulations\footnote{Instead, the innermost protoplanets 
-patiently `wait' for this phase of evolution to complete everywhere in the disk} \textbf{(a notable exception being \citet{emsenhuber21a, emsenhuber21b})}, and appears to be an
+accounted for in planet formation simulations \textbf{(a notable exception being \citet{emsenhuber21a, emsenhuber21b})}, and appears to be an
 important component to forming realistic solar system analogs
@@
 final masses of the bodies (in units of feeding zone size) are shown
-as a function of orbital period. The feeding zone size $\tilde{b}$ \textbf{is described in units of the local Hill radius and is} calculated according to \citet{kokubo02}
-\begin{equation}\label{eq:iso}
-	M = \left[ \frac{\left( 2 \pi a^2 \Sigma \tilde{b} \right)^3}{3 M_{*}} \right]^{1/2},
-\end{equation}
-where $M$ is taken to be the final mass of each body.
-\textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and
+as a function of orbital period.
+\textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso2} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and
 that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 
@@
 \tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
-clearly visible. For two bodies on circular, non-inclined orbits,  $\tilde{b} = 2
-\sqrt{3}$ (indicated by the horizontal dashed line) is the smallest orbital separation that produces a non-negative Jacobi energy
-and permits a close encounter (see \citet{naka88}). In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
+clearly visible. \textbf{The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{nazakawa88} is shown by the
+horizontal dashed line.} In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
 to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 

### 2023-04-27 main.tex
Fix broken references

@@
 \noindent \textbf{For bodies on circular, non-inclined orbits, $\tilde{b} = 2 \sqrt{3}$ is the smallest orbital separation that produces a non-negative
-Jacobi energy and permits a close encounter \citep{nakazawa88}.
+Jacobi energy and permits a close encounter \citep{naka88}.
 This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet, as oligarchic growth tends to ensure that embryos stay on near-circular orbits as they grow.}
@@
 equal to the mutual escape velocity of the bodies. This is shown for planetesimals
-with an internal density of $3 g cm^{-3}$ ranging from 10 to 200km in size.}
+with an internal density of 3 g $cm^{-3}$ ranging from 10 to 200 km in size.}
 
@@
 inside-out fashion, with the outermost regions of the disk completing
-the protoplanet assembly phase last \textbf{(as an example, see figure 1 of \citet{kokubo02)}}. This radial timescale dependence is not typically
+the protoplanet assembly phase last \textbf{(as an example, see figure 1 of \citet{kokubo02}}. This radial timescale dependence is not typically
 accounted for in planet formation simulations \textbf{(a notable exception being \citet{emsenhuber21a, emsenhuber21b})}, and appears to be an
@@
 \tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
-clearly visible. \textbf{The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{nazakawa88} is shown by the
+clearly visible. \textbf{The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{naka88} is shown by the
 horizontal dashed line.} In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 

### 2023-04-27 refereeResponse.txt
Cleanup TODOs in referee response

@@
 	To address this concern, we have run four more versions of the fdHi, fdHiSteep and fdHiShallow simulations using different random number seeds.
-These are first shown in figure 8 and it is now much more clear that the accretion bounary (defined by the orbital period at which \tilde{b} crosses 2\sqrt{3}) is quite fuzzy and lies somewhere between ~40 and ~70 days, like the referee suggests.
+These are first shown in figure 8 and it is now much more apparent that the accretion bounary (defined by the orbital period at which \tilde{b} crosses 2\sqrt{3}) is rather fuzzy and lies somewhere between ~40 and ~70 days, like the referee suggests.
 
@@
 We have also colored the curves by orbital period, rather than applying a hard cut at 60 days.
-Upon doing so, it is now apparent that all of the orbital period bins exterior to ~40 days follow a self-similar trajectory in this space.
-Interior to 40 days, the planetesimal surface density actually depletes slower, relative to the initial local accretion time (why?)
+Upon doing so, the orbital period bins exterior to ~40 days follow a self-similar trajectory in this space.
+Interior to 40 days, the planetesimal surface density actually depletes more slowly, relative to the initial local accretion time.
 
-	We have also modified figure 9 to include all 5 iterations of the fdHi, fdHiSteep and fdHiShallow simulations, in addition to removing the hard cut at 60 days and instead coloring the points by final orbital period.
+	We have also modified figure 9 to include all 5 iterations of the fdHi, fdHiSteep and fdHiShallow simulations.
+We have also removed the hard cut at 60 days and instead colored the points by final orbital period of each body.
 In all cases, there is a clear qualitative shift in the behavior of accretion interior to ~40 days.
 
-	I think these changes all support the referee's feeling that the accretion mode boundary is not as sharply defined as we had originally suggested.
+	I think these changes all support the referee's feeling that the accretion mode boundary is not as sharply defined as originally suggested.
 Instead, the accretion seems to behave in a fully non-oligarchic way interior to ~40 days, and the transition between non-oligarcic and oligarchic growth seems to happen between ~40-70 days.
@@
 	As we discussed above, it is now more clear that the accretion mode transition happens between 40-70 days.
-This corresponds to alpha = 0.2-0.1 and appears to be true for all of the initial solid surface density profiles we have chosen A detailed study of three-body encounters with different values of alpha would help elucidate why alpha ~ 1e-1 is so special, but is definitely beyond the scope of this paper.
-At the very least, the derived scaling relation between alpha and bulk density is useful for predicting how this 40-70 boundary moves after the artifical enhancement to the collision cross sections are removed.
+This corresponds to alpha = 0.2-0.1 and appears to be true for all of the initial solid surface density profiles we have chosen.
+A detailed numerical study of three-body encounters using different values of alpha would help elucidate why alpha ~ 1e-1 is so special, but is beyond the scope of this paper.
+At the very least, the derived scaling relation between alpha and bulk density is useful for predicting how this 40-70 day boundary moves after the artifical enhancement to the collision cross sections is removed.
 
@@
 
-	Assuming the embryos are able to eventually grow to full size, the size of the fragments being fed shouldn't matter.
+	Assuming the embryos are able to eventually grow to full size, the size of the fragments shouldn't matter.
 This is because the alpha value of a body is completely independent of its size (r_pl and r_hill both scale with M^1/3).
@@
 
-	Hill radius, along with hill eccentricity and inclination, are now formally defined in section 2.1
-	TODO: Formally introduce isolation mass and b_tilde in section 2.1.
+	Hill radius, e_h, i_h \tilde{b} and isolation mass, are now formally defined in section 2.1.
 
@@
 Specific comments, notes and suggestions.
-
-TODO: First few edits need to be highlighted in manuscript with strikethroughs and bold face.
 
@@
 17-18: something is missing in the second part of this sentence.
-	Missing words at the end of L17: 'investigate *the effects*'
+	Missing words at the end of L17: 'investigate *the effects*' have been added
 
@@
 144 onwards: indices in math upright
-	Fixed
+	TODO: is there an easy, global way to do this? Also need to do this for figure text
 152: Define rms velocity
-	TODO: not sure what the referee wants? Its defined in equation 1?
+	Done
 161: What does "orderly" fashion mean exactly?
@@
 204: I suggest more formally introducing the concept of Hill sphere and hill factor.
-	TODO: Where to put this?
+	This is now done at the beginning of section 2.1.
 209: This sentence seems not necessary.
@@
 	The y axis now represents e_h, and the space on the plot is colored by t_relax/t_coll.
-Rather than choosing arbitrary values of e_h, we have overplotted curves which represent the equilibirum eccentricity (setting the viscous stirring timescale equal to the gas drag timescale) of solids as a function of orbital period.
-Here, the free parameter plotted is now the dust to gas ratio, which shortens the viscous stirring time as it is increased.
 Also, I think it would be nice to have a reference for what values of e_h are standard for certain disk conditions, i.e.
@@
 Or do we expect e_h = 1 as the standard?
-	See previous comment
+	Rather than choosing arbitrary values of e_h, we have overplotted curves with represent the value of e_h for which <v^2>^{1/2} = v_esc as a function of orbital period, for a range of initial planetesimal sizes.
+Because gravitational stirring slows as the random velocity approaches the escape velocity, these curves should be interpreted as rough upper limits.
+A more detailed calculation, which we have saved for section 5, involves balancing viscous stirring with aerodynamic gas drag.
 Also, I recommend adjusting the x-limits of the plot to correspond to the limits of the orbital period.
@@
 This is interesting because this accretion mode could potentially be relevant for ring systems!
-(TODO: Is this worth discussing in the text?)
+TODO: update
 289: gravitational radius: is this physically motivated? Maybe reference
@@
 
+TODO
+
 3. Numerical Methods
@@
 	We've been representing the collision history of a particle with a tree structure.
-Following computer science convention, our tree is flipped upside down, with the original planetesimals at the bottom (hence calling them children).
+Following computer scientist convention, our tree is flipped upside down, with the original planetesimals at the bottom (hence calling them children).
 I agree that calling them 'parents' is probably more intuitive for most readers, however.
@@
 I think this is 0.33 Earth masses, within 0.1 AU of Earth, the feeding zone of Earth.
-	I don't think I like the idea of providing more physical motivation here.
-This was meant to be a study of the effects of varying alpha and beta.
-I think some of these points should be saved for the full disk section.
-Perhaps it would be better if I described everything in dimensionless units?
-TODO
+	As we dicuss below, we have chosen to represent masses in M_earth, which we feel is a more appropriate than Ceres masses.
+Densities are radii before for both chosen values of alpha are now listed.
+The bulk density and radius corresponding to the high-alpha particles is most certainly unphysical, but is meant to mimic how a body would fill its Hill sphere if it were placed closer to the star.
+The initial planetesimal mass is meant to match Kokubo + Ida  1998 for easy comparison, and is definitely unrealistically large in relation to more recent works (e.g Morbidelli 09).
+The total disk mass (in M_earth) is listed as well.
 

### 2023-04-27 main.tex
Cleanup TODOs in referee response

@@
 \usepackage{natbib}
-\usepackage[LGRgreek]{mathastext}
 %\definecolor{orcidlogocol}{HTML}{A6CE39}
@@
 small body populations. However, planetesimal accretion has not yet
-been fully explored in the context of the wide variety of recently discovered extrasolar planetary systems,
+been fully explored in the context of the \textbf{wide variety} of recently discovered extrasolar planetary systems,
 particularly those that host short-period terrestrial planets. In this work, we
@@
 result in collisions, rather than scattering, and the system does not
-develop a bimodal population of dynamically hot planetesimals and
+develop a bimodal population \textbf{of} dynamically hot planetesimals and
 dynamically cold oligarchs, like is seen in previous studies. The highly
@@
 results to assumptions about the initial disk model, and also
-investigate the effects that our simplified collision model has on the emergence
+investigate \textbf{the effects} that our simplified collision model has on the emergence
 of this non-oligarchic growth mode in a planet forming disk.
@@
 moon-sized objects known as planetary embryos. In the earliest stages
-of the planet formation process, beginning from $\mu$m sizes, aerodynamic forces dominate the
+of the planet formation process, \textbf{beginning from $\mu$m sizes,} aerodynamic forces dominate the
 growth and evolution of the solids and statistical models
@@
 For a swarm of planetesimals on randomly oriented orbits, $v$ is typically
-taken to the rms velocity, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \citep{lissauer93}:
+taken to the rms velocity $\left< v^{2} \right>^{1/2}$, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \citep{lissauer93}:
 \begin{equation}\label{eq:ecc_vel}
@@
 \begin{equation}\label{eq:iso}
-	M_{iso} = \left[ \frac{\left( 2 \pi a^2 \Sigma \tilde{b} \right)^3}{3 M_{*}} \right]^{1/2}.
+	M_{iso} = \left[ \frac{\left( 2 \pi a^2 \Sigma_{pl} \tilde{b} \right)^3}{3 M_{*}} \right]^{1/2}.
 \end{equation}
@@
 and $\beta$ are varied individually. 4000 planetesimals with
-individual masses of $5 \times 10^{23}$ g are placed with semimajor
+individual masses of \textbf{$8.37 \times 10^{-5} M_{\earth}$ } are placed with semimajor
 axes drawn \textbf{from a uniform distribution} between 0.95 and 1.05 AU about a 1 $M_{\odot}$
-star. The argument of perihelion, $\omega$, longitude of ascending node,
+star. \textbf{In total, the disk contains $\sim$ 0.33 $M_{\earth}$ of material.} The argument of perihelion, $\omega$, longitude of ascending node,
 $\Omega$, and mean anomaly, M, for each body is drawn from a uniform
@@
 cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 
-10^{-3}$. These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth. 
+10^{-3}$. \textbf{This corresponds to a radius of 341 km} These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth. 
 To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by 
-a factor of $\sim$ 7100, which produces $\alpha = 1$.
-\textbf{In this case, a planetesimal completely fills its Hill sphere, and one should expect no strong gravitational scattering to occur.} To vary $\beta$, the eccentricity dispersion is increased.
-For the high-$
+a factor of $\sim$ 7100, which produces $\alpha = 1$. \textbf{This corresponds to a bulk density of $4.2 \times 10^{-4}$ g cm$^{-3}$ and a radius of 6,500 km. 
+Although this is most certainly unphysical, the purpose of this modification is to have a planetesimal completely fills its Hill sphere so that no strong 
+gravitational scattering should occur.} To vary $\beta$, the eccentricity dispersion is increased. For the high-$
 \beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
@@
 
-\noindent \textbf{where we have assumed the local number density of particles n is set by the surface density and the local scale height of the disk.
+\noindent \textbf{where we have assumed the local number density of particles n is set by the surface density and the local scale height of the disk (see section \ref{sec:theory}).
 The effective collision cross section is set by gravitational focusing and is given by equation \ref{eq:gravfocus}.}

### 2023-04-28 refereeResponse.txt
Almost finished addressing referee comments

@@
 I appreciate the authors' work and look forward to seeing the progress on the manuscript.
+
+TODOs:
+	Dont italicze math subscripts (do this for figures too)
+	Discussion of Roche limit at end of section 2
+	Centering of note text under table 1
+	Centering of white in figure 1 colorbar (colormap on plot is correctly scaled)
+	Add a note explaing why no fdLo on the collision plots
+	Explanation of \tilde{b} in section 5 ok?
 
@@
 Horizontal lines in each panel showing where e_h is
-	Might skip this, depending on whether I remove the e_h lines from figure 1. TODO
+	Alongside the text describing this figure, we have added a note describing where e_h = 1 (the boundary between shear and dispersion dominated encounters) and <v^2>^{1/2} = v_esc lies in eccentricity space.
+These should be interpreted as rough lower and upper limits for reasonable values of the planetesimal eccentrities.
 Maybe consider having beta value as a column label and alpha value as a row label. I would also explicitly state the values for alpha.
@@
 Also, isn't this also not just very expected since alpha exactly quantifies the relative importance of scattering vs accretion?
-	I'm assuming this is referring to the statement that begins with 'The lack of high eccentricity planetesimals...'.
-I think you must be misinterpreting what we said in the text here, because it sounds like we are both making the same point.
-When we turn up alpha, the high eccentricity planetesimals dissapear.
-This is expected, because large alpha makes gravitational scattering difficult, so those bodies that undergo close encounters end up being accreted by the protoplanets, rather than getting kicked onto high eccentricity orbits.
-If there is something that needs to be clarified in the text, please let us know!
+	The point we were trying to make was this: Had scattering been more important than accretion, not only would there still be planetesimals left over, but they would have been moved to higher eccentricity orbits.
+Although in the case of small alpha, large beta, it appears as if the embryos instead cool off relative to the planetesimals.
+We have reworded this to say 'the lack of high eccentricity planetesimals, relative to the protoplanets'.
 
 394: small alpha, large beta doesn't look dynamically cool to me.
-	This should have been referring to the dynamical state of the growing protoplanets, relative to the initial eccentricities of the planetesimals. This has now been clarified in the text.
+	Related to the last point, this is referring to the dynamical state of the protoplanets, relative to the initial planetesimals. This has now been clarified in the text.
 400: Small alpha large beta does not look dynamically cooler than large alpha large beta to me. In fact, the opposite.
-	You are correct! This is a mistake in the text (replaced 'latter' with 'former').
+	This is a mistake in the text (replaced 'latter' with 'former').
 402: I don't really understand why small alpha small beta leads to so many dynamically hot bodies, both planetesimals and protoplanets. Maybe the authors can elaborate.
-	TODO: Is this not talking about small alpha, large beta as well? They look about the same to me
+	Is this specifically referring to small alpha, small beta (and not small alpha, large beta)? The final eccentricities of the planetesimals and protoplanets look about the same to me.
 	The small alpha disks ends up the hottest because of two effects:
 		1. Less collisions overall, so less inelastic damping to remove energy
-		2. Physically smaller bodies, so close encounters are more likely to result in gravitational
-		scattering, which converts the overall shearing motion of the disk into random motion
+		2. Close encounters are more likely to result in a scattering event,
+		which converts the overall shearing motion of the disk into random motion
 
@@
 I would express the mass in units of e.g. Ceres
-	Todo: Lets use Earth units. Ceres is too asteroid-belt specific.
+	We feel that Ceres masses are a little too asteroid belt-specific. We have instead chosen to describe the masses in M_earth.
 406: I'm not sure about "significantly" larger. The biggest body in large alpha, small beta is about a factor 3 more massive than in small alpha, small beta. This is only a factor of 1.4 in size.
@@
 That would also underscore that the turnover is driven by an increase in <m> rather than m_max.
-	We have now added a second panel to figure 4 which shows the evolution of these quantities separately. Todo: Units? Why does the max mass decrease for case a?
+	We have now added a second panel to figure 4 which shows the evolution of these quantities separately.
+It is now clear that the turnover of the blue and orange curves on the original plot are driven by a continued increase in <m>.
+This is now stated in the text as well.
 
 418: I would specifically state that for the large alpha cases runaway growth only occurs at the start, to avoid initial confusion that the slope turns around when the planetesimal supply is depleted.
+	This is now stated in the text.
 
@@
 I don't think the notes are necessary
-	Content from the notes has been added to the column headers in the table.
+	We could use some clarification here. Is this because the variables in table 1 are already defined elsewhere in the text? Or should we incorporate the information from the notes in some other way?
 I would probably put the planetesimal masses in units of Ceres
@@
 499: Maybe elaborate on why this equilibrium is physical? Are there other works which use the same balance to inform initial conditions?
-	t_vs = t_gas is more of an upper limit on the eccentricity, although this is the same technique that Kokubo + Ida 1998 use to set up their initial conditions.
+	t_vs = t_gas is more of an upper limit on the eccentricity, although this is the same technique that Kokubo 2002 uses to set up the initial conditions.
 It's certainly possible that the disk could have started out dynamically colder, although as we showed in figure 2, this doesn't seem to affect the resulting protoplanets.
-We have added a short discussion of these points to the text.
+We have added a short discussion about this to the text.
 504: missing respectively. And semi-major axes.
@@
 I think the authors could be over-estimating the gas density by up to a factor of a 100, which means the stopping time would be a factor of 100 longer.
-	TODO: Fix
+	A d/g ratio of 1/240 is the value inferred for the inner solar system using the original MMSN analysis in Hayashi 1981.
+However, we agree that there is a rather large range of possibilities for the actual gas surface density, given that there are no direct measurements of Sigma_gas for the inner regions of a planet-forming disk (and it isn't clear exactly when the planet formation process should start).
+A variation in the gas surface density of by factor of 100 could either make gas drag entirely unimportant, or act to completely remove solids from the inner disk, in which case we wouldn't be able to form any protoplanets.
+
+	As is done by Hansen + Murray 2012, we will assume that the gas profile follows something resembling the MMSN and the various solid surface density profiles we test broadly account for the different mechanisms that might act to deliver enough solid material to the inner disk.
+
+	These points are now discussed at the end of section 5.1
 516: I suggest using another symbol for the temperature power law, since Q is associated with the Toomre value of the disk, for example q. Also, this equation should read T(r) = T_0(r/1AU)^-q, right?
@@
 521: Where is that equation coming from? Maybe add reference.
-	This is equation 4.30 from Phil Armitage's 'Astrophysics of Planet Formation'. A reference has been added to the text.
+	This is equation 4.30 from 'Astrophysics of Planet Formation' by Phil Armitage. A reference has been added to the text.
 
@@
 While I'm inclined to believe that the error is only marginal, I think having some sort of test (or a reference to one) would make the results more steadfast.
-	I'm fairly certain that we are the first ones to try this.
-I've added an appendix that compares this timestepping scheme against a fixed timestep case.
-There appear to be no meaningful differences.
-TODO: Show mass distribution as differential or cumulative?
+	I'm fairly certain that we are the first ones to try this. I've added an appendix that compares this timestepping scheme against a fixed timestep case. There appear to be no meaningful differences.
 
@@
 What is the rescaled integration time?
-	TODO: Not sure where to explain table columns now?
+	Because we inflated the collision cross sections by a factor of 6, the growth timescale was shortened by a factor of 36.
+The rescaled integration time is the actual integration time multiplied by this factor.
+This is explained in the note underneath the table.
 
@@
 I think the bottom panel should have a log y-axis
-	Can you elaborate on why the bottom panel needs a log y-axis? The way \tilde_b is defined, a linear scale on this plot translates to a non-linear scale for mass already.
+	TODO: I dont think this is necessary? If I make this change, do I need to do the same thing for figure 8? The way \tilde_b is defined we are already showing mass in a non-linear way.
 I would make the color of the dots consistent with Fig.2, where the final outcome is orange
@@
 See our updated version of figure 6.
-The time is now shown in units of the local accretion timescale, and it is now apparent that the planetesimal surface density curves all follow the same trajectory exterior of 60d.
+The time is now shown in units of the local accretion timescale, and it is now apparent that the planetesimal surface density curves all follow the same trajectory outside of about 40d.
+In a rather counter-intuitive fashion, planetesimals actually appear to deplete more slowly (relative to the initial planetesimal-planetesimal accretion time) at short period.
+The lack of gravitational scattering in the inner disk means that embryos do not exhibit any 'mass preference' in who they collide with.
 Figure 6:
@@
 	See our response to the previous concern, along with our response to major comment #1.
-	TODO: Update text to reflect changes to figure 6.
-	TODO: Run fdhi for a thousand steps at higher output cadence, so the innermost curve starts sooner
 665: I struggle to see that there is a significant qualitative difference in the behavior in the lines just inside and just outside the boundary of 60 orbits.
@@
 Seems to me that for all bodies, regardless of mass and orbital period, major mergers are significantly more important - that is at least with the author's definition of major and minor merger.
-	I think we need to loosen our definition what a 'planetesimal' is here. 
-	I agree that 1-10% is a small fraction. The mass cutoff should definitely be larger. TODO: Change mass cutoff and hopefully the same scaling with mass remains.
+	This statement makes a little more sense after broadening or definition of 'minor mergers' to include m < 100 m_0.
 In the legend, I think "orbit" should be put in the subscript instead of P_orbit
 746: This is just because in the inner disk there are no primordial planetesimals left to build the more massive bodies, right?
-	No, the accretion mode should be qualitatively different, even before the planetesimals run out.
-TODO: Hopefully including more data in the plot and maybe increasing the mass cutoff for 'smooth' accretion will make this more obvious.
+	After coloring the points by orbital period, its clear that this isn't the case.
+In the inner disk, there is a huge amount of variation in the smooth accretion fraction for a given mass.
+This suggests that inner disk protoplanets collide with any and everything, while the outer disk protoplanets tend to avoid each other.
+We have altered the wording of this sentence to reflect this.
 750: use /citep[see][]{Kokubo}
@@
 802: As I argued above, I'm unconvinced in this clear-cut boundary at 60 days. Maybe the authors could put a quantitative uncertainty to this number?
-	TODO
+	The additional simulations included in figure 8, along with the difference in accretion characteristics near ~30-40d (see figures 9 and 10) suggests that the boundary lies somewhere between 40 and 70 days.
+This is now stated here in the text.
 816: I'm not following where the factor of 15 comes from. Maybe the authors can write down the explicit proportionality used to obtain this value.
@@
 Add a description of what green and orange means to the plot.
-	TODO
+	A legend depicting the colors has been added to the top panel of the plot.
 901: Are the populations really indistinguishable? The authors could perform for example a Kolmogorov-Smirnov test to underline this statement. If not, I would suggest softening this statement.
-	KS value is large because of the extra planetesimals in the bounce-merge sim. TODO: Should I exclude these?
+	A KS test yields a p-value of 1e-5 for these distributions, although excluding the handful of initial planetesimals yields a p-value of 0.1.
+We therefore conclude that the distribution of protoplanets are indistinguishable, although the bounce-merge model does produce a small amount of residual planetesimals.
+This is now stated in the text.
 912: The authors perform this collisional model test very close-in where residual planetesimal populations are suppressed anyways.
@@
 972: Refer to Fig. 10.
-	TODO: Fig 9 and 10 have been changed
+	A reference has been added to figures 9 and 10.
 978: Missing a verb, maybe "differs" ? Also the second part of the sentence "along with [...]" seems odd to me. Maybe rephrase it in two sentences?

### 2023-04-28 main.tex
Almost finished addressing referee comments

@@
 In the ``fiducial'' case, we give the bodies a bulk density of 3 g
-cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 
-10^{-3}$. \textbf{This corresponds to a radius of 341 km} These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth. 
+cm$^{-3}$ \textbf{(for a radius of 341 km)}, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
+These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth.
 To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by 
@@
 \beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
-\textbf{This is the largest value of $\beta$ that permits a particle at 1 AU to still have an apocenter and pericenter distance that lies within the boundaries of the disk.}
-
-\textbf{This choice of $\beta$ places the system firmly in the $v > v_{esc}$ regime, while still allowing growth to occur in a reasonable number of timesteps.}
+\textbf{This is the largest value of $\beta$ that permits a particle at 1 AU to still have an apocenter and pericenter distance that lies within the boundaries of the disk.
+This choice of $\beta$ places the system firmly in the $v > v_{esc}$ regime, while still allowing growth to occur in a reasonable number of timesteps.}
 
@@
 $\alpha$ (case c, d)} does a residual population of dynamically hot planetesimals
-develop. The lack of high eccentricity planetesimals in the large
-$\alpha$ \textbf{(case a, b) simulation} suggests that most encounters result in accretion
+develop. The lack of high eccentricity planetesimals \textbf{(relative to the protoplanets)} in the large
+$\alpha$ \textbf{(case a, b) simulations} suggests that most encounters result in accretion
 rather than scattering. \textbf{For} large $\beta$ \textbf{(case b, d)}, the \textbf{growing} protoplanets
@@
 
-In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}.
-In addition to leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce \textbf{embryos that are a factor of a few larger}.
-Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) appears to have no significant effect on the final distribution of masses.
+In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}. In addition to 
+leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce \textbf{embryos that are a factor of a few larger}. Despite the 
+vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) 
+appears to have no significant effect on the final distribution of masses. \textbf{For reference, the boundary between shear and dispersion-dominated 
+encounters ($e_{h}$ = 1) lies around e = $4 \times 10^{-4}$ for the planetesimal mass we have chosen. The eccentricity at which $\left< v^{2} \right>^{1/2} = 
+v_{esc}$ for the planetesimals is around $10^{-2}$.}
 
@@
 the growth rate is accelerating with mass). This behavior is
-evident in all four cases. Even with a large
+evident in all four cases \textbf{although the small $\alpha$ simulations eventually reach a stage where the curves
+ turn over as the planetesimal supply depletes.}. Even with a large
 $\beta$, where the effective collision cross section is
@@
 \textbf{In the bottom panel of figure \ref{fig:alpha_beta_evo}, we separately show the evolution of
-the maximum (solid lines) and mean (dashed lines) mass for each case. Here, it is evident}
-that \textbf{the turnover in $M/\left< m \right>$} is
+the maximum (solid lines) and mean (dashed lines) mass for each case. Here, it is evident
+that the turnover in $M/\left< m \right>$ is
 driven by an increase in the average mass as the planetesimal population
-becomes depleted. \textbf{For small $\alpha$, one would expect that planetesimal accretion should also eventually come to a halt as
+becomes depleted. For small $\alpha$, one would expect that planetesimal accretion should also eventually come to a halt as
 the growth timescale lengthens due to the planetesimal surface density decreasing and the residual bodies being scattered onto high
@@
 ascending node $\Omega$, and mean anomaly M for the planetesimals are drawn from a uniform distribution $\in [0, 2 \pi)$.
+
+\textbf{One should note that this choice for the gas disk profile almost certainly does not capture the wide range of possibilities in real planet-forming disks. 
+On one hand, a larger initial gas surface density could act to completely remove solids via radial drift, rendering in-situ accretion of solids impossible. On the 
+other hand, a more tenuous gas disk might render aerodynamic drag forces completely unimportant. In this case, the random velocity of the initial 
+planetesimals should be close to their mutual escape velocity. As we showed in section \ref{sec:narrow}, the initial dynamical state of the solids seems to 
+have a very minimal effect on the final outcome of planetesimal accretion. In a similar vein to \citet{hansen12}, we choose to use a MMSN-like profile for the 
+gas disk and instead vary the solid surface density profile to capture the range of mechanisms that might have acted to facilitate planetesimal formation in the 
+first place.}
 
@@
     \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi 
-    simulation. Each curve represents a radial slice of the disk. The outermost region evolves the slowest, and is therefore 
-    represented by the top curve. The dashed lines indicate radial zones interior to the 60 day orbital period boundary.\label{fig:pl_frac_time}}
+    simulation. Each curve represents a radial slice of the disk. \textbf{The time is measured in units of the local accretion 
+    timescale at the center of each radial zone. The colors represent the orbital period at the center of each zone.}\label{fig:pl_frac_time}}
 \end{center}
@@
 \begin{tabular}{lccccccc} \hline \hline
-Simulation Name & $m_{pl} [M_{\earth}]$ &$N_{pl}$ & A & d & $M_{PP}  [M_{\earth}]$ & $T_{int} [yr]$ & $T_{int, 1} [yr]$ \\ \hline
+Simulation Name & $m_{pl} [M_{\earth}]$ &$N_{pl}$ & A & $\delta$ & $M_{PP}  [M_{\earth}]$ & $T_{int} [yr]$ & $T_{int, 1} [yr]$ \\ \hline
 fdHi              & $8.37 \times 10^{-6}$ & 903,687 & 100 & 1.5 & 1.00 & 456 & 16,377  \\
@@
 as a function of orbital period.
-\textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso2} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and
+\textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and
 that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 
@@
 
-\textbf{The color of the curves indicate the orbital period bin which is being measured. From about 40 to 100 days in orbital period, the planetesimal surface density 
-follows a similar trajectory as accretion proceeds. Interior to about 40 days, however, the rate at which $\sigma$ decays actually beings to decrease for the shortest 
-period orbits. In other words, growth is actually fueled less vigorously by planetesimals in this region. In the next section, the accretion history of bodies in this region is 
-qualitatively different than the outer disk as well.} In the inner disk, this value asymptotes to zero as the 
+\textbf{The color of the curves indicate the orbital period bin which is being measured. From about 40 to 100 days in orbital period, the planetesimal surface 
+density follows a similar trajectory as accretion proceeds. Interior to about 40 days, $\sigma$ actually decays more slowly. In other words, growth is actually 
+fueled less vigorously by planetesimals in this region. This highlights the fact that accretion proceeds in a qualitatively different way in the inner disk. For the 
+outer disk, gravitational focusing tends to facilitate collisions between protoplanets and preferentially smaller bodies. At short period, however, all close 
+encounters result in a collision, regardless of mass. In a rather counterintuitive fashion, planetesimals in the inner disk actually persist for longer. In section 
+\ref{sec:assembly}, we examine the assembly history of the embryos and show that there is much less of a preference for planetesimal-embryo collisions at 
+short period as well.}
+
+In the inner disk, this value asymptotes to zero as the 
 planetesimal population entirely depletes. In the outer disk, dynamical friction between the embryos and planetesimals 
@@
 The variation in smooth accretion fraction with mass for the short period bodies suggests that the planetesimal and embryo populations interact differently than those in the outer disk.
-Exterior to the accretion mode boundary, the growing embryos continue to accrete planetesimals as they near their final mass.
-Inside the boundary, however, later growth events tend to be dominated by embryo-embryo collisions, and the smooth accretion fraction drops as mergers with planetesimals play a less significant role.
-Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion \citep{kokubo98}, and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
+Exterior to the accretion mode boundary, the growing embryos continue to accrete planetesimals \textbf{while avoiding each other} as they near their final mass.
+Inside the boundary, however, \textbf{any and all bodies collide with each other, and the occasional embryo-embryo collision tends to dominate growth and drive down the smooth accretion fraction.} Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion \citep{kokubo98}, and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
 As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zone size predicted by an oligarchic growth model.
@@
     indicating relative mass. The blue points represent the initial state of the simulations. The bottom panel compares the final 
-    cumulative mass distributions of the bodies. \label{fig:frag_ecc}}
+    \textbf{differential} mass distributions of the bodies. \label{fig:frag_ecc}}
 \end{center}
@@
 Although the bounce-merge simulation takes much longer to reach the same phase of evolution, the resulting orbital properties
-and mass distribution (with the exception of some extra residual planetesimals) are indistinguishable from the merger-only case.
+are indistinguishable from the merger-only case. \textbf{Performing a Kolmogrov-Smirnov test on the two mass distributions yields
+a p-value of $2 \times 10^{-5}$, which tells us that the two mass distributions are quite firmly statistically different. If we remove
+the initial mass planetesimals, a KS test yields a p-value of 0.1. We conclude that the embryo populations are nearly indistinguishable,
+but the bounce-merge model produces a small amount of residual planetesimals.}
 
@@
 In addition, the sizes of the feeding zones, along with qualitative differences in the
-accretion history of embryos on both sides of the boundary provide further evidence to
+accretion history of embryos on both sides of the boundary \textbf{(see figures \ref{fig:minor_frac} and \ref{fig:acc_zones})} provide further evidence to
 suggest that oligarchic growth is not operating in the inner disk.
@@
 The blue points represent the initial state of the simulations.
-The bottom panel compares the final mass distributions of the bodies (diff or cumulative?).\label{fig:rung_ecc}}
+The bottom panel compares the final mass distributions of the bodies.\label{fig:rung_ecc}}
 \end{center}
@@
 In addition, the masses of both the protoplanets and the remaining growing planetesimals are indistinguishable.
+In this case, a KS test of the two mass distributions yields a p-value of $\sim 0.34$.
 We therefore safely conclude that the timestepping scheme used in this work does not alter the growth of the protoplanets in any meaningful way.

### 2023-04-28 makeFig.py

@@ -35,6 +35,7 @@ s = 0.005
 lw = 4
 blue = '#1f77b4'
 orange = '#ff7f0e'
+green = '#2ca02c'
 refmass = (1*u.M_earth).to(u.M_sun).value
 
 num_bins = 50
@@ -229,17 +230,22 @@ def plot_timescales():
 	axes.set_xscale('log')
 	axes.set_yscale('log')
 
-	#cb = plt.colorbar(cm.ScalarMappable(norm=norm, cmap=cmap), ax=axes)
 	cb = plt.colorbar(cax, ax=axes)
 	cb.set_label(r'$t_{relax}/t_{collision}$')
 	axes.set_xlabel('Orbital Period [d]')
 	axes.set_ylabel(r'$e_{h}$')
 
-	dust_to_gas = [1e-4, 1e-3, 1e-2, 1e-1, 1]
-	labels = [r'$\epsilon = 10^{-4}$', '$\epsilon = 10^{-3}$', '$\epsilon = 10^{-2}$',\
-	'$\epsilon = 10^{-1}$', '$\epsilon = 1$']
-	for idx, dg in enumerate(dust_to_gas):
-		yval = calc_eqh(dg).value
+	pl_sizes = [50, 100, 200, 400]
+	pl_sizes_cm = (pl_sizes*u.km).to(u.cm).value
+	pl_masses_g = 3*4/3*np.pi*pl_sizes_cm**3
+	labels = ['10 km', '50 km', '100 km', '200 km']
+	m_pl_g = (m_pl*u.M_sun).to(u.g).value
+	r_pl_cm = (r_pl*u.AU).to(u.cm).value
+	for idx, size in enumerate(pl_sizes):
+		v_k = np.sqrt(G.cgs.value*mstar.value/avals)
+		v_esc = np.sqrt(2*G.cgs.value*pl_masses_g[idx]/pl_sizes_cm[idx])
+		e_esc = v_esc/v_k
+		yval = e_esc*(m_pl_g/(3*mstar.value))**(-1/3)
 		axes.plot(pvals, yval, color='white', lw=4, ls='--')
 		axes.text(1.5, yval[0]*0.9, labels[idx], rotation=15, color='white', ha='center', va='center')
 
@@ -287,8 +293,26 @@ def plot_alpha_beta():
 
 	fig.supxlabel('Semimajor Axis [AU]')
 	fig.supylabel('Eccentricity')
-
+	
 	plt.subplots_adjust(wspace=0, hspace=0)
+
[…]

### 2023-04-28 refereeResponse.txt
Address more comments

@@
-cript at hand presents a numerical study of planetesimal accretion.
+Spencer TODOs:
+	Schematic showing physical meaning of r_pl, r_h and r_g for different alpha, beta values
+	Non-italiczed math subscripts (do this for figures too)
+	How to properly align text for the 'note' underneath table 1?
+	Centering of white in figure 1 colorbar is wrong (colormap on plot is correctly scaled, however)
+	Fix M_earth in figure labels
+
+We appreciate the referee's thorough and careful comments. We will address concerns with the manuscript one by one, with the original comment listed first, followed by our response (indented).
+
+The manuscript at hand presents a numerical study of planetesimal accretion.
 The authors identify a novel mode of accretion that operates if the primary's radius is a significant fraction of its hill-radius - a criterion the authors find to be met at short orbital periods in circumstellar disks.
@@
 I appreciate the authors' work and look forward to seeing the progress on the manuscript.
-
-TODOs:
-	Dont italicze math subscripts (do this for figures too)
-	Discussion of Roche limit at end of section 2
-	Centering of note text under table 1
-	Centering of white in figure 1 colorbar (colormap on plot is correctly scaled)
-	Add a note explaing why no fdLo on the collision plots
-	Explanation of \tilde{b} in section 5 ok?
 
@@
 
-	I think these changes all support the referee's feeling that the accretion mode boundary is not as sharply defined as originally suggested.
+	I think these changes all support the referee's intuition that the accretion mode boundary is not as sharply defined as originally suggested.
 Instead, the accretion seems to behave in a fully non-oligarchic way interior to ~40 days, and the transition between non-oligarcic and oligarchic growth seems to happen between ~40-70 days.
@@
 So long as radial drift does not start removing a significant amount of these smaller bodies, destructive collisions should only act to lengthen the growth timescale.
-TODO: Discusss this in the paper?
+TODO: Does this need to be discussed in the paper?
 Do we need to worry about inelastic damping here?
@@
 
-	Hill radius, e_h, i_h \tilde{b} and isolation mass, are now formally defined in section 2.1.
+	The concepts of Hill radius, e_h, i_h \tilde{b} and isolation mass, are now formally defined in section 2.1.
 
@@
 This is interesting because this accretion mode could potentially be relevant for ring systems!
-TODO: update
+This is now noted in the text.
 289: gravitational radius: is this physically motivated? Maybe reference
@@
 606: How can a mass be expressed in units of feeding zone size?
-	We are solving equation 11 for \tilde{b} and using the initial local surface density, along with the final particle mass to calculate the feeding zone size.
-We tried to explain this starting on line 611, but it sounds like some further clarification is needed.
-Some additional text has been added to the paragraph following equation 11 to explain where the value for \tilde{b} comes from.
+	The added explanation of Hill radius, \tilde{b} and isolation mass in section 2.1 hopefully makes this more clear now.
+See equation 8 in the revised manuscript.
+We have solved this equation for \tilde{b}, and use the present mass of the body as M_iso.
+One way to interpret this is the following: for a protoplanet with semimajor axis a, it must have carved an annulus of width \tilde{b} out of the planetestimal disk, where the initial local solid surface density was \Sigma_pl, in order to obtain its current mass M.
+This is also explained in the text alongside the description of figure 5.
 620: What is the intuition behind tilde b, how exactly is it defined?
@@
 Do I understand correctly that a body with tilde b less than 2 sqrt(3) is associated with a feeding zone so small that close encounters are not possible, and thus are not expected to grow further?
-	This is buried in some of the references in this section (Nazakawa + Ida 1988, Kokubo 1998, Kokubo 2002), but I'm realizing this is not stated explicitly anywhere in the paper so I will do so: \tilde{b} is a length in units of the local Hill radius.
-	The \tilde{b} = 2\sqrt{3} value is important because this is the smallest possible feeding zone size that a body can have.
-As eccentricity decreases, the feeding zone size decreases, but has a minimum value of 2\sqrt{3} for (e,i) = (0,0) (See section 6 of Nazakawa + Ida 1988 for an explanation as to why).
-Therefore, a protoplanet undergoing oligarchic growth (in which gravitational scattering events are frequent and keeps the largest bodies on circular orbits) will not accrete more than 2\sqrt{3}*r_h*Sigma worth of material from its surroundings.
-The key takeaway from the bottom panel of figure 5 is that there are bodies interior to 60d that must have accreted material from a much wider annulus than this, and so oligarchic growth is not operating here.
-	TODO: Update text somewhere?
+	See our additions to section 2.1, along with our response to the previous comment.
+To address your question, feeding zone size scales with eccentricity, but takes on a minimum value of 2\sqrt{3} for e, i = 0.
+Because oligarchic growth tends to maintain low eccentricity, low inclination orbits, we can be sure that this accretion mode is likely not operating wherever \tilde{b} > 2 \sqrt{3}.
 632: Why are the bodies expected to follow the tilde b = 2sqrt(3) from a theoretical perspective?
 Also, I'm unconvinced that the bodies do that at all in the presented simulations - they fall below this value but don't follow it.
-	See response to 620.
-You are right that the outer disk bodies do not all reach \tilde{b} = 2\sqrt{3}.
-TODO: Should probably mention that this should be interpreted as a maximum.
-Not feasible to run the outer disk to completetion (especially in the fdSteep case).
+	See responses to previous concerns, along with the additional simulation data added to figure 8.
 640: If anything the opposite seems to be true, no? Maybe have a specific value for the expected eccentricity of protoplanets with and without inelastic damping.
-	TODO
+	Yes, the protoplanets in the inner disk seem to have heated up.
+For a collection of 1 M_earth bodies, <v^2>^{1/2} = v_esc corresponds to <e^2>^{1/2} = 0.05, which roughly matches the dynamical excitation of the innermost bodies.
+I'm not sure of a way to estimate the expected eccentricity without inelastic damping, but it seems safe to conclude that the inner protoplanets have heated themselves up via self-stirring.
+This is now explained in the text.
 644: If I look at the contour map by eye, the eccentricity distribution doesn't seem all that different in the inner vs outer disk. Maybe the difference can be quantified?
@@
 if the simulation is initialized with a different random seed, by how much does the final distribution change?
-	We were saving these for the follow up paper, but we do have multiple versions of fdHi, fdSteep and fdShallow!
-These have now been added to figure 8.
-The added data does make it clear that the boundary is quite fuzzy.
-I've also plotted the mean and standard deviation of the \tilde{b} in a number of orbital period bins.
-I think this makes the accretion boundary a little more apparent.
-With the exception of maybe the fdShallow simulation, the locations in the disk where \tilde{b} drops below 2\sqrt{3} are broadly consistent, which supports our claim that the boundary location is driven by the local value of alpha.
-	TODO: Update text to recflect changes to figure.
+	We have now included four more versions of the fdHi, fdHiSteep and fdHiShallow simulations in this figure.
+Your intuition appears correct that the boundary is rather fuzzy (somewhere between 40 and 70 days).
+The orbital period at which \tilde{b} reaches 2\sqrt{3} does appear to be broadly consistent across all simulations, however.
 
@@
 726: I think it could be explicitly stated that smooth accretion = minor mergers.
-	TODO: How to address this?
+	Done
 730 & onwards: Can the authors quantify this trend?
@@
 See my major comments
-	TODO: Include more sims in top panel of figure 11?
+	We have added an orange and blue vertical line through both panels of this figure that highlights the match between the crossing of \tilde{b} = 2 \sqrt{3} and \alpha = 0.1.
+Without a detailed numerical study of three-body encounters with various values of \alpha, there is not much we can say about why \alpha > 0.1 is special, other than the fact that r_pl begins to take up a significant amount of the Hill sphere.
 

### 2023-04-28 main.tex
Address more comments

@@
 
-\textbf{Tidal interactions between protoplanets and the gaseous disk keep eccentricities and inclinations low until the gas disk dissipates (typically over the course of a few Myr \citep{mamajek09}).
+\textbf{Tidal interactions between protoplanets and the gaseous disk keep eccentricities and inclinations low until the gas disk dissipates, typically over the course of a few Myr \citep{mamajek09}.
 Eventually, gravitational perturbations eventually trigger an instability which drives bodies onto crossing orbits.
@@
 \textbf{\noindent where $M_{*}$ is the mass of the central star.
-The Hill radius of a body gives distance where the gravity of the growing planetesimal dominates over the gravity of the star.
+The Hill radius of a body describes the size scale over which the gravity of the growing planetesimal dominates over the gravity of the star.
 Using equation \ref{eq:hillfac}, the eccentricity, inclination and separation between orbiting bodies can be defined as}
@@
 
-\textbf{Using this formalism, $e_{h}$ and $i_{h}$ describe the radial and vertical excursions of an orbiting body in units of its Hill radius.
-For $e_{h} > 1$, the random velocity dispersion dominates over the shearing motion over a separation of $1 r_{h}$ and encounters can be treated with a two-body formalism.}
+\noindent \textbf{Using this formalism, $e_{h}$ and $i_{h}$ describe the radial and vertical excursions of an orbiting body in units of its Hill radius.
+For $e_{h} > 1$, the random velocity dispersion dominates over the shearing motion across a separation of $1 r_{h}$ and encounters can be treated with a two-body formalism.}
 
@@
 
-In the case where the collision cross section depends only
+\noindent In the case where the collision cross section depends only
 on the physical size of the planetesimals, the growth scales sub-linearly
@@
 $b = \tilde{b} r_{h}$ of its orbit.
-The total mass of planetesimals within this feeding zone is then $2 \pi a \left(2 \tilde{b} r_{h} \right) \Sigma_{pl}$, where a is the semimajor axis of the growing protoplanet and $\Sigma_{pl}$ is the initial local planetesimal surface density.
-The ``'isolation mass'' of the protoplanet can then be obtained by setting the protoplanet mass equal to the total mass of planetesimals within the feeding zone such that}
+The total mass of planetesimals within this distance is then $2 \pi a \left(2 \tilde{b} r_{h} \right) \Sigma_{pl}$, where a is the semimajor axis of the growing protoplanet.
+The ``isolation mass'' of the protoplanet can then be obtained by setting the protoplanet mass equal to the total mass of planetesimals within accretionary reach such that}
 
@@
 Jacobi energy and permits a close encounter \citep{naka88}.
-This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet, as oligarchic growth tends to ensure that embryos stay on near-circular orbits as they grow.}
+This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet because oligarchic growth tends to maintain near-circular orbits for the growing protoplanets.}
 
@@
 equal to the mutual escape velocity of the bodies. This is shown for planetesimals
-with an internal density of 3 g $cm^{-3}$ ranging from 10 to 200 km in size.}
+with an internal density of 3 g cm$^{-3}$ ranging from 10 to 200 km in size.}
 
@@
 implies that the Hill sphere of a body becomes smaller than its physical size.
-\textbf{As an additional note, the Roche limit of the central body and the distance at which $\alpha = 1$ are
-similar, but not identical.
-For a rigid spherical body, $a_{Roche} \simeq 0.88 a_{\alpha = 1}$.
+\textbf{As an additional note, the Roche limit of the central body and the distance at which $\alpha = 1$ are equivalent for a rigid spherical body.
 Applying a hydrostatic correction to the Roche limit, $a_{Roche} \simeq 0.6 a_{\alpha = 1}$.
-This accretion mode should
-therefore be relevant for ring systems.}
+This accretion mode should therefore be relevant for ring systems, which is a topic that deserves further study using high resolution N-body techniques.}
 
@@
 \end{tabular}\\
-A summary of the four `full disk' simulations presented in section \ref{sec:fulldisk}.
+\textit{Note:} A summary of the four `full disk' simulations presented in section \ref{sec:fulldisk}.
 $m_{pl}$ and $N_{pl}$ are the initial masses and number of planetesimals.
@@
 the protoplanet assembly phase last \textbf{(as an example, see figure 1 of \citet{kokubo02}}. This radial timescale dependence is not typically
-accounted for in planet formation simulations \textbf{(a notable exception being \citet{emsenhuber21a, emsenhuber21b})}, and appears to be an
+accounted for in planet formation simulations \textbf{a notable exception being \citet{emsenhuber21a, emsenhuber21b}}, and appears to be an
 important component to forming realistic solar system analogs
@@
 indicates the relative mass of the bodies. In the bottom panel, the
-final masses of the bodies (in units of feeding zone size) are shown
+final masses of the bodies (in units of feeding zone size \textbf{$\tilde{b}$}) are shown
 as a function of orbital period.
-\textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and
-that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 
-size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $
+\textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.
+In other words, $\tilde{b}$ is describing the size of the annulus that must be cut out of the planetesimal disk in order to produce a protoplanet of the current mass.} By plotting the derived value of $
 \tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
@@
 region of the disk should lower the overall eccentricity of the protoplanets there. This behavior is not immediately apparent in the 
-top panel of figure \ref{fig:fulldisk_e_m}. There are, however, a couple of factors in the wide disk simulations that could make this 
+top panel of figure \ref{fig:fulldisk_e_m}. \textbf{In fact, the opposite appears to be true.} There are, however, a couple of factors in the wide disk simulations that could make this 
 extra dynamical cooling mechanism difficult to see. Firstly, the initial eccentricity distributions of the inner and outer disk are 
@@
 the same moment in time somewhat inappropriate.
+\textbf{A quick back of the envelope calculation yields $\left< e^2 \right>^{1/2} = 0.05$ for a population of $\sim 1 M_{\earth}$ bodies with a random velocity dispersion equal to their mutual escape velocity.
+It is therefore likely the case that the innermost protoplanets have had ample time to self-stir.}
 
@@
 traced between each planetary embryo and the initial planetesimals.
+\textbf{For the fdHi, fdHiSteep and fdHiShallow simulations, protoplanets gain a factor of $\sim 10^6$ in mass relative to the intial planetesimals.
+For the fdLo simulation, this growth factor is nearly a thousand times smaller, which produces rather shallow and noisy collision histories.
+For this reason, we choose to exclude the fdLo simulation from our analysis in this section.}
 
@@
 \textbf{In figure \ref{fig:minor_frac}, we retrieve the collision events for all bodies in all five iterations of the fdHi, fdHiSteep and fdHiShallow
-simulations and plot the total mass fraction attained through minor merger events as a function of the final mass of the body. Here, we define a minor merger
+simulations and plot the total mass fraction attained through minor merger (smooth accretion) events as a function of the final mass of the body. Here, we define a minor merger
 to be any collision involving a planetesimal with $m < 100 m_{0}$. The color of the
@@
     bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the location at 
-    which $\tilde{b}$ exceeds $2 \sqrt{3}$. The shaded region
+    which $\tilde{b}$ exceeds $2 \sqrt{3}$ \textbf{This is highlighted by the vertical dashed lines.}. The shaded region
     in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
@@
 the initial mass planetesimals, a KS test yields a p-value of 0.1. We conclude that the embryo populations are nearly indistinguishable,
-but the bounce-merge model produces a small amount of residual planetesimals.}
+while the bounce-merge model produces a small amount of residual planetesimals.}
 
@@
 and showing that the boundary moves to the predicted location when running a simulation with a slightly smaller inflation factor. 
-For rocky planetesimals with a realistic bulk density \textbf{3 g $cm^{-3}$}, \textbf{our results suggest that} this boundary should lie around 5 days in orbital period.
+For rocky planetesimals with a realistic bulk density \textbf{3 g cm$^{-3}$}, \textbf{our results suggest that} this boundary should lie around 5 days in orbital period.
 
@@
 
-As described in section \ref{sec:methods}, {\sc ChaNGa} evolves the motions of the particles in the planetesimal disk using a multi-tiered timestepping scheme.
+\textbf{As described in section \ref{sec:methods}, {\sc ChaNGa} evolves the motions of the particles in the planetesimal disk using a multi-tiered timestepping scheme.
 Due to the extremely short dynamical timescale at the inner edge of the disk, the outer disk would require a prohibitive number of timesteps to reach the protoplanet phase using a fixed timestep scheme.To circumvent this, particles are evolved in discrete power-of-two timestep groups.
 In the event that a collision occurs between two particles on different timesteps, a slight error is introduced to the energy and angular momentum of the merged particle.
-Due to the nonlinear nature of the runaway growth phase, this slight error tends to trigger more subsequent collisions at the timestep boundary in the disk, and causes protoplanets to preferentially form at the boundaries.
-
-To circumvent this issue, we prohibit particles on different timesteps from merging until the runaway growth phase is well underway.
+Due to the nonlinear nature of the runaway growth phase, this slight error tends to trigger more subsequent collisions at the timestep boundary in the disk, and causes protoplanets to preferentially form at the boundaries.}
+
+\textbf{To circumvent this issue, we prohibit particles on different timesteps from merging until the runaway growth phase is well underway.
 For the fdHi simulation, multi-tiered mergers are not allowed during the first thousand steps.
@@
 In the first case, the aforementioned timestepping scheme is used.
-In the second case, all particles are evolved on the timestep appropriate for the inner edge of the disk.
+In the second case, all particles are evolved on the timestep appropriate for the inner edge of the disk.}
 
@@
     \includegraphics[width=0.5\textwidth]{figures/rung_ecc.png}
-    \caption{A comparison between the innermost region of the fdHi (orange) simulation, and a second version using a fixed timestep appropriate for the inner edge of the disk (green).
+    \caption{\textbf{A comparison between the innermost region of the fdHi (orange) simulation, and a second version using a fixed timestep appropriate for the inner edge of the disk (green).
 In the top panel, the period-eccentricity state of the particles is shown, with marker sizes indicating relative mass.
 The blue points represent the initial state of the simulations.
-The bottom panel compares the final mass distributions of the bodies.\label{fig:rung_ecc}}
-\end{center}
-\end{figure}
-
-In figure \ref{fig:rung_ecc}, we compare the final period-eccentricity state and final mass distributions to each other.
+The bottom panel compares the final mass distributions of the bodies.}\label{fig:rung_ecc}}
+\end{center}
+\end{figure}
+
+\textbf{In figure \ref{fig:rung_ecc}, we compare the final period-eccentricity state and final mass distributions to each other.
 There do not appear to be any differences between the two protoplanet distributions, particularly near the timestep boundary at 2 days.
@@
 In this case, a KS test of the two mass distributions yields a p-value of $\sim 0.34$.
-We therefore safely conclude that the timestepping scheme used in this work does not alter the growth of the protoplanets in any meaningful way.
+We therefore safely conclude that the timestepping scheme used in this work does not alter the growth of the protoplanets in any meaningful way.}
 

### 2023-04-28 makeFig.py

@@ -308,6 +308,14 @@ def plot_alpha_beta():
 	print('e_h = 1 corresponds to e = ' + str(e1))
 	print('v = v_esc corresponds to e = ' + str(e_esc))
 
+	mp = (0.8*u.M_earth).to(u.g).value
+	rhop = 3
+	rp = (3*mp/(4*np.pi*rhop))**(1/3)
+	vesc = np.sqrt(G.cgs.value*mp/rp)
+	vk = np.sqrt(G.cgs.value*0.08*mstar/(0.01*u.AU).to(u.cm).value)
+	e_esc_pp = vesc/vk
+	print('v = v_esc for protoplanets corresponds to e = ' + str(e_esc_pp))
+
 	rhop = 3.0/7100
 	rp = (3*mp/(4*np.pi*rhop))**(1/3)
 	vesc = np.sqrt(G.cgs.value*mp/rp)
@@ -1178,6 +1186,8 @@ def plot_f6f4_b():
 
 	fig, ax = plt.subplots(figsize=(8,8), nrows=2, sharex=True)
 
+	p1, p2 = 35, 60
+
 	axes = ax[0]
 
 	#surf_den = (p_vhi_ic['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)
@@ -1200,6 +1210,9 @@ def plot_f6f4_b():
 	axes.set_xlim(-5, 100)
 	axes.set_ylabel(r'Required $\tilde{b}$')
 	axes.legend()
+
+	axes.axvline(p1, ls='--', color=orange)
+	axes.axvline(p2, ls='--', color=blue)
 
 	axes = ax[1]
 	f = 6
@@ -1229,7 +1242,8 @@ def plot_f6f4_b():
 	alpha10g = r_pl_varyrho/(p_vhi_ic['a']*(m_pl/(3*mCentral))**(1/3))
 	#axes.semilogy(prof_perIC, alpha, ls=':')
 
-	print(prof_perIC, alpha1g, alpha10g)
+	axes.axvline(p1, ls='--', color=orange)
+	axes.axvline(p2, ls='--', color=blue)
 
 	axes.fill_between(prof_perIC.value, alpha1g, alpha10g, alpha=0.5)
 
@@ -1473,8 +1487,8 @@ def plot_rung_ecc():
 #plot_smooth_acc()
 #plot_acc_zones()
 #plot_f6f4()
-#plot_f6f4_b()
[…]

### 2023-05-03 makeFig.py
Fix m_earth labels on plots

@@ -283,8 +283,8 @@ def plot_alpha_beta():
 	l1 = plt.scatter([],[], edgecolor='black', color=orange, s=(1e-2*u.M_earth).to(u.M_sun).value/refmass*1e3)
 	l2 = plt.scatter([],[], edgecolor='black', color=orange, s=(1e-1*u.M_earth).to(u.M_sun).value/refmass*1e3)
 	l3 = plt.scatter([],[], edgecolor='black', color=orange, s=(1*u.M_earth).to(u.M_sun).value/refmass*1e3)
-	labels = ['0.01 M_earth', '0.1 M_earth', '1 M_earth']
-	ax[0][0].legend(handles=[l1, l2, l3], labels=['0.01 M_earth', '0.1 M_earth', '1 M_earth'], loc=2)
+	labels = [r'0.01 M$_{\oplus}$', r'0.1 M$_{\oplus}$', r'1 M$_{\oplus}$']
+	ax[0][0].legend(handles=[l1, l2, l3], labels=labels, loc=2)
 
 	ax[0][0].set_ylabel(r'Large $\alpha$')
 	ax[1][0].set_ylabel(r'Small $\alpha$')
@@ -900,7 +900,6 @@ def plot_smooth_acc():
 		cbs = ax.scatter(xvals, yvals, edgecolor='black', \
 			linewidth=0.4, c=porb, cmap=cm.jet, vmin=0.0, vmax=100.0, marker='o')
 
-		axes.set_xlabel('Mass [M_earth]')
 		axes.set_ylabel('Smooth Accretion Mass Fraction')
 
 		return cbs
@@ -934,6 +933,8 @@ def plot_smooth_acc():
 	cbs = plot_smooth_sim(axes, 'fdvhishallowe', 313000)
 	cb = fig.colorbar(cbs, ax=axes)
 	cb.set_label('Orbital Period [d]')
+
+	axes.set_xlabel(r'Mass [M$_{\oplus}$]')
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
@@ -1300,7 +1301,7 @@ def plot_frag_ecc():
 	axes.set_xscale('log')
 	axes.set_yscale('log')
 
-	axes.set_xlabel('Mass [M_earth]')
+	axes.set_xlabel(r'Mass [M$_{\oplus}$]')
 	axes.set_ylabel('dn/dm')
 
[…]

### 2023-05-03 makeFig.py
Fix colorbar in figure 1

@@ -224,7 +224,9 @@ def plot_timescales():
 			x, y = [np.log(self.vmin), np.log(self.midpoint), np.log(self.vmax)], [0, 0.5, 1]
 			return np.ma.masked_array(np.interp(np.log(value), x, y))
 
-	norm = MidPointLogNorm(vmin=np.min(trel_div_tcoll), midpoint=1.0, vmax=np.max(trel_div_tcoll))
+	# Matplotlib bug: the midpoint on the colorbar has to be exactly in the center
+	# of min and max, otherwise the colorbar doesnt match the colormap
+	norm = MidPointLogNorm(vmin=np.min(1e-3), midpoint=1.0, vmax=np.max(1e3))
 	cax = axes.pcolormesh(pvals, ehvals, np.flipud(np.rot90(trel_div_tcoll)), \
 							norm=norm, cmap=cmap)
 	axes.set_xscale('log')
@@ -1471,7 +1473,7 @@ def plot_rung_ecc():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
-#plot_timescales()
+plot_timescales()
 #plot_alpha_beta()
 #plot_alpha_beta_evo()
 #plot_alpha_beta_mass()
@@ -1481,7 +1483,7 @@ def plot_rung_ecc():
 #plot_surfden_profiles()
 #plot_surfden_iso()
 #plot_surfden_b()
-plot_smooth_acc()
+#plot_smooth_acc()
 #plot_acc_zones()
 #plot_f6f4()
 #plot_f6f4_b()

### 2023-05-04 refereeResponse.txt
Fix m_earth labels on plots
Fix colorbar in figure 1
Fix table and caption width

@@
 	Non-italiczed math subscripts (do this for figures too)
-	How to properly align text for the 'note' underneath table 1?
-	Centering of white in figure 1 colorbar is wrong (colormap on plot is correctly scaled, however)
-	Fix M_earth in figure labels
 

### 2023-05-04 main.tex
Fix table and caption width

@@
 \bibliographystyle{aasjournal}
+\usepackage{tabularx}
 
@@
 \caption{Summary of Full Disk Simulations}
-\begin{tabular}{lccccccc} \hline \hline
+\begin{tabularx}{1.0\textwidth}{l@{\extracolsep{\fill}}ccccccc} \hline \hline
 Simulation Name & $m_{pl} [M_{\earth}]$ &$N_{pl}$ & A & $\delta$ & $M_{PP}  [M_{\earth}]$ & $T_{int} [yr]$ & $T_{int, 1} [yr]$ \\ \hline
@@
 fdLo             & $8.37 \times 10^{-6}$ & 45,185  & 1      & 1.5 & $1.77 \times 10^{-3}$ & 3,713 & 133,651 \\ \hline
-\end{tabular}\\
+\end{tabularx}\\
+\begin{flushleft}
 \textit{Note:} A summary of the four `full disk' simulations presented in section \ref{sec:fulldisk}.
@@
 $T_{int, 1}$ is the integration time scaled by a factor of $f^{2}$, which accounts for the fact that the accretion timescale has been shortened by the inflated collision cross sections.
+\end{flushleft}
 \label{tab:sim_properties}
 \end{center}
-Text goes here
 \end{table*}

### 2023-05-14 main.tex
Upright math subscripts
Mostly typos fixes.

@@
 
+% upright subscripts in math mode
+\def\subinrm#1{\sb{\mathrm{#1}}}
+{\catcode`\_=13 \global\let_=\subinrm}
+\mathcode`_="8000
+\def\supinrm#1{\sp{\mathrm{#1}}}
+{\catcode`\^=13 \global\let^=\supinrm}
+\mathcode`^="8000
+\def\upsubscripts{\catcode`\_=12 } \def\normalsubscripts{\catcode`\_=8 }
+\def\upsupscripts{\catcode`\^=12 } \def\normalsupscripts{\catcode`\^=7 }
 \begin{document}
+\upsubscripts
 
@@
 For a swarm of planetesimals on randomly oriented orbits, $v$ is typically
-taken to the rms velocity $\left< v^{2} \right>^{1/2}$, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \citep{lissauer93}:
+taken to be the rms velocity, $\left< v^{2} \right>^{1/2}$, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \citep{lissauer93}:
 \begin{equation}\label{eq:ecc_vel}
@@
 \end{equation}
-
 \textbf{\noindent where $M_{*}$ is the mass of the central star.
@@
 \end{equation}
-
 \noindent In the case where the collision cross section depends only
@@
 In this case,
-
 \begin{equation}\label{eq:gravfocus}
@@
 \end{equation}
-
 \citep{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
@@
 stage of accretion can be obtained using the initial solid surface density profile. A growing protoplanet will eventually accrete material within a distance
-$b = \tilde{b} r_{h}$ of its orbit.
-The total mass of planetesimals within this distance is then $2 \pi a \left(2 \tilde{b} r_{h} \right) \Sigma_{pl}$, where a is the semimajor axis of the growing protoplanet.
+$b = \tilde{b} r_{h}$ of its orbit. The total mass of planetesimals
+within this distance is then $2 \pi a \left(2 \tilde{b} r_{h} \right)
+\Sigma_{pl}$, where $a$ is the semimajor axis of the growing protoplanet.
 The ``isolation mass'' of the protoplanet can then be obtained by setting the protoplanet mass equal to the total mass of planetesimals within accretionary reach such that}
-
 \begin{equation}\label{eq:iso_mass1}
@@
 \end{equation}
-
 \noindent \textbf{Solving for $M_{iso}$ gives}
-
 \begin{equation}\label{eq:iso}
@@
 \end{equation}
-
 \noindent \textbf{For bodies on circular, non-inclined orbits, $\tilde{b} = 2 \sqrt{3}$ is the smallest orbital separation that produces a non-negative
@@
 In the case where $r_{g}$ is smaller than the size of a planetesimal, the gravitational focusing enhancement factor will be between 0 and 1 and the collision cross section is mostly set by the geometric value.
-\textbf{For very large values of $r_{g}$ ($\beta \gg 1$), the effective collision cross section is almost entirely set by gravitational scattering.}
+\textbf{For very large values of $r_{g}$ ($\beta \ll 1$), the effective collision cross section is almost entirely set by gravitational scattering.}
 
@@
 \end{equation}
-
-where $M_{*}$ is the mass of the central star, $\Sigma_{MMSN} = 10$ g
+where $M_{*}$ is the mass of the central star, 10 g
 cm$^{-2}$ is the surface density of the minimum-mass solar nebula
-\citep{hayashi81} at 1 AU, $A$ is an enhancement factor and $\delta$ is the power law index.
+\citep[MMSN]{hayashi81} at 1 AU, $A$ is an enhancement factor and $\delta$ is the power law index.
 In the first case (fdHi), we model a disk that follows a MMSN power law slope ($\delta$ = 1.5), with the overall normalization enhanced by a factor of 100.
@@
 
-In addition to the mutual gravitational forces, a Stokes drag force due to the the gas disk is applied to each particle, following the prescription described in section 2.2.1 of \citet{morishima10}.
-For the initial mass planetesimals, the \textbf{Stokes number ($\textrm{St} = t_{s} \Omega$) at the inner and outer disk edge is roughly $2 \times 10^{5}$ and $10^{7}$, respectively.
-For $\tau_{s} \gg 1$, bodies are decoupled from the gas and are only weakly affected by it.
-Because $\tau_{s} \sim m^{1/3}$, the Stokes number grows as planetesimal accretion proceeds, and the drag force plays an increasingly minor role.} Although the aerodynamic gas drag is not expected to significantly alter the final protoplanet distribution, we include its effects here to be self-consistent with the initial conditions, which were constructed by balancing the effects of viscous stirring with gas drag.
+In addition to the mutual gravitational forces, a Stokes drag force
+due to the the gas disk is applied to each particle, following the
+prescription described in section 2.2.1 of \citet{morishima10}. For
+the initial mass planetesimals, the \textbf{Stokes number
+  ($\textrm{St} = t_{s} \Omega$) at the inner and outer disk edge is
+  roughly $2 \times 10^{5}$ and $10^{7}$, respectively. For $t_{s} \gg
+  1$, bodies are decoupled from the gas and are only weakly affected
+  by it.
+Because $t_{s} \sim m^{1/3}$, the Stokes number grows as planetesimal accretion proceeds, and the drag force plays an increasingly minor role.} Although the aerodynamic gas drag is not expected to significantly alter the final protoplanet distribution, we include its effects here to be self-consistent with the initial conditions, which were constructed by balancing the effects of viscous stirring with gas drag.
 
@@
 growth history of the planetary embryos. Because all collisions are directly resolved by the N-body code, a lineage can be 
-traced between each planetary embryo and the initial planetesimals.
-\textbf{For the fdHi, fdHiSteep and fdHiShallow simulations, protoplanets gain a factor of $\sim 10^6$ in mass relative to the intial planetesimals.
+traced between each planetary embryo and the initial
+planetesimals. \textbf{For the fdHi, fdHiSteep and fdHiShallow
+  simulations, protoplanets gain a factor of $\sim 10^6$ in mass
+  relative to the initial planetesimals.
 For the fdLo simulation, this growth factor is nearly a thousand times smaller, which produces rather shallow and noisy collision histories.
@@
     \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
-    \caption{\textbf{The relative separation between a body the mean orbital periods of its accretion zone at the end of the fdHi, fdHiSteep and fdHiShallow simulations.
+    \caption{\textbf{The relative separation between the final period
+        of a body and the mean orbital periods of its accretion zone at the end of the fdHi, fdHiSteep and fdHiShallow simulations.
 The marker type and color denotes the simulation used, while the marker sizes indicate the relative masses of bodies.
@@
 and showing that the boundary moves to the predicted location when running a simulation with a slightly smaller inflation factor. 
-For rocky planetesimals with a realistic bulk density \textbf{3 g cm$^{-3}$}, \textbf{our results suggest that} this boundary should lie around 5 days in orbital period.
+For rocky planetesimals with a realistic bulk density, \textbf{3 g cm$^{-3}$}, \textbf{our results suggest that} this boundary should lie around 5 days in orbital period.
 
@@
 
-\textbf{As described in section \ref{sec:methods}, {\sc ChaNGa} evolves the motions of the particles in the planetesimal disk using a multi-tiered timestepping scheme.
-Due to the extremely short dynamical timescale at the inner edge of the disk, the outer disk would require a prohibitive number of timesteps to reach the protoplanet phase using a fixed timestep scheme.To circumvent this, particles are evolved in discrete power-of-two timestep groups.
+\textbf{As described in section \ref{sec:methods}, {\sc ChaNGa}
+  evolves the motions of the particles in the planetesimal disk using
+  a multi-tiered timestepping scheme. Due to the extremely short
+  dynamical timescale at the inner edge of the disk, the outer disk
+  would require a prohibitive number of timesteps to reach the
+  protoplanet phase using a fixed timestep scheme.
+To circumvent this, particles are evolved in discrete power-of-two timestep groups.
 In the event that a collision occurs between two particles on different timesteps, a slight error is introduced to the energy and angular momentum of the merged particle.

### 2023-05-22 refereeResponse.txt
Upright math subscripts

@@
 	Schematic showing physical meaning of r_pl, r_h and r_g for different alpha, beta values
-	Non-italiczed math subscripts (do this for figures too)
 
@@
 Therefore, a 1m body will fill the same fraction of its Hill sphere as a 100km body, so long as they are made of the same material.
-I would expect that this non-oligarchic accretion mode would behave very similarly had we used a collision model that allowed for destructive interactions.
+We would expect that this non-oligarchic accretion mode would behave very similarly had we used a collision model that allowed for destructive interactions.
 So long as radial drift does not start removing a significant amount of these smaller bodies, destructive collisions should only act to lengthen the growth timescale.
@@
 88: Add reference maybe.
-	I don't know of any references which have tested the applicability of statistical methods during the oligarchic growth phase, but maybe some clarification would help.
+	We don't know of any references which have tested the applicability of statistical methods during the oligarchic growth phase, but maybe some clarification would help.
 The runaway growth phase produces a small number of large bodies, which eventually interact and terminate runaway growth (Ida + Makino 1993, Kokubo + Ida 1995).
@@
 Following computer scientist convention, our tree is flipped upside down, with the original planetesimals at the bottom (hence calling them children).
-I agree that calling them 'parents' is probably more intuitive for most readers, however.
+We agree that calling them 'parents' is probably more intuitive for most readers, however.
 We have changed 'children' to 'parents' here.
@@
 I think this is 0.33 Earth masses, within 0.1 AU of Earth, the feeding zone of Earth.
-	As we dicuss below, we have chosen to represent masses in M_earth, which we feel is a more appropriate than Ceres masses.
-Densities are radii before for both chosen values of alpha are now listed.
+	As we dicuss below, we have chosen to represent masses in
+        M_earth, which we feel is a more appropriate than Ceres
+        masses.
+Densities and radii for both chosen values of alpha are now listed.
 The bulk density and radius corresponding to the high-alpha particles is most certainly unphysical, but is meant to mimic how a body would fill its Hill sphere if it were placed closer to the star.
@@
 377: is alpha=1 chosen because it is the highest stable alpha? If so I would write that. Why is beta = 15000 chosen?
-	Alpha = 1 corresponds to r_pl = r_hill.
-One would expect that gravitational scattering should completely shut off for alpha >= 1.
-Beta = 15,000 corresponds to <e^{1/2}>^2 = 0.05, which is the largest eccentricity for which a particle at 1 AU will an apo and pericenter distance that is still within the boundaries of the disk.
+	Alpha = 1 corresponds to r_pl = r_hill. One would expect that
+	gravitational scattering should completely shut off for alpha
+	>= 1. Beta = 15,000 corresponds to <e^{1/2}>^2 = 0.05, which
+	is the largest eccentricity for which a particle at 1 AU will
+	have an apo and pericenter distance that is still within the boundaries of the disk.
 For an eccentricity dispersion this large, the stirring timescale is much longer than the simulation time, so we can be confident that the boundary effects do not get worse.
@@
 640: If anything the opposite seems to be true, no? Maybe have a specific value for the expected eccentricity of protoplanets with and without inelastic damping.
-	Yes, the protoplanets in the inner disk seem to have heated up.
-For a collection of 1 M_earth bodies, <v^2>^{1/2} = v_esc corresponds to <e^2>^{1/2} = 0.05, which roughly matches the dynamical excitation of the innermost bodies.
-I'm not sure of a way to estimate the expected eccentricity without inelastic damping, but it seems safe to conclude that the inner protoplanets have heated themselves up via self-stirring.
+	Yes, the protoplanets in the inner disk seem to have heated
+        up. For a collection of 1 M_earth bodies, <v^2>^{1/2} = v_esc
+        corresponds to <e^2>^{1/2} = 0.05, which roughly matches the
+        dynamical excitation of the innermost bodies.
+We're not sure of a way to estimate the expected eccentricity without inelastic damping, but it seems safe to conclude that the inner protoplanets have heated themselves up via self-stirring.
 This is now explained in the text.
@@
 668: add reference. Also footnote 5 can probably go in the main text. Can the authors provide an equation that converts tilde b to units of r_h?
-	\tilde{b} is already in units of r_h.
-This is now clarified near line 620 in the text.
-The 30 percent value simply comes from removing the size of the feeding zone (2\sqrt{3}) from the spacing between oligarchs (10).
-This is now clarified in the text here.
-I think the footnote text can be removed after adding this clarification.
+	\tilde{b} is already in units of r_h. This is now clarified
+        near line 620 in the text. The 30 percent value simply comes
+        from removing the size of the feeding zone (2\sqrt{3}) from
+        the spacing between oligarchs (10). This is now clarified in
+        the text here. We think the footnote text can be removed after adding this clarification.
 682: This statement seems only to be true for fdshallow. The others have a spread in eccentricity that covers two orders of magnitude...
@@
 685: It is not clear to me why more inelastic collisions lead to a more sharply peaked eccentricity distribution, and not just more damping like the authors argue for the fdLo simulation.
-	I'm not sure what you mean by 'more shaply peaked'?
+	I'm not sure what you mean by 'more sharply peaked'?
 The argument we're trying to make here is this: In the case that the initial surface density is large (e.g.
@@
 Seems to me that for all bodies, regardless of mass and orbital period, major mergers are significantly more important - that is at least with the author's definition of major and minor merger.
-	This statement makes a little more sense after broadening or definition of 'minor mergers' to include m < 100 m_0.
+	This statement makes a little more sense after broadening our definition of 'minor mergers' to include m < 100 m_0.
 In the legend, I think "orbit" should be put in the subscript instead of P_orbit

### 2023-06-26 refereeResponse.txt
Add alpha beta diagram, update referee response

@@
-Spencer TODOs:
-	Schematic showing physical meaning of r_pl, r_h and r_g for different alpha, beta values
-
 We appreciate the referee's thorough and careful comments. We will address concerns with the manuscript one by one, with the original comment listed first, followed by our response (indented).
@@
 
-TODO
+	We have added an additional figure (fig 2 in the updated paper) that showing a diagram that details the geometry of a two-body encounter for different combinations of \alpha and \beta.
 
@@
 415: the y-label in Fig.6 does not match the description in the text
-	This comment must be referring to figure 4? If so, 'm_max' in the text has been changed to 'M'.
+	This comment must be referring to figure 4 (figure 5 in the updated paper)? If so, 'm_max' in the text has been changed to 'M'.
 Figure 4:
@@
 That would also underscore that the turnover is driven by an increase in <m> rather than m_max.
-	We have now added a second panel to figure 4 which shows the evolution of these quantities separately.
+	We have now added a second panel to figure 4 (figure 5 in the updated paper) which shows the evolution of these quantities separately.
 It is now clear that the turnover of the blue and orange curves on the original plot are driven by a continued increase in <m>.
@@
 	t_vs = t_gas is more of an upper limit on the eccentricity, although this is the same technique that Kokubo 2002 uses to set up the initial conditions.
-It's certainly possible that the disk could have started out dynamically colder, although as we showed in figure 2, this doesn't seem to affect the resulting protoplanets.
+It's certainly possible that the disk could have started out dynamically colder, although as we showed in figure 2 (figure 3 in the updated paper), this doesn't seem to affect the resulting protoplanets.
 We have added a short discussion about this to the text.
@@
 I think the bottom panel should have a log y-axis
-	TODO: I dont think this is necessary? If I make this change, do I need to do the same thing for figure 8? The way \tilde_b is defined we are already showing mass in a non-linear way.
+	We feel that a linear y-axis better presents the data here.
+Perhaps the referee could provide some motivation for why they feel a log y-axis would be better?
+Because we are presenting the masses in terms of \tilde_b, the mass is already plotted in a non-linear way.
+Using a log scale here takes the focus away from the embryos on the plot.
 I would make the color of the dots consistent with Fig.2, where the final outcome is orange
@@
 If so the statement should be rephrased to make the causal connection clear.
-	The y axis on the bottom panel of figure 5 is now log-scaled.
-Point colors in both panels have been changed to orange, to be consistent with figure 2.
+	Point colors in both panels have been changed to orange, to be consistent with figure 2 (figure 3 in the updated paper).
 The dashed line in the bottom panel is now labeled.
@@
 One way to interpret this is the following: for a protoplanet with semimajor axis a, it must have carved an annulus of width \tilde{b} out of the planetestimal disk, where the initial local solid surface density was \Sigma_pl, in order to obtain its current mass M.
-This is also explained in the text alongside the description of figure 5.
+This is also explained in the text alongside the description of figure 5 (figure 6 in the updated paper).
 620: What is the intuition behind tilde b, how exactly is it defined?
@@
 Also, I'm unconvinced that the bodies do that at all in the presented simulations - they fall below this value but don't follow it.
-	See responses to previous concerns, along with the additional simulation data added to figure 8.
+	See responses to previous concerns, along with the additional simulation data added to figure 8 (figure 9 in the updated paper).
 640: If anything the opposite seems to be true, no? Maybe have a specific value for the expected eccentricity of protoplanets with and without inelastic damping.
@@
 	Yes!
-See our updated version of figure 6.
+See our updated version of figure 6 (figure 7 in the updated paper).
 The time is now shown in units of the local accretion timescale, and it is now apparent that the planetesimal surface density curves all follow the same trajectory outside of about 40d.
@@
 Your point about the smooth accretion fraction always being small due to this overly strict cutoff is a good one.
-We have reconstructed figure 9 using a mass cutoff of 100 m_0 for major/minor collisions.
+We have reconstructed figure 9 (figure 10 in the updated paper) using a mass cutoff of 100 m_0 for major/minor collisions.
 724: Why are only the 100 largest bodies chosen?
@@
 	The 100 body cutoff was chosen because the analysis script we were using the construct the collision history was rather slow when asked to include all ~10,000 particles in the snapshot.
-This has been optimized and all bodies larger than 100 m_0 are now included in figure 9.
+This has been optimized and all bodies larger than 100 m_0 are now included in figure 9 (figure 10 in the updated paper).
 fdHi is chosen to be the 'fiducial' simulation for most of this paper.
@@
 I would argue that more massive bodies require more time to build up and during later stages there are simply less primordial planetesimals left so collisions are just more likely to be major mergers.
-	See updated version of figure 9.
+	See updated version of figure 9 (figure 10 in the updated paper).
 After including data from more simulations and coloring the points by orbital period, it is clear that there is a difference between the smooth accretion fraction of bodies in the inner disk, compared to the outer disk.
@@
 802: As I argued above, I'm unconvinced in this clear-cut boundary at 60 days. Maybe the authors could put a quantitative uncertainty to this number?
-	The additional simulations included in figure 8, along with the difference in accretion characteristics near ~30-40d (see figures 9 and 10) suggests that the boundary lies somewhere between 40 and 70 days.
+	The additional simulations included in figure 8 (figure 9 in the updated paper), along with the difference in accretion characteristics near ~30-40d (see figures 10 and 11 in the updated paper) suggests that the boundary lies somewhere between 40 and 70 days.
 This is now stated here in the text.
@@
 954: Refer to figure where this is shown. I think Fig.2? Also "the same" is very strong. Maybe "very similar" instead.
-	A reference to figure 2 has been added here. 'The same' has been has been changed to 'very similar'.
+	A reference to figure 2 (figure 3 in the updated paper) has been added here. 'The same' has been has been changed to 'very similar'.
 959: Sentence is currently implying that the boundary location is set by the distance to the star which doesn't really work in my opinion.
@@
 972: Refer to Fig. 10.
-	A reference has been added to figures 9 and 10.
+	A reference has been added to figures 9 and 10 (figures 11 and 12 in the updated paper).
 978: Missing a verb, maybe "differs" ? Also the second part of the sentence "along with [...]" seems odd to me. Maybe rephrase it in two sentences?

### 2023-06-26 main.tex
Add alpha beta diagram, update referee response

@@
 These scaling considerations motivate the range of parameters we choose for the numerical experiments presented in the next section, where we aim to understand where and when runaway and oligarchic growth can operate.
+\textbf{In figure \ref{fig:alpha_beta_diagram}, we show a schematic which relates $\alpha$ and $\beta$ to the geometry of a two-body encounter.
+For large values of $\alpha$, the Hill radius of a body (dashed circle) becomes comparable to its physical radius (solid circle).
+As $\beta$ increases, the trajectory of a body undergoing a flyby becomes more straight.}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/diagram.png}
+    \caption{\textbf{A diagram detailing how varying the values of $\alpha$ and $\beta$ affect the geometry of a two-body encounter.
+The solid circles represent the physical radius of a body and the dashed circles represent the Hill radius.
+As $\alpha$ is increased, the Hill radius and the physical radius become comparable in size.
+As $\beta$ is increased, the trajectory of a passing body for a fixed impact parameter is bent less and less.}
+      \label{fig:alpha_beta_diagram}}
+\end{center}
+\end{figure}
 

### 2023-06-26 makeFig.py

@@ -691,7 +691,7 @@ def plot_surfden_iso():
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 def plot_surfden_b():
-	file_str = 'figures/surfden_b.' + fmt
+	file_str = 'figures/surfden_b_log.' + fmt
 	if not clobber and os.path.exists(file_str):
 		return
 
@@ -800,8 +800,8 @@ def plot_surfden_b():
 	axes.set_title('fdLo')
 
 	axes.set_xlim(-5, 100)
-	#axes.set_yscale('log')
-	axes.set_ylim(0, 20)
+	axes.set_yscale('log')
+	axes.set_ylim(1e-2, 1e2)
 	axes.set_xlabel('Orbital Period [d]')
 	#axes.legend()
 
@@ -1473,7 +1473,7 @@ def plot_rung_ecc():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
-plot_timescales()
+#plot_timescales()
 #plot_alpha_beta()
 #plot_alpha_beta_evo()
 #plot_alpha_beta_mass()
@@ -1482,7 +1482,7 @@ plot_timescales()
 #plot_pl_frac_time()
 #plot_surfden_profiles()
 #plot_surfden_iso()
-#plot_surfden_b()
+plot_surfden_b()
 #plot_smooth_acc()
 #plot_acc_zones()
 #plot_f6f4()

### 2023-07-12 refereeResponse2.txt
Round 2 referee edits

We again appreciate the referee's thorough and careful comments. We will address comments on the second version of the manuscript one by one, with the original comment listed first, followed by our response (indented). Note that the removal of the boldface text from the previous version of the manuscript has altered the line numbers. We will provide the new line number in the updated version of the manuscript alongside each response.

General comment: I very much recommend the use of perceptually uniform color maps for accessibility and readability.
	Figures 7 and 10 now use a perceptually uniform colormap

78: Sentence sounds vague. Maybe combine with subsequent sentence
	These sentences have been combined (78)
257: change "will eventually accrete" to "is expected to eventually accrete"
	Changed (252)
343: This sentence seems incomplete.
	Changed to "a_roche is equivalent to 0.6 a_{alpha = 1}" (333)
345: Do you mean planetary rings?
	Yes, changed to "planetary ring systems" (336)
384 and Caption figure 2: change "is bent less and less" to "is less affected"
	"Bent less and less" has been changed to "less affected". "More straight" has been changed to "less affected by the encounter". (373)
559: change "the Hill sphere of a body is mostly empty space" to "the planetesimal only fills a small portion of its Hill sphere"
	Changed (544)
608: Streaming instability is one pathway of forming planetesimals but not the only one, so I would soften that statement. Also, instead of "triggered" I would write something along the lines of "streaming instability requires sufficiently large concentrations of solid material".
	Agreed that the streaming instability is not the only viable way of creating planetesimals. This sentence has been changed to "Many recent planetesimal formation models invoke streaming instabilities, which first require sufficiently large amounts of solid material concentrating at preferential locations in the disk." (592)
1163: I'm not sure why one would (or would not) include the initial planetesimals. Maybe clarify? Also a KS p-value of 0.1 is typically not low enough to reject the null hypothesis, so I would also soften the statement in 1166.
	The idea here is that the populations *are* statistically similar if you ignore the handful of residual planetesimals. Had the remaining planetesimals been accreted by the larger bodies, the masses of the larger bodies would hardly change, but the p-value of the KS test would be quite different (the remaining planetesimals only make up ~0.1% of the total mass). I think this highlights a limitation of using a KS test to compare the mass distributions, in that the larger bodies should be given more importance. The last two sentences of this paragraph have been modified to clarify. (1121)
1368: Delete "safely"
	Done (1323)

### 2023-07-12 main.tex
Round 2 referee edits

--- 2023-05-14 main.tex
@@
 small body populations. However, planetesimal accretion has not yet
-been fully explored in the context of the \textbf{wide variety} of recently discovered extrasolar planetary systems,
+been fully explored in the context of the wide variety of recently discovered extrasolar planetary systems,
 particularly those that host short-period terrestrial planets. In this work, we
@@
 result in collisions, rather than scattering, and the system does not
-develop a bimodal population \textbf{of} dynamically hot planetesimals and
+develop a bimodal population of dynamically hot planetesimals and
 dynamically cold oligarchs, like is seen in previous studies. The highly
@@
 results to assumptions about the initial disk model, and also
-investigate \textbf{the effects} that our simplified collision model has on the emergence
+investigate the effects that our simplified collision model has on the emergence
 of this non-oligarchic growth mode in a planet forming disk.
@@
 moon-sized objects known as planetary embryos. In the earliest stages
-of the planet formation process, \textbf{beginning from $\mu$m sizes,} aerodynamic forces dominate the
+of the planet formation process, beginning from $\mu$m sizes, aerodynamic forces dominate the
 growth and evolution of the solids and statistical models
-\citep{johansen14, birnstiel16} are appropriate to describe how these
+\cite{johansen14, birnstiel16} are appropriate to describe how these
 numerous, small bodies coagulate.
@@
 exerts a headwind on any solids large enough to decouple from the gas
-\citep{weidenschilling77}. Around a meter in size, this headwind
+\cite{weidenschilling77}. Around a meter in size, this headwind
 is maximally effective at sapping away orbital angular momentum, and planet-building material can fall onto the central star on 
-catastrophically short timescales \citep{weidenschilling77, nakagawa86}. Additionally, laboratory experiments suggest that 
+catastrophically short timescales \cite{weidenschilling77, nakagawa86}. Additionally, laboratory experiments suggest that 
 collisions between mm- to cm- sized solids tend to result in bounces or destruction, rather than continued growth
-\citep{blum93, colwell03, beitz11}.
+\cite{blum93, colwell03, beitz11}.
 
 For these reasons, a number of mechanisms to radially concentrate solids in a planet-forming disk have been proposed to 
-facilitate fast growth from mm to km sizes \citep{johansen07, lyra08, bai10} in order to surmount these barriers. Interestingly, 
-formation models for the short-period multiplanet systems revealed by Kepler \citep{fabrycky14} also seem to require enhanced 
-concentrations of planet-building material to reproduce the observed architectures \citep{raymond07, hansen12}.
+facilitate fast growth from mm to km sizes \cite{johansen07, lyra08, bai10} in order to surmount these barriers. Interestingly, 
+formation models for the short-period multiplanet systems revealed by Kepler \cite{fabrycky14} also seem to require enhanced 
+concentrations of planet-building material to reproduce the observed architectures \cite{raymond07, hansen12}.
 
@@
 plays an increasingly unimportant role beyond this size. During this phase, collision cross sections are enhanced as gravitational 
-focusing \citep{safronov69} acts to bend the trajectories of bodies undergoing close encounters. Because gravitational focusing 
-becomes more effective as bodies grow larger, a period of runaway growth occurs \citep{wetherill89, kokubo96, barnes09} and a 
+focusing \cite{safronov69} acts to bend the trajectories of bodies undergoing close encounters. Because gravitational focusing 
+becomes more effective as bodies grow larger, a period of runaway growth occurs \cite{wetherill89, kokubo96, barnes09} and a 
 power law spectrum of masses develop. Eventually, the largest bodies (known as oligarchs) dynamically heat the remaining 
-planetesimals, severely limiting further growth \citep{kokubo98}. The final outcome of this phase is a bimodal population of 
+planetesimals, severely limiting further growth \cite{kokubo98}. The final outcome of this phase is a bimodal population of 
 dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals. Lines of evidence suggest 
-that the asteroid belt \textbf{\citep{bottke05, morbidelli09}}, Kuiper belt \textbf{\citep{duncan89, levison08, sheppard10}} and the Oort cloud \textbf{\citep{levison11}} are largely composed of the leftovers of this stage of planet formation.
-
-\textbf{Tidal interactions between protoplanets and the gaseous disk keep eccentricities and inclinations low until the gas disk dissipates, typically over the course of a few Myr \citep{mamajek09}.
-Eventually, gravitational perturbations eventually trigger an instability which drives bodies onto crossing orbits.
-This instability occurs on a timescale of $\sim 10^{5}$ years and involves large scale oscillations of the eccentricity and inclinations of the bodies as they strongly interact through secular resonances \citep{chambers98}.}
+that the asteroid belt \cite{bottke05, morbidelli09}, Kuiper belt \cite{duncan89, levison08, sheppard10} and the Oort cloud  \cite{levison11} are largely composed of the leftovers of this stage of planet formation.
+
+Tidal interactions between protoplanets and the gaseous disk keep eccentricities and inclinations low until the gas disk dissipates, typically over the course of a few Myr \cite{mamajek09}.
+\textbf{On a timescale of roughly $10^{5}$ yr, gravitational perturbations trigger an instability which involves large scale oscillations of the eccentricity and inclinations of bodies as they strongly interact through secular resonances \cite{chambers98}.}
 As a consequence of the instability, the oligarchics are no longer
@@
 through a series of extremely energetic giant 
-impacts \citep{kokubo02, raymond05, raymond06}.
+impacts \cite{kokubo02, raymond05, raymond06}.
 
@@
 many particles to directly track with traditional N-body codes, while
-the gravitational interactions between the \textbf{few massive bodies produced by the runaway growth phase \citep{ida93, kokubo95, kokubo98} render statistical methods inappropriate}.
+the gravitational interactions between the few massive bodies produced by the runaway growth phase \cite{ida93, kokubo95, kokubo98} render statistical methods inappropriate.
 Due to computational expense, N-body simulations of
 planetesimal accretion are usually modeled in a narrow
-ring \citep{kokubo96, kokubo98}, and the results and timescales are then scaled to suit whatever relevant orbital period is being 
+ring \cite{kokubo96, kokubo98}, and the results and timescales are then scaled to suit whatever relevant orbital period is being 
 studied. N-body simulations of terrestrial planet assembly typically begin with a series of neatly spaced oligarchs, whose mass 
@@
 Given that Systems of Tightly-packed Inner Planets (STIPs) appear to
-be a common outcome of planet formation \citep{lantham11, lissauer11, rowe14}, understanding exactly how
+be a common outcome of planet formation \cite{lantham11, lissauer11, rowe14}, understanding exactly how
 solids accumulate at short orbital periods is crucial. Although
 gas-disk driven migration of the planets themselves is often invoked
-to explain the observed architectures \textbf{\citep{izidoro17, izidoro21}}, we will focus on an in-situ
+to explain the observed architectures \cite{izidoro17, izidoro21}, we will focus on an in-situ
 model in this paper. That is, once the planetesimals themselves form,
@@
 In doing so, we will assess whether the typical initial conditions (fully formed, evenly spaced protoplanets, e.g.
-\citet{raymond06}) used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
+\cite{raymond06}) used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
 
@@
 For a swarm of planetesimals on randomly oriented orbits, $v$ is typically
-taken to be the rms velocity, $\left< v^{2} \right>^{1/2}$, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \citep{lissauer93}:
+taken to be the rms velocity, $\left< v^{2} \right>^{1/2}$, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \cite{lissauer93}:
 \begin{equation}\label{eq:ecc_vel}
@@
 
-\textbf{The dynamical interactions between growing planetesimals can be somewhat simplified by scaling the orbital elements of the bodies by
-the Hill radius}
+The dynamical interactions between growing planetesimals can be somewhat simplified by scaling the orbital elements of the bodies by
+the Hill radius
 
@@
 \end{equation}
-\textbf{\noindent where $M_{*}$ is the mass of the central star.
+\noindent where $M_{*}$ is the mass of the central star.
 The Hill radius of a body describes the size scale over which the gravity of the growing planetesimal dominates over the gravity of the star.
-Using equation \ref{eq:hillfac}, the eccentricity, inclination and separation between orbiting bodies can be defined as}
+Using equation \ref{eq:hillfac}, the eccentricity, inclination and separation between orbiting bodies can be defined as
 
@@
 
-\noindent \textbf{Using this formalism, $e_{h}$ and $i_{h}$ describe the radial and vertical excursions of an orbiting body in units of its Hill radius.
-For $e_{h} > 1$, the random velocity dispersion dominates over the shearing motion across a separation of $1 r_{h}$ and encounters can be treated with a two-body formalism.}
+\noindent Using this formalism, $e_{h}$ and $i_{h}$ describe the radial and vertical excursions of an orbiting body in units of its Hill radius.
+For $e_{h} > 1$, the random velocity dispersion dominates over the shearing motion across a separation of $1 r_{h}$ and encounters can be treated with a two-body formalism.
 
@@
 \end{equation}
-\citep{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
+\cite{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
 
@@
 accelerates with mass. This mode of growth was confirmed with N-body
-simulations by \citet{kokubo96} and appears necessary to construct
-protoplanets within the lifetime of a protoplanetary disk \textbf{\citep{lissauer87}, although one should note that pebble accretion \citep{lambrechts12, lambrechts14, bitsch15} is a viable alternative scenario}.
+simulations by \cite{kokubo96} and appears necessary to construct
+protoplanets within the lifetime of a protoplanetary disk \cite{lissauer87}, although one should note that pebble accretion \cite{lambrechts12, lambrechts14, bitsch15} is a viable alternative scenario.
 Due to the
@@
 Keplerian shear into random motion, raises the typical encounter velocity
-between planetesimals over time \citep{weidenschilling89, ida90} and diminishes the effectiveness of gravitational
+between planetesimals over time \cite{weidenschilling89, ida90} and diminishes the effectiveness of gravitational
 focusing. As the mass spectrum of the system evolves away from uniformity, these velocity differences become even more
@@
 motions rather than Keplerian shear (dispersion dominated), the timescale for gravitational stirring is described by the two-body 
-relaxation time \citep{ida93}
+relaxation time \cite{ida93}
 \begin{equation}\label{eq:relax}
@@
 where $\ln \Lambda$ is the Coulomb logarithm,
-typically taken to be \textbf{$\approx 3$ for a planetesimal disk \citep{ida90, stewart00}}. Despite
+typically taken to be $\approx 3$ for a planetesimal disk \cite{ida90, stewart00}. Despite
 the fact that the behavior of gravitational stirring is well-described
-by a two-body formula, \citep{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters, which 
+by a two-body formula, \cite{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters, which 
 requires a three-body formalism. As we will show in section \ref{sec:narrow}, gravitational stirring effectively shuts off when the 
@@
 
-\citet{kokubo98} showed that \textbf{the runaway growth process described above} is actually self-limiting. As the runaway
-bodies develop, they become increasingly effective at \textbf{dynamically} heating the
+\cite{kokubo98} showed that the runaway growth process described above is actually self-limiting. As the runaway
+bodies develop, they become increasingly effective at dynamically heating the
 remaining planetesimals, which diminishes the
@@
 by a factor of $\sim 50-100$
-\citep{ida93} a phase of less vigorous ``oligarchic'' 
+\cite{ida93} a phase of less vigorous ``oligarchic'' 
 growth commences, in which the largest bodies continue to 
@@
 
-\textbf{Regardless of the mechanism that eventually limits the growth of the planetary embryos, a maximum estimate for the masses produced during this 
-stage of accretion can be obtained using the initial solid surface density profile. A growing protoplanet will eventually accrete material within a distance
+Regardless of the mechanism that eventually limits the growth of the planetary embryos, a maximum estimate for the masses produced during this 
+stage of accretion can be obtained using the initial solid surface density profile. A growing protoplanet \textbf{is expected to accrete} material within a distance
 $b = \tilde{b} r_{h}$ of its orbit. The total mass of planetesimals
@@
 \Sigma_{pl}$, where $a$ is the semimajor axis of the growing protoplanet.
-The ``isolation mass'' of the protoplanet can then be obtained by setting the protoplanet mass equal to the total mass of planetesimals within accretionary reach such that}
+The ``isolation mass'' of the protoplanet can then be obtained by setting the protoplanet mass equal to the total mass of planetesimals within accretionary reach such that
+
 \begin{equation}\label{eq:iso_mass1}
@@
 \end{equation}
-\noindent \textbf{Solving for $M_{iso}$ gives}
+\noindent Solving for $M_{iso}$ gives
 \begin{equation}\label{eq:iso}
@@
 \end{equation}
-\noindent \textbf{For bodies on circular, non-inclined orbits, $\tilde{b} = 2 \sqrt{3}$ is the smallest orbital separation that produces a non-negative
-Jacobi energy and permits a close encounter \citep{naka88}.
-This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet because oligarchic growth tends to maintain near-circular orbits for the growing protoplanets.}
-
-The picture described above relies upon \textbf{a} crucial assumption, which
+\noindent For bodies on circular, non-inclined orbits, $\tilde{b} = 2 \sqrt{3}$ is the smallest orbital separation that produces a non-negative
+Jacobi energy and permits a close encounter \cite{naka88}.
+This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet because oligarchic growth tends to maintain near-circular orbits for the growing protoplanets.
+
+The picture described above relies upon a crucial assumption, which
 is that the mass distribution evolves slowly enough for gravitational stirring to maintain energy equipartition.
-In other words, the relaxation timescale must remain short relative to the \textbf{collision} timescale.
+In other words, the relaxation timescale must remain short relative to the collision timescale.
 For typical conditions near the terrestrial region of the solar system, this timescale condition is satisfied.
@@
 simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2
-\right>^{1/2}$ \citep{ida93a} and that the eccentricity dispersion is
-constant with orbital period. \textbf{The coloring indicates the ratio between
+\right>^{1/2}$ \cite{ida93a} and that the eccentricity dispersion is
+constant with orbital period. The coloring indicates the ratio between
 $t_{relax}$ and $t_{coll}$. The dashed lines denote the eccentricity at which the
@@
 equal to the mutual escape velocity of the bodies. This is shown for planetesimals
-with an internal density of 3 g cm$^{-3}$ ranging from 10 to 200 km in size.}
-
-\textbf{A physically realistic value of $e_{h}$ for a population of planetesimals is going to depend on the structure
+with an internal density of 3 g cm$^{-3}$ ranging from 10 to 200 km in size.
+
+A physically realistic value of $e_{h}$ for a population of planetesimals is going to depend on the structure
 of the gaseous disk (which we will address in section \ref{sec:fulldisk}). However, the eccentricity
 dispersion will typically increase over time until $\left< v^{2} \right>^{1/2} = v_{esc}$ and this is
-often used to construct the initial conditions (e.g. \citet{barnes09}). Therefore, the curves in this figure
-should be interpreted as upper limits.}
+often used to construct the initial conditions (e.g. \cite{barnes09}). Therefore, the curves in this figure
+should be interpreted as upper limits.
 
@@
       timescale for a population of equal-mass planetesimals with an
-      internal density of 3 g cm$^{-3}$. \textbf{The dashed curves show 
+      internal density of 3 g cm$^{-3}$. The dashed curves show 
       the value of $e_{h}$ for which the random velocity dispersion is equal
-      to the escape velocity of the planetesimals for a range of sizes.} Only
+      to the escape velocity of the planetesimals for a range of sizes. Only
       in regions where $t_{relax} \gg t_{coll}$ can the velocity distribution 
@@
 of the bodies are both a function of time. Due to the interdependence
-of these quantities, it is not clear whether the \textbf{ratio between the relaxation and collision timescales will remain constant} as the
+of these quantities, it is not clear whether the ratio between the relaxation and collision timescales will remain constant as the
 oligarchs develop. In the case of the solar system, $t_{relax} \ll t_{coll}$ likely continued to remain true, otherwise runaway 
@@
 implies that the Hill sphere of a body becomes smaller than its physical size.
-\textbf{As an additional note, the Roche limit of the central body and the distance at which $\alpha = 1$ are equivalent for a rigid spherical body.
-Applying a hydrostatic correction to the Roche limit, $a_{Roche} \simeq 0.6 a_{\alpha = 1}$.
-This accretion mode should therefore be relevant for ring systems, which is a topic that deserves further study using high resolution N-body techniques.}
+As an additional note, the Roche limit of the central body and the distance at which $\alpha = 1$ are equivalent for a rigid spherical body.
+\textbf{After applying a hydrostatic correction to the Roche limit, $a_{Roche}$ is equivalent to 0.6 times this distance.} This accretion mode should therefore be relevant for \textbf{planetary} ring systems, which is a topic that deserves further study using high resolution N-body techniques.
 
@@
 \end{equation}
-where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body (see eq 4.1 of \citet{ida90}).
+where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body (see eq 4.1 of \cite{ida90}).
 Encounters between bodies inside of a distance of $r_{g}$ result in significant deflections of their trajectories.
@@
 In the case where $r_{g}$ is smaller than the size of a planetesimal, the gravitational focusing enhancement factor will be between 0 and 1 and the collision cross section is mostly set by the geometric value.
-\textbf{For very large values of $r_{g}$ ($\beta \ll 1$), the effective collision cross section is almost entirely set by gravitational scattering.}
+For very large values of $r_{g}$ ($\beta \ll 1$), the effective collision cross section is almost entirely set by gravitational scattering.
 
 These scaling considerations motivate the range of parameters we choose for the numerical experiments presented in the next section, where we aim to understand where and when runaway and oligarchic growth can operate.
+In figure \ref{fig:alpha_beta_diagram}, we show a schematic which relates $\alpha$ and $\beta$ to the geometry of a two-body encounter.
+For large values of $\alpha$, the Hill radius of a body (dashed circle) becomes comparable to its physical radius (solid circle).
+As $\beta$ increases, the trajectory of a body undergoing a flyby \textbf{is less affected by the encounter}.
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/diagram.png}
+    \caption{A diagram detailing how varying the values of $\alpha$ and $\beta$ affect the geometry of a two-body encounter.
+The solid circles represent the physical radius of a body and the dashed circles represent the Hill radius.
+As $\alpha$ is increased, the Hill radius and the physical radius become comparable in size.
+As $\beta$ is increased, the trajectory of a passing body for a fixed impact parameter is \textbf{less affected}.
+      \label{fig:alpha_beta_diagram}}
+\end{center}
+\end{figure}
 
@@
     \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
-    \caption{\textbf{Top:} The evolution of the ratio between the maximum and mean mass for the four simulations presented
+    \caption{Top: The evolution of the ratio between the maximum and mean mass for the four simulations presented
     in section \ref{sec:narrow}. The runaway growth phase can be identified by a positive trend in this ratio. For all values of 
-    $\alpha$, an increase in $\beta$ has the effect of delaying runaway growth. \textbf{Bottom: The evolution of the maximum
-    (solid lines) and mean (dashed lines) shown individually.}\label{fig:alpha_beta_evo}}
+    $\alpha$, an increase in $\beta$ has the effect of delaying runaway growth. Bottom: The evolution of the maximum
+    (solid lines) and mean (dashed lines) shown individually.\label{fig:alpha_beta_evo}}
 \end{center}
@@
 
-We use the tree-based N-body code {\sc ChaNGa}\footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}} to model the gravitational and collisional evolution of a swarm of planetesimals.
-{\sc ChaNGa} is written using the {\sc CHARM++} parallel programming language and has been shown to perform well on up to half a million processors \citep{menon15} and can follow the evolution of gravitationally interacting collections of up to billions of particles.
+We use the tree-based N-body code {\sc ChaNGa} to model the gravitational and collisional evolution of a swarm of planetesimals.
+{\sc ChaNGa} is written using the {\sc CHARM++} parallel programming language and has been shown to perform well on up to half a million processors \cite{menon15} and can follow the evolution of gravitationally interacting collections of up to billions of particles.
 Using a modified Barnes-Hut tree with hexadecapole expansions of the moments to approximate forces, {\sc ChaNGa} integrates the equations of motion using a kick-drift-kick leapfrog scheme.
 For all of the simulations presented in this paper, we use a node opening criteria of $\theta_{BH}$ = 0.7.
-Additional information about the code is available in \citep{jetley08,menon15}.
+Additional information about the code is available in \cite{jetley08,menon15}.
 
@@
 solid-body collision implementation in {\sc PKDGRAV}, which is
-described in \citet{richardson94} and \citet{richardson00}. To
+described in \cite{richardson94} and \cite{richardson00}. To
 summarize, imminent collisions are detected during the ``drift'' phase
@@
 body, which is given the center of mass position and velocity of the
-two \textbf{parents}. Resolving a collision can produce another imminent
+two parents. Resolving a collision can produce another imminent
 collision, so collisions are handled one-by-one and another full
@@
 more detailed description of the collision module in {\sc ChaNGa}, see
-\citep{wallace19}.
+\cite{wallace19}.
 Particles are advanced on individual timesteps chosen as a
@@
 We begin by 
-\textbf{exploring the outcome of planetesimal accretion in different parts of the $\left( \alpha, \beta \right)$
-parameter space.} The choices of $\alpha$ and $\beta$ are motivated by two questions raised in section \ref{sec:theory}. 1) Does
+exploring the outcome of planetesimal accretion in different parts of the $\left( \alpha, \beta \right)$
+parameter space. The choices of $\alpha$ and $\beta$ are motivated by two questions raised in section \ref{sec:theory}. 1) Does
 runaway growth still operate when the condition that $v \ll v_{esc}$
@@
 and $\beta$ are varied individually. 4000 planetesimals with
-individual masses of \textbf{$8.37 \times 10^{-5} M_{\earth}$ } are placed with semimajor
-axes drawn \textbf{from a uniform distribution} between 0.95 and 1.05 AU about a 1 $M_{\odot}$
-star. \textbf{In total, the disk contains $\sim$ 0.33 $M_{\earth}$ of material.} The argument of perihelion, $\omega$, longitude of ascending node,
+individual masses of $8.37 \times 10^{-5} M_{\earth}$ are placed with semimajor
+axes drawn from a uniform distribution between 0.95 and 1.05 AU about a 1 $M_{\odot}$
+star. In total, the disk contains $\sim$ 0.33 $M_{\earth}$ of material. The argument of perihelion, $\omega$, longitude of ascending node,
 $\Omega$, and mean anomaly, M, for each body is drawn from a uniform
@@
 from a Rayleigh distribution with
-$\left< i^{2} \right> = 1/2 \left< e^{2} \right>$ \citep{ida93a}.
+$\left< i^{2} \right> = 1/2 \left< e^{2} \right>$ \cite{ida93a}.
 
 In the ``fiducial'' case, we give the bodies a bulk density of 3 g
-cm$^{-3}$ \textbf{(for a radius of 341 km)}, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
-These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth.
+cm$^{-3}$ (for a radius of 341 km), and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
+These parameters are chosen to match the initial conditions of \cite{kokubo98}, which gave rise to oligarchic growth.
 To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by 
-a factor of $\sim$ 7100, which produces $\alpha = 1$. \textbf{This corresponds to a bulk density of $4.2 \times 10^{-4}$ g cm$^{-3}$ and a radius of 6,500 km. 
+a factor of $\sim$ 7100, which produces $\alpha = 1$. This corresponds to a bulk density of $4.2 \times 10^{-4}$ g cm$^{-3}$ and a radius of 6,500 km. 
 Although this is most certainly unphysical, the purpose of this modification is to have a planetesimal completely fills its Hill sphere so that no strong 
-gravitational scattering should occur.} To vary $\beta$, the eccentricity dispersion is increased. For the high-$
+gravitational scattering should occur. To vary $\beta$, the eccentricity dispersion is increased. For the high-$
 \beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
-\textbf{This is the largest value of $\beta$ that permits a particle at 1 AU to still have an apocenter and pericenter distance that lies within the boundaries of the disk.
-This choice of $\beta$ places the system firmly in the $v > v_{esc}$ regime, while still allowing growth to occur in a reasonable number of timesteps.}
+This is the largest value of $\beta$ that permits a particle at 1 AU to still have an apocenter and pericenter distance that lies within the boundaries of the disk.
+This choice of $\beta$ places the system firmly in the $v > v_{esc}$ regime, while still allowing growth to occur in a reasonable number of timesteps.
 
@@
 snapshots from each of the 4 simulations. The size of the points
-indicates the relative masses of the bodies. Only \textbf{with small
-$\alpha$ (case c, d)} does a residual population of dynamically hot planetesimals
-develop. The lack of high eccentricity planetesimals \textbf{(relative to the protoplanets)} in the large
-$\alpha$ \textbf{(case a, b) simulations} suggests that most encounters result in accretion
-rather than scattering. \textbf{For} large $\beta$ \textbf{(case b, d)}, the \textbf{growing} protoplanets
+indicates the relative masses of the bodies. Only with small
+$\alpha$ (case c, d) does a residual population of dynamically hot planetesimals
+develop. The lack of high eccentricity planetesimals (relative to the protoplanets) in the large
+$\alpha$ (case a, b) simulations suggests that most encounters result in accretion
+rather than scattering. For large $\beta$ (case b, d), the growing protoplanets
 and end up in a dynamically cool state,
-\textbf{relative} with the initial conditions. This is due to kinetic energy 
+relative with the initial conditions. This is due to kinetic energy 
 being lost as particles inelastically collide. One last point we note
 is the difference between the eccentricities of protoplanets in the 
-large $\alpha$, large $\beta$ \textbf{(case b)} and the small $\alpha$,
-large $\beta$ \textbf{(case d) simulation}. The dynamically cooler result of the \textbf{former} case
+large $\alpha$, large $\beta$ (case b) and the small $\alpha$,
+large $\beta$ (case d) simulation. The dynamically cooler result of the former case
 is likely due to the dominant role that inelastic collisions play here.
 
-In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}. In addition to 
-leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce \textbf{embryos that are a factor of a few larger}. Despite the 
+In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four simulations. In addition to 
+leaving fewer residual planetesimals, the large $\alpha$ (case a, b) simulations produce embryos that are a factor of a few larger. Despite the 
 vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) 
-appears to have no significant effect on the final distribution of masses. \textbf{For reference, the boundary between shear and dispersion-dominated 
+appears to have no significant effect on the final distribution of masses. For reference, the boundary between shear and dispersion-dominated 
 encounters ($e_{h}$ = 1) lies around e = $4 \times 10^{-4}$ for the planetesimal mass we have chosen. The eccentricity at which $\left< v^{2} \right>^{1/2} = 
-v_{esc}$ for the planetesimals is around $10^{-2}$.}
+v_{esc}$ for the planetesimals is around $10^{-2}$.
 
@@
 masses in each simulation. The ratio $M/\left< m \right>$ is plotted
-in \textbf{the top panel of} figure \ref{fig:alpha_beta_evo}. \textbf{Here}, a positive slope
+in the top panel of figure \ref{fig:alpha_beta_evo}. Here, a positive slope
 indicates that the quantities are diverging (i.e.
 the growth rate is accelerating with mass). This behavior is
-evident in all four cases \textbf{although the small $\alpha$ simulations eventually reach a stage where the curves
- turn over as the planetesimal supply depletes.}. Even with a large
+evident in all four cases although the small $\alpha$ simulations eventually reach a stage where the curves
+ turn over as the planetesimal supply depletes. Even with a large
 $\beta$, where the effective collision cross section is
@@
 gravity is the dominant force in the system. For large $\alpha$
-\textbf{(case a, b)}, the curves in this figure eventually turn over and begin to decline.
-\textbf{In the bottom panel of figure \ref{fig:alpha_beta_evo}, we separately show the evolution of
+(case a, b), the curves in this figure eventually turn over and begin to decline.
+In the bottom panel of figure \ref{fig:alpha_beta_evo}, we separately show the evolution of
 the maximum (solid lines) and mean (dashed lines) mass for each case. Here, it is evident
@@
 the growth timescale lengthens due to the planetesimal surface density decreasing and the residual bodies being scattered onto high
-eccentricity orbits with negligible gravitational focusing factors. Many more timesteps, however, would be required to reach this point.}
+eccentricity orbits with negligible gravitational focusing factors. Many more timesteps, however, would be required to reach this point.
 
@@
 facilitate oligarchic growth. In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and 
-embryos \citep{weidenschilling89, ida90}.
-\textbf{When $\alpha \ll 1$, the Hill sphere of a body is mostly empty space and the majority of close encounters result in viscous stirring, rather than accretion.
-In the opposite regime,} we
+embryos \cite{weidenschilling89, ida90}.
+When $\alpha \ll 1$, the \textbf{planetesimal fills only a small portion of its Hill sphere} and the majority of close encounters result in viscous stirring, rather than accretion.
+In the opposite regime, we
 observe that runaway growth still occurs, but nearly all of the planetesimals are consumed by the forming protoplanets, rather 
 than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of 
-planet formation \citep{kokubo98, kokubo00}.
+planet formation \cite{kokubo98, kokubo00}.
 
@@
 typically begin with a chain of neatly-spaced, isolation mass 
-(see \citet{kokubo00} eq. 20) protoplanets, it is pertinent to determine 
+(see \cite{kokubo00} eq. 20) protoplanets, it is pertinent to determine 
 whether the high $\alpha$ growth mode we revealed
@@
 Given the dearth of short-period terrestrial planets observed around M stars (e.g.
-TRAPPIST-1 \textbf{\citep{gillon16, gillon17, agol21}}), we chose to model the evolution of a series of wide planetesimal disks, which span from 1 to 100 days in orbital period, orbiting a late-type M star of mass 0.08 $M_{\odot}$.
+TRAPPIST-1 \cite{gillon16, gillon17, agol21}), we chose to model the evolution of a series of wide planetesimal disks, which span from 1 to 100 days in orbital period, orbiting a late-type M star of mass 0.08 $M_{\odot}$.
 For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this orbital period range corresponds to $\alpha \in (0.7, 0.05)$.
@@
 cm$^{-2}$ is the surface density of the minimum-mass solar nebula
-\citep[MMSN]{hayashi81} at 1 AU, $A$ is an enhancement factor and $\delta$ is the power law index.
+\cite[MMSN]{hayashi81} at 1 AU, $A$ is an enhancement factor and $\delta$ is the power law index.
 In the first case (fdHi), we model a disk that follows a MMSN power law slope ($\delta$ = 1.5), with the overall normalization enhanced by a factor of 100.
-This choice of normalization for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \citep{hansen12}.
-\textbf{The most current planetesimal formation models all involve streaming instabilities triggered by solid material concentrating at preferential locations in the disk.
-This can occur via zonal flows \citep{johansen2009b, simon12}, vortices \citep{klahr03}, or through mechanisms that produce a pressure bump in the gas disk, such as an ionization \citep{lyra08} or condensation front \citep{brauer08b, drkazowska13}, or even the perturbations from an existing planet \citep{shibaike20}.
-\citet{drkazowska18} showed that evolution of the snow line boundary can cause planetesimal formation over a significant area of the disk, producing mass concentrations at least as large as the ones we use here.
-We argue that this is a particularly attractive mechanism for widespread planetesimal formation around low-mass stars, as their extreme pre-main sequence evolution is particularly conducive to significant movement of the condensation fronts \citep{baraffe15}.}
+This choice of normalization for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \cite{hansen12}.
+\textbf{Many recent planetesimal formation models invoke streaming instabilities, which first require sufficiently large amounts of solid material concentrating} at preferential locations in the disk.
+This can occur via zonal flows \cite{johansen2009b, simon12}, vortices \cite{klahr03}, or through mechanisms that produce a pressure bump in the gas disk, such as an ionization \cite{lyra08} or condensation front \cite{brauer08b, drkazowska13}, or even the perturbations from an existing planet \cite{shibaike20}.
+\cite{drkazowska18} showed that evolution of the snow line boundary can cause planetesimal formation over a significant area of the disk, producing mass concentrations at least as large as the ones we use here.
+We argue that this is a particularly attractive mechanism for widespread planetesimal formation around low-mass stars, as their extreme pre-main sequence evolution is particularly conducive to significant movement of the condensation fronts \cite{baraffe15}.
 
 Additionally, we vary the power law index (fdHiShallow, fdHiSteep) and overall normalization (fdLo) of $\Sigma(r)$.
-\textbf{Although there is no way to reliably measure the uncertainty on the MMSN power law slope, \citet{chiang13} applied a similar analysis to a sample of Kepler multiplanet systems and found a variation of $\sim 0.2$.
-Sub-millimeter observations of the outer regions of cold protoplanetary disks find that $\delta$ can be as low as 0.5 \citep{mundy00, andrews09, andrews10}.
-Therefore, we vary $\delta$ by a value of $1.0$ relative to the MMSN value for the fdHiShallow and fdHiSteep simulations.}
-
-In all cases, the eccentricities and inclinations of the bodies are randomly drawn from a Rayleigh distribution, with $\left< e^{2} \right>^{1/2} = 2\left<i^{2} \right>^{1/2} = e_{eq}$ \citep{ida93}.
-\textbf{Following \citet{kokubo98},} the value of $e_{eq}$ is chosen such that the timescales for viscous stirring and aerodynamic gas drag on the planetesimals are in equilibrium.
-\textbf{Although this approach assumes that these two mechanisms are in balance, there is nothing preventing planetesimal accretion from getting underway before the disk is sufficiently hot to be limited by gas drag.
-However, as we showed in the previous section, the initial dynamical state of the planetesimals does not seem to affect the outcome of accretion, so it is safe to assume that the resulting distribution of protoplanets would remain unchanged had we started with a colder disk.} The viscous stirring timescale is given by \citet{ida93} as
+Although there is no way to reliably measure the uncertainty on the MMSN power law slope, \cite{chiang13} applied a similar analysis to a sample of Kepler multiplanet systems and found a variation of $\sim 0.2$.
+Sub-millimeter observations of the outer regions of cold protoplanetary disks find that $\delta$ can be as low as 0.5 \cite{mundy00, andrews09, andrews10}.
+Therefore, we vary $\delta$ by a value of $1.0$ relative to the MMSN value for the fdHiShallow and fdHiSteep simulations.
+
+In all cases, the eccentricities and inclinations of the bodies are randomly drawn from a Rayleigh distribution, with $\left< e^{2} \right>^{1/2} = 2\left<i^{2} \right>^{1/2} = e_{eq}$ \cite{ida93}.
+Following \cite{kokubo98}, the value of $e_{eq}$ is chosen such that the timescales for viscous stirring and aerodynamic gas drag on the planetesimals are in equilibrium.
+Although this approach assumes that these two mechanisms are in balance, there is nothing preventing planetesimal accretion from getting underway before the disk is sufficiently hot to be limited by gas drag.
+However, as we showed in the previous section, the initial dynamical state of the planetesimals does not seem to affect the outcome of accretion, so it is safe to assume that the resulting distribution of protoplanets would remain unchanged had we started with a colder disk.
+The viscous stirring timescale is given by \cite{ida93} as
 
@@
 \end{equation}
-where $\Omega$, $a$ and $e$ are the orbital frequencies, semi-major axes and eccentricities of the individual planetesimals, \textbf{respectively}.
-In the Stokes regime, \textbf{where the mean-free path of the gas is much smaller than the solid particles, the gas can be treated as a fluid and} the drag timescale is given by \citet{adachi76} as
+where $\Omega$, $a$ and $e$ are the orbital frequencies, semi-major axes and eccentricities of the individual planetesimals, respectively.
+In the Stokes regime, where the mean-free path of the gas is much smaller than the solid particles, the gas can be treated as a fluid and the drag timescale is given by \cite{adachi76} as
+
 \begin{equation}\label{eq:ts_stokes}
@@
 \end{equation}
+
 where $C_{D}$ is a drag coefficient of order unity, $\rho_{g}$ is the local gas volume density and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal.
@@
 where $\Sigma_{g}$ is the gas surface density (taken to be
-240 times the solid surface density \citep{hayashi81}, $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
+240 times the solid surface density \cite{hayashi81}, $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
 The sound speed profile is given by $c_{s} = \sqrt{k_{B} T(r) / \left( \mu m_{H} \right)}$, where $k_{B}$ is Boltzmann's constant, $T(r) = T_{0} \left( r / 1 \textrm{AU} \right)^{-q}$, $\mu = 2.34$ and $m_{h}$ is the mass of a hydrogen atom.
-For a protoplanetary disk around a typical M star, $T_{0} = 148$ K and $q$ = 0.58 \citep{andrews05}.
+For a protoplanetary disk around a typical M star, $T_{0} = 148$ K and $q$ = 0.58 \cite{andrews05}.
 
@@
 
-\noindent where $v_{k}$ is the local Keplerian velocity \textbf{(see eq. 4.30 of \citet{armitage20})}. As in section
+\noindent where $v_{k}$ is the local Keplerian velocity (see eq. 4.30 of \cite{armitage20}). As in section
 \ref{sec:narrow}, the argument of perihelion $\omega$, longitude of
@@
 
-\textbf{One should note that this choice for the gas disk profile almost certainly does not capture the wide range of possibilities in real planet-forming disks. 
+One should note that this choice for the gas disk profile almost certainly does not capture the wide range of possibilities in real planet-forming disks. 
 On one hand, a larger initial gas surface density could act to completely remove solids via radial drift, rendering in-situ accretion of solids impossible. On the 
@@
 planetesimals should be close to their mutual escape velocity. As we showed in section \ref{sec:narrow}, the initial dynamical state of the solids seems to 
-have a very minimal effect on the final outcome of planetesimal accretion. In a similar vein to \citet{hansen12}, we choose to use a MMSN-like profile for the 
+have a very minimal effect on the final outcome of planetesimal accretion. In a similar vein to \cite{hansen12}, we choose to use a MMSN-like profile for the 
 gas disk and instead vary the solid surface density profile to capture the range of mechanisms that might have acted to facilitate planetesimal formation in the 
-first place.}
+first place.
 
@@
 due to the the gas disk is applied to each particle, following the
-prescription described in section 2.2.1 of \citet{morishima10}. For
-the initial mass planetesimals, the \textbf{Stokes number
+prescription described in section 2.2.1 of \cite{morishima10}. For
+the initial mass planetesimals, the Stokes number
   ($\textrm{St} = t_{s} \Omega$) at the inner and outer disk edge is
@@
   by it.
-Because $t_{s} \sim m^{1/3}$, the Stokes number grows as planetesimal accretion proceeds, and the drag force plays an increasingly minor role.} Although the aerodynamic gas drag is not expected to significantly alter the final protoplanet distribution, we include its effects here to be self-consistent with the initial conditions, which were constructed by balancing the effects of viscous stirring with gas drag.
+Because $t_{s} \sim m^{1/3}$, the Stokes number grows as planetesimal accretion proceeds, and the drag force plays an increasingly minor role.
+Although the aerodynamic gas drag is not expected to significantly alter the final protoplanet distribution, we include its effects here to be self-consistent with the initial conditions, which were constructed by balancing the effects of viscous stirring with gas drag.
 
@@
 based on their most recently calculated gravitational
-acceleration. \textbf{This scheme is used on almost all works using ChaNGa,
-and is common among large-scale simulation codes.}
+acceleration. This scheme is used on almost all works using ChaNGa,
+and is common among large-scale simulation codes.
 
@@
 boundaries, while also minimizing the number of `skipped' collisions.
-\textbf{In the case of the fdHi simulation, only about 20 collisions out of an eventual 900,000 are ignored.
+In the case of the fdHi simulation, only about 20 collisions out of an eventual 900,000 are ignored.
 To verify that this timestepping scheme does not affect protoplanet growth, we tested an annulus of growing planetesimals with both fixed steps and our two-phase variable timestepping scheme.
-The results of these tests are shown in appendix \ref{sec:rung_ecc}.}
+The results of these tests are shown in appendix \ref{sec:rung_ecc}.
 
@@
       the final masses of the bodies. The dashed line indicates the feeding
-      zone size expected for bodies on circular orbits. \textbf{For the shorter period bodies,
+      zone size expected for bodies on circular orbits. For the shorter period bodies,
       the feeding zone size exceeds this expected value, which indicates that oligarchic growth is
-      not operating here. This boundary occurs near roughly 60 d in orbital period.}\label{fig:fulldisk_e_m}}
+      not operating here. This boundary occurs near roughly 60 d in orbital period.\label{fig:fulldisk_e_m}}
 \end{center}
@@
     \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi 
-    simulation. Each curve represents a radial slice of the disk. \textbf{The time is measured in units of the local accretion 
-    timescale at the center of each radial zone. The colors represent the orbital period at the center of each zone.}\label{fig:pl_frac_time}}
+    simulation. Each curve represents a radial slice of the disk. The time is measured in units of the local accretion 
+    timescale at the center of each radial zone. The colors represent the orbital period at the center of each zone.\label{fig:pl_frac_time}}
 \end{center}
@@
     simulations listed in table \ref{tab:sim_properties}.
-\textbf{For the fdHi, fdHiSteep and fdHiShallow simulations, we have included the results from five separate iterations of the simulations, each using a different random number seed.} The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$.
+For the fdHi, fdHiSteep and fdHiShallow simulations, we have included the results from five separate iterations of the simulations, each using a different random number seed.
+The horizontal dashed line indicates $\tilde{b} = 2 \sqrt{3}$.
 Despite the
@@
 inside-out fashion, with the outermost regions of the disk completing
-the protoplanet assembly phase last \textbf{(as an example, see figure 1 of \citet{kokubo02}}. This radial timescale dependence is not typically
-accounted for in planet formation simulations \textbf{a notable exception being \citet{emsenhuber21a, emsenhuber21b}}, and appears to be an
+the protoplanet assembly phase last (as an example, see figure 1 of \cite{kokubo02}. This radial timescale dependence is not typically
+accounted for in planet formation simulations a notable exception being \cite{emsenhuber21a, emsenhuber21b}, and appears to be an
 important component to forming realistic solar system analogs
-\citep{clement20}. As with the narrow annulus simulations, we stop the
+\cite{clement20}. As with the narrow annulus simulations, we stop the
 integration once the masses of protoplanets in the outermost region of
@@
 indicates the relative mass of the bodies. In the bottom panel, the
-final masses of the bodies (in units of feeding zone size \textbf{$\tilde{b}$}) are shown
+final masses of the bodies (in units of feeding zone size $\tilde{b}$) are shown
 as a function of orbital period.
-\textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.
-In other words, $\tilde{b}$ is describing the size of the annulus that must be cut out of the planetesimal disk in order to produce a protoplanet of the current mass.} By plotting the derived value of $
+The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.
+In other words, $\tilde{b}$ is describing the size of the annulus that must be cut out of the planetesimal disk in order to produce a protoplanet of the current mass.
+By plotting the derived value of $
 \tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
-clearly visible. \textbf{The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{naka88} is shown by the
-horizontal dashed line.} In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
+clearly visible. The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \cite{naka88} is shown by the
+horizontal dashed line. In typical oligarchic growth simulations \cite{kokubo98}, protoplanets tend 
 to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
@@
 
-A qualitative shift in the protoplanet and planetesimal distribution is visible \textbf{inside of} $\sim$ 60 days. Interior to this location, there are 
+A qualitative shift in the protoplanet and planetesimal distribution is visible inside of $\sim$ 60 days. Interior to this location, there are 
 very few remaining planetesimals and the embryos formed have larger feeding zones. Exterior to the boundary, the residual 
@@
 region of the disk should lower the overall eccentricity of the protoplanets there. This behavior is not immediately apparent in the 
-top panel of figure \ref{fig:fulldisk_e_m}. \textbf{In fact, the opposite appears to be true.} There are, however, a couple of factors in the wide disk simulations that could make this 
+top panel of figure \ref{fig:fulldisk_e_m}. In fact, the opposite appears to be true. There are, however, a couple of factors in the wide disk simulations that could make this 
 extra dynamical cooling mechanism difficult to see. Firstly, the initial eccentricity distributions of the inner and outer disk are 
 different because of the dependence of the viscous stirring and gas drag timescales on orbital period.
-\textbf{The mean eccentricity at the outer disk edge is 4x larger than at the inner disk edge.} Additionally, the
+The mean eccentricity at the outer disk edge is 4x larger than at the inner disk edge.
+Additionally, the
 protoplanet formation timescales for the inner and outer disk are vastly different, making a comparison between these regions at 
 the same moment in time somewhat inappropriate.
-\textbf{A quick back of the envelope calculation yields $\left< e^2 \right>^{1/2} = 0.05$ for a population of $\sim 1 M_{\earth}$ bodies with a random velocity dispersion equal to their mutual escape velocity.
-It is therefore likely the case that the innermost protoplanets have had ample time to self-stir.}
-
-To ensure that the boundary seen \textbf{around} 60 days in orbital period is not
+A quick back of the envelope calculation yields $\left< e^2 \right>^{1/2} = 0.05$ for a population of $\sim 1 M_{\earth}$ bodies with a random velocity dispersion equal to their mutual escape velocity.
+It is therefore likely the case that the innermost protoplanets have had ample time to self-stir.
+
+To ensure that the boundary seen around 60 days in orbital period is not
 simply a transient product of the inside-out growth throughout the
@@
 $\sigma/\Sigma$ is plotted as a function of time in 10 orbital period
-bins, each with a width of 10 days. \textbf{To determine whether the evolution of the planetesimal surface density behaves self-similarly across the disk,
-we normalize the time values in each bin by the local accretion timescale at the beginning of the simulation, which is given by}
+bins, each with a width of 10 days. To determine whether the evolution of the planetesimal surface density behaves self-similarly across the disk,
+we normalize the time values in each bin by the local accretion timescale at the beginning of the simulation, which is given by
 
@@
 
-\noindent \textbf{where we have assumed the local number density of particles n is set by the surface density and the local scale height of the disk (see section \ref{sec:theory}).
-The effective collision cross section is set by gravitational focusing and is given by equation \ref{eq:gravfocus}.}
-
-\textbf{The color of the curves indicate the orbital period bin which is being measured. From about 40 to 100 days in orbital period, the planetesimal surface 
+\noindent where we have assumed the local number density of particles n is set by the surface density and the local scale height of the disk (see section \ref{sec:theory}).
+The effective collision cross section is set by gravitational focusing and is given by equation \ref{eq:gravfocus}.
+
+The color of the curves indicate the orbital period bin which is being measured. From about 40 to 100 days in orbital period, the planetesimal surface 
 density follows a similar trajectory as accretion proceeds. Interior to about 40 days, $\sigma$ actually decays more slowly. In other words, growth is actually 
@@
 \ref{sec:assembly}, we examine the assembly history of the embryos and show that there is much less of a preference for planetesimal-embryo collisions at 
-short period as well.}
+short period as well.
 
@@
 planetesimal population entirely depletes. In the outer disk, dynamical friction between the embryos and planetesimals 
-eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals. \textbf{It 
+eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals. It 
 should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle 
-onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent \textbf{($2\sqrt{3}/10 \simeq 0.3$)} of the planetesimals
-should remain out of reach of the protoplanets.}
+onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent ($2\sqrt{3}/10 \simeq 0.3$) of the planetesimals
+should remain out of reach of the protoplanets.
 
@@
 contains a bimodal population of planetesimals and embryos, with a clear separation in eccentricity between the two. Despite 
-having significantly different masses, the \textbf{semimajor axis-eccentricity} distributions of the planetary embryos formed in all simulations \textbf{are} remarkably similar. This 
+having significantly different masses, the semimajor axis-eccentricity distributions of the planetary embryos formed in all simulations are remarkably similar. This 
 is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which 
@@
 \tilde{b}$ (see equation \ref{eq:iso}).
-\textbf{To make the trend between $\tilde{b}$ and orbital period more clear, we ran four more versions of the fdHi, fdHiSteep and fdHiShallow simulations using different random number seeds and included these in the figure as well.}
+To make the trend between $\tilde{b}$ and orbital period more clear, we ran four more versions of the fdHi, fdHiSteep and fdHiShallow simulations using different random number seeds and included these in the figure as well.
 As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) is the  
 feeding zone width that a body on a circular orbit will have. In all four simulations, the feeding zone width exceeds the 
-minimum value in the inner disk and approaches $2 \sqrt{3}$ \textbf{around $\sim$ 40 to 60 days}. The orbital periods at which this transition 
+minimum value in the inner disk and approaches $2 \sqrt{3}$ around $\sim$ 40 to 60 days. The orbital periods at which this transition 
 occurs are quite similar between simulations, despite the vastly different solid surface density profiles used. This indicates that 
@@
 traced between each planetary embryo and the initial
-planetesimals. \textbf{For the fdHi, fdHiSteep and fdHiShallow
+planetesimals. For the fdHi, fdHiSteep and fdHiShallow
   simulations, protoplanets gain a factor of $\sim 10^6$ in mass
@@
 For the fdLo simulation, this growth factor is nearly a thousand times smaller, which produces rather shallow and noisy collision histories.
-For this reason, we choose to exclude the fdLo simulation from our analysis in this section.}
+For this reason, we choose to exclude the fdLo simulation from our analysis in this section.
 
@@
 for cosmological simulations of galaxy formation, we divide growth events for
-a given body into ``major'' and ``minor'' mergers \citep{kauffmann93, murali02, lhullier12}. 
+a given body into ``major'' and ``minor'' mergers \cite{kauffmann93, murali02, lhullier12}. 
 Here, we define minor events as any collision involving an initial mass 
 planetesimal, while major events consist of a merger between any two larger bodies.
-\textbf{In figure \ref{fig:minor_frac}, we retrieve the collision events for all bodies in all five iterations of the fdHi, fdHiSteep and fdHiShallow
+In figure \ref{fig:minor_frac}, we retrieve the collision events for all bodies in all five iterations of the fdHi, fdHiSteep and fdHiShallow
 simulations and plot the total mass fraction attained through minor merger (smooth accretion) events as a function of the final mass of the body. Here, we define a minor merger
@@
 Beyond $\sim$ 20 to 30 days in orbital period, minor mergers make up a significant fraction of the final mass of a body.
-Interior to this, the smooth accretion fraction drops significantly and the mass contribution to minor mergers can vary by over an order of magnitude.}
+Interior to this, the smooth accretion fraction drops significantly and the mass contribution to minor mergers can vary by over an order of magnitude.
 
@@
     \includegraphics[width=0.5\textwidth]{figures/minor_frac.png}
-    \caption{\textbf{For all bodies with $m > 100 m_{0}$ at the end of the high surface density simulations}, the fraction of their total mass attained through mergers with initial mass planetesimals (smooth accretion) as a function of total mass.
-\textbf{Colors indicate the orbital periods of the bodies in the final simulation snapshot.
-Bodies interior to $\sim$ 20 to 30 days attain up to an order of magnitude less of their mass through minor merger events, while accretion of planetesimals plays a much more significant role at longer orbital periods.}\label{fig:minor_frac}}
+    \caption{For all bodies with $m > 100 m_{0}$ at the end of the high surface density simulations, the fraction of their total mass attained through mergers with initial mass planetesimals (smooth accretion) as a function of total mass.
+Colors indicate the orbital periods of the bodies in the final simulation snapshot.
+Bodies interior to $\sim$ 20 to 30 days attain up to an order of magnitude less of their mass through minor merger events, while accretion of planetesimals plays a much more significant role at longer orbital periods.\label{fig:minor_frac}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
-    \caption{\textbf{The relative separation between the final period
+    \caption{The relative separation between the final period
         of a body and the mean orbital periods of its accretion zone at the end of the fdHi, fdHiSteep and fdHiShallow simulations.
 The marker type and color denotes the simulation used, while the marker sizes indicate the relative masses of bodies.
-In each case, all five iterations of the simulations are plotted simultaneously.}\label{fig:acc_zones}}
+In each case, all five iterations of the simulations are plotted simultaneously.\label{fig:acc_zones}}
 \end{center}
@@
 The variation in smooth accretion fraction with mass for the short period bodies suggests that the planetesimal and embryo populations interact differently than those in the outer disk.
-Exterior to the accretion mode boundary, the growing embryos continue to accrete planetesimals \textbf{while avoiding each other} as they near their final mass.
-Inside the boundary, however, \textbf{any and all bodies collide with each other, and the occasional embryo-embryo collision tends to dominate growth and drive down the smooth accretion fraction.} Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion \citep{kokubo98}, and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
+Exterior to the accretion mode boundary, the growing embryos continue to accrete planetesimals while avoiding each other as they near their final mass.
+Inside the boundary, however, any and all bodies collide with each other, and the occasional embryo-embryo collision tends to dominate growth and drive down the smooth accretion fraction.
+Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion \cite{kokubo98}, and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
 As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zone size predicted by an oligarchic growth model.
@@
 figure \ref{fig:acc_zones}.
-\textbf{Here, we measure the initial orbital period distribution of bodies used to construct each embryo and calculate its mean $\left<  P_{acc} \right>$.
+Here, we measure the initial orbital period distribution of bodies used to construct each embryo and calculate its mean $\left<  P_{acc} \right>$.
 Point sizes indicate the relative final masses of bodies.
@@
 On the other hand, bodies further from the dashed line must have experienced a strong gravitational scattering event during or after their accretion has completed.
-For all of the high surface density simulations, the accretion zones and present positions of the embryos appear to diverge beyond $\sim$ 20 days in orbital period.}
-
-\textbf{Coupled with the strong decrease in smooth accretion fraction for bodies in this region (seen in figure \ref{fig:minor_frac}), it appears as if the relative importance of collisions and gravitational scattering seems to shift around $\sim$ 20 days.
+For all of the high surface density simulations, the accretion zones and present positions of the embryos appear to diverge beyond $\sim$ 20 days in orbital period.
+
+Coupled with the strong decrease in smooth accretion fraction for bodies in this region (seen in figure \ref{fig:minor_frac}), it appears as if the relative importance of collisions and gravitational scattering seems to shift around $\sim$ 20 days.
 For the shortest period bodies, growth events are sudden and stochastic, often involving collisions between bodies of comparable mass.
@@
 In the outer disk, these encounters tend to result in a scattering event which moves bodies away from their initial feeding zones.
-We find that the accretion zone shapes for the longer period bodies are also much more smooth and unimodal, which suggests that scattering tends to occur after accretion has largely completed.}
+We find that the accretion zone shapes for the longer period bodies are also much more smooth and unimodal, which suggests that scattering tends to occur after accretion has largely completed.
 
@@
 oligarchic growth and the highly-efficient short period accretion
-region lies \textbf{between 40 and 70} days in orbital period. As discussed in section \ref{sec:sizeandhill}, the mode of accretion is
+region lies between 40 and 70 days in orbital period. As discussed in section \ref{sec:sizeandhill}, the mode of accretion is
 set entirely by the local value of $\alpha$, which scales with both
@@
 equation \ref{eq:alpha}). Because we chose to artificially inflate the
-collision cross section of the particles in our simulations \textbf{by a factor of $f$}, the bulk densities
+collision cross section of the particles in our simulations by a factor of $f$, the bulk densities
 of the particles are reduced, and the accretion boundary is shifted outward.
@@
 presented in this paper use a collision cross section enhancement factor of 6, which moves the boundary outward in orbital
-period by a factor of approximately 15 \textbf{(For a fixed value of $\alpha$, equation \ref{eq:alpha} gives $a \sim r_{pl} \sim f$ and therefore $P_{orbit} \sim f^{-3/2}$)}.
-One would therefore expect the accretion boundary to lie \textbf{between 3 and 5} days in orbital period
+period by a factor of approximately 15 (For a fixed value of $\alpha$, equation \ref{eq:alpha} gives $a \sim r_{pl} \sim f$ and therefore $P_{orbit} \sim f^{-3/2}$).
+One would therefore expect the accretion boundary to lie between 3 and 5 days in orbital period
 for 3 g $cm^{-3}$ bodies.
@@
 enhancement greatly reduces the size of the non-oligarchic region, it still should be expected to cover a portion of the
-disk where planetesimals might be expected to form \textbf{\citep{mulders18}} for a wide range of $\rho_{pl}$.
+disk where planetesimals might be expected to form \cite{mulders18} for a wide range of $\rho_{pl}$.
 
@@
     bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the location at 
-    which $\tilde{b}$ exceeds $2 \sqrt{3}$ \textbf{This is highlighted by the vertical dashed lines.}. The shaded region
+    which $\tilde{b}$ exceeds $2 \sqrt{3}$ This is highlighted by the vertical dashed lines. The shaded region
     in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
@@
     indicating relative mass. The blue points represent the initial state of the simulations. The bottom panel compares the final 
-    \textbf{differential} mass distributions of the bodies. \label{fig:frag_ecc}}
+    differential mass distributions of the bodies. \label{fig:frag_ecc}}
 \end{center}
@@
 perfect merger might result in overly efficient growth, particularly in the innermost region of the disk where the encounter 
-velocities are largest. \textbf{Given that we have just shown that a distinctly non-oligarchic growth mode emerges in the inner disk when the 
+velocities are largest. Given that we have just shown that a distinctly non-oligarchic growth mode emerges in the inner disk when the 
 collision timescale is short relative to the gravitational scattering timescale, one might be concerned that a more realistic collision model would act 
@@
 operates, more realistic collision models have been shown to simply lengthen the timescale for planetary embryos to form 
-\citep{wetherill93, leinhardt05}.} A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic 
-model (see \citet{leinhardt12}). However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of 
+\cite{wetherill93, leinhardt05}. A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic 
+model (see \cite{leinhardt12}). However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of 
 bodies to bounce is too expensive to model, even with {\sc ChaNGa}.
@@
 Because the accretion outcome is all or nothing, this model should restrict growth more than a partial accretion model 
-\citep{leinhardt12}. Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner 
+\cite{leinhardt12}. Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner 
 disk's planetesimal accretion phase, and so a more realistic partial accretion model should do the same.
@@
 Although the bounce-merge simulation takes much longer to reach the same phase of evolution, the resulting orbital properties
-are indistinguishable from the merger-only case. \textbf{Performing a Kolmogrov-Smirnov test on the two mass distributions yields
+are indistinguishable from the merger-only case. Performing a Kolmogrov-Smirnov test on the two mass distributions yields
 a p-value of $2 \times 10^{-5}$, which tells us that the two mass distributions are quite firmly statistically different. If we remove
-the initial mass planetesimals, a KS test yields a p-value of 0.1. We conclude that the embryo populations are nearly indistinguishable,
-while the bounce-merge model produces a small amount of residual planetesimals.}
+the initial mass planetesimals, a KS test yields a p-value of 0.1, \textbf{which suggests that the distributions are statistically similar.
+Because the remaining planetesimals only make up about 0.1 percent of the total mass of the disk,} we conclude that the embryo populations are nearly indistinguishable, while the bounce-merge model produces a small amount of residual planetesimals.
 
@@
 
-As a final note, \citet{childs22} found that a more realistic collision model also enhanced radial mixing in their simulations. Upon 
+As a final note, \cite{childs22} found that a more realistic collision model also enhanced radial mixing in their simulations. Upon 
 calculating the planetesimal accretion zones using the same method as was done to produce figure \ref{fig:acc_zones}, we find 
@@
 of embryos with a modest amount of residual planetesimals. This
-corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}, which is often used as a starting point for late-stage 
-accretion models (e.g. \citet{kokubo02, raymond05, raymond06}). In the second mode, the gravitational feedback does not 
-\textbf{play a significant role}, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
+corresponds to the ``oligarchic growth'' case revealed by \cite{kokubo98}, which is often used as a starting point for late-stage 
+accretion models (e.g. \cite{kokubo02, raymond05, raymond06}). In the second mode, the gravitational feedback does not 
+play a significant role, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
 oligarchic growth.
@@
 We have demonstrated the outcome of both accretion modes through a
-simple parameter study using a narrow annulus of planetesimals \textbf{(section \ref{sec:narrow})}. The initial planetesimal distribution can be described in terms of two dimensionless 
+simple parameter study using a narrow annulus of planetesimals (section \ref{sec:narrow}). The initial planetesimal distribution can be described in terms of two dimensionless 
 constants, $\alpha$ and $\beta$, which describe the ratio between the physical radius of the planetesimals and the Hill ($r_{h}$) 
@@
 $\beta$ scales with the level of dynamical excitation of the disk.
-We showed that $\alpha \ll 1$ leads to oligarchic growth, while \textbf{an $\alpha$ close to unity} produces this newly revealed non-oligarchic growth mode \textbf{(see figure \ref{fig:alpha_beta})}.
+We showed that $\alpha \ll 1$ leads to oligarchic growth, while an $\alpha$ close to unity produces this newly revealed non-oligarchic growth mode (see figure \ref{fig:alpha_beta}).
 Within this non-oligarchic mode, we find that
-the resulting masses and eccentricities of the embryos come out \textbf{very similar}, regardless of the initial value of $\beta$.
+the resulting masses and eccentricities of the embryos come out very similar, regardless of the initial value of $\beta$.
 
@@
 
-We have verified that the growth boundary location \textbf{does not strongly depend} of the
+We have verified that the growth boundary location does not strongly depend of the
 solid surface density distribution by testing the outcome of the planetesimal
@@
 In addition, the sizes of the feeding zones, along with qualitative differences in the
-accretion history of embryos on both sides of the boundary \textbf{(see figures \ref{fig:minor_frac} and \ref{fig:acc_zones})} provide further evidence to
+accretion history of embryos on both sides of the boundary (see figures \ref{fig:minor_frac} and \ref{fig:acc_zones}) provide further evidence to
 suggest that oligarchic growth is not operating in the inner disk.
 
-\textbf{Finally, we have examined how our assumption of perfect accretion, along with the collision cross section enhancement used, might alter our results. 
+Finally, we have examined how our assumption of perfect accretion, along with the collision cross section enhancement used, might alter our results. 
 We verified that these modifications, meant to make the simulations less computationally expensive, would still allow for the emergence of this 
-non-oligarchic growth mode.}
+non-oligarchic growth mode.
 We showed that a much more restrictive collision model, in which only low-velocity collisions produce a merger, still allows for 
 this growth mode to occur at the innermost part of the disk, where encounter speeds are most vigorous. In a real planet-forming 
-disk, partial accretion events should allow growth to happen more quickly than what was seen in this test case \textbf{(see figure 8 of \citet{leinhardt15})}, so this growth 
+disk, partial accretion events should allow growth to happen more quickly than what was seen in this test case (see figure 8 of \cite{leinhardt15}), so this growth 
 mode should certainly still occur. We also showed that the collision cross section enhancement moves the accretion boundary 
@@
 and showing that the boundary moves to the predicted location when running a simulation with a slightly smaller inflation factor. 
-For rocky planetesimals with a realistic bulk density, \textbf{3 g cm$^{-3}$}, \textbf{our results suggest that} this boundary should lie around 5 days in orbital period.
+For rocky planetesimals with a realistic bulk density, 3 g cm$^{-3}$, our results suggest that this boundary should lie around 5 days in orbital period.
 
@@
 with such a large value of $\alpha$.
-\textbf{Typically, it is assumed that $\alpha \ll 1$ (e.g.
-\citet{lithwick14}), which is certainly true for material at and beyond the Earth's orbit.} However, a value of $\alpha = 1$
+Typically, it is assumed that $\alpha \ll 1$ (e.g.
+\cite{lithwick14}), which is certainly true for material at and beyond the Earth's orbit.
+However, a value of $\alpha = 1$
 corresponds to the Roche limit of a three-body system, and so one
@@
 which use N-body methods to examine in-situ satellitesimal accretion
-\citep{ida97, richardson00, kokubo00b, ida20}, although some of these simulations involve a complex interaction between spiral 
-density waves formed inside of the Roche limit and the material exterior to it\textbf{, making the dynamics driving accretion distinctly non-local, in contrast to what we have presented in this work}.
-\citet{ida97} was able to form 1-2
+\cite{ida97, richardson00, kokubo00b, ida20}, although some of these simulations involve a complex interaction between spiral 
+density waves formed inside of the Roche limit and the material exterior to it, making the dynamics driving accretion distinctly non-local, in contrast to what we have presented in this work.
+\cite{ida97} was able to form 1-2
 large moons just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over. 
 The widest disk they modeled extended out to $\alpha = 0.5$. Qualitatively, this result is very similar to the short period 
-planetesimal accretion mode observed in our simulations. \citet{ida20} modeled a much wider satellitesimal disk, which extends 
-out to about $\alpha \approx 0.05$. Inside to the $\alpha = 0.1$ accretion boundary (which lies near 15 \textbf{planetary radii} in figure 1 of 
-\citet{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary. In addition, a 
+planetesimal accretion mode observed in our simulations. \cite{ida20} modeled a much wider satellitesimal disk, which extends 
+out to about $\alpha \approx 0.05$. Inside to the $\alpha = 0.1$ accretion boundary (which lies near 15 planetary radii in figure 1 of 
+\cite{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary. In addition, a 
 residual population of satellitesimals is still present beyond the boundary, which suggests that oligarchic growth is indeed 
@@
 results do highlight is that the initial conditions used for most late-stage planet formation simulations are overly simplistic. 
-\citet{clement20} recently simulated planetesimal accretion in a disk extending from the orbit of Mercury to the asteroid belt and 
+\cite{clement20} recently simulated planetesimal accretion in a disk extending from the orbit of Mercury to the asteroid belt and 
 found that the disk never reaches a state in which equally-spaced, isolation mass embryos are present everywhere 
 simultaneously. Instead, different annuli reach a `giant impact' phase at different times, preventing the onset of a global instability 
-throughout the entire disk, as is common in classic terrestrial planet formation models \citep{chambers01, raymond09}.
+throughout the entire disk, as is common in classic terrestrial planet formation models \cite{chambers01, raymond09}.
 
@@
 \section*{Acknowledgements}
+We would like to thank the anonomyous referee for their thorough and careful comments which greatly improved the quality of this manuscript.
 This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number ACI-1548562.
@@
 \appendix
-\section{Robustness of Timestepping Scheme}\label{sec:rung_ecc}
-
-\textbf{As described in section \ref{sec:methods}, {\sc ChaNGa}
+
+\section{Appendix A: Robustness of Timestepping Scheme}\label{sec:rung_ecc}
+
+As described in section \ref{sec:methods}, {\sc ChaNGa}
   evolves the motions of the particles in the planetesimal disk using
@@
 In the event that a collision occurs between two particles on different timesteps, a slight error is introduced to the energy and angular momentum of the merged particle.
-Due to the nonlinear nature of the runaway growth phase, this slight error tends to trigger more subsequent collisions at the timestep boundary in the disk, and causes protoplanets to preferentially form at the boundaries.}
-
-\textbf{To circumvent this issue, we prohibit particles on different timesteps from merging until the runaway growth phase is well underway.
+Due to the nonlinear nature of the runaway growth phase, this slight error tends to trigger more subsequent collisions at the timestep boundary in the disk, and causes protoplanets to preferentially form at the boundaries.
+
+To circumvent this issue, we prohibit particles on different timesteps from merging until the runaway growth phase is well underway.
 For the fdHi simulation, multi-tiered mergers are not allowed during the first thousand steps.
@@
 In the first case, the aforementioned timestepping scheme is used.
-In the second case, all particles are evolved on the timestep appropriate for the inner edge of the disk.}
+In the second case, all particles are evolved on the timestep appropriate for the inner edge of the disk.
 
@@
     \includegraphics[width=0.5\textwidth]{figures/rung_ecc.png}
-    \caption{\textbf{A comparison between the innermost region of the fdHi (orange) simulation, and a second version using a fixed timestep appropriate for the inner edge of the disk (green).
+    \caption{A comparison between the innermost region of the fdHi (orange) simulation, and a second version using a fixed timestep appropriate for the inner edge of the disk (green).
 In the top panel, the period-eccentricity state of the particles is shown, with marker sizes indicating relative mass.
 The blue points represent the initial state of the simulations.
-The bottom panel compares the final mass distributions of the bodies.}\label{fig:rung_ecc}}
-\end{center}
-\end{figure}
-
-\textbf{In figure \ref{fig:rung_ecc}, we compare the final period-eccentricity state and final mass distributions to each other.
+The bottom panel compares the final mass distributions of the bodies.\label{fig:rung_ecc}}
+\end{center}
+\end{figure}
+
+In figure \ref{fig:rung_ecc}, we compare the final period-eccentricity state and final mass distributions to each other.
 There do not appear to be any differences between the two protoplanet distributions, particularly near the timestep boundary at 2 days.
@@
 In this case, a KS test of the two mass distributions yields a p-value of $\sim 0.34$.
-We therefore safely conclude that the timestepping scheme used in this work does not alter the growth of the protoplanets in any meaningful way.}
+We therefore conclude that the timestepping scheme used in this work does not alter the growth of the protoplanets in any meaningful way.
 

### 2023-07-12 makeFig.py

@@ -585,7 +585,7 @@ def plot_pl_frac_time():
 		prof_arr[:,idx] = (p_vhi_m1['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)/(p_vhi_m2['density']*u.M_sun/u.AU**2).to(u.g/u.cm**2)
 
 	fig, axes = plt.subplots(figsize=(8,4))
-	col = cm.jet(np.linspace(0, 1, len(pbins)))
+	col = cm.viridis(np.linspace(0, 1, len(pbins)))
 	for idx in range(len(bins1[:-1])):
 		tdyn_loc = pbins[idx]/(2*np.pi)
 
@@ -612,7 +612,7 @@ def plot_pl_frac_time():
 	axes.set_xlim(4e-2, 40)
 
 	norm = colors.Normalize(vmin=0, vmax=100)
-	sm = cm.ScalarMappable(cmap=cm.jet, norm=norm)
+	sm = cm.ScalarMappable(cmap=cm.viridis, norm=norm)
 	cb = plt.colorbar(sm)
 	cb.set_label('Orbital Period [d]')
 
@@ -900,7 +900,7 @@ def plot_smooth_acc():
 
 		import matplotlib.cm as cm
 		cbs = ax.scatter(xvals, yvals, edgecolor='black', \
-			linewidth=0.4, c=porb, cmap=cm.jet, vmin=0.0, vmax=100.0, marker='o')
+			linewidth=0.4, c=porb, cmap=cm.viridis, vmin=0.0, vmax=100.0, marker='o')
 
 		axes.set_ylabel('Smooth Accretion Mass Fraction')
 
@@ -1314,6 +1314,7 @@ def plot_frag_ecc():
 	mask2 = q2 > 1e-5
 	stat, pval = stats.kstest(q1[mask1], q2[mask2])
 	print('Frag ecc KS pval after cut: '+ str(pval))
+	print('Fractional mass difference: ' + str(np.sum(q1[mask1])/np.sum(q1)))
 
 	fig.tight_layout()
 
@@ -1482,12 +1483,12 @@ def plot_rung_ecc():
 #plot_pl_frac_time()
 #plot_surfden_profiles()
 #plot_surfden_iso()
-plot_surfden_b()
+#plot_surfden_b()
 #plot_smooth_acc()
 #plot_acc_zones()
 #plot_f6f4()
 #plot_f6f4_b()
-#plot_frag_ecc()
[…]

### 2023-07-12 stip_tools.py

@@ -1,0 +1,194 @@
+import numpy as np
+import astropy.units as u
+from astropy.constants import G
+import KeplerOrbit as ko
+import pandas as pd
+import pynbody as pb
+
+# Each node represents a particle
+class Node:
+    def __init__(self):
+        self.iord = -1
+        self.children = []
+        self.parent = None
+        self.parent_time = 99999999999999 # Time at which this node connected to the parent
+
+# Load a changa output file as a pynbody snapshot
+# deltaT - timestep in 2 pi years
+# mCentral - central mass in Msun
+def load_changa(filename, deltaT, mCentral):
+    snap = pb.load(filename)
+    pl = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
+    if filename.split('.')[-1].isnumeric():
+        time = int(filename.split('.')[-1])*deltaT/(2*np.pi)/1e6
+    else:
+        time = 0.0
+
+    return pl, time
+
+# Load a genga output file as a pynbody snapshot
+# deltaT - timestep in days
+# mCentral - central mass in Msun
+def load_genga(filename, deltaT, mCentral):
+    nam = ['t', 'i1', 'm1', 'r1', 'x1', 'y1', 'z1', 'vx1', 'vy1', 'vz1', 'Sx1', 'Sy1', 'Sz1', 'amin1', 'amax1', 'emin1', 'emax1', 'aecount1', 'aecountT1', 'enccountT1', 'test1']
+    time = (int(filename.split('_')[-1].split('.')[0])*deltaT*u.d).to(u.Myr).value
+    df = pd.read_csv(filename, names=nam, sep=' ', index_col=False)
+    a, e, inc, asc_node, omega, M = ko.cart2kep(df['x1'], df['y1'], df['z1'], \
+                                                df['vx1'], df['vy1'], df['vz1'], \
+                                                mCentral, df['m1'])
+    snap = pb.new(len(df))
+    snap['pos'][:,0] = df['x1']
+    snap['pos'][:,1] = df['y1']
+    snap['pos'][:,2] = df['z1']
+    snap['vel'][:,0] = df['vx1']
+    snap['vel'][:,1] = df['vy1']
+    snap['vel'][:,2] = df['vz1']
[…]

### 2023-07-13 main.tex
Fix broken citations, change paths to data in python script

@@
 \begin{abstract}
-Formation models in which terrestrial bodies grow via the pairwise
-accretion of planetesimals have been reasonably successful at
-reproducing the general properties of the solar system, including
-small body populations. However, planetesimal accretion has not yet
-been fully explored in the context of the wide variety of recently discovered extrasolar planetary systems,
-particularly those that host short-period terrestrial planets. In this work, we
-use direct N-body simulations to explore and understand the growth of
-planetary embryos from planetesimals in disks extending down to
-$\simeq$ 1 day orbital periods. We show that planetesimal accretion
-becomes nearly 100 percent efficient at short orbital periods, leading
-to embryo masses that are much larger than the classical
-isolation mass. For rocky bodies, the physical size of the object
-begins to occupy a significant fraction of its Hill sphere towards the inner edge of the disk. In this regime, most close encounters
-result in collisions, rather than scattering, and the system does not
-develop a bimodal population of dynamically hot planetesimals and
-dynamically cold oligarchs, like is seen in previous studies. The highly
-efficient accretion seen at short orbital periods implies that systems
-of tightly-packed inner planets should be almost completely devoid of
-any residual small bodies. We demonstrate the robustness of our
-results to assumptions about the initial disk model, and also
-investigate the effects that our simplified collision model has on the emergence
-of this non-oligarchic growth mode in a planet forming disk.
+Formation models in which terrestrial bodies grow via the pairwise accretion of planetesimals have been reasonably successful at reproducing the general properties of the solar system, including small body populations.
+However, planetesimal accretion has not yet been fully explored in the context of the wide variety of recently discovered extrasolar planetary systems, particularly those that host short-period terrestrial planets.
+In this work, we use direct N-body simulations to explore and understand the growth of planetary embryos from planetesimals in disks extending down to $\simeq$ 1 day orbital periods.
+We show that planetesimal accretion becomes nearly 100 percent efficient at short orbital periods, leading to embryo masses that are much larger than the classical isolation mass.
+For rocky bodies, the physical size of the object begins to occupy a significant fraction of its Hill sphere towards the inner edge of the disk.
+In this regime, most close encounters result in collisions, rather than scattering, and the system does not develop a bimodal population of dynamically hot planetesimals and dynamically cold oligarchs, like is seen in previous studies.
+The highly efficient accretion seen at short orbital periods implies that systems of tightly-packed inner planets should be almost completely devoid of any residual small bodies.
+We demonstrate the robustness of our results to assumptions about the initial disk model, and also investigate the effects that our simplified collision model has on the emergence of this non-oligarchic growth mode in a planet forming disk.
 \end{abstract}
@@
 growth and evolution of the solids and statistical models
-\cite{johansen14, birnstiel16} are appropriate to describe how these
+\citep{johansen14, birnstiel16} are appropriate to describe how these
 numerous, small bodies coagulate.
@@
 exerts a headwind on any solids large enough to decouple from the gas
-\cite{weidenschilling77}. Around a meter in size, this headwind
+\citep{weidenschilling77}. Around a meter in size, this headwind
 is maximally effective at sapping away orbital angular momentum, and planet-building material can fall onto the central star on 
-catastrophically short timescales \cite{weidenschilling77, nakagawa86}. Additionally, laboratory experiments suggest that 
+catastrophically short timescales \citep{weidenschilling77, nakagawa86}. Additionally, laboratory experiments suggest that 
 collisions between mm- to cm- sized solids tend to result in bounces or destruction, rather than continued growth
-\cite{blum93, colwell03, beitz11}.
+\citep{blum93, colwell03, beitz11}.
 
 For these reasons, a number of mechanisms to radially concentrate solids in a planet-forming disk have been proposed to 
-facilitate fast growth from mm to km sizes \cite{johansen07, lyra08, bai10} in order to surmount these barriers. Interestingly, 
-formation models for the short-period multiplanet systems revealed by Kepler \cite{fabrycky14} also seem to require enhanced 
-concentrations of planet-building material to reproduce the observed architectures \cite{raymond07, hansen12}.
+facilitate fast growth from mm to km sizes \citep{johansen07, lyra08, bai10} in order to surmount these barriers. Interestingly, 
+formation models for the short-period multiplanet systems revealed by Kepler \citep{fabrycky14} also seem to require enhanced 
+concentrations of planet-building material to reproduce the observed architectures \citep{raymond07, hansen12}.
 
@@
 plays an increasingly unimportant role beyond this size. During this phase, collision cross sections are enhanced as gravitational 
-focusing \cite{safronov69} acts to bend the trajectories of bodies undergoing close encounters. Because gravitational focusing 
-becomes more effective as bodies grow larger, a period of runaway growth occurs \cite{wetherill89, kokubo96, barnes09} and a 
+focusing \citep{safronov69} acts to bend the trajectories of bodies undergoing close encounters. Because gravitational focusing 
+becomes more effective as bodies grow larger, a period of runaway growth occurs \citep{wetherill89, kokubo96, barnes09} and a 
 power law spectrum of masses develop. Eventually, the largest bodies (known as oligarchs) dynamically heat the remaining 
-planetesimals, severely limiting further growth \cite{kokubo98}. The final outcome of this phase is a bimodal population of 
+planetesimals, severely limiting further growth \citep{kokubo98}. The final outcome of this phase is a bimodal population of 
 dynamically cold oligarchs, surrounded by dynamically hot, difficult to accrete residual planetesimals. Lines of evidence suggest 
-that the asteroid belt \cite{bottke05, morbidelli09}, Kuiper belt \cite{duncan89, levison08, sheppard10} and the Oort cloud  \cite{levison11} are largely composed of the leftovers of this stage of planet formation.
-
-Tidal interactions between protoplanets and the gaseous disk keep eccentricities and inclinations low until the gas disk dissipates, typically over the course of a few Myr \cite{mamajek09}.
-\textbf{On a timescale of roughly $10^{5}$ yr, gravitational perturbations trigger an instability which involves large scale oscillations of the eccentricity and inclinations of bodies as they strongly interact through secular resonances \cite{chambers98}.}
+that the asteroid belt \citep{bottke05, morbidelli09}, Kuiper belt \citep{duncan89, levison08, sheppard10} and the Oort cloud  \citep{levison11} are largely composed of the leftovers of this stage of planet formation.
+
+Tidal interactions between protoplanets and the gaseous disk keep eccentricities and inclinations low until the gas disk dissipates, typically over the course of a few Myr \citep{mamajek09}.
+\textbf{On a timescale of roughly $10^{5}$ yr, gravitational perturbations trigger an instability which involves large scale oscillations of the eccentricity and inclinations of bodies as they strongly interact through secular resonances \citep{chambers98}.}
 As a consequence of the instability, the oligarchics are no longer
@@
 through a series of extremely energetic giant 
-impacts \cite{kokubo02, raymond05, raymond06}.
+impacts \citep{kokubo02, raymond05, raymond06}.
 
@@
 many particles to directly track with traditional N-body codes, while
-the gravitational interactions between the few massive bodies produced by the runaway growth phase \cite{ida93, kokubo95, kokubo98} render statistical methods inappropriate.
+the gravitational interactions between the few massive bodies produced by the runaway growth phase \citep{ida93, kokubo95, kokubo98} render statistical methods inappropriate.
 Due to computational expense, N-body simulations of
 planetesimal accretion are usually modeled in a narrow
-ring \cite{kokubo96, kokubo98}, and the results and timescales are then scaled to suit whatever relevant orbital period is being 
+ring \citep{kokubo96, kokubo98}, and the results and timescales are then scaled to suit whatever relevant orbital period is being 
 studied. N-body simulations of terrestrial planet assembly typically begin with a series of neatly spaced oligarchs, whose mass 
@@
 Given that Systems of Tightly-packed Inner Planets (STIPs) appear to
-be a common outcome of planet formation \cite{lantham11, lissauer11, rowe14}, understanding exactly how
+be a common outcome of planet formation \citep{lantham11, lissauer11, rowe14}, understanding exactly how
 solids accumulate at short orbital periods is crucial. Although
 gas-disk driven migration of the planets themselves is often invoked
-to explain the observed architectures \cite{izidoro17, izidoro21}, we will focus on an in-situ
+to explain the observed architectures \citep{izidoro17, izidoro21}, we will focus on an in-situ
 model in this paper. That is, once the planetesimals themselves form,
@@
 In doing so, we will assess whether the typical initial conditions (fully formed, evenly spaced protoplanets, e.g.
-\cite{raymond06}) used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
+\citet{raymond06}) used in studies of terrestrial planet formation are actually appropriate for understanding STIPs.
 
@@
 For a swarm of planetesimals on randomly oriented orbits, $v$ is typically
-taken to be the rms velocity, $\left< v^{2} \right>^{1/2}$, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \cite{lissauer93}:
+taken to be the rms velocity, $\left< v^{2} \right>^{1/2}$, which can be related to the eccentricity and inclination distribution $(e, i)$ in the following way \citep{lissauer93}:
 \begin{equation}\label{eq:ecc_vel}
@@
 \end{equation}
-\cite{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
+\citep{safronov69}, where $v_{esc}$ is the escape velocity from the two bodies at the point of contact.
 
@@
 accelerates with mass. This mode of growth was confirmed with N-body
-simulations by \cite{kokubo96} and appears necessary to construct
-protoplanets within the lifetime of a protoplanetary disk \cite{lissauer87}, although one should note that pebble accretion \cite{lambrechts12, lambrechts14, bitsch15} is a viable alternative scenario.
+simulations by \citet{kokubo96} and appears necessary to construct
+protoplanets within the lifetime of a protoplanetary disk \citep{lissauer87}, although one should note that pebble accretion \citep{lambrechts12, lambrechts14, bitsch15} is a viable alternative scenario.
 Due to the
@@
 Keplerian shear into random motion, raises the typical encounter velocity
-between planetesimals over time \cite{weidenschilling89, ida90} and diminishes the effectiveness of gravitational
+between planetesimals over time \citep{weidenschilling89, ida90} and diminishes the effectiveness of gravitational
 focusing. As the mass spectrum of the system evolves away from uniformity, these velocity differences become even more
@@
 motions rather than Keplerian shear (dispersion dominated), the timescale for gravitational stirring is described by the two-body 
-relaxation time \cite{ida93}
+relaxation time \citep{ida93}
 \begin{equation}\label{eq:relax}
@@
 where $\ln \Lambda$ is the Coulomb logarithm,
-typically taken to be $\approx 3$ for a planetesimal disk \cite{ida90, stewart00}. Despite
+typically taken to be $\approx 3$ for a planetesimal disk \citep{ida90, stewart00}. Despite
 the fact that the behavior of gravitational stirring is well-described
-by a two-body formula, \cite{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters, which 
+by a two-body formula, \citep{ida93} found that the stirring in a planetesimal disk is actually driven by close encounters, which 
 requires a three-body formalism. As we will show in section \ref{sec:narrow}, gravitational stirring effectively shuts off when the 
@@
 
-\cite{kokubo98} showed that the runaway growth process described above is actually self-limiting. As the runaway
+\citet{kokubo98} showed that the runaway growth process described above is actually self-limiting. As the runaway
 bodies develop, they become increasingly effective at dynamically heating the
@@
 by a factor of $\sim 50-100$
-\cite{ida93} a phase of less vigorous ``oligarchic'' 
+\citep{ida93} a phase of less vigorous ``oligarchic'' 
 growth commences, in which the largest bodies continue to 
@@
 \noindent For bodies on circular, non-inclined orbits, $\tilde{b} = 2 \sqrt{3}$ is the smallest orbital separation that produces a non-negative
-Jacobi energy and permits a close encounter \cite{naka88}.
+Jacobi energy and permits a close encounter \citep{naka88}.
 This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet because oligarchic growth tends to maintain near-circular orbits for the growing protoplanets.
@@
 simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2
-\right>^{1/2}$ \cite{ida93a} and that the eccentricity dispersion is
+\right>^{1/2}$ \citep{ida93a} and that the eccentricity dispersion is
 constant with orbital period. The coloring indicates the ratio between
@@
 dispersion will typically increase over time until $\left< v^{2} \right>^{1/2} = v_{esc}$ and this is
-often used to construct the initial conditions (e.g. \cite{barnes09}). Therefore, the curves in this figure
+often used to construct the initial conditions (e.g. \citet{barnes09}). Therefore, the curves in this figure
 should be interpreted as upper limits.
@@
 \end{equation}
-where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body (see eq 4.1 of \cite{ida90}).
+where $r_{g} = G m_{pl} / v^{2}$ is the gravitational radius of a body (see eq 4.1 of \citet{ida90}).
 Encounters between bodies inside of a distance of $r_{g}$ result in significant deflections of their trajectories.
@@
 We use the tree-based N-body code {\sc ChaNGa} to model the gravitational and collisional evolution of a swarm of planetesimals.
-{\sc ChaNGa} is written using the {\sc CHARM++} parallel programming language and has been shown to perform well on up to half a million processors \cite{menon15} and can follow the evolution of gravitationally interacting collections of up to billions of particles.
+{\sc ChaNGa} is written using the {\sc CHARM++} parallel programming language and has been shown to perform well on up to half a million processors \citep{menon15} and can follow the evolution of gravitationally interacting collections of up to billions of particles.
 Using a modified Barnes-Hut tree with hexadecapole expansions of the moments to approximate forces, {\sc ChaNGa} integrates the equations of motion using a kick-drift-kick leapfrog scheme.
 For all of the simulations presented in this paper, we use a node opening criteria of $\theta_{BH}$ = 0.7.
-Additional information about the code is available in \cite{jetley08,menon15}.
+Additional information about the code is available in \citep{jetley08,menon15}.
 
@@
 solid-body collision implementation in {\sc PKDGRAV}, which is
-described in \cite{richardson94} and \cite{richardson00}. To
+described in \citet{richardson94} and \citet{richardson00}. To
 summarize, imminent collisions are detected during the ``drift'' phase
@@
 more detailed description of the collision module in {\sc ChaNGa}, see
-\cite{wallace19}.
+\citep{wallace19}.
 Particles are advanced on individual timesteps chosen as a
@@
 from a Rayleigh distribution with
-$\left< i^{2} \right> = 1/2 \left< e^{2} \right>$ \cite{ida93a}.
+$\left< i^{2} \right> = 1/2 \left< e^{2} \right>$ \citep{ida93a}.
 
@@
 cm$^{-3}$ (for a radius of 341 km), and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$.
-These parameters are chosen to match the initial conditions of \cite{kokubo98}, which gave rise to oligarchic growth.
+These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth.
 To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by 
@@
 facilitate oligarchic growth. In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and 
-embryos \cite{weidenschilling89, ida90}.
+embryos \citep{weidenschilling89, ida90}.
 When $\alpha \ll 1$, the \textbf{planetesimal fills only a small portion of its Hill sphere} and the majority of close encounters result in viscous stirring, rather than accretion.
@@
 than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of 
-planet formation \cite{kokubo98, kokubo00}.
+planet formation \citep{kokubo98, kokubo00}.
 
@@
 typically begin with a chain of neatly-spaced, isolation mass 
-(see \cite{kokubo00} eq. 20) protoplanets, it is pertinent to determine 
+(see \citet{kokubo00} eq. 20) protoplanets, it is pertinent to determine 
 whether the high $\alpha$ growth mode we revealed
@@
 Given the dearth of short-period terrestrial planets observed around M stars (e.g.
-TRAPPIST-1 \cite{gillon16, gillon17, agol21}), we chose to model the evolution of a series of wide planetesimal disks, which span from 1 to 100 days in orbital period, orbiting a late-type M star of mass 0.08 $M_{\odot}$.
+TRAPPIST-1 \citep{gillon16, gillon17, agol21}), we chose to model the evolution of a series of wide planetesimal disks, which span from 1 to 100 days in orbital period, orbiting a late-type M star of mass 0.08 $M_{\odot}$.
 For a population of planetesimals with a bulk density of 3 g cm$^{-3}$, this orbital period range corresponds to $\alpha \in (0.7, 0.05)$.
@@
 cm$^{-2}$ is the surface density of the minimum-mass solar nebula
-\cite[MMSN]{hayashi81} at 1 AU, $A$ is an enhancement factor and $\delta$ is the power law index.
+\citep[MMSN]{hayashi81} at 1 AU, $A$ is an enhancement factor and $\delta$ is the power law index.
 In the first case (fdHi), we model a disk that follows a MMSN power law slope ($\delta$ = 1.5), with the overall normalization enhanced by a factor of 100.
-This choice of normalization for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \cite{hansen12}.
+This choice of normalization for the solid surface density profile appears necessary in order to reproduce many observed short period terrestrial worlds in-situ \citep{hansen12}.
 \textbf{Many recent planetesimal formation models invoke streaming instabilities, which first require sufficiently large amounts of solid material concentrating} at preferential locations in the disk.
-This can occur via zonal flows \cite{johansen2009b, simon12}, vortices \cite{klahr03}, or through mechanisms that produce a pressure bump in the gas disk, such as an ionization \cite{lyra08} or condensation front \cite{brauer08b, drkazowska13}, or even the perturbations from an existing planet \cite{shibaike20}.
-\cite{drkazowska18} showed that evolution of the snow line boundary can cause planetesimal formation over a significant area of the disk, producing mass concentrations at least as large as the ones we use here.
-We argue that this is a particularly attractive mechanism for widespread planetesimal formation around low-mass stars, as their extreme pre-main sequence evolution is particularly conducive to significant movement of the condensation fronts \cite{baraffe15}.
+This can occur via zonal flows \citep{johansen2009b, simon12}, vortices \citep{klahr03}, or through mechanisms that produce a pressure bump in the gas disk, such as an ionization \citep{lyra08} or condensation front \citep{brauer08b, drkazowska13}, or even the perturbations from an existing planet \citep{shibaike20}.
+\citet{drkazowska18} showed that evolution of the snow line boundary can cause planetesimal formation over a significant area of the disk, producing mass concentrations at least as large as the ones we use here.
+We argue that this is a particularly attractive mechanism for widespread planetesimal formation around low-mass stars, as their extreme pre-main sequence evolution is particularly conducive to significant movement of the condensation fronts \citep{baraffe15}.
 
 Additionally, we vary the power law index (fdHiShallow, fdHiSteep) and overall normalization (fdLo) of $\Sigma(r)$.
-Although there is no way to reliably measure the uncertainty on the MMSN power law slope, \cite{chiang13} applied a similar analysis to a sample of Kepler multiplanet systems and found a variation of $\sim 0.2$.
-Sub-millimeter observations of the outer regions of cold protoplanetary disks find that $\delta$ can be as low as 0.5 \cite{mundy00, andrews09, andrews10}.
+Although there is no way to reliably measure the uncertainty on the MMSN power law slope, \citet{chiang13} applied a similar analysis to a sample of Kepler multiplanet systems and found a variation of $\sim 0.2$.
+Sub-millimeter observations of the outer regions of cold protoplanetary disks find that $\delta$ can be as low as 0.5 \citep{mundy00, andrews09, andrews10}.
 Therefore, we vary $\delta$ by a value of $1.0$ relative to the MMSN value for the fdHiShallow and fdHiSteep simulations.
 
-In all cases, the eccentricities and inclinations of the bodies are randomly drawn from a Rayleigh distribution, with $\left< e^{2} \right>^{1/2} = 2\left<i^{2} \right>^{1/2} = e_{eq}$ \cite{ida93}.
-Following \cite{kokubo98}, the value of $e_{eq}$ is chosen such that the timescales for viscous stirring and aerodynamic gas drag on the planetesimals are in equilibrium.
+In all cases, the eccentricities and inclinations of the bodies are randomly drawn from a Rayleigh distribution, with $\left< e^{2} \right>^{1/2} = 2\left<i^{2} \right>^{1/2} = e_{eq}$ \citep{ida93}.
+Following \citet{kokubo98}, the value of $e_{eq}$ is chosen such that the timescales for viscous stirring and aerodynamic gas drag on the planetesimals are in equilibrium.
 Although this approach assumes that these two mechanisms are in balance, there is nothing preventing planetesimal accretion from getting underway before the disk is sufficiently hot to be limited by gas drag.
 However, as we showed in the previous section, the initial dynamical state of the planetesimals does not seem to affect the outcome of accretion, so it is safe to assume that the resulting distribution of protoplanets would remain unchanged had we started with a colder disk.
-The viscous stirring timescale is given by \cite{ida93} as
+The viscous stirring timescale is given by \citet{ida93} as
 
@@
 where $\Omega$, $a$ and $e$ are the orbital frequencies, semi-major axes and eccentricities of the individual planetesimals, respectively.
-In the Stokes regime, where the mean-free path of the gas is much smaller than the solid particles, the gas can be treated as a fluid and the drag timescale is given by \cite{adachi76} as
+In the Stokes regime, where the mean-free path of the gas is much smaller than the solid particles, the gas can be treated as a fluid and the drag timescale is given by \citet{adachi76} as
 
@@
 where $\Sigma_{g}$ is the gas surface density (taken to be
-240 times the solid surface density \cite{hayashi81}, $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
+240 times the solid surface density \citep{hayashi81}, $h_{g} = c_{s} / \Omega$ is the local gas scale height and $z$ is the height above the disk midplane.
 The sound speed profile is given by $c_{s} = \sqrt{k_{B} T(r) / \left( \mu m_{H} \right)}$, where $k_{B}$ is Boltzmann's constant, $T(r) = T_{0} \left( r / 1 \textrm{AU} \right)^{-q}$, $\mu = 2.34$ and $m_{h}$ is the mass of a hydrogen atom.
-For a protoplanetary disk around a typical M star, $T_{0} = 148$ K and $q$ = 0.58 \cite{andrews05}.
+For a protoplanetary disk around a typical M star, $T_{0} = 148$ K and $q$ = 0.58 \citep{andrews05}.
 
@@
 
-\noindent where $v_{k}$ is the local Keplerian velocity (see eq. 4.30 of \cite{armitage20}). As in section
+\noindent where $v_{k}$ is the local Keplerian velocity (see eq. 4.30 of \citet{armitage20}). As in section
 \ref{sec:narrow}, the argument of perihelion $\omega$, longitude of
@@
 planetesimals should be close to their mutual escape velocity. As we showed in section \ref{sec:narrow}, the initial dynamical state of the solids seems to 
-have a very minimal effect on the final outcome of planetesimal accretion. In a similar vein to \cite{hansen12}, we choose to use a MMSN-like profile for the 
+have a very minimal effect on the final outcome of planetesimal accretion. In a similar vein to \citet{hansen12}, we choose to use a MMSN-like profile for the 
 gas disk and instead vary the solid surface density profile to capture the range of mechanisms that might have acted to facilitate planetesimal formation in the 
@@
 due to the the gas disk is applied to each particle, following the
-prescription described in section 2.2.1 of \cite{morishima10}. For
+prescription described in section 2.2.1 of \citet{morishima10}. For
 the initial mass planetesimals, the Stokes number
@@
 inside-out fashion, with the outermost regions of the disk completing
-the protoplanet assembly phase last (as an example, see figure 1 of \cite{kokubo02}. This radial timescale dependence is not typically
-accounted for in planet formation simulations a notable exception being \cite{emsenhuber21a, emsenhuber21b}, and appears to be an
+the protoplanet assembly phase last (as an example, see figure 1 of \citet{kokubo02}. This radial timescale dependence is not typically
+accounted for in planet formation simulations a notable exception being \citet{emsenhuber21a, emsenhuber21b}, and appears to be an
 important component to forming realistic solar system analogs
-\cite{clement20}. As with the narrow annulus simulations, we stop the
+\citep{clement20}. As with the narrow annulus simulations, we stop the
 integration once the masses of protoplanets in the outermost region of
@@
 \tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
-clearly visible. The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \cite{naka88} is shown by the
-horizontal dashed line. In typical oligarchic growth simulations \cite{kokubo98}, protoplanets tend 
+clearly visible. The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{naka88} is shown by the
+horizontal dashed line. In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
 to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
@@
 for cosmological simulations of galaxy formation, we divide growth events for
-a given body into ``major'' and ``minor'' mergers \cite{kauffmann93, murali02, lhullier12}. 
+a given body into ``major'' and ``minor'' mergers \citep{kauffmann93, murali02, lhullier12}. 
 Here, we define minor events as any collision involving an initial mass 
@@
 Inside the boundary, however, any and all bodies collide with each other, and the occasional embryo-embryo collision tends to dominate growth and drive down the smooth accretion fraction.
-Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion \cite{kokubo98}, and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
+Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion \citep{kokubo98}, and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits.
 As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zone size predicted by an oligarchic growth model.
@@
 enhancement greatly reduces the size of the non-oligarchic region, it still should be expected to cover a portion of the
-disk where planetesimals might be expected to form \cite{mulders18} for a wide range of $\rho_{pl}$.
+disk where planetesimals might be expected to form \citep{mulders18} for a wide range of $\rho_{pl}$.
 
@@
 operates, more realistic collision models have been shown to simply lengthen the timescale for planetary embryos to form 
-\cite{wetherill93, leinhardt05}. A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic 
-model (see \cite{leinhardt12}). However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of 
+\citep{wetherill93, leinhardt05}. A proper way to handle this would be to allow for a range of collision outcomes, based on a semianalytic 
+model (see \citet{leinhardt12}). However, resolving collisional debris, or even prolonging growth by forcing high-velocity pairs of 
 bodies to bounce is too expensive to model, even with {\sc ChaNGa}.
@@
 Because the accretion outcome is all or nothing, this model should restrict growth more than a partial accretion model 
-\cite{leinhardt12}. Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner 
+\citep{leinhardt12}. Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner 
 disk's planetesimal accretion phase, and so a more realistic partial accretion model should do the same.
@@
 
-As a final note, \cite{childs22} found that a more realistic collision model also enhanced radial mixing in their simulations. Upon 
+As a final note, \citet{childs22} found that a more realistic collision model also enhanced radial mixing in their simulations. Upon 
 calculating the planetesimal accretion zones using the same method as was done to produce figure \ref{fig:acc_zones}, we find 
@@
 of embryos with a modest amount of residual planetesimals. This
-corresponds to the ``oligarchic growth'' case revealed by \cite{kokubo98}, which is often used as a starting point for late-stage 
-accretion models (e.g. \cite{kokubo02, raymond05, raymond06}). In the second mode, the gravitational feedback does not 
+corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}, which is often used as a starting point for late-stage 
+accretion models (e.g. \citet{kokubo02, raymond05, raymond06}). In the second mode, the gravitational feedback does not 
 play a significant role, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
@@
 this growth mode to occur at the innermost part of the disk, where encounter speeds are most vigorous. In a real planet-forming 
-disk, partial accretion events should allow growth to happen more quickly than what was seen in this test case (see figure 8 of \cite{leinhardt15}), so this growth 
+disk, partial accretion events should allow growth to happen more quickly than what was seen in this test case (see figure 8 of \citet{leinhardt15}), so this growth 
 mode should certainly still occur. We also showed that the collision cross section enhancement moves the accretion boundary 
@@
 Typically, it is assumed that $\alpha \ll 1$ (e.g.
-\cite{lithwick14}), which is certainly true for material at and beyond the Earth's orbit.
+\citet{lithwick14}), which is certainly true for material at and beyond the Earth's orbit.
 However, a value of $\alpha = 1$
@@
 which use N-body methods to examine in-situ satellitesimal accretion
-\cite{ida97, richardson00, kokubo00b, ida20}, although some of these simulations involve a complex interaction between spiral 
+\citep{ida97, richardson00, kokubo00b, ida20}, although some of these simulations involve a complex interaction between spiral 
 density waves formed inside of the Roche limit and the material exterior to it, making the dynamics driving accretion distinctly non-local, in contrast to what we have presented in this work.
-\cite{ida97} was able to form 1-2
+\citet{ida97} was able to form 1-2
 large moons just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over. 
 The widest disk they modeled extended out to $\alpha = 0.5$. Qualitatively, this result is very similar to the short period 
-planetesimal accretion mode observed in our simulations. \cite{ida20} modeled a much wider satellitesimal disk, which extends 
+planetesimal accretion mode observed in our simulations. \citet{ida20} modeled a much wider satellitesimal disk, which extends 
 out to about $\alpha \approx 0.05$. Inside to the $\alpha = 0.1$ accretion boundary (which lies near 15 planetary radii in figure 1 of 
-\cite{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary. In addition, a 
+\citet{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary. In addition, a 
 residual population of satellitesimals is still present beyond the boundary, which suggests that oligarchic growth is indeed 
@@
 results do highlight is that the initial conditions used for most late-stage planet formation simulations are overly simplistic. 
-\cite{clement20} recently simulated planetesimal accretion in a disk extending from the orbit of Mercury to the asteroid belt and 
+\citet{clement20} recently simulated planetesimal accretion in a disk extending from the orbit of Mercury to the asteroid belt and 
 found that the disk never reaches a state in which equally-spaced, isolation mass embryos are present everywhere 
 simultaneously. Instead, different annuli reach a `giant impact' phase at different times, preventing the onset of a global instability 
-throughout the entire disk, as is common in classic terrestrial planet formation models \cite{chambers01, raymond09}.
+throughout the entire disk, as is common in classic terrestrial planet formation models \citep{chambers01, raymond09}.
 
@@
 \section*{Data Availability}
-The data presented in this article are available on our GitHub repository, at \url{https://github.com/spencerw/stip_planetesimal_paper}.
+The data presented in this article, along with a python script to generate the figures are available at at \url{XX.XXXX/zenodo.XXXXXXX}.
 

### 2023-07-13 makeFig.py

@@ -10,7 +10,6 @@ import natsort as ns
 import glob as gl
 import re
 import os
-import profileTools as pt
 import pickle
 
 from astropy import units as u
@@ -46,10 +45,10 @@ mCentralg = (mCentral*u.M_sun).to(u.g)
 bins = np.linspace(0.01, 0.3, num_bins)
 perbins = 2*np.pi*np.sqrt((bins*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
 
-snap = pb.load('data/fullDiskVHia.ic')
+snap = pb.load('data/mmsn/hi/fullDiskVHia.ic')
 plVHiIC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi_ic = pb.analysis.profile.Profile(plVHiIC.d, bins=bins, calc_x = lambda x: x['a'])
-snap = pb.load('data/fullDiskVHi1.250000')
+snap = pb.load('data/mmsn/hi/fullDiskVHi1.250000')
 plVHi = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhi = pb.analysis.profile.Profile(plVHi.d, bins=bins, calc_x = lambda x: x['a'])
 perIC = 2*np.pi*np.sqrt((plVHiIC['a']*u.AU).to(u.cm)**3/(G.cgs*mCentralg)).to(u.d)
@@ -62,40 +61,40 @@ m_pl = np.min(plVHi['mass'])
 rho = 3 # Rocky bodies
 r_pl = ((3*(m_pl*u.M_sun).to(u.g).value/(4*np.pi*rho))**(1/3)*u.cm).to(u.AU).value
 
-snap = pb.load('data/fullDiskVHif4.ic')
+snap = pb.load('data/mmsn/f4/fullDiskVHif4.ic')
 plVHif4IC = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
 p_vhif4_ic = pb.analysis.profile.Profile(plVHif4IC.d, bins=bins, calc_x = lambda x: x['a'])
-snap = pb.load('data/fullDiskVHif41.152000')
+snap = pb.load('data/mmsn/f4/fullDiskVHif41.152000')
 plVHif4 = ko.orb_params(snap, isHelio=True, mCentral=mCentral)
[…]
